### 2018-03-06 paper/paper.tex
added paper

% THIS IS AN EXAMPLE DOCUMENT FOR VLDB 2010
% based on ACM SIGPROC-SP.TEX VERSION 2.7
% Modified by  Gerald Weber <gerald@cs.auckland.ac.nz>

% This example *does* use the .bib file (from which the .bbl file
% is produced). REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission, you need to 'insert'  your .bbl file into
% your source .tex file so as to provide ONE 'self-contained' source file.

\documentclass{vldb}
\usepackage{graphicx}
\usepackage{balance}  % for  \balance command ON LAST PAGE  (only there!)

\begin{document}

% ****************** TITLE ****************************************

\title{A Sample {\ttlit Proceedings of the VLDB Endowment} Paper in LaTeX
Format\titlenote{for use with vldb.cls}}

% possible, but not really needed or used for PVLDB:
%\subtitle{[Extended Abstract]
%\titlenote{A full version of this paper is available as\textit{Author's Guide to Preparing ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and BibTeX} at \texttt{www.acm.org/eaddress.htm}}}

% ****************** AUTHORS **************************************

% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{8} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.

\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Ben Trovato\titlenote{Dr.~Trovato insisted his name be first.}\\
       \affaddr{Institute for Clarity in Documentation}\\
       \affaddr{1932 Wallamaloo Lane}\\
       \affaddr{Wallamaloo, New Zealand}\\
       \email{trovato@corporation.com}
% 2nd. author
\alignauthor
G.K.M. Tobin\titlenote{The secretary disavows
any knowledge of this author's actions.}\\
       \affaddr{Institute for Clarity in Documentation}\\
       \affaddr{P.O. Box 1212}\\
       \affaddr{Dublin, Ohio 43017-6221}\\
       \email{webmaster@marysville-ohio.com}
% 3rd. author
\alignauthor Lars Th{\Large{\sf{\o}}}rv{$\ddot{\mbox{a}}$}ld\titlenote{This author is the
one who did all the really hard work.}\\
       \affaddr{The Th{\large{\sf{\o}}}rv{$\ddot{\mbox{a}}$}ld Group}\\
       \affaddr{1 Th{\large{\sf{\o}}}rv{$\ddot{\mbox{a}}$}ld Circle}\\
       \affaddr{Hekla, Iceland}\\
       \email{larst@affiliation.org}
\and  % use '\and' if you need 'another row' of author names
% 4th. author
\alignauthor Lawrence P. Leipuner\\
       \affaddr{Brookhaven Laboratories}\\
       \affaddr{Brookhaven National Lab}\\
       \affaddr{P.O. Box 5000}\\
       \email{lleipuner@researchlabs.org}
% 5th. author
\alignauthor Sean Fogarty\\
       \affaddr{NASA Ames Research Center}\\
       \affaddr{Moffett Field}\\
       \affaddr{California 94035}\\
       \email{fogartys@amesres.org}
% 6th. author
\alignauthor Charles Palmer\\
       \affaddr{Palmer Research Laboratories}\\
       \affaddr{8600 Datapoint Drive}\\
       \affaddr{San Antonio, Texas 78229}\\
       \email{cpalmer@prl.com}
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
\additionalauthors{Additional authors: John Smith (The Th{\o}rv\"{a}ld Group,
email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
(The Kumquat Consortium, email: {\small \texttt{jpkumquat@consortium.net}})}
\date{30 July 1999}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

\maketitle

\begin{abstract}
The abstract for your paper for the PVLDB Journal submission.
The template and the example document are based on the ACM SIG Proceedings  templates. This file is part of a package for preparing the submissions for review. These files are in the camera-ready format, but they do not contain the full copyright note.
Note that after the notification of acceptance, there will be an updated style file for the camera-ready submission containing the copyright note.
\end{abstract}

\section{Introduction}
The \textit{proceedings} are the records of a conference.
ACM, as well as PVLDB, seeks to give these conference by-products a uniform,
high-quality appearance.  To do this, ACM / PVLDB has some rigid
requirements for the format of the proceedings documents: there
is a specified format (balanced  double columns), a specified
set of fonts (Arial or Helvetica and Times Roman) in
certain specified sizes (for instance, 9 point for body copy),
a specified live area (18 $\times$ 23.5 cm [7" $\times$ 9.25"]) centered on
the page, specified size of margins (2.54cm [1"] top and
bottom and 1.9cm [.75"] left and right; specified column width
(8.45cm [3.33"]) and gutter size (.083cm [.33"]).

The good news is, with only a handful of manual
settings\footnote{Two of these, the {\texttt{\char'134 numberofauthors}}
and {\texttt{\char'134 alignauthor}} commands, you have
already used; another, {\texttt{\char'134 balancecolumns}}, will
be used in your very last run of \LaTeX\ to ensure
balanced column heights on the last page.}, the \LaTeX\ document
class file handles all of this for you.

The remainder of this document is concerned with showing, in
the context of an ``actual'' document, the \LaTeX\ commands
specifically available for denoting the structure of a
proceedings paper, rather than with giving rigorous descriptions
or explanations of such commands.

\section{The {\secit Body} of The Paper}
Typically, the body of a paper is organized
into a hierarchical structure, with numbered or unnumbered
headings for sections, subsections, sub-subsections, and even
smaller sections.  The command \texttt{{\char'134}section} that
precedes this paragraph is part of such a
hierarchy.\footnote{This is the second footnote.  It
starts a series of three footnotes that add nothing
informational, but just give an idea of how footnotes work
and look. It is a wordy one, just so you see
how a longish one plays out.} \LaTeX\ handles the numbering
and placement of these headings for you, when you use
the appropriate heading commands around the titles
of the headings.  If you want a sub-subsection or
smaller part to be unnumbered in your output, simply append an
asterisk to the command name.  Examples of both
numbered and unnumbered headings will appear throughout the
balance of this sample document.

Because the entire article is contained in
the \textbf{document} environment, you can indicate the
start of a new paragraph with a blank line in your
input file; that is why this sentence forms a separate paragraph.
\section{Problem}
The problem we are dealing with is the fuzzy join problem. EXPAND
\section{Algorithm}
We started our process with a simple rule based method for matching and another one for blocking. We then replaced individual peices with a machine learning method and compared the preformance. In the final product we have an elegant completly machine learning based method.
\begin{table}
\centering
\caption{Table 1}
\begin{tabular}{|c|c|} \hline
Name&Match\\ \hline
Douglas Adams&Douglas Noel Adams\\ \hline
Andreas Capellanus&Andrea Cappellano \\ \hline
John Adams Whipple&John A. Whipple \\
\hline\end{tabular}
\end{table}

\begin{table*}
\centering
\caption{Table 2}
\begin{tabular}{|c|c|} \hline
Bucket Name&Contents\\ \hline
A&\{John A. Whipple\} \\ \hline
Adams&\{Douglas Adams, Douglas Noel Adams, John Adams Whipple\} \\ \hline
Andreas&\{Andreas Capellanus\} \\ \hline
Andrea&\{Andrea Cappellano\} \\ \hline
Cappellano&\{Andrea Cappellano\} \\ \hline
Capellanus&\{Andreas Capellanus\} \\ \hline
Douglas&\{Douglas Adams, Douglas Noel Adams\} \\ \hline
John&\{John Adams Whipple, John A. Whipple\} \\ \hline
Noel&\{Douglas Noel Adams\} \\ \hline
Whipple&\{John Adams Whipple, John A. Whipple\} \\ \hline
\hline\end{tabular}
\end{table*}

In the rule-based method we block based on items that have one word in common. This is the simplest reasonable blocking strategy. In table 2 we see a what the blocking of the three names from table 1 would look like. Out of NUMBER1 pairs NUMBER2 ended up in the same bucket as all their correct matches. NUMBER3 had at least one correct match in the same bucket. To preform the actuall matching we used three simple rules. One, if two items share a word that only those two have in common match them. Two, if the we remove spaces and one of the items is a substring of the other match them. Three, if we treat each word as a member of a set representing the entity, and one set is a subset of the other we match them. We found that most of the problem with this method was not enough positives, so we accepted if any of the rules matched the two items. If we treat it as a success if the correct match is any of the top 3 we get an fscore of FSCORE1. Since the issue is mostly false-negitives, even if we accept any of the top 1000 as a success, we get FSCORE2, not much better.

The first part we replaced was the matcher. To compare the two matchers we created a rule-based matcher using the rules from the rule-based system. To replace it we created a siamese network (figure 1) INSERT FIGURE 1. A Siamese network is two deep neural networks that share weights. One entity is fed into each of the two networks. The output of the two networks is fed into a final layer which determines the distance between the two outputs and accepts or rejects. Siamese networks have been shown to work well for image matching.\footnote{CITE} Before feeding the entities into the networks, we used Kazuma charecter embeddings to encode each entity as a vector. We trained the network on our NUMBER1*0.95 pairs and withheld NUMBER1*0.05 for testing. We chose an equal number of negitive pairs to train the model on. We chose negitive pairs that had at least one word in common with the positive ones. We found that the fscore on the training data was FSCORE3 and FSCORE4 on the test date. This was better than the rule-based matcher which had an f-score of FSCORE5.

We next approached the blocking problem with machine learning. Since the hidden layer of the siamese network is optimized for matching, it should output an embedding of the entity which has its essential qualities with regaurds to matching (figure 2). We then used an aproximate nearest neighbors algorithm to find the nearest neighbors. EXPLAIN MORE Using these techniques we can find the most similar items without needing to block at all. The problem we ran into is only PERCENT1 of the correct matches were in the 10 nearest neighbors. The problem seems to be that since we trained the model using negative pairs that have at least one word in common, it did not learn that names that are completly different should be mapped seperatly (figure 3). We could try to fix this by feeding the model better negative pairs, but we found a more elegant solution. Instead of trying to aproximate the correct location using a siamese network trained for matching, we can use a triplet loss function and teach it to maximize the distance to the closest false pair and minimize the distance to the true matches. To find these closest entities we use our charecter embedings. This allowed us to get an f-score of FSCORE6 on the training set and FSCORE7 on the test set reading the 10 closest entities. Notice that at this point we can do away with the matching algorithm alltogether. We simply use the closest entiies as our matches.
\section{Related Works}
There have been a number of attemts to solve the fuzzy join problem. Many of the attemts use varios string matching algorithms for example [Fast-Join: An Efficient Method for Fuzzy TokenMatching based String Similarity Join]. The main issue with using string matching comparisons is that they do not work across a wide variaty of enties ASK DR. SRINIVAS. To our knowledge no serios machine learning aproach has been used for this problem. The problem of blocking has also been dealt with using MapReduce [Efficient Parallel Set-Similarity Joins Using MapReduce]. This approach requires alot of computing power and, since they use a string matching approach in the end, is hard to generalize accross many types of entities.

\subsection{Type Changes and {\subsecit Special} Characters}
We have already seen several typeface changes in this sample.  You
can indicate italicized words or phrases in your text with
the command \texttt{{\char'134}textit}; emboldening with the
command \texttt{{\char'134}textbf}
and typewriter-style (for instance, for computer code) with
\texttt{{\char'134}texttt}.  But remember, you do not
have to indicate typestyle changes when such changes are
part of the \textit{structural} elements of your
article; for instance, the heading of this subsection will
be in a sans serif\footnote{A third footnote, here.
Let's make this a rather short one to
see how it looks.} typeface, but that is handled by the
document class file. Take care with the use
of\footnote{A fourth, and last, footnote.}
the curly braces in typeface changes; they mark
the beginning and end of
the text that is to be in the different typeface.

You can use whatever symbols, accented characters, or
non-English characters you need anywhere in your document;
you can find a complete list of what is
available in the \textit{\LaTeX\
User's Guide}\cite{Lamport:LaTeX}.

\subsection{Math Equations}
You may want to display math equations in three distinct styles:
inline, numbered or non-numbered display.  Each of
the three are discussed in the next sections.

\subsubsection{Inline (In-text) Equations}
A formula that appears in the running text is called an
inline or in-text formula.  It is produced by the
\textbf{math} environment, which can be
invoked with the usual \texttt{{\char'134}begin. . .{\char'134}end}
construction or with the short form \texttt{\$. . .\$}. You
can use any of the symbols and structures,
from $\alpha$ to $\omega$, available in
\LaTeX\cite{Lamport:LaTeX}; this section will simply show a
few examples of in-text equations in context. Notice how
this equation: \begin{math}\lim_{n\rightarrow \infty}x=0\end{math},
set here in in-line math style, looks slightly different when
set in display style.  (See next section).

\subsubsection{Display Equations}
A numbered display equation -- one set off by vertical space
from the text and centered horizontally -- is produced
by the \textbf{equation} environment. An unnumbered display
equation is produced by the \textbf{displaymath} environment.

Again, in either environment, you can use any of the symbols
and structures available in \LaTeX; this section will just
give a couple of examples of display equations in context.
First, consider the equation, shown as an inline equation above:
\begin{equation}\lim_{n\rightarrow \infty}x=0\end{equation}
Notice how it is formatted somewhat differently in
the \textbf{displaymath}
environment.  Now, we'll enter an unnumbered equation:
\begin{displaymath}\sum_{i=0}^{\infty} x + 1\end{displaymath}
and follow it with another numbered equation:
\begin{equation}\sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f\end{equation}
just to demonstrate \LaTeX's able handling of numbering.

\subsection{Citations}
Citations to articles \cite{bowman:reasoning, clark:pct, braams:babel, herlihy:methodology},
conference
proceedings \cite{clark:pct} or books \cite{salas:calculus, Lamport:LaTeX} listed
in the Bibliography section of your
article will occur throughout the text of your article.
You should use BibTeX to automatically produce this bibliography;
you simply need to insert one of several citation commands with
a key of the item cited in the proper location in
the \texttt{.tex} file \cite{Lamport:LaTeX}.
The key is a short reference you invent to uniquely
identify each work; in this sample document, the key is
the first author's surname and a
word from the title.  This identifying key is included
with each item in the \texttt{.bib} file for your article.

The details of the construction of the \texttt{.bib} file
are beyond the scope of this sample document, but more
information can be found in the \textit{Author's Guide},
and exhaustive details in the \textit{\LaTeX\ User's
Guide}\cite{Lamport:LaTeX}.

This article shows only the plainest form
of the citation command, using \texttt{{\char'134}cite}.
This is what is stipulated in the SIGS style specifications.
No other citation format is endorsed.

\subsection{Tables}
Because tables cannot be split across pages, the best
placement for them is typically the top of the page
nearest their initial cite.  To
ensure this proper ``floating'' placement of tables, use the
environment \textbf{table} to enclose the table's contents and
the table caption.  The contents of the table itself must go
in the \textbf{tabular} environment, to
be aligned properly in rows and columns, with the desired
horizontal and vertical rules.  Again, detailed instructions
on \textbf{tabular} material
is found in the \textit{\LaTeX\ User's Guide}.

Immediately following this sentence is the point at which
Table 1 is included in the input file; compare the
placement of the table here with the table in the printed
dvi output of this document.

\begin{table}
\centering
\caption{Frequency of Special Characters}
\begin{tabular}{|c|c|l|} \hline
Non-English or Math&Frequency&Comments\\ \hline
\O & 1 in 1,000& For Swedish names\\ \hline
$\pi$ & 1 in 5& Common in math\\ \hline
\$ & 4 in 5 & Used in business\\ \hline
$\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
\hline\end{tabular}
\end{table}

To set a wider table, which takes up the whole width of
the page's live area, use the environment
\textbf{table*} to enclose the table's contents and
the table caption.  As with a single-column table, this wide
table will ``float" to a location deemed more desirable.
Immediately following this sentence is the point at which
Table 2 is included in the input file; again, it is
instructive to compare the placement of the
table here with the table in the printed dvi
output of this document.

\begin{table*}
\centering
\caption{Some Typical Commands}
\begin{tabular}{|c|c|l|} \hline
Command&A Number&Comments\\ \hline
\texttt{{\char'134}alignauthor} & 100& Author alignment\\ \hline
\texttt{{\char'134}numberofauthors}& 200& Author enumeration\\ \hline
\texttt{{\char'134}table}& 300 & For tables\\ \hline
\texttt{{\char'134}table*}& 400& For wider tables\\ \hline\end{tabular}
\end{table*}
% end the environment with {table*}, NOTE not {table}!

\subsection{Figures}
Like tables, figures cannot be split across pages; the
best placement for them
is typically the top or the bottom of the page nearest
their initial cite.  To ensure this proper ``floating'' placement
of figures, use the environment
\textbf{figure} to enclose the figure and its caption.

This sample document contains examples of \textbf{.pdf} files to be
displayable with \LaTeX.  More details on each of these is found in the
\textit{Author's Guide}.

\begin{figure}
\centering
\includegraphics{fly}
\caption{A sample black and white graphic (.pdf format).}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=1in,height=1in]{fly}
\caption{A sample black and white graphic (.pdf format)
that has been resized with the \texttt{includegraphics} command.}
\end{figure}

As was the case with tables, you may want a figure
that spans two columns.  To do this, and still to
ensure proper ``floating'' placement of tables, use the environment
\textbf{figure*} to enclose the figure and its caption.

Note that only {\textbf{.pdf}} files were used; if you want to include
{\textbf{.ps}} or {\textbf{.eps}} formats, you can use the
\texttt{{\char'134}epsfig} or \texttt{{\char'134}psfig}
commands as appropriate for the different file types.

\subsection{Theorem-like Constructs}
Other common constructs that may occur in your article are
the forms for logical constructs like theorems, axioms,
corollaries and proofs.  There are
two forms, one produced by the
command \texttt{{\char'134}newtheorem} and the
other by the command \texttt{{\char'134}newdef}; perhaps
the clearest and easiest way to distinguish them is
to compare the two in the output of this sample document:

This uses the \textbf{theorem} environment, created by
the\linebreak\texttt{{\char'134}newtheorem} command:
\newtheorem{theorem}{Theorem}
\begin{theorem}
Let $f$ be continuous on $[a,b]$.  If $G$ is
an antiderivative for $f$ on $[a,b]$, then
\begin{displaymath}\int^b_af(t)dt = G(b) - G(a).\end{displaymath}
\end{theorem}

The other uses the \textbf{definition} environment, created
by the \texttt{{\char'134}newdef} command:
\newdef{definition}{Definition}
\begin{definition}
If $z$ is irrational, then by $e^z$ we mean the
unique number which has
logarithm $z$: \begin{displaymath}{\log e^z = z}\end{displaymath}
\end{definition}

\begin{figure}
\centering
\includegraphics[height=1in,width=1in]{rosette}
\caption{A sample black and white graphic (.pdf format) that has
been resized with the \texttt{includegraphics} command.}
\end{figure}

Two lists of constructs that use one of these
forms is given in the
\textit{Author's  Guidelines}.

\begin{figure*}
\centering
\includegraphics{flies}
\caption{A sample black and white graphic (.pdf format)
that needs to span two columns of text.}
\end{figure*}
and don't forget to end the environment with
{figure*}, not {figure}!

There is one other similar construct environment, which is
already set up
for you; i.e. you must \textit{not} use
a \texttt{{\char'134}newdef} command to
create it: the \textbf{proof} environment.  Here
is a example of its use:
\begin{proof}
Suppose on the contrary there exists a real number $L$ such that
\begin{displaymath}
\lim_{x\rightarrow\infty} \frac{f(x)}{g(x)} = L.
\end{displaymath}
Then
\begin{displaymath}
l=\lim_{x\rightarrow c} f(x)
= \lim_{x\rightarrow c}
\left[ g{x} \cdot \frac{f(x)}{g(x)} \right ]
= \lim_{x\rightarrow c} g(x) \cdot \lim_{x\rightarrow c}
\frac{f(x)}{g(x)} = 0\cdot L = 0,
\end{displaymath}
which contradicts our assumption that $l\neq 0$.
\end{proof}

Complete rules about using these environments and using the
two different creation commands are in the
\textit{Author's Guide}; please consult it for more
detailed instructions.  If you need to use another construct,
not listed therein, which you want to have the same
formatting as the Theorem
or the Definition\cite{salas:calculus} shown above,
use the \texttt{{\char'134}newtheorem} or the
\texttt{{\char'134}newdef} command,
respectively, to create it.

\subsection*{A {\secit Caveat} for the \TeX\ Expert}
Because you have just been given permission to
use the \texttt{{\char'134}newdef} command to create a
new form, you might think you can
use \TeX's \texttt{{\char'134}def} to create a
new command: \textit{Please refrain from doing this!}
Remember that your \LaTeX\ source code is primarily intended
to create camera-ready copy, but may be converted
to other forms -- e.g. HTML. If you inadvertently omit
some or all of the \texttt{{\char'134}def}s recompilation will
be, to say the least, problematic.

\section{Conclusions}
This paragraph will end the body of this sample document.
Remember that you might still have Acknowledgments or
Appendices; brief samples of these
follow.  There is still the Bibliography to deal with; and
we will make a disclaimer about that here: with the exception
of the reference to the \LaTeX\ book, the citations in
this paper are to articles which have nothing to
do with the present subject and are used as
examples only.
%\end{document}  % This is where a 'short' article might terminate

% ensure same length columns on last page (might need two sub-sequent latex runs)
\balance

%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}
This section is optional; it is a location for you
to acknowledge grants, funding, editing assistance and
what have you.  In the present case, for example, the
authors would like to thank Gerald Murray of ACM for
his help in codifying this \textit{Author's Guide}
and the \textbf{.cls} and \textbf{.tex} files that it describes.

% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{vldb_sample}  % vldb_sample.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references

\subsection{References}
Generated by bibtex from your ~.bib file.  Run latex,
then bibtex, then latex twice (to resolve references)
to create the ~.bbl file.  Insert that ~.bbl file into
the .tex source file and comment out
the command \texttt{{\char'134}thebibliography}.

% ****************** APPENDIX **************************************

% Example of an appendix; typically would start on a new page
%pagebreak

\begin{appendix}
\section{PVLDB Format has  8+4 pages}
The PVLDB paper length is limited to 8 pages. You are permitted a 4 page appendix beyond these 8 pages. However, reviewers (as well as any readers) are not required to read this appendix, and the paper should be self-contained, complete and understandable within the 8 pages. Typically, it is appropriate to place proofs, algorithm pseudocode, data set descriptions, etc. in the appendix.

Any references to the appendix from the main paper should only be in the nature of "for additional detail see..". In particular, there should be nothing in the appendix that is necessary for a reader to understand the paper. This 8+4 page rule applies to both submissions and camera-ready.

\section{Final Thoughts on Good Layout}
Please restrain yourself from squeezing too much information into the first eight pages; you can use the appendix for optional proofs or details of your evaluation which are not absolutely necessary to the core understanding of your paper. This way, you can use readable font sizes in the figures and graphs, as well as avoid tempering with the correct border values, and the spacing (and format) of both text and captions of the PVLDB format (e.g. captions are bold).

At the end, please check for an overall pleasant layout, e.g. by ensuring a readable and logical positioning of any floating figures and tables. Please also check for any line overflows, which are only allowed in extraordinary circumstances (such as wide formulas or URLs where a line wrap would be counterintuitive).

Use the \texttt{balance} package together with a \texttt{\char'134 balance} command at the end of your document to ensure that the last page has balanced (i.e. same length) columns.

\end{appendix}

\end{document}

### 2018-03-07 paper/introduction.tex
intro checked in

\section{Introduction}

Joining two datasets is a key step in preparing the data for subsequent operations such as performing business analytics, building predictive models etc.  Data management systems have largely focussed solely on equi-joins, which is based on exact equality of strings or numeric values.  However, in many circumstances, exact equality is inadequate because the same entity may in many cases be expressed with slight variations of the same name, as shown in Figure~\ref{table-example} (e.g., \textit{Douglas Adams} and \textit{Douglas Noel Adams}).  Although Figure~\ref{table-example} illustrates the problem for people's names, the same problem occurs for other entity types, such as company names, addresses, states in countries, and countries.

One common technique to automating joins of the sort described in Figure \ref{table-example} is string matching.  String matching approaches use variants of string similarity measures such as edit-distance, Jaro-Winkler and TF-IDF (e.g., \cite{Cohen2003}) to perform matching.  Typically to scale the problem to a large number of rows in each table, a filtering or blocking strategy is used to reduce the number of pairs to be considered for string matching.  For instance, prefix, string length, or suffix based filtering are often applied to the strings in the two tables to identify potentially joinable pairs that need to be matched.  For the examples shown in Figure~\ref{table-example}, the prefix filtering step will ensure that \textit{Douglas Adams} will be compared only with \textit{Douglas Noel Adams} and \textit{Doug C. Engelbart} to determine their string similarity, assuming the prefix used for filtering is \textit{Doug}.

More recently, data driven approaches have emerged as a powerful alternative to string matching techniques for the join problem described in Figure~\ref{table-example}.  Data driven approaches mine patterns in the data to determine the `rules' for joining a given entity type.  One example of such an approach is illustrated in \cite{He:2015:SJS:2824032.2824036}, which determines which cell values should be joined based on whether those cell values co-occur on the same row across disparate tables in a very large corpus of data.  Such a system can perform `semantic joins' such as mapping country names to country codes in new unseen tables.  Another example of a data driven approach is work by \cite{auto-join-joining-tables-leveraging-transformations} that uses program synthesis techniques to learn the right set of transformations needed to perform the entity matching operation, based on a numerous examples.  Unlike string matching algorithms, which apply the same generic operator to a cell value regardless of entity type, the approach outlined in \cite{auto-join-joining-tables-leveraging-transformations} can learn different programs to transform cell values for different entity types.

In this paper, we propose a novel data driven approach to the problem of joining semantically different representations of data.  Our approach relies on building supervised deep learning models to automatically learn the correct set of transformations needed to compute the equality of two cell values.  Because a deep learning model can pick up the appropriate features of what should be used for matching from correlations in the data, it should in theory be able to generalize better across join problems than the data driven approaches outlined in \cite{He:2015:SJS:2824032.2824036}.   Conceptually, our approach is similar in spirit to the approach described in \cite{auto-join-joining-tables-leveraging-transformations}, but we use deep neural networks to learn the right function for the join operation instead of synthesizing different programs for different entity types.  The advantage of building such a function over the approach described in \cite{auto-join-joining-tables-leveraging-transformations} is that we can use this function in novel ways to completely eliminate the filtering that is typically needed to identify the set of potentially joinable rows, as we describe below.

Our specific solution to the join problem involves building a deep neural network that learns to produce a small distance estimate for elements of a name pair that represent the same entity (e.g., \textit{Douglas Adams}-\textit{Douglas Noel Adams} should produce a distance estimate $d$ that is closest to 0), and a much larger distance estimate for elements of the name pair that do not represent the same entity (e.g., \textit{Douglas Adams}-\textit{John Adams} should produce a distance estimate $d$ that is greater than some margin $m$).  The function learnt by such a network (often called a `siamese network') is conceptually one that maps input vectors for the same entity closer together in vector space, while mapping input vectors for a different entity to a distance that is at least \textit{m} distance away from the vectors for the same entity, as shown in Figure \ref{fig-1}.  This sort of function can be used to determine join equality on a subset of string pairs that are considered joinable using some sort of filtering step, as is often done in approaches to the semantic join type problem (e.g. \cite{auto-join-joining-tables-leveraging-transformations}).

However, our observation is that one can actually exploit what the siamese network produces to eliminate this filtering step altogether.  Specifically, the last hidden layer of the siamese network is effectively a `vector embedding' for the same versus different estimate.  That is, the last layer is a vector in a lower dimensional space that contains the critical features needed for computing the distance estimate.  We can in fact take these vector embeddings for all vectors in the two tables to be joined, and use approximate nearest neighbors algorithms to find the nearest neighbors.  Ideally, the nearest neighbor that has a distance lower the margin $m$ should be the correct match.  Because approximate nearest neighbor algorithms have been applied successfully to millions of items, this approach should scale just as well as filtering/join algorithms, but have the added advantage that the filtering step is also data driven, and hence can adapt to different entity types very effectively.

\begin{figure}
\centering
\includegraphics[width=1\linewidth]{fig1}
\label{table-example}
\caption{Example of a join problem}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=1\linewidth]{fig2}
\label{fig-1}
\caption{Conceptual overview of neural network approach to matching}
\end{figure}

Our key contributions to the join problem are as follows:
\begin{itemize}
\item We demonstrate that we can use siamese networks to learn a distance function that successfully discriminates same pairs from distance pairs with an F score of .9.  Our results suggest that deep learning models can be used successfully as another mechanism for data driven joins, assuming some sort of filtering approach has been applied to the data.
\item We explore whether it is possible to extend this further, which is to see if the output of the function can in fact be used in an approximate nearest neighbor algorithm to identify neighbors to match with, without any filtering.  
\end{itemize}

### 2018-03-07 paper/paper.tex
intro checked in

@@
 
-\section{Introduction}
-The \textit{proceedings} are the records of a conference.
-ACM, as well as PVLDB, seeks to give these conference by-products a uniform,
-high-quality appearance.  To do this, ACM / PVLDB has some rigid
-requirements for the format of the proceedings documents: there
-is a specified format (balanced  double columns), a specified
-set of fonts (Arial or Helvetica and Times Roman) in
-certain specified sizes (for instance, 9 point for body copy),
-a specified live area (18 $\times$ 23.5 cm [7" $\times$ 9.25"]) centered on
-the page, specified size of margins (2.54cm [1"] top and
-bottom and 1.9cm [.75"] left and right; specified column width
-(8.45cm [3.33"]) and gutter size (.083cm [.33"]).
-
-The good news is, with only a handful of manual
-settings\footnote{Two of these, the {\texttt{\char'134 numberofauthors}}
-and {\texttt{\char'134 alignauthor}} commands, you have
-already used; another, {\texttt{\char'134 balancecolumns}}, will
-be used in your very last run of \LaTeX\ to ensure
-balanced column heights on the last page.}, the \LaTeX\ document
-class file handles all of this for you.
-
-The remainder of this document is concerned with showing, in
-the context of an ``actual'' document, the \LaTeX\ commands
-specifically available for denoting the structure of a
-proceedings paper, rather than with giving rigorous descriptions
-or explanations of such commands.
+\include{introduction}
 
@@
 In the final product we have an elegant completly machine learning based method.
+
+\subsection{Rule-based Matching}
 \begin{table}
@@
 Noel&\{Douglas Noel Adams\} \\ \hline
-Whipple&\{John Adams Whipple, John A. Whipple\} \\ \hline
+Whipple&\{John Adams Whipple, John A. Whipple\} \\
 \hline\end{tabular}
@@
 
-In the rule-based method we block based on items that have one word in common.
+In the rule-based method, we block based on items that have one word in common.
 This is the simplest reasonable blocking strategy.
-In table 2 we see a what the blocking of the three names from table 1 would look like.
-Out of NUMBER1 pairs NUMBER2 ended up in the same bucket as all their correct matches.
+Table 2 illustrates what the blocking of the three names from Table 1 would look like.
+Out of NUMBER1 pairs, NUMBER2 ended up in the same bucket as all their correct matches.
 NUMBER3 had at least one correct match in the same bucket.
-To preform the actuall matching we used three simple rules.
-One, if two items share a word that only those two have in common match them.
-Two, if the we remove spaces and one of the items is a substring of the other match them.
-Three, if we treat each word as a member of a set representing the entity, and one set is a subset of the other we match them.
-We found that most of the problem with this method was not enough positives, so we accepted if any of the rules matched the two items.
-If we treat it as a success if the correct match is any of the top 3 we get an fscore of FSCORE1.
-Since the issue is mostly false-negitives, even if we accept any of the top 1000 as a success, we get FSCORE2, not much better.
+To perform the actual matching, we used three simple rules see Table 3:
+\begin{enumerate}
 
+\item If a word is unique to two items, we match them. (`John Adams Whipple' matches `John A. Whipple' since `Whipple' only apears in those two names)
+\item If, when all spaces are removed, one of the items is a substring of the other, we match them.
+(`the flower company' matches `theflowercompany.com' since `theflowercompany' is a subset of `theflowercompany.com')
+\item If we treat each name as a set of words, and one set is a subset of the other set, we match them.
+(`Douglas Adams' matches `Douglas Noel Adams' since \{`Douglas', `Adams'\} $\subseteq$ \{`Douglas', `Noel', `Adams'\})
+
+\end{enumerate} 
+Even using these three rules in combination resulted in too many false negatives.
+Therefore we decided to treat all matches resulting from any of the three rules as valid.
+If we treat it as a success if there is a correct match in any of the first three slots, we get an F\textsubscript{1} of FSCORE1.
+Since the issue is mostly false negatives, and therefore even some of the first three slots were often empty, so even if we accept any of the top 1000 as a success, we get FSCORE2, not much better.
+\subsection{Siamese Netwok}
 The first part we replaced was the matcher.
@@
 The output of the two networks is fed into a final layer which determines the distance between the two outputs and accepts or rejects.
-Siamese networks have been shown to work well for image matching.\footnote{CITE} Before feeding the entities into the networks, we used Kazuma charecter embeddings to encode each entity as a vector.
+Siamese networks have been shown to work well for image matching.\cite{Hasdell:Siamese} Before feeding the entities into the networks, we used Kazuma charecter embeddings to encode each entity as a vector.
 We trained the network on our NUMBER1*0.95 pairs and withheld NUMBER1*0.05 for testing.
@@
 There have been a number of attemts to solve the fuzzy join problem.
-Many of the attemts use varios string matching algorithms for example [Fast-Join: An Efficient Method for Fuzzy TokenMatching based String Similarity Join].
+Many of the attemts use varios string matching algorithms for example \cite{Wang:String}.
 The main issue with using string matching comparisons is that they do not work across a wide variaty of enties ASK DR.
@@
 To our knowledge no serios machine learning aproach has been used for this problem.
-The problem of blocking has also been dealt with using MapReduce [Efficient Parallel Set-Similarity Joins Using MapReduce].
+The problem of blocking has also been dealt with using MapReduce \cite{Vernica:MapReduce}.
 This approach requires alot of computing power and, since they use a string matching approach in the end, is hard to generalize accross many types of entities.
@@
 \bibliographystyle{abbrv}
-\bibliography{vldb_sample}  % vldb_sample.bib is the name of the Bibliography in this case
+\bibliography{paper}  % vldb_sample.bib is the name of the Bibliography in this case
 % You must have a proper ".bib" file

### 2018-03-08 paper/dirlim.tex
first version of siamese

\subsection{Dimensionality Reduction by Learning an Invariant Mapping}

The problem of dimensionality reduction, mapping a high dimensional group of entities onto a low dimensional manifold, is an important problem in many areas of machine learning. Dimensionality Reduction by Learning an Invariant Mapping(DrLIM) is a technique for solving this problem by mapping points using a set of previously known matches and non-matches.\cite{Hasdell:Siamese} The goal of this technique is to minimize the distance between matched pairs and maximize the distance between unmatched pairs. This is accomplished using a network architecture know as a Siamese network. In this architecture there are two deep neural networks that share weights attached to a final output layer that determines the distance between the output of the two hidden networks. The network is trained by inputing known pairs and training the network to minimize or maximize the loss function.

### 2018-03-08 paper/drlim.tex
first version of siamese

\subsection{Dimensionality Reduction by Learning an Invariant Mapping}

The problem of dimensionality reduction, mapping a high dimensional group of entities onto a low dimensional manifold, is an important problem in many areas of machine learning. Dimensionality Reduction by Learning an Invariant Mapping is a technique for solving this problem by mapping points onto the manifold using a set of previously known matches and non-matches described by \cite{Hasdell:Siamese}. The goal of this technique is to minimize the distance between matched pairs and maximize the distance between unmatched pairs. This is accomplished using a network architecture know as a \textit{siamese} network. In this architecture there are two deep neural networks that share weights attached to a final layer that determines the distance between the output of the two hidden networks and minimizes the loss function. . To train the network a set of matched and non-matched pairs of inputs is sent through the network and the weights are adjusted to maximize or minimize distance accordingly.

By mapping the inputs onto meaningful locations on a manifold, this method clusters similar inputs close to each other. Using this property we can use the distance layer to decide if two inputs are matched. We simply set a limit for euclidean distance and match if the outputs of the hidden layers are within that limit, as in Figure \ref{siamese}. This lets us use this method for our problem of matching, we treat items as similar to each other if they are aliases for the same entity and different otherwise. To begin with we created the non-matched pairs by choosing other entities with at least one word in common, to avoid the network learning a useless function. This successfully brought the matches close together in the input but failed to properly distance pairs that should be different, as shown in Figure \ref{comp_dif_fail}. Since we never fed the network pairs that were completely different it did not learn to distinguish them from matches. To combat this we created two types of different pairs: ones that share at least one word in common and ones that are completely different.

\begin{figure}
\centering
\includegraphics[width=1\linewidth]{word_in_common}
\caption{The model preformed well on somewhat similar names and badly on completely different names}
\label{comp_dif_fail}
\end{figure}
\begin{figure}
\centering
\includegraphics[width=0.5\linewidth]{siamese_arc}
\caption{A siamese network has two networks which share weights which feed into a distance estimator}
\label{siamese}
\end{figure}

### 2018-03-08 paper/paper.tex
first version of siamese

@@
 \include{introduction}
-
-\section{The {\secit Body} of The Paper}
-Typically, the body of a paper is organized
-into a hierarchical structure, with numbered or unnumbered
-headings for sections, subsections, sub-subsections, and even
-smaller sections.  The command \texttt{{\char'134}section} that
-precedes this paragraph is part of such a
-hierarchy.\footnote{This is the second footnote.  It
-starts a series of three footnotes that add nothing
-informational, but just give an idea of how footnotes work
-and look. It is a wordy one, just so you see
-how a longish one plays out.} \LaTeX\ handles the numbering
-and placement of these headings for you, when you use
-the appropriate heading commands around the titles
-of the headings.  If you want a sub-subsection or
-smaller part to be unnumbered in your output, simply append an
-asterisk to the command name.  Examples of both
-numbered and unnumbered headings will appear throughout the
-balance of this sample document.
-
-Because the entire article is contained in
-the \textbf{document} environment, you can indicate the
-start of a new paragraph with a blank line in your
-input file; that is why this sentence forms a separate paragraph.
-\section{Problem}
-The problem we are dealing with is the fuzzy join problem. EXPAND
+\section{Algorithm}
+\input{drlim}
 \section{Algorithm}
 We started our process with a simple rule based method for matching and another one for blocking.
-We then replaced individual peices with a machine learning method and compared the preformance.
-In the final product we have an elegant completly machine learning based method.
+We then replaced individual pieces with a machine learning method and compared the performance.
+In the final product we have an elegant completely machine learning based method.
 
@@
 
-\subsection{Type Changes and {\subsecit Special} Characters}
-We have already seen several typeface changes in this sample.  You
-can indicate italicized words or phrases in your text with
-the command \texttt{{\char'134}textit}; emboldening with the
-command \texttt{{\char'134}textbf}
-and typewriter-style (for instance, for computer code) with
-\texttt{{\char'134}texttt}.  But remember, you do not
-have to indicate typestyle changes when such changes are
-part of the \textit{structural} elements of your
-article; for instance, the heading of this subsection will
-be in a sans serif\footnote{A third footnote, here.
-Let's make this a rather short one to
-see how it looks.} typeface, but that is handled by the
-document class file. Take care with the use
-of\footnote{A fourth, and last, footnote.}
-the curly braces in typeface changes; they mark
-the beginning and end of
-the text that is to be in the different typeface.
-
-You can use whatever symbols, accented characters, or
-non-English characters you need anywhere in your document;
-you can find a complete list of what is
-available in the \textit{\LaTeX\
-User's Guide}\cite{Lamport:LaTeX}.
-
-\subsection{Math Equations}
-You may want to display math equations in three distinct styles:
-inline, numbered or non-numbered display.  Each of
-the three are discussed in the next sections.
-
-\subsubsection{Inline (In-text) Equations}
-A formula that appears in the running text is called an
-inline or in-text formula.  It is produced by the
-\textbf{math} environment, which can be
-invoked with the usual \texttt{{\char'134}begin. . .{\char'134}end}
-construction or with the short form \texttt{\$. . .\$}. You
-can use any of the symbols and structures,
-from $\alpha$ to $\omega$, available in
-\LaTeX\cite{Lamport:LaTeX}; this section will simply show a
-few examples of in-text equations in context. Notice how
-this equation: \begin{math}\lim_{n\rightarrow \infty}x=0\end{math},
-set here in in-line math style, looks slightly different when
-set in display style.  (See next section).
-
-\subsubsection{Display Equations}
-A numbered display equation -- one set off by vertical space
-from the text and centered horizontally -- is produced
-by the \textbf{equation} environment. An unnumbered display
-equation is produced by the \textbf{displaymath} environment.
-
-Again, in either environment, you can use any of the symbols
-and structures available in \LaTeX; this section will just
-give a couple of examples of display equations in context.
-First, consider the equation, shown as an inline equation above:
-\begin{equation}\lim_{n\rightarrow \infty}x=0\end{equation}
-Notice how it is formatted somewhat differently in
-the \textbf{displaymath}
-environment.  Now, we'll enter an unnumbered equation:
-\begin{displaymath}\sum_{i=0}^{\infty} x + 1\end{displaymath}
-and follow it with another numbered equation:
-\begin{equation}\sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f\end{equation}
-just to demonstrate \LaTeX's able handling of numbering.
-
-\subsection{Citations}
-Citations to articles \cite{bowman:reasoning, clark:pct, braams:babel, herlihy:methodology},
-conference
-proceedings \cite{clark:pct} or books \cite{salas:calculus, Lamport:LaTeX} listed
-in the Bibliography section of your
-article will occur throughout the text of your article.
-You should use BibTeX to automatically produce this bibliography;
-you simply need to insert one of several citation commands with
-a key of the item cited in the proper location in
-the \texttt{.tex} file \cite{Lamport:LaTeX}.
-The key is a short reference you invent to uniquely
-identify each work; in this sample document, the key is
-the first author's surname and a
-word from the title.  This identifying key is included
-with each item in the \texttt{.bib} file for your article.
-
-The details of the construction of the \texttt{.bib} file
-are beyond the scope of this sample document, but more
-information can be found in the \textit{Author's Guide},
-and exhaustive details in the \textit{\LaTeX\ User's
-Guide}\cite{Lamport:LaTeX}.
-
-This article shows only the plainest form
-of the citation command, using \texttt{{\char'134}cite}.
-This is what is stipulated in the SIGS style specifications.
-No other citation format is endorsed.
-
-\subsection{Tables}
-Because tables cannot be split across pages, the best
-placement for them is typically the top of the page
-nearest their initial cite.  To
-ensure this proper ``floating'' placement of tables, use the
-environment \textbf{table} to enclose the table's contents and
-the table caption.  The contents of the table itself must go
-in the \textbf{tabular} environment, to
-be aligned properly in rows and columns, with the desired
-horizontal and vertical rules.  Again, detailed instructions
-on \textbf{tabular} material
-is found in the \textit{\LaTeX\ User's Guide}.
-
-Immediately following this sentence is the point at which
-Table 1 is included in the input file; compare the
-placement of the table here with the table in the printed
-dvi output of this document.
-
-\begin{table}
-\centering
-\caption{Frequency of Special Characters}
-\begin{tabular}{|c|c|l|} \hline
-Non-English or Math&Frequency&Comments\\ \hline
-\O & 1 in 1,000& For Swedish names\\ \hline
-$\pi$ & 1 in 5& Common in math\\ \hline
-\$ & 4 in 5 & Used in business\\ \hline
-$\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
-\hline\end{tabular}
-\end{table}
-
-To set a wider table, which takes up the whole width of
-the page's live area, use the environment
-\textbf{table*} to enclose the table's contents and
-the table caption.  As with a single-column table, this wide
-table will ``float" to a location deemed more desirable.
-Immediately following this sentence is the point at which
-Table 2 is included in the input file; again, it is
-instructive to compare the placement of the
-table here with the table in the printed dvi
-output of this document.
-
-\begin{table*}
-\centering
-\caption{Some Typical Commands}
-\begin{tabular}{|c|c|l|} \hline
-Command&A Number&Comments\\ \hline
-\texttt{{\char'134}alignauthor} & 100& Author alignment\\ \hline
-\texttt{{\char'134}numberofauthors}& 200& Author enumeration\\ \hline
-\texttt{{\char'134}table}& 300 & For tables\\ \hline
-\texttt{{\char'134}table*}& 400& For wider tables\\ \hline\end{tabular}
-\end{table*}
-% end the environment with {table*}, NOTE not {table}!
-
-\subsection{Figures}
-Like tables, figures cannot be split across pages; the
-best placement for them
-is typically the top or the bottom of the page nearest
-their initial cite.  To ensure this proper ``floating'' placement
-of figures, use the environment
-\textbf{figure} to enclose the figure and its caption.
-
-This sample document contains examples of \textbf{.pdf} files to be
-displayable with \LaTeX.  More details on each of these is found in the
-\textit{Author's Guide}.
-
-\begin{figure}
-\centering
-\includegraphics{fly}
-\caption{A sample black and white graphic (.pdf format).}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=1in,height=1in]{fly}
-\caption{A sample black and white graphic (.pdf format)
-that has been resized with the \texttt{includegraphics} command.}
-\end{figure}
-
-As was the case with tables, you may want a figure
-that spans two columns.  To do this, and still to
-ensure proper ``floating'' placement of tables, use the environment
-\textbf{figure*} to enclose the figure and its caption.
-
-Note that only {\textbf{.pdf}} files were used; if you want to include
-{\textbf{.ps}} or {\textbf{.eps}} formats, you can use the
-\texttt{{\char'134}epsfig} or \texttt{{\char'134}psfig}
-commands as appropriate for the different file types.
-
-\subsection{Theorem-like Constructs}
-Other common constructs that may occur in your article are
-the forms for logical constructs like theorems, axioms,
-corollaries and proofs.  There are
-two forms, one produced by the
-command \texttt{{\char'134}newtheorem} and the
-other by the command \texttt{{\char'134}newdef}; perhaps
-the clearest and easiest way to distinguish them is
-to compare the two in the output of this sample document:
-
-This uses the \textbf{theorem} environment, created by
-the\linebreak\texttt{{\char'134}newtheorem} command:
-\newtheorem{theorem}{Theorem}
-\begin{theorem}
-Let $f$ be continuous on $[a,b]$.  If $G$ is
-an antiderivative for $f$ on $[a,b]$, then
-\begin{displaymath}\int^b_af(t)dt = G(b) - G(a).\end{displaymath}
-\end{theorem}
-
-The other uses the \textbf{definition} environment, created
-by the \texttt{{\char'134}newdef} command:
-\newdef{definition}{Definition}
-\begin{definition}
-If $z$ is irrational, then by $e^z$ we mean the
-unique number which has
-logarithm $z$: \begin{displaymath}{\log e^z = z}\end{displaymath}
-\end{definition}
-
-\begin{figure}
-\centering
-\includegraphics[height=1in,width=1in]{rosette}
-\caption{A sample black and white graphic (.pdf format) that has
-been resized with the \texttt{includegraphics} command.}
-\end{figure}
-
-Two lists of constructs that use one of these
-forms is given in the
-\textit{Author's  Guidelines}.
-
-\begin{figure*}
-\centering
-\includegraphics{flies}
-\caption{A sample black and white graphic (.pdf format)
-that needs to span two columns of text.}
-\end{figure*}
-and don't forget to end the environment with
-{figure*}, not {figure}!
-
-There is one other similar construct environment, which is
-already set up
-for you; i.e. you must \textit{not} use
-a \texttt{{\char'134}newdef} command to
-create it: the \textbf{proof} environment.  Here
-is a example of its use:
-\begin{proof}
-Suppose on the contrary there exists a real number $L$ such that
-\begin{displaymath}
-\lim_{x\rightarrow\infty} \frac{f(x)}{g(x)} = L.
-\end{displaymath}
-Then
-\begin{displaymath}
-l=\lim_{x\rightarrow c} f(x)
-= \lim_{x\rightarrow c}
-\left[ g{x} \cdot \frac{f(x)}{g(x)} \right ]
-= \lim_{x\rightarrow c} g(x) \cdot \lim_{x\rightarrow c}
-\frac{f(x)}{g(x)} = 0\cdot L = 0,
-\end{displaymath}
-which contradicts our assumption that $l\neq 0$.
-\end{proof}
-
-Complete rules about using these environments and using the
-two different creation commands are in the
-\textit{Author's Guide}; please consult it for more
-detailed instructions.  If you need to use another construct,
-not listed therein, which you want to have the same
-formatting as the Theorem
-or the Definition\cite{salas:calculus} shown above,
-use the \texttt{{\char'134}newtheorem} or the
-\texttt{{\char'134}newdef} command,
-respectively, to create it.
-
-\subsection*{A {\secit Caveat} for the \TeX\ Expert}
-Because you have just been given permission to
-use the \texttt{{\char'134}newdef} command to create a
-new form, you might think you can
-use \TeX's \texttt{{\char'134}def} to create a
-new command: \textit{Please refrain from doing this!}
-Remember that your \LaTeX\ source code is primarily intended
-to create camera-ready copy, but may be converted
-to other forms -- e.g. HTML. If you inadvertently omit
-some or all of the \texttt{{\char'134}def}s recompilation will
-be, to say the least, problematic.
-
 \section{Conclusions}
-This paragraph will end the body of this sample document.
-Remember that you might still have Acknowledgments or
-Appendices; brief samples of these
-follow.  There is still the Bibliography to deal with; and
-we will make a disclaimer about that here: with the exception
-of the reference to the \LaTeX\ book, the citations in
-this paper are to articles which have nothing to
-do with the present subject and are used as
-examples only.
 %\end{document}  % This is where a 'short' article might terminate
@@
 \section{Acknowledgments}
-This section is optional; it is a location for you
-to acknowledge grants, funding, editing assistance and
-what have you.  In the present case, for example, the
-authors would like to thank Gerald Murray of ACM for
-his help in codifying this \textit{Author's Guide}
-and the \textbf{.cls} and \textbf{.tex} files that it describes.
 
@@
 \begin{appendix}
-\section{PVLDB Format has  8+4 pages}
-The PVLDB paper length is limited to 8 pages.
-You are permitted a 4 page appendix beyond these 8 pages.
-However, reviewers (as well as any readers) are not required to read this appendix, and the paper should be self-contained, complete and understandable within the 8 pages.
-Typically, it is appropriate to place proofs, algorithm pseudocode, data set descriptions, etc.
-in the appendix.
-
-Any references to the appendix from the main paper should only be in the nature of "for additional detail see..".
-In particular, there should be nothing in the appendix that is necessary for a reader to understand the paper.
-This 8+4 page rule applies to both submissions and camera-ready.
-
-\section{Final Thoughts on Good Layout}
-Please restrain yourself from squeezing too much information into the first eight pages; you can use the appendix for optional proofs or details of your evaluation which are not absolutely necessary to the core understanding of your paper.
-This way, you can use readable font sizes in the figures and graphs, as well as avoid tempering with the correct border values, and the spacing (and format) of both text and captions of the PVLDB format (e.g.
-captions are bold).
-
-At the end, please check for an overall pleasant layout, e.g.
-by ensuring a readable and logical positioning of any floating figures and tables.
-Please also check for any line overflows, which are only allowed in extraordinary circumstances (such as wide formulas or URLs where a line wrap would be counterintuitive).
-
-Use the \texttt{balance} package together with a \texttt{\char'134 balance} command at the end of your document to ensure that the last page has balanced (i.e. same length) columns.
 

### 2018-03-11 Named_Entity_Recognition_Modified.py
adding extra difft pairs to the network with contrastive loss

@@ -32,8 +32,9 @@ from keras.optimizers import RMSprop
 from keras import backend as K
 from keras import regularizers
 from keras.regularizers import L1L2
-
-
+from sqlalchemy.sql import select
+import random
+import argparse
 
 BASE_DIR = './Machine_Learning/'
 
@@ -41,7 +42,7 @@ GLOVE_DIR = BASE_DIR + 'glove/'
 
 TEXT_DATA_DIR = BASE_DIR + 'nerData'
 
-DO_ANN_ON_EMBEDDINGS = True
+DO_ANN_ON_EMBEDDINGS = False
 
 # number of words an entity is allowed to have
 
@@ -86,8 +87,77 @@ def check_for_zeroes(to_check, intro_string):
         else:
                 print(intro_string + ' found this many: '+ str(found))
 
+def get_diff_names_with_overlap(con, aliases):
+    no_match_texts = []
+    texts = []
+    # load a mapping from entity id to names
+    entityid2names = {}
+    for row in aliases:
+        if row[2] in entityid2names:
+            names = entityid2names[row[2]];
+        else:
+            names = []
+            entityid2names[row[2]] = names
+        names.append(row[0])
+        names.append(row[1])
+        texts.append(row[0])
+
+    print(len(aliases))
+
+    print("getting word2entities")
+    # load a mapping from words to entities
+    word2entities = {}
+    rows = con.execute("select word, entities from word2entities;")
+    for row in rows:
+        word2entities[row[0]] = row[1]
+
+   
+    for index in range(len(texts)):
+        name_arr = texts[index].split()
+        new_text = ''
+        for n in name_arr:
+            # a name part may have been filtered out of word2entities
+            if n not in word2entities:
+                continue
+            if new_text:
+                break
+            for e in word2entities[n]:
+                if e == texts[index] or e not in entityid2names:   # if the entity is the same as this anchor's text skip it
+                    continue
+                names = entityid2names[e]
+                for x in names:
+                    if n in x:
+                        new_text = x
+                        break
+        if new_text:
+            no_match_texts.append(new_text)
+        else:
+            no_match_texts.append(texts[index + 1])
+    print("done processing matches with overlap")
+
[…]

### 2018-03-11 matcher_functions.py

@@ -15,6 +15,17 @@ def connect(user, password, db, host='localhost', port=5432):
     meta = sqlalchemy.MetaData(bind=con, reflect=True)
 
     return con, meta
+
+# create a set of tuples for the machine learning model where each entity name is matched
+# with at least 2 other names of the same entity, and each entity is paired with 2 other
+# names of a different entity.  The different pairs are chosen based on the fact that the have the 
+# same name part, or are completely different.  If the name is unique then the 2 different pairs
+# are just 2 random pairs.
+def create_tuples_for_siamese_network():
+    aliases_m = meta.tables['aliases']
+    word2entities_m= meta.tables['words2entities']
+
+
 #this should combine several functions and return alisases and bucket lists.
 def condensed_start():
     pass

### 2018-03-11 names_cleanser.py

@@ -104,6 +104,7 @@ class GenericDataCleanser(object):
 				if part not in ret:
 					part = self.remove_bad(part)
 					if part:
+						part = part.replace(',', ' , ').replace('-', ' - ').replace('.', ' . ').replace('  ', ' ')
 						ret.append(part)
 		if len(ret) != self.pairs:
 			return None
@@ -124,7 +125,7 @@ class GenericDataCleanser(object):
 				entity_id += 1
 				newline =''
 				for i in range(1, len(ret)):
-					newline += anchor + '|' + ret[i] + "|" + str(entity_id) + '\n'
+					newline = anchor + '|' + ret[i] + "|" + str(entity_id) + '\n'
 					if self.get:
 						self.number_of_names -= 1
 						if self.number_of_names >= 0:
@@ -163,7 +164,23 @@ class NameDataCleanser(GenericDataCleanser):
 			self.number_of_names = number
 		else:
 			self.get = False
-		self.pairs = 2
+		self.pairs = pairs
+
+
+	def create_new_name(self, name, current_name_set):
+		names = name.split()
+		ret = set([])
+
+		if len(names) <= 2:
+			ret.add(names[1] + ' , ' + names[0])
+			ret.add(names[0][0] + ' . ' + names[1])
+			ret.add(names[1] + ' , ' + names[0][0])
+		elif len(names) > 2:
+			ret.add(names[0] + ' ' + names[1][0] + ' . ' + names[-1])
+			ret.add(names[-1] + ' , ' + names[0] + ' ' + names[1])
+			ret.add(names[-1] + ' , ' + names[0] + ' ' + names[1][0] + ' . ')
+		diff = ret.difference(set(current_name_set))
+		return diff
 
 
 	def cleanse_data(self, line):
@@ -186,6 +203,12 @@ class NameDataCleanser(GenericDataCleanser):
 		line = re.sub('[^\x00-\x7F\x80-\xFF\u0100-\u017F\u0180-\u024F\u1E00-\u1EFF]','',line)
 		arr = line.split("|")
 
+		dups = []
+		for name in arr:
+			dups.append(name.replace(',', ' , ').replace('-', ' - ').replace('.', ' . ').replace('  ', ' '))
+
+		if (len(set(dups))) == 1:
+			return
 
 		# remove silly names
 		cleansed_arr = []
@@ -198,6 +221,9 @@ class NameDataCleanser(GenericDataCleanser):
 			# remove all single names
[…]

### 2018-03-11 run_script.sh

@@ -56,7 +56,7 @@ else
 		$temp_psql $db_name -U $user -f ./process_data.sql
 	fi
 	if [ "$machine" = "1" ]; then
-		$temp_python ./Named_Entity_Recognition_Modified.py $user $passsword $db_name
+		$temp_python ./Named_Entity_Recognition_Modified.py -u $user -p $passsword -d $db_name
 	else
 		$temp_python ./matcher.py $user $passsword $db_name
 	fi

### 2018-03-12 Named_Entity_Recognition_Modified.py
initial results checked in for 1/3 difft pairs with overlap, 2/3 difft pairs no overlap

@@ -270,7 +270,7 @@ def compute_accuracy(predictions, labels):
 
 def get_aliases_with_ids(con, meta):
     #load pairs from database
-    aliases = con.execute("select alias1, alias2, entityid from aliases;")
+    aliases = con.execute("select alias1, alias2, entityid from aliases order by entityid;")
     entities = []
     for row in aliases:
         entities.append((row[0], row[1], row[2]))
@@ -312,6 +312,7 @@ if __name__ == '__main__':
     parser.add_argument('-u', dest="user", help="username")
     parser.add_argument('-p', dest="password", help="password")
     parser.add_argument('-d', dest="db", help="dbname")
+    parser.add_argument('-a', dest="num_pairs", help="number of same pairs in db", nargs='?', default=2, type=int)
 
     args = parser.parse_args()
 
@@ -324,13 +325,15 @@ if __name__ == '__main__':
 
     unique_aliases = []
 
-    i  = 0
+    # collect up all the anchors that are unique (anchors will get repeated if num_pairs > 2)
+    prev = int(aliases[0][2])
+    unique_aliases.append(aliases[0])
     for tuple in aliases:
         texts1.append(tuple[0])
         texts2.append(tuple[1])
-        if i % 2 == 0:
+        if int(tuple[2]) != prev:
             unique_aliases.append(tuple)
-        i += 1
+            prev = int(tuple[2])
 
     print('Found %s texts.' % len(texts1))
 
@@ -340,8 +343,19 @@ if __name__ == '__main__':
     print(len(texts2))
  
     # get the different pairs
-    texts3.extend(get_diff_names_with_overlap(connect(args.user, args.password, args.db)[0], unique_aliases))
-    texts3.extend(get_diff_names_with_no_overlap(unique_aliases))
+    if args.num_pairs == 2:
+        print("args num pairs is 2")
+        texts3.extend(get_diff_names_with_overlap(connect(args.user, args.password, args.db)[0], unique_aliases))
+    elif args.num_pairs == 3:
+        print("args num pairs is 3")
+        texts3.extend(get_diff_names_with_overlap(connect(args.user, args.password, args.db)[0], unique_aliases))
+        texts3.extend(get_diff_names_with_no_overlap(unique_aliases))
+    elif args.num_pairs == 4:
+        print("args num pairs is 4")
+        texts3.extend(get_diff_names_with_overlap(connect(args.user, args.password, args.db)[0], unique_aliases))
[…]

### 2018-03-12 run_script.sh

@@ -56,7 +56,7 @@ else
 		$temp_psql $db_name -U $user -f ./process_data.sql
 	fi
 	if [ "$machine" = "1" ]; then
-		$temp_python ./Named_Entity_Recognition_Modified.py -u $user -p $passsword -d $db_name
+		$temp_python ./Named_Entity_Recognition_Modified.py -u $user -p $passsword -d $db_name -a $temp_pairs
 	else
 		$temp_python ./matcher.py $user $passsword $db_name
 	fi

### 2018-03-13 paper/Aproximate_Nearest_Neighbors.tex
finished changes for todays meeting

\subsection{Approximate Nearest Neighbors}
We used the ANNOY package to find the nearest neighbors in output of the hidden layer computed in the previous section.\cite{annoy_impl} This package approximates the nearest neighbors by first calculating binary trees using the randomized k-d forest method.\cite{ann_paper} These trees are calculated by splitting the vector space by drawing random hyperplanes. Each side of the hyperplane is one node of the binary tree. The algorithm then continues to split each subspace recursively until no more than a predetermined number of items are in each subsection. Some of the neighbors can be found by looking at the items in the same subspace, or subspaces near the target item in the tree. The processes of building a tree is repeated a number of times. By taking a union of the points from all the trees, a reasonable neighborhood is approximated. Once we have a neighborhood of points, we can calculate distance and sort the subset of points. Since much of the time goes into creating the trees, queries can be executed quickly, in logarithmic time.

### 2018-03-13 paper/drlim.tex
removed an extra period
finished changes for todays meeting

@@
 Dimensionality Reduction by Learning an Invariant Mapping is a technique for solving this problem by mapping points onto the manifold using a set of previously known matches and non-matches described by \cite{Hasdell:Siamese}.
+We used this technique not for reducing the dimensionality, but for logically mapping points onto a vector space.
 The goal of this technique is to minimize the distance between matched pairs and maximize the distance between unmatched pairs.
@@
 In this architecture there are two deep neural networks that share weights attached to a final layer that determines the distance between the output of the two hidden networks and minimizes the loss function.
-.
 To train the network a set of matched and non-matched pairs of inputs is sent through the network and the weights are adjusted to maximize or minimize distance accordingly.
+This is accomplished using the following loss function \[ L(W, Y, \vec{X}_1, \vec{X}_2) = (1 - Y)\frac{1}{2}(D_W)^2 + (Y)\frac{1}{2}\{max(0, m - (D_W))\}^2\] Where \(D_W\) is the euclidean distance between the two outputs, \textit{m} is a radius beyond which we ignore dissimilar points, and Y is the similar or dissimilar label.
 

### 2018-05-09 paper/Triplet_loss.tex
rough draft of paper is up

\subsection{Triplet Loss}
While the previos aproach maps 2 entities at a time using 2 networks that share weights, this aproach maps 3 entities at a time with 3 networks: the anchor the positive and the negative. By doing this we can at the same time maximise the distance between two unmatched pairs and minimize the distance between two matched pairs.\cite{schroff2015facenet} We do this by minimizing the following loss function: \[ L(\vec{X}_a, \vec{X}_n, \vec{X}_p) = |\:||\vec{X}_a - \vec{X}_p||^2 - ||\vec{X}_a - \vec{X}_n||^2 + \alpha|\] where \vec{X}_a, \vec{X}_n, \vec{X}_p are the embedded anchor, negative and positive vectors and \alpha is a constant margin. The key choice here is which vectors to include in the training set. If too many easy triplets are including it will slow down the learning since the constraint will be easily satisfied. If too many hard triplets are included the network will learn a strange function based on unusual cases.

### 2018-05-09 paper/paper.tex
finished changes for todays meeting
rough draft of paper is up

@@
 
-\title{A Sample {\ttlit Proceedings of the VLDB Endowment} Paper in LaTeX
-Format\titlenote{for use with vldb.cls}}
+\title{Using Machine Learning to Preform Single Column Fuzzy Joins}
 
@@
 
-\numberofauthors{8} %  in this sample file, there are a *total*
+\numberofauthors{3} %  in this sample file, there are a *total*
 % of EIGHT authors. SIX appear on the 'first-page' (for formatting
@@
 \alignauthor
-Ben Trovato\titlenote{Dr.~Trovato insisted his name be first.}\\
-       \affaddr{Institute for Clarity in Documentation}\\
-       \affaddr{1932 Wallamaloo Lane}\\
-       \affaddr{Wallamaloo, New Zealand}\\
-       \email{trovato@corporation.com}
+Abraham Judah Gale \\
+% \titlenote{Dr.~Trovato insisted his name be first.}\\
+       \affaddr{Yeshiva University}\\
+ %      \affaddr{1932 Wallamaloo Lane}\\
+  %     \affaddr{Wallamaloo, New Zealand}\\
+       \email{yehuda.gale@gmail.com}
 % 2nd. author
 \alignauthor
-G.K.M. Tobin\titlenote{The secretary disavows
-any knowledge of this author's actions.}\\
-       \affaddr{Institute for Clarity in Documentation}\\
-       \affaddr{P.O. Box 1212}\\
-       \affaddr{Dublin, Ohio 43017-6221}\\
-       \email{webmaster@marysville-ohio.com}
+Kavitha Srinivas \\
+% \titlenote{The secretary disavows
+% any knowledge of this author's actions.}\\
+       \affaddr{Rivet Labs}\\
+%       \affaddr{P.O. Box 1212}\\
+ %      \affaddr{Dublin, Ohio 43017-6221}\\
+       \email{Kavitha@rivetlabs.io}
 % 3rd. author
@@
        \email{larst@affiliation.org}
-\and  % use '\and' if you need 'another row' of author names
-% 4th. author
-\alignauthor Lawrence P. Leipuner\\
-       \affaddr{Brookhaven Laboratories}\\
-       \affaddr{Brookhaven National Lab}\\
-       \affaddr{P.O. Box 5000}\\
-       \email{lleipuner@researchlabs.org}
-% 5th. author
-\alignauthor Sean Fogarty\\
-       \affaddr{NASA Ames Research Center}\\
-       \affaddr{Moffett Field}\\
-       \affaddr{California 94035}\\
-       \email{fogartys@amesres.org}
-% 6th. author
-\alignauthor Charles Palmer\\
-       \affaddr{Palmer Research Laboratories}\\
-       \affaddr{8600 Datapoint Drive}\\
-       \affaddr{San Antonio, Texas 78229}\\
-       \email{cpalmer@prl.com}
 }
@@
 \include{introduction}
-\section{Algorithm}
-\input{drlim}
+\input{previos_work}
 \section{Algorithm}
 We started our process with a simple rule based method for matching and another one for blocking.
-We then replaced individual pieces with a machine learning method and compared the performance.
-In the final product we have an elegant completely machine learning based method.
 
@@
 Since the issue is mostly false negatives, and therefore even some of the first three slots were often empty, so even if we accept any of the top 1000 as a success, we get FSCORE2, not much better.
-\subsection{Siamese Netwok}
-The first part we replaced was the matcher.
-To compare the two matchers we created a rule-based matcher using the rules from the rule-based system.
-To replace it we created a siamese network (figure 1) INSERT FIGURE 1.
-A Siamese network is two deep neural networks that share weights.
-One entity is fed into each of the two networks.
-The output of the two networks is fed into a final layer which determines the distance between the two outputs and accepts or rejects.
-Siamese networks have been shown to work well for image matching.\cite{Hasdell:Siamese} Before feeding the entities into the networks, we used Kazuma charecter embeddings to encode each entity as a vector.
-We trained the network on our NUMBER1*0.95 pairs and withheld NUMBER1*0.05 for testing.
-We chose an equal number of negitive pairs to train the model on.
-We chose negitive pairs that had at least one word in common with the positive ones.
-We found that the fscore on the training data was FSCORE3 and FSCORE4 on the test date.
-This was better than the rule-based matcher which had an f-score of FSCORE5.
-
-We next approached the blocking problem with machine learning.
-Since the hidden layer of the siamese network is optimized for matching, it should output an embedding of the entity which has its essential qualities with regaurds to matching (figure 2).
-We then used an aproximate nearest neighbors algorithm to find the nearest neighbors.
-EXPLAIN MORE Using these techniques we can find the most similar items without needing to block at all.
-The problem we ran into is only PERCENT1 of the correct matches were in the 10 nearest neighbors.
-The problem seems to be that since we trained the model using negative pairs that have at least one word in common, it did not learn that names that are completly different should be mapped seperatly (figure 3).
-We could try to fix this by feeding the model better negative pairs, but we found a more elegant solution.
-Instead of trying to aproximate the correct location using a siamese network trained for matching, we can use a triplet loss function and teach it to maximize the distance to the closest false pair and minimize the distance to the true matches.
-To find these closest entities we use our charecter embedings.
-This allowed us to get an f-score of FSCORE6 on the training set and FSCORE7 on the test set reading the 10 closest entities.
-Notice that at this point we can do away with the matching algorithm alltogether.
-We simply use the closest entiies as our matches.
-\section{Related Works}
-There have been a number of attemts to solve the fuzzy join problem.
-Many of the attemts use varios string matching algorithms for example \cite{Wang:String}.
-The main issue with using string matching comparisons is that they do not work across a wide variaty of enties ASK DR.
-SRINIVAS.
-To our knowledge no serios machine learning aproach has been used for this problem.
-The problem of blocking has also been dealt with using MapReduce \cite{Vernica:MapReduce}.
-This approach requires alot of computing power and, since they use a string matching approach in the end, is hard to generalize accross many types of entities.
-
+\input{drlim}
+\input{Aproximate_Nearest_Neighbors}
+\input{Triplet_loss}
+\section{Experiments}
+\input{siamese_exper}
 \section{Conclusions}

### 2018-05-09 paper/siamese_exper.tex
rough draft of paper is up

\subsection{Siamese Network}
Our first experiment was using a Siamese network to match already blocked entities. The architecture of the network was as shown in Figure \ref{siamese}. As described above this involves two networks that share weights mapping the inputs onto a vector space and computing distance. Before feeding the entities into the networks, we used Kazuma character embeddings to encode each entity as a vector. We used character level embeddings since many names would not have been represented at all if we had used word level embeddings. We then trained the network on our 182772 pairs of names pulled from DBpedia. These are the pairs we have after running the data through the cleanser. We used 95\% of them for training and withheld 5\% for testing. In addition to these pairs we created an equal number of negative pairs to train the model. Wherever possible, the negative pairs had at least one word in common with each other. This was done so that the model would not just learn the obvious function of reject unrelated pairs. We trained the model in 10 epochs. We found that the fscore on the training data was FSCORE3 and FSCORE4 on the test data. This showed that this architecture is an effective matcher. However we only successfully included the correct match in around 15\% of pairs in the top five. This was barley better than the 5\% we got from the embedding alone. This shows that the Siamese network was an infective blocker
\subsection{Triplet Loss}
The triplet loss experiment was extremely similar to the Siamese one, only we used the Triplet loss network instead of the Siamese one. We used a margin of 1. We also used an LSTM instead of a regular deep neural network to capture more meaning. The last change we used was in selection of negative points, instead of picking them based on some rule, we picked the closest 40 points that were not matches from the character embedding, when we did this we got 69\% of the items in the top 40. This is a relatively effective blocker. It also correctly placed 97\% of positives closer to the anchor than negatives, making it a very effective matcher.

### 2018-05-09 paper/Triplet_loss.tex
next draft of paper

@@
 While the previos aproach maps 2 entities at a time using 2 networks that share weights, this aproach maps 3 entities at a time with 3 networks: the anchor the positive and the negative.
-By doing this we can at the same time maximise the distance between two unmatched pairs and minimize the distance between two matched pairs.\cite{schroff2015facenet} We do this by minimizing the following loss function: \[ L(\vec{X}_a, \vec{X}_n, \vec{X}_p) = |\:||\vec{X}_a - \vec{X}_p||^2 - ||\vec{X}_a - \vec{X}_n||^2 + \alpha|\] where \vec{X}_a, \vec{X}_n, \vec{X}_p are the embedded anchor, negative and positive vectors and \alpha is a constant margin.
+The loss function minimizes the difference between the anchor and the positive at the same time as it maximises the difference between the anchor and the negative.
+By doing this we can deal with an unmatched pair and a matched pair at the same time: the anchor is one name, the positive is a match for that name and the negative is another name which is not a match.\cite{schroff2015facenet} We accomplish this by minimizing the following loss function: \[ L(\vec{X}_a, \vec{X}_n, \vec{X}_p) = |\:||\vec{X}_a - \vec{X}_p||^2 - ||\vec{X}_a - \vec{X}_n||^2 + \alpha|\] where $\vec{X}_a$, $\vec{X}_n$, $\vec{X}_p$ are the embedded anchor, negative and positive vectors and $\alpha$ is a constant margin.
 The key choice here is which vectors to include in the training set.
 If too many easy triplets are including it will slow down the learning since the constraint will be easily satisfied.
-If too many hard triplets are included the network will learn a strange function based on unusual cases.
+If too many hard triplets are included the network will learn a strange function based on unusual cases

### 2018-05-09 paper/introduction.tex
next draft of paper

@@
 \begin{itemize}
-\item We demonstrate that we can use siamese networks to learn a distance function that successfully discriminates same pairs from distance pairs with an F score of .9.
+\item We demonstrate that we can use a triplet loss network to learn a distance function that successfully discriminates same pairs from different pairs with an accuracy of 97\%.
 Our results suggest that deep learning models can be used successfully as another mechanism for data driven joins, assuming some sort of filtering approach has been applied to the data.
-\item We explore whether it is possible to extend this further, which is to see if the output of the function can in fact be used in an approximate nearest neighbor algorithm to identify neighbors to match with, without any filtering.
+\item We try to extend this further; to see if the output of the function can in fact be used in an approximate nearest neighbor algorithm to identify neighbors to match with, without any filtering. 
 \end{itemize}

### 2018-05-09 paper/paper.tex
next draft of paper

@@
 
-\title{Using Machine Learning to Preform Single Column Fuzzy Joins}
+\title{Using Deep Learning to Perform Fuzzy Joins}
 
@@
 % 1st. author
-\alignauthor
-Abraham Judah Gale \\
+\alignauthor Abraham Judah Gale \\
 % \titlenote{Dr.~Trovato insisted his name be first.}\\
+       \affaddr{Thesis Submitted to}\\
        \affaddr{Yeshiva University}\\
- %      \affaddr{1932 Wallamaloo Lane}\\
   %     \affaddr{Wallamaloo, New Zealand}\\
@@
 % any knowledge of this author's actions.}\\
+     \affaddr{Advisor}\\
        \affaddr{Rivet Labs}\\
-%       \affaddr{P.O. Box 1212}\\
  %      \affaddr{Dublin, Ohio 43017-6221}\\
@@
 % 3rd. author
-\alignauthor Lars Th{\Large{\sf{\o}}}rv{$\ddot{\mbox{a}}$}ld\titlenote{This author is the
-one who did all the really hard work.}\\
-       \affaddr{The Th{\large{\sf{\o}}}rv{$\ddot{\mbox{a}}$}ld Group}\\
-       \affaddr{1 Th{\large{\sf{\o}}}rv{$\ddot{\mbox{a}}$}ld Circle}\\
-       \affaddr{Hekla, Iceland}\\
-       \email{larst@affiliation.org}
+\alignauthor Judah Diament\\
+       \affaddr{Advisor}\\
+       \affaddr{Yeshiva University }\\
+       \email{diament@yu.edu}
 }
@@
 % in the \additional authors block, viz.
-\additionalauthors{Additional authors: John Smith (The Th{\o}rv\"{a}ld Group,
-email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
-(The Kumquat Consortium, email: {\small \texttt{jpkumquat@consortium.net}})}
-\date{30 July 1999}
+% \additionalauthors{Additional authors: John Smith (The Th{\o}rv\"{a}ld Group,
+% email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
+% (The Kumquat Consortium, email: {\small \texttt{jpkumquat@consortium.net}})}
+% \date{30 July 1999}
 % Just remember to make sure that the TOTAL number of authors
@@
 
-\begin{abstract}
-The abstract for your paper for the PVLDB Journal submission.
-The template and the example document are based on the ACM SIG Proceedings  templates.
-This file is part of a package for preparing the submissions for review.
-These files are in the camera-ready format, but they do not contain the full copyright note.
-Note that after the notification of acceptance, there will be an updated style file for the camera-ready submission containing the copyright note.
-\end{abstract}
-
-\include{introduction}
+\input{introduction}
 \input{previos_work}
 \section{Algorithm}
+\subsection{Rule Based}
 We started our process with a simple rule based method for matching and another one for blocking.
-
-\subsection{Rule-based Matching}
-\begin{table}
-\centering
-\caption{Table 1}
-\begin{tabular}{|c|c|} \hline
-Name&Match\\ \hline
-Douglas Adams&Douglas Noel Adams\\ \hline
-Andreas Capellanus&Andrea Cappellano \\ \hline
-John Adams Whipple&John A. Whipple \\
-\hline\end{tabular}
-\end{table}
 
@@
 Whipple&\{John Adams Whipple, John A. Whipple\} \\
-\hline\end{tabular}
+\hline
+\label{word_table}
+\end{tabular}
 \end{table*}
@@
 This is the simplest reasonable blocking strategy.
-Table 2 illustrates what the blocking of the three names from Table 1 would look like.
-Out of NUMBER1 pairs, NUMBER2 ended up in the same bucket as all their correct matches.
-NUMBER3 had at least one correct match in the same bucket.
+Table \ref{word_table} illustrates what the blocking of the three names from Figure \ref{table-example} would look like.
 To perform the actual matching, we used three simple rules see Table 3:
@@
 \end{enumerate} 
-Even using these three rules in combination resulted in too many false negatives.
-Therefore we decided to treat all matches resulting from any of the three rules as valid.
-If we treat it as a success if there is a correct match in any of the first three slots, we get an F\textsubscript{1} of FSCORE1.
-Since the issue is mostly false negatives, and therefore even some of the first three slots were often empty, so even if we accept any of the top 1000 as a success, we get FSCORE2, not much better.
+Even using these three rules in combination resulted in too many false negatives. Therefore we decided to treat all matches resulting from any of the three rules as valid.
 \input{drlim}
@@
 \input{Triplet_loss}
+\input{LSTM}
 \section{Experiments}
+\subsection{Rule Based}
+If we treat it as a success if there is a correct match in any of the first three slots, we get an F\textsubscript{1} score of 0.7.
+Since the issue is mostly false negatives, and therefore even some of the first three slots were often empty, so even if we accept any of the top 1000 as a success, we get FSCORE2, not much better.
 \input{siamese_exper}
 \section{Conclusions}
+While we have a very good machine learning based matcher, that does not appear to translate into very good blocking.
+We still need to explore why we only getting around 69\% of the matches in the top 40 items, when we have the positive closer than the negative in 97\% of cases.
 %\end{document}  % This is where a 'short' article might terminate
@@
 %ACKNOWLEDGMENTS are optional
-\section{Acknowledgments}
 
@@
 
-\subsection{References}
-Generated by bibtex from your ~.bib file.  Run latex,
-then bibtex, then latex twice (to resolve references)
-to create the ~.bbl file.  Insert that ~.bbl file into
-the .tex source file and comment out
-the command \texttt{{\char'134}thebibliography}.
-
 % ****************** APPENDIX **************************************
@@
 
-\begin{appendix}
-
-\end{appendix}
-
 \end{document}

### 2018-05-09 paper/siamese_exper.tex
next draft of paper

@@
 We trained the model in 10 epochs.
-We found that the fscore on the training data was FSCORE3 and FSCORE4 on the test data.
+We found that the fscore on the training data was .89 on the test data.
 This showed that this architecture is an effective matcher.
 However we only successfully included the correct match in around 15\% of pairs in the top five.
-This was barley better than the 5\% we got from the embedding alone.
-This shows that the Siamese network was an infective blocker
+This was barely better than the 5\% we got from the embedding alone.
 \subsection{Triplet Loss}
@@
 We used a margin of 1.
-We also used an LSTM instead of a regular deep neural network to capture more meaning.
-The last change we used was in selection of negative points, instead of picking them based on some rule, we picked the closest 40 points that were not matches from the character embedding, when we did this we got 69\% of the items in the top 40.
+We also used a GRU instead of a regular deep neural network to capture the order of the words.
+The last change we used was in selection of negative points, instead of picking them based on some rule, we picked the closest 40 points that were not matches from the character embedding.
+We did this since those names are the hardest ones for the model to learn, this also avoids the problem in Figure \ref{comp_dif_fail}.
+When we did this we got 69\% of the items in the top 40.
 This is a relatively effective blocker.

### 2018-07-21 paper2018/introduction.tex
first draft

\section{Introduction}

Merging two datasets (the so-called join operation) is a key operation in data management.  Data management systems have largely focussed solely on equi-joins, where equality of strings or numeric values of the two columns determines if rows should be joined.  However, equality at a string level is inadequate because the same entity may in many cases be expressed with slight variations of the same name, as shown in Table~\ref{table-example} (e.g., \textit{Douglas Adams} and \textit{Douglas Noel Adams}).  This problem occurs for many entity types such as company names, addresses, product descriptions, and conference venues.

A common technique to overcome this problem is to perform fuzzy joins using string similarity algorithms such as edit-distance, Jaro-Winkler and TF-IDF (e.g., \cite{Cohen2003}).  In applying fuzzy joins, a key problem is to avoid quadratic comparisons between pairs of strings drawn from the two columns.  A blocking strategy is used to reduce the number of pairs for fuzzy joins, such that only strings that share a common prefix, or suffix will be compared further.  String matching algorithms often do not work because transformations of entity names in perfectly valid ways can yield very different strings (e.g., switching the last name and first name of a person, or providing acronyms for a company name).

More recently, data driven approaches have emerged as a powerful alternative to string matching techniques for fuzzy joins.  Data driven approaches mine patterns in the data to determine the `rules' for joining a given entity type.  One example of such an approach is illustrated in \cite{He:2015:SJS:2824032.2824036}, which determines which cell values should be joined based on whether those cell values co-occur on the same row across disparate tables in a very large corpus of data.  Another example of a data driven approach is work by \cite{auto-join-joining-tables-leveraging-transformations} where program synthesis techniques are used to learn the right set of transformations needed to perform the entity matching operation.

In this paper, we propose a novel data driven approach to the problem of joining different representations of the same entity.  Our approach relies on building supervised deep learning models to automatically learn the correct set of transformations needed to compute the equality of two cell values.  Because a deep learning model can learn the features necessary for matching from the data, it should in theory be able to generalize better to new datasets than the data driven approaches outlined in \cite{He:2015:SJS:2824032.2824036}.   Conceptually, our approach is similar in spirit to the approach described in \cite{auto-join-joining-tables-leveraging-transformations}, but we use deep neural networks to learn the right function for the join operation instead of synthesizing different programs for different entity types.  The advantage of building such a function over the approach described in \cite{auto-join-joining-tables-leveraging-transformations} is that we can use this function in novel ways to completely eliminate the blocking step that is typically needed to identify the set of potentially joinable rows, as we describe below.

Our solution to the join problem involves building a system that performs deep metric learning.  That is, the specific function the network learns is to map input vectors corresponding to same entity closer in vector space compared to vectors that correspond to different entities.  This is typically achieved by training a so-called `triplet siamese network'.  At training, the network is given a triplet consisting of an `anchor' (e.g. \textit{Douglas Adams}), a positive element (e.g. \textit{Douglas Noel Adams}) and a negative element (e.g., John Adams), and it learns to produce a small distance estimate for the positive pair (close to 0), and a large distance estimate for the negative pair (above some margin $m$). A classification form of this function that simply learns whether two names belong to the same entity can be used to perform fuzzy joins, but then we would need a blocking strategy analogous to what has been used in the literature to identify the set of joinable pairs \cite{auto-join-joining-tables-leveraging-transformations}.

Our observation is that one can actually exploit what the siamese network produces to eliminate this blocking step altogether.  Specifically, the last hidden layer of the siamese network is effectively a `vector embedding' that contains the critical features needed for computing the distance estimate.  If such models are pre-built for a given entity type, we can then use the models to produce vector embeddings for all cell values in the two columns to be joined in a single linear pass, and index just the second column values in an approximate nearest neighbors index.  Then, for each cell value in the first column to be joined, querying the k-nearest neighbors should provide the set of values in the second column that can be joined.  Because approximate nearest neighbor algorithms have been applied successfully to billions of items \cite{JDH17}, this approach should scale just as well as join algorithms based on blocking, but has the added advantage that the blocking step is also data driven, and hence can adapt to different entity types very effectively.

Siamese networks (and in particular their `triplet' variants) have been used heavily in the space of face recognition and person re-identification.  To our knowledge though, we know of no work that has applied the same techniques to the problem of fuzzy joins for entity names.  As we point out in the paper, entity names have very different properties from faces, so it is not surprising that the techniques applied in face recognition for selection of samples for training, as well as loss functions do not generalize well to entity names.   
\begin{table}[!htb]
    \caption{Example of a join problem}
    \begin{subtable}{.5\linewidth}
      \centering
        \caption{Table A}
        \begin{tabular}{|l|l|}
          \hline
           Dept & Name \\
           \hline
           1    & Douglas Adams \\
           2    & John Adams \\
           3  & Douglas Bard \\
           \hline
        \end{tabular}
    \end{subtable}%
    \begin{subtable}{.5\linewidth}
      \centering
        \caption{Table B}
        \begin{tabular}{|l|l|}
          \hline
           Name & Salary \\
           \hline
           Douglas N. Adams & 2000 \\
           Adams, John & 3000 \\
           John Smith & 3000 \\
           \hline
        \end{tabular}
    \end{subtable}
    \label{table-example}
\end{table}

Our key contributions are as follows:
\begin{itemize}
\item We demonstrate that triplet loss based siamese networks can be used to learn a distance function that successfully discriminates same entity pairs from different pairs with an accuracy of 98\% and 97\% for about 200,000 people's names and 70,000 company names respectively, drawn from Wikidata.  More importantly, we show that such a network has a high recall of 83\% and 79\%, finding the variants of an entity name in the top 20 neighbors for people and companies respectively.  Moreover, within the 20 neighbors, 77\% and 75\% of the positive names were closer to the anchor than negative names for people and companies respectively.  Our results suggest that deep learning models can be used successfully for data driven joins, assuming that such models are built for common entity types.
\item Training neural networks for deep metric learning is difficult because one cannot show quadratic combinations of the data to the system.  In face recognition, a number of techniques exist for triplet selection, and methods for selecting triples is an active area of research.  We developed a new technique for triplet selection for entity names because the techniques from face recognition do not generalize well to entity names.
\item We also developed a novel loss function to train the network to discriminate entity names from names of other entities.  We compare the results for this loss function with the ones that have been used for face recognition, and show that this loss function can perform much better than the existing functions for deep learning in this domain.
\end{itemize}

The rest of the paper is organized as follows: Section~\ref{siamese networks} describes how we adapted siamese networks to the problem of entity matching, specifically the problem of triplet selection for entity names, and the need for a new type of loss function to improve metric learning for this problem, section ~\ref{dataset} describes characteristics of the datasets we used for training, as well as cleansing and data augmentation techniques we used to generate data, section ~\ref{results} provides the experimental results, section~\ref{related work} covers related work, and section~\ref{conclusions} describes future work and conclusions.

### 2018-07-21 paper2018/main.tex
first draft

\def\year{2018}\relax
%File: formatting-instruction.tex
\documentclass[letterpaper]{article} %DO NOT CHANGE THIS
\usepackage{aaai18}  %Required
\usepackage{times}  %Required
\usepackage{helvet}  %Required
\usepackage{courier}  %Required
\usepackage{url}  %Required
\usepackage{graphicx}  %Required
\usepackage{subcaption}

\frenchspacing  %Required
\setlength{\pdfpagewidth}{8.5in}  %Required
\setlength{\pdfpageheight}{11in}  %Required
%PDF Info Is Required:
  \pdfinfo{
/Title (Fuzzy joins through deep learning)
/Author (Kavitha Srinivas, Yehuda Gale, Julian Dolby)}
\setcounter{secnumdepth}{0}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Fuzzy joins through deep learning}

\author{Kavitha Srinivas \\ IBM Research
\And Yehuda Gale \\ Yeshiva University
\And Julian Dolby \\ IBM Research}

\maketitle
\begin{abstract}
AAAI creates proceedings, working notes, and technical reports directly from electronic source furnished by the authors. To ensure that all papers in the publication have a uniform appearance, authors must adhere to the following instructions. 
\end{abstract}

\input{introduction}
\input{siamese_networks}

%References and End of Paper
  %These lines must be placed at the end of your paper
  \bibliography{paper}
  \bibliographystyle{aaai}
  \end{document}

### 2018-07-21 paper2018/siamese_networks.tex
first draft

\section{Siamese networks}
\label{siamese networks}

Section~\ref{acrhitecture} describes our overall network architecture for entity matching. Section~\ref{loss_functions} enumerates the different loss functions which have been used in prior work, and a new loss function which appears to do better in metric learning for entities.  Section~\ref{triplet_selection} describes a novel triplet selection mechanisms for entity matching.

\subsection{Network Architecture}
\label{architecture}
\begin{figure}
\includegraphics[width=1.0\linewidth]{triplet_siamese_network}
\caption{Architecture of the siamese network}
\label{siamese_nets}
\end{figure}

Figure~\ref{siamese_nets} illustrates overall network architecture we used to build a system for fuzzy joins.  Input vectors were computed assuming a maximum name length of 10 for each entity (i.e., no entity could have a name that spanned more than 10 words).  A 100 dimensional character embedding was computed for each `word' in the entity using pretrained embeddings \cite{hashimoto-jmt:2017:EMNLP2017}, which resulted in a 100 x 10 character encoding for each name used in a triplet.  As described earlier, in a triplet, each entity name (or \textit{anchor}) is paired with another name for the same entity (or \textit{positive}), and with a name for a completely different entity (or \textit{negative}).  The three input vectors from each triplet are fed to three identical networks that share the same weights.  Weight sharing ensures that the networks learn the same mapping function for any given input vector.  In our implementation, each of the three networks had 4 stacked layers of 128 unit Gated Recurrent Units (or GRUs) to capture the sequential nature of the input.

GRUs are a type of recurrent network \cite{cho-al-emnlp14} where each hidden unit updates its weights at a specific step in the sequence $t$ based on the current input $x_t$ and the value of the hidden unit from the prior step $h_{t-1}$.  $r_t$ is a reset gate which determines whether the state from the previous step $h_{t-1}$ should be ignored. $z_t$ is an update gate which determines whether the current hidden state should be updated with the new hidden state $\tilde{h_t}$.  Equations~\ref{eq_1}-\ref{eq_4} that govern the update at $h_t$, as summarized by \cite{colah}.
\begin{equation}
z_t = \sigma(W_z . [h_{t-1}, x_t])
\label{eq_1}
\end{equation}

\begin{equation}
r_t = \sigma(W_r . [h_{t-1}, x_t])
\label{eq_2}
\end{equation}

\begin{equation}
\tilde{h_t} = tanh (W . [r_t * h_{t-1}, x_t])
\label{eq_3}
\end{equation}

\begin{equation}
h_t = (1- z_t) * h_{t-1} + z_t * \tilde{h_t}
\label{eq_4}
\end{equation}

The output of the last layer shown in the Figure~\ref{siamese_nets} as a dark gray layer produces a vector embedding for the inputs.  These are fed to two layers which compute a euclidean distance between the \textit{anchor} and the \textit{positive} elements of a triplet (\textit{positive distance}), and the \textit{anchor} and the \textit{negative} elements of a triplet (\textit{negative distance}).  Conceptually, there are two dual objects in metric learning, one to minimize \textit{positive distances}, and the other to maximize \textit{negative distances}.  As described below, this dual objective is achieved by different loss functions in the literature.

\subsection{Loss functions}
\label{loss_functions}
Let $f(x)$ represent an embedding for an entity name, $f(x_i^a)$,$f(x_i^p)$, $f(x_i^n)$ reflect the vector embeddings of the \textit{anchor}, \textit{positive} and \textit{negative}, respectively.  We investigated four different loss functions to explore their effectiveness for the entity metric learning problem.
\begin{itemize}
\item For face recognition, Schroff et al. \cite{DBLP:conf/cvpr/SchroffKP15} propose a triplet loss function where the squared \textit{positive distances} for each triplet $i$ in the set of $N$ triplets is separated from the squared \textit{negative distances} by a margin of $\alpha$:
\begin{equation}
  L = \sum_{i}^N(\left[\|f(x_i^a) - f(x_i^p)\|_{2}^2 - \|f(x_i^a)- f(x_i^n)\|_{2}^2 + \alpha \right]
\label{schroff}
\end{equation}
Note that in this formulation, it is assumed that embedding is normalized so $\| f(x) \|_2 = 1$.  In other words, the vector embeddings are normalized using the L2 norm.  The value of $\alpha$ in the original work \cite{DBLP:conf/cvpr/SchroffKP15} is also set to 0.2.
\end{itemize}

### 2018-07-25 paper2018/siamese_networks.tex
newer version

@@
 We investigated four different loss functions to explore their effectiveness for the entity metric learning problem.
-\begin{itemize}
-\item For face recognition, Schroff et al.
+\subsubsection{Triplet loss}
+For face recognition, Schroff et al.
 \cite{DBLP:conf/cvpr/SchroffKP15} propose a triplet loss function where the squared \textit{positive distances} for each triplet $i$ in the set of $N$ triplets is separated from the squared \textit{negative distances} by a margin of $\alpha$:
@@
 The value of $\alpha$ in the original work \cite{DBLP:conf/cvpr/SchroffKP15} is also set to 0.2.
-\end{itemize}
+
+\subsubsection{Improved Loss}
+ An improvement over the triplet loss function is proposed by \cite{DBLP:conf/cvpr/SchroffKP15} for the recognition of faces in videos \cite{Zhang:2016:DML:3088616.3088665}.
+Conceptually, this function that we refer to as `improved loss' in the paper considers the distances from the \textit{positive} element of the triplet to the \textit{negative} element as well, and tries to maximize that difference as well as the distance from \textit{anchor} to the \textit{negative}.
+In addition, they try to correct that  original triplet loss function has no constraints on how close the positive distance should be.
+For instance, it is possible for the \textit{anchor} and \textit{positive} form a large cluster with a large intra-class distance.
+The equations that achieve these constraints are described below.
+Equation~\ref{psi} tries to reduce intra-class distance by ensuring it is less than $\hat{\alpha}$.
+Equation~\ref{phi} tries to maximize inter-class distance by ensuring that the distance from the \textit{anchor} and \textit{positive} to the negative are both taken into account.
+Equation~\ref{improved_loss} balances inter-class constraints with intra-class constraints with the parameter $\lambda$.
+
+\begin{equation}
+  \psi = \sum_{i}^N(\left[\|f(x_i^a) - f(x_i^p)\|_{2}^2 - \hat{\alpha} \right]
+\label{psi}
+\end{equation}
+\begin{equation}
+  \phi = \|f(x_i^a) - f(x_i^p)\|_{2}^2 - \left( (\|f(x_i^a)- f(x_i^n)\|_{2}^2 + \|f(x_i^p) - f(x_i^n)\|_{2}^2) / 2 \right) + \alpha
+\label{phi}
+\end{equation}
+\begin{equation}
+  L = max(0, \phi) + \lambda * max(0, \psi)
+\label{improved_loss}
+\end{equation}
+The parameter $\hat{\alpha}$ for equation~\ref{psi} is set to 0.1, and $\lambda$ is set to .02 in equation~\ref{improved_loss}, and $\alpha$ was set to 1 in the paper \cite{Zhang:2016:DML:3088616.3088665}.
+
+\subsubsection{Angular Loss}
+Wang et al.
+\cite{DBLP:journals/corr/abs-1708-01682} define a novel angular loss function which is not based on pairwise distances, but rather is based on the angles of the triangle formed by the \textit{anchor}, \textit{positive} and the \textit{negative} triplet.
+Conceptually, they point out that since the \textit{anchor} and the \textit{positive} pairs belong to the same class, the angle formed by the \textit{anchor}, \textit{negative}, and \textit{positive} elements should be as small as possible within that triangle.
+Their loss function is an attempt to minimize this angle, as defined in the equation below.
+
+\begin{equation}
+L = max(0, \left[\|f(x_i^a) - f(x_i^p)\|_{2}^2 - 4 \tan^2 \alpha \|f(x_i^n) - f(x_i^c)\|_{2}^2 \right])
+\end{equation}

### 2018-07-26 paper2018/siamese_networks.tex
changed notation for schroff loss

@@
 These are fed to two layers which compute a euclidean distance between the \textit{anchor} and the \textit{positive} elements of a triplet (\textit{positive distance}), and the \textit{anchor} and the \textit{negative} elements of a triplet (\textit{negative distance}).
-Conceptually, there are two dual objects in metric learning, one to minimize \textit{positive distances}, and the other to maximize \textit{negative distances}.
+Conceptually, there are two objectives in metric learning, one to minimize \textit{positive distances}, and the other to maximize \textit{negative distances}.
 As described below, this dual objective is achieved by different loss functions in the literature.
@@
 \label{loss_functions}
-Let $f(x)$ represent an embedding for an entity name, $f(x_i^a)$,$f(x_i^p)$, $f(x_i^n)$ reflect the vector embeddings of the \textit{anchor}, \textit{positive} and \textit{negative}, respectively.
+Let $\mathbf{x}$ represent an embedding for an entity name, and $\bf{x_{a}}$, $\bf{x_{p}}$, $\bf{x_{n}}$ reflect the vector embeddings of the \textit{anchor}, \textit{positive} and \textit{negative}, respectively.
 We investigated four different loss functions to explore their effectiveness for the entity metric learning problem.
@@
 For face recognition, Schroff et al.
-\cite{DBLP:conf/cvpr/SchroffKP15} propose a triplet loss function where the squared \textit{positive distances} for each triplet $i$ in the set of $N$ triplets is separated from the squared \textit{negative distances} by a margin of $\alpha$:
+\cite{DBLP:conf/cvpr/SchroffKP15} propose a triplet loss function where the \textit{positive distances} for each triplet $i$ in the set of $N$ triplets is separated from \textit{negative distances} by a margin of $\alpha$.
+For each of $N$ triples, $l_{triple}$ reflects the loss for a given triple as follows:
 \begin{equation}
-  L = \sum_{i}^N(\left[\|f(x_i^a) - f(x_i^p)\|_{2}^2 - \|f(x_i^a)- f(x_i^n)\|_{2}^2 + \alpha \right]
+  l_{triple} =  \left[\|\bf{x_a} - \bf{x_p}\|^2 - \|\bf{x_a} -\bf{x_n}\|^2 + \alpha \right]_+
 \label{schroff}
 \end{equation}
-Note that in this formulation, it is assumed that embedding is normalized so $\| f(x) \|_2 = 1$.
-In other words, the vector embeddings are normalized using the L2 norm.
-The value of $\alpha$ in the original work \cite{DBLP:conf/cvpr/SchroffKP15} is also set to 0.2.
+where
+\begin{equation}
+ \left[.\right]_{+} = max(0, .)
+\end{equation}
+and the loss function that is minimized across all $N$ triples is given by
+\begin{equation}
+ L = \sum_{i}^{N} l_{triple}
+\end{equation}
+Note that in this formulation, it is assumed that embedding is normalized so $\|\bf{x} \| = 1$ because this normalization is robust across variations in illumination and contrast.
+The value of $\alpha$ in the original work is a hyper-parameter that \cite{DBLP:conf/cvpr/SchroffKP15} was set to 0.2.
 

### 2018-07-27 paper2018/siamese_networks.tex
more cleaned up version of loss functions

@@
 \subsubsection{Triplet loss}
+
+\begin{figure}
+\includegraphics[width=1.0\linewidth]{schroff_triplet}
+\caption{Triplet loss}
+\label{schroff_loss}
+\end{figure}
+
 For face recognition, Schroff et al.
-\cite{DBLP:conf/cvpr/SchroffKP15} propose a triplet loss function where the \textit{positive distances} for each triplet $i$ in the set of $N$ triplets is separated from \textit{negative distances} by a margin of $\alpha$.
+\cite{DBLP:conf/cvpr/SchroffKP15} propose a triplet loss function where the \textit{positive distances} for each triplet $i$ in the set of $N$ triplets is separated from \textit{negative distances} by a margin of $\alpha$, as shown in Figure~\ref{schroff_loss}.
 For each of $N$ triples, $l_{triple}$ reflects the loss for a given triple as follows:
@@
 Conceptually, this function that we refer to as `improved loss' in the paper considers the distances from the \textit{positive} element of the triplet to the \textit{negative} element as well, and tries to maximize that difference as well as the distance from \textit{anchor} to the \textit{negative}.
-In addition, they try to correct that  original triplet loss function has no constraints on how close the positive distance should be.
+In addition,it corrects the fact the  original triplet loss function has no constraints on how close the positive distance should be.
 For instance, it is possible for the \textit{anchor} and \textit{positive} form a large cluster with a large intra-class distance.
@@
 \begin{equation}
-  \psi = \sum_{i}^N(\left[\|f(x_i^a) - f(x_i^p)\|_{2}^2 - \hat{\alpha} \right]
+  \psi_{triple} = \|\bf{x_{a}} - \bf{x_{p}}\|^2 - \hat{\alpha}
 \label{psi}
@@
 \begin{equation}
-  \phi = \|f(x_i^a) - f(x_i^p)\|_{2}^2 - \left( (\|f(x_i^a)- f(x_i^n)\|_{2}^2 + \|f(x_i^p) - f(x_i^n)\|_{2}^2) / 2 \right) + \alpha
+  \phi_{triple} = \|\bf{x_{a}} - \bf{x_{p}}\|^2 - (\|\bf{x_{a}}- \bf{x_{n}}\|^2 + \|\bf{x_{p}} - \bf{x_{n}}\|^2) / 2  + \alpha
 \label{phi}
@@
 \begin{equation}
-  L = max(0, \phi) + \lambda * max(0, \psi)
+  l_{triple} = max(0, \phi) + \lambda * max(0, \psi)
 \label{improved_loss}
@@
 The parameter $\hat{\alpha}$ for equation~\ref{psi} is set to 0.1, and $\lambda$ is set to .02 in equation~\ref{improved_loss}, and $\alpha$ was set to 1 in the paper \cite{Zhang:2016:DML:3088616.3088665}.
+As in Schroff et al.
+\cite{DBLP:conf/cvpr/SchroffKP15}, the embeddings are normalized to 1.
 
@@
 Their loss function is an attempt to minimize this angle, as defined in the equation below.
-
 \begin{equation}
-L = max(0, \left[\|f(x_i^a) - f(x_i^p)\|_{2}^2 - 4 \tan^2 \alpha \|f(x_i^n) - f(x_i^c)\|_{2}^2 \right])
+\bf{x_{c}} = (\bf{x_{a}} + \bf{x_{c}}) / 2
 \end{equation}
+\begin{equation}
+l_{triplet} = \left[[\bf{x_{a}} - \bf{x_{p}}\|^2 - 4 \tan^2 \alpha \|\bf{x_{n}} - \bf{x_{c}}\|^2 \right])_{+}
+\end{equation}

### 2018-07-27 paper2018/siamese_networks.tex
added another figure

@@
 \begin{figure}
-\includegraphics[width=1.0\linewidth]{schroff_triplet}
+\includegraphics[width=0.5\linewidth]{schroff_triplet}
 \caption{Triplet loss}
@@
 \subsubsection{Improved Loss}
+
+\begin{figure}
+\includegraphics[width=0.5\linewidth]{modified_loss}
+\caption{Modified loss}
+\label{modified_loss}
+\end{figure}
+
  An improvement over the triplet loss function is proposed by \cite{DBLP:conf/cvpr/SchroffKP15} for the recognition of faces in videos \cite{Zhang:2016:DML:3088616.3088665}.

### 2018-07-28 paper2018/introduction.tex
move face recognition motivation discussion earlier

@@
 Our approach relies on building supervised deep learning models to automatically learn the correct set of transformations needed to compute the equality of two cell values.
+For face recognition and person re-identification, siamese networks---in particular their `triplet' variants---have been used heavily; they are a natural fit for our problem too, since they train on both same and different data in comparisons, which is what we need for entity recognition.
+We know of no work that has applied these techniques to the problem of fuzzy joins for entity names; furthermore, entity names have very different properties from faces, so we needed new techniques for selection of samples for training, and new loss functions.
+
 Because a deep learning model can learn the features necessary for matching from the data, it should in theory be able to generalize better to new datasets than the data driven approaches outlined in \cite{He:2015:SJS:2824032.2824036}.
@@
 
-Siamese networks (and in particular their `triplet' variants) have been used heavily in the space of face recognition and person re-identification.
-To our knowledge though, we know of no work that has applied the same techniques to the problem of fuzzy joins for entity names.
-As we point out in the paper, entity names have very different properties from faces, so it is not surprising that the techniques applied in face recognition for selection of samples for training, as well as loss functions do not generalize well to entity names.
 \begin{table}[!htb]

### 2018-07-28 paper2018/introduction.tex
edit networks a bit

@@
 Our approach relies on building supervised deep learning models to automatically learn the correct set of transformations needed to compute the equality of two cell values.
-For face recognition and person re-identification, siamese networks---in particular their `triplet' variants---have been used heavily; they are a natural fit for our problem too, since they train on both same and different data in comparisons, which is what we need for entity recognition.
+For face recognition and person re-identification, siamese networks---in particular their `triplet' variants---have been used successfully; they are a natural fit for our problem too, since they train on both same and different data in comparisons, which is what we need for entity recognition.
 We know of no work that has applied these techniques to the problem of fuzzy joins for entity names; furthermore, entity names have very different properties from faces, so we needed new techniques for selection of samples for training, and new loss functions.
@@
 That is, the specific function the network learns is to map input vectors corresponding to same entity closer in vector space compared to vectors that correspond to different entities.
-This is typically achieved by training a so-called `triplet siamese network'.
+As in face recognition, we do this by training a `triplet siamese network'.
 At training, the network is given a triplet consisting of an `anchor' (e.g.
@@
 Our observation is that one can actually exploit what the siamese network produces to eliminate this blocking step altogether.
-Specifically, the last hidden layer of the siamese network is effectively a `vector embedding' that contains the critical features needed for computing the distance estimate.
+Specifically, the last hidden layer (JD: output layer?) of the siamese network is effectively a `vector embedding' that contains the critical features needed for computing the distance estimate.
 If such models are pre-built for a given entity type, we can then use the models to produce vector embeddings for all cell values in the two columns to be joined in a single linear pass, and index just the second column values in an approximate nearest neighbors index.

### 2018-07-28 paper2018/siamese_networks.tex
adding angular loss
edit networks a bit

@@
 
-Section~\ref{acrhitecture} describes our overall network architecture for entity matching.
+Section~\ref{architecture} describes our overall network architecture for entity matching.
 Section~\ref{loss_functions} enumerates the different loss functions which have been used in prior work, and a new loss function which appears to do better in metric learning for entities.
@@
 Figure~\ref{siamese_nets} illustrates overall network architecture we used to build a system for fuzzy joins.
-Input vectors were computed assuming a maximum name length of 10 for each entity (i.e., no entity could have a name that spanned more than 10 words).
-A 100 dimensional character embedding was computed for each `word' in the entity using pretrained embeddings \cite{hashimoto-jmt:2017:EMNLP2017}, which resulted in a 100 x 10 character encoding for each name used in a triplet.
-As described earlier, in a triplet, each entity name (or \textit{anchor}) is paired with another name for the same entity (or \textit{positive}), and with a name for a completely different entity (or \textit{negative}).
-The three input vectors from each triplet are fed to three identical networks that share the same weights.
+Input is initially triples of a name (anchor), another name for the same entity (positive) and a name of another entity (negative).
+For the network, input vectors are computed for each entity assuming a maximum name length of 10 for each entity (i.e., no entity could have a name that spanned more than 10 tokens).
+A 100 dimensional character embedding was computed for each token in the entity using pretrained embeddings \cite{hashimoto-jmt:2017:EMNLP2017}, which resulted in a 100 x 10 character encoding for each name used in a triplet.
+These three input vectors from each triplet are fed to three identical networks that share the same weights.
 Weight sharing ensures that the networks learn the same mapping function for any given input vector.
@@
 
-The output of the last layer shown in the Figure~\ref{siamese_nets} as a dark gray layer produces a vector embedding for the inputs.
+The output of the last layer shown in the Figure~\ref{siamese_nets} as a dark gray layer produces an output vector embedding for the inputs.
 These are fed to two layers which compute a euclidean distance between the \textit{anchor} and the \textit{positive} elements of a triplet (\textit{positive distance}), and the \textit{anchor} and the \textit{negative} elements of a triplet (\textit{negative distance}).
@@
 \subsubsection{Angular Loss}
+
+\begin{figure}
+\includegraphics[width=1\linewidth]{angular_loss}
+\caption{Angular loss}
+\label{angular_loss}
+\end{figure}
+
 Wang et al.

### 2018-07-28 paper2018/siamese_networks.tex
work on figures

@@
 \label{loss_functions}
+
 Let $\mathbf{x}$ represent an embedding for an entity name, and $\bf{x_{a}}$, $\bf{x_{p}}$, $\bf{x_{n}}$ reflect the vector embeddings of the \textit{anchor}, \textit{positive} and \textit{negative}, respectively.
 We investigated four different loss functions to explore their effectiveness for the entity metric learning problem.
-\subsubsection{Triplet loss}
 
-\begin{figure}
-\includegraphics[width=0.5\linewidth]{schroff_triplet}
+\begin{figure*}[htb]
+    \centering
+    \begin{subfigure}[t]{0.23\textwidth}
+        \centering
+        \includegraphics[width=.9\linewidth]{schroff_triplet}
         \caption{Triplet loss}
         \label{schroff_loss}
-\end{figure}
+    \end{subfigure}%
+    ~ 
+    \begin{subfigure}[t]{0.23\textwidth}
+        \centering 
+        \includegraphics[width=.9\linewidth]{modified_loss}
+        \caption{Modified loss}
+        \label{modified_loss}
+    \end{subfigure}
+    ~ 
+    \begin{subfigure}[t]{0.23\textwidth}
+        \centering 
+        \includegraphics[width=.9\linewidth]{angular_loss}
+        \caption{Angular loss}
+        \label{angular_loss}
+    \end{subfigure}
+    ~ 
+    \begin{subfigure}[t]{0.23\textwidth}
+        \centering 
+        \includegraphics[width=.9\linewidth]{tanh_triplet}
+        \caption{$Tanh$ loss}
+        \label{tanh_loss}
+    \end{subfigure}
+    \caption{Loss functions}
+\end{figure*}
+
+\subsubsection{Triplet loss}
 
@@
 \subsubsection{Improved Loss}
-
-\begin{figure}
-\includegraphics[width=0.5\linewidth]{modified_loss}
-\caption{Modified loss}
-\label{modified_loss}
-\end{figure}
 
@@
 
-\begin{figure}
-\includegraphics[width=1\linewidth]{angular_loss}
-\caption{Angular loss}
-\label{angular_loss}
-\end{figure}
-
 Wang et al.
@@
 \end{equation}
+
+\subsubsection{Hyperbolic Tangent Loss}

### 2018-07-28 paper2018/siamese_networks.tex
loss functions

@@
 \subsubsection{Hyperbolic Tangent Loss}
+
+The inspiration for our loss is that triplet loss, in effect, only pushes the negative distance as far as $\alpha$; if the negative distance is larger than that, the total loss can become negative, which is then forced to 0.
+However, the further the negative point is from the anchor, the better, so we want to push it as far away as possible, without a limit like $\alpha$.
+To achieve this, we use hyperbolic tangent to compress all distances to the range 0 to 1, and substract the negative distance from 1.
+Then our loss function simply needs to minimize both positive and negative numbers:
+
+ \begin{equation}
+  l_{triple} =  tanh\left(\|\bf{x_a} - \bf{x_p}\|\right) + \left(1-tanh\left(\|\bf{x_a} -\bf{x_n}\|\right)\right)
+\label{tanh}
+\end{equation}

### 2018-07-29 TripletLossFacenetLSTM-hpo.py
use K... consistently

@@ -181,7 +181,7 @@ def angular_loss(y_true, y_pred):
     Facenet triplet loss function: https://arxiv.org/pdf/1503.03832.pdf
 """
 def schroff_triplet_loss(y_true, y_pred):
-    margin = K.constant(MARGIN)
+    margin = K.constant(0.2)
     return K.mean(K.maximum(K.constant(0), K.square(y_pred[:,0,0]) - K.square(y_pred[:,1,0]) + margin))
 
 def triplet_loss(y_true, y_pred):
@@ -199,13 +199,13 @@ def triplet_tanh_loss(y_true, y_pred):
 # the following triplet loss function is from: Deep Metric Learning with Improved Triplet Loss for 
 # Face clustering in Videos 
 def improved_loss(y_true, y_pred):
-    margin = K.constant(MARGIN)
-    lambda_p = 0.02
-    threshold = 0.1
+    margin = K.constant(1)
+    lambda_p = K.constant(0.02)
+    threshold = K.constant(0.1)
     a_p_distance = y_pred[:,0,0]
     a_n_distance = y_pred[:,1,0]
     p_n_distance = y_pred[:,2,0]
-    phi = a_p_distance - ((a_n_distance + p_n_distance) / 2) + margin
+    phi = a_p_distance - ((a_n_distance + p_n_distance) / K.constant(2)) + margin
     psi = a_p_distance - threshold 
 
     return K.maximum(K.constant(0), phi) + lambda_p * K.maximum(K.constant(0), psi) 

### 2018-07-29 paper2018/introduction.tex
minor change in flow

--- 2018-07-21 paper2018/introduction.tex
@@
 
-Merging two datasets (the so-called join operation) is a key operation in data management.
+Merging two datasets using joins is a key operation in data management.
 Data management systems have largely focussed solely on equi-joins, where equality of strings or numeric values of the two columns determines if rows should be joined.
@@
 Our approach relies on building supervised deep learning models to automatically learn the correct set of transformations needed to compute the equality of two cell values.
+For the closely related problem of face recognition and person re-identification, deep learning networks have been used successfully to discriminate pairs that represent the same entity from those that don't.
+However, we know of no work that has adapted these techniques to the problem of fuzzy joins for entity names.
+
 Because a deep learning model can learn the features necessary for matching from the data, it should in theory be able to generalize better to new datasets than the data driven approaches outlined in \cite{He:2015:SJS:2824032.2824036}.
@@
 That is, the specific function the network learns is to map input vectors corresponding to same entity closer in vector space compared to vectors that correspond to different entities.
-This is typically achieved by training a so-called `triplet siamese network'.
+As in face recognition, we do this by training a `triplet siamese network'.
+However, entity names have very different properties from faces, so we needed to adapt the approaches used in face recognition to the entity matching problem with a novel method to choose the sample for training, and novel loss functions as objectives for the metric learning problem.
+
 At training, the network is given a triplet consisting of an `anchor' (e.g.
 \textit{Douglas Adams}), a positive element (e.g.
-\textit{Douglas Noel Adams}) and a negative element (e.g., John Adams), and it learns to produce a small distance estimate for the positive pair (close to 0), and a large distance estimate for the negative pair (above some margin $m$).
+\textit{Douglas Noel Adams}) and a negative element (e.g., John Adams), and it learns to produce a small distance estimate for the positive pair (close to 0), and a large distance estimate for the negative pair, using an objective function.
 A classification form of this function that simply learns whether two names belong to the same entity can be used to perform fuzzy joins, but then we would need a blocking strategy analogous to what has been used in the literature to identify the set of joinable pairs \cite{auto-join-joining-tables-leveraging-transformations}.

### 2018-07-29 paper2018/triplet_selection.tex
adding more

\subsubsection{Triplet Selection}
Deep metric learning for faces is a difficult problem for neural networks to learn because improper sample selection can make it difficult for the network to converge.  In Schroff et al.'s work~\cite{DBLP:conf/cvpr/SchroffKP15} they discuss various online and offline approaches for the problem of triplet selection.  Conceptually, sampling the `right' triples for fast network learning, as Schroff et al. point out requires sampling a set of \textit{hard positives} and a set of \textit{hard negatives}, where a hard positive is defined as $argmax^i \| x_{a} - x_{p}^i \|^2$, where $i$ ranges over all $x_p$ and a hard negative is defined as $argmin^i \| x_{a} - x{_n}^i \|^2$.

However, it is infeasible to compute these values for the entire dataset for selection.  As a result, the triplets can be generated either offline, for every n steps, or online, by selecting the hard positive and negative exemplars within a batch of examples.  In Schroff et al.'s work, they focus on the online generation case.  In practice, instead of focusing on finding \textit{hard positives}, they instead pair every possible positive in the sample with selected negatives, since the set of positives is usually quite small.  Furthermore, for negative examples, they try to select what they term \textit{semi-hard negatives} instead of \textit{hard negatives}, where a \textit{semi-hard negative} has the property that $\|x_a - x_p \|^2 < \|x_a - x_n \|^2$.  That is, \textit{semi-hard negative} is further from the \textit{anchor} than the \textit{positive}, but is not distant by the margin $\alpha$ that is used in the triplet-loss function.  Schroff et al. argue selecting \textit{hard negatives} may in practice lead to bad local minima early on in training, and lead to a collapsed model where the function always learns to return a value of 0, regardless of the pair being considered.

### 2018-07-29 paper2018/triplet_selection.tex
added section on triplet selection

@@
-\subsubsection{Triplet Selection}
+\subsection{Triplet Selection}
 Deep metric learning for faces is a difficult problem for neural networks to learn because improper sample selection can make it difficult for the network to converge.
+We describe a popular approach from the face recognition literature first before we describe a new mechanism for triplet selection.
+
+\subsubsection{Batch Based Triple Selection}
 In Schroff et al.'s work~\cite{DBLP:conf/cvpr/SchroffKP15} they discuss various online and offline approaches for the problem of triplet selection.
@@
 In Schroff et al.'s work, they focus on the online generation case.
+
 In practice, instead of focusing on finding \textit{hard positives}, they instead pair every possible positive in the sample with selected negatives, since the set of positives is usually quite small.
@@
 argue selecting \textit{hard negatives} may in practice lead to bad local minima early on in training, and lead to a collapsed model where the function always learns to return a value of 0, regardless of the pair being considered.
+
+\subsubsection{Metric Based Triplet Selection}
+Although the computation of there is $argmax^i \| x_{a} - x_{p}^i \|^2$ and $argmin^i \| x_{a} - x{_n}^i \|^2$ is infeasible because it involves quadratic comparisons within a dataset, we observe that the use of approximate nearest neighbor (ANN) indexes can actually make this problem tractable for the selection of triples.
+
+Approximate nearest neighbor indexes are highly efficient methods for selecting the top-K neighbors of a given vector by Euclidean distance or cosine similarity.
+They are based on space partitioning algorithms, such as \textit{k-d trees}, where the vector space is iteratively bisected into two disjoint regions.
+Finding the nearest neighbors of a vector involves traversal of the tree to a leaf by evaluating the queried vector at each split point in the tree.
+Depending on the position of the vector within the space bounded by a split point, it may need to traverse both points the split.
+However, large portions of the tree (and hence most vectors in the dataset) never get compared to each other.
+The average complexity to query the vectors of a neighbor is in fact $O(log N)$ where N is the number of vectors in the dataset.
+Implementations exist now for fast, memory-efficient ANN indexes that scale up to a billion vectors \cite{JDH17} using techniques to compress vectors in memory efficiently.
+In our work, we used the Annoy ANN implementation \cite{annoy_git} in our work which is based on the refinements to \textit{k-d trees} ideas described in \cite{annoy-paper}.
+
+Assuming one has the entire dataset indexed in an ANN index, the problem of triplet selection can be simplified by asking the ANN index for the top k-nearest neighbors of an \textit{anchor}, where k is given by the number of triplets that one desires to generate for each anchor.
+Selection of \textit{hard positives} is not really relevant because all positive data should be used to teach the network the right function, as Schroff et al.
+point out.
+\textit{Hard negatives} are simply the negatives that appear in the top-K.
+
+The selection of \textit{semi-hard negatives} is a bit more difficult and depends on the characteristics of the dataset.
+In some cases, there may be very few \textit{semi-hard negatives} because the positives are more distant than the negatives.
+This was a rather serious problem in our people's name matching dataset.
+If we take the character embeddings of each of the names in our name matching dataset, index it in an ANN, and then ask for the top-k neighbors we find somewhat troubling properties for an approach that tries to select \textit{semi-hard} negatives.
+First, \textit{positives} appeared in the top 20 neighbors only in 3.2\% of the dataset.
+Explicitly computing the distance between the \textit{anchor} and the \textit{positive} yielded a mean of 9.07, with a standard deviation of 3.07.
+The mean distances between the \textit{anchor} and the \textit{negatives} for those negatives in the top 20 was 3.16 with a standard deviation of 1.17.
+Given that only 3.2\% of positives actually even appeared in the top-K nearest neighbors, selection of \textit{semi-hard} negatives is reduced to a very small fraction of the dataset.
+We therefore used a k-nearest neighbor approach to triplet selection instead, picking all positive triplets, and a set of \textit{hard negative} triplets based on the top-k nearest neighbors.
+As we show later this approach generalizes to datasets such as company names where it is less extreme in terms of reversal of \textit{positive} and \textit{negative} distances.

### 2018-07-30 paper2018/siamese_networks.tex
adding more
refer to figures in text

@@
 
-For face recognition, Schroff et al.
-\cite{DBLP:conf/cvpr/SchroffKP15} propose a triplet loss function where the \textit{positive distances} for each triplet $i$ in the set of $N$ triplets is separated from \textit{negative distances} by a margin of $\alpha$, as shown in Figure~\ref{schroff_loss}.
-For each of $N$ triples, $l_{triple}$ reflects the loss for a given triple as follows:
+For face recognition, Schroff et al. \cite{DBLP:conf/cvpr/SchroffKP15}
+propose a triplet loss function where the \textit{positive distances}
+for each triplet $i$ in the set of $N$ triplets is separated from
+\textit{negative distances} by a margin of $\alpha$, as shown in
+Figure~\ref{schroff_loss} with the arrow pushing toward $\alpha$.  For
+each of $N$ triples, $l_{triple}$ reflects the loss for a given triple
+as follows: 
 \begin{equation}
@@
 
- An improvement over the triplet loss function is proposed by \cite{DBLP:conf/cvpr/SchroffKP15} for the recognition of faces in videos \cite{Zhang:2016:DML:3088616.3088665}.
-Conceptually, this function that we refer to as `improved loss' in the paper considers the distances from the \textit{positive} element of the triplet to the \textit{negative} element as well, and tries to maximize that difference as well as the distance from \textit{anchor} to the \textit{negative}.
-In addition,it corrects the fact the  original triplet loss function has no constraints on how close the positive distance should be.
+ An improvement over the triplet loss function is proposed by
+ \cite{DBLP:conf/cvpr/SchroffKP15} for the recognition of faces in
+ videos \cite{Zhang:2016:DML:3088616.3088665}.  Conceptually, this
+ function that we refer to as `improved loss' in the paper considers
+ the distances from the \textit{positive} element of the triplet to
+ the \textit{negative} element, and tries to push that
+ difference toward $\alpha$ as well as the distance from
+ \textit{anchor} to the \textit{negative}.  We show this in
+ Figure~\ref{modified_loss} with two push arrows.
+In addition, it corrects the fact the  original triplet loss function has no constraints on how close the positive distance should be.
 For instance, it is possible for the \textit{anchor} and \textit{positive} form a large cluster with a large intra-class distance.
@@
 
-Wang et al.
-\cite{DBLP:journals/corr/abs-1708-01682} define a novel angular loss function which is not based on pairwise distances, but rather is based on the angles of the triangle formed by the \textit{anchor}, \textit{positive} and the \textit{negative} triplet.
-Conceptually, they point out that since the \textit{anchor} and the \textit{positive} pairs belong to the same class, the angle formed by the \textit{anchor}, \textit{negative}, and \textit{positive} elements should be as small as possible within that triangle.
-Their loss function is an attempt to minimize this angle, as defined in the equation below.
+Wang et al. \cite{DBLP:journals/corr/abs-1708-01682} define a novel
+angular loss function which is not based on pairwise distances, but
+rather is based on the angles of the triangle formed by the
+\textit{anchor}, \textit{positive} and the \textit{negative} triplet.
+Conceptually, they point out that since the \textit{anchor} and the
+\textit{positive} pairs belong to the same class, the angle formed by
+the \textit{anchor}, \textit{negative}, and \textit{positive} elements
+should be as small as possible within that triangle.  Their loss
+function is an attempt to minimize this angle, as defined in the
+equations below.  The rough idea is that moving the positive nearer
+and the negative further away each reduce the angle, which we
+illustrate in Figure~\ref{angular_loss} with the angle to shrink.
 \begin{equation}
@@
 
-The inspiration for our loss is that triplet loss, in effect, only pushes the negative distance as far as $\alpha$; if the negative distance is larger than that, the total loss can become negative, which is then forced to 0.
-However, the further the negative point is from the anchor, the better, so we want to push it as far away as possible, without a limit like $\alpha$.
-To achieve this, we use hyperbolic tangent to compress all distances to the range 0 to 1, and substract the negative distance from 1.
-Then our loss function simply needs to minimize both positive and negative numbers:
+The inspiration for our loss is that triplet loss, in effect, only
+pushes the negative distance as far as $\alpha$; if the negative
+distance is larger than that, the total loss can become negative,
+which is then forced to 0.  However, the further the negative point is
+from the anchor, the better, so we want to push it as far away as
+possible, without a limit like $\alpha$.  This is illustrated in
+Figure~\ref{tanh_loss} by pushing toward $\infty$.  To achieve this,
+we use hyperbolic tangent to compress all distances to the range 0 to
+1, and substract the negative distance from 1.  Then our loss function
+simply needs to minimize both positive and negative numbers:
 
@@
 \end{equation}
+
+\input{triplet_selection}

### 2018-07-31 paper2018/triplet_selection.tex
added figures for triplet selection

@@
 \subsubsection{Batch Based Triple Selection}
-In Schroff et al.'s work~\cite{DBLP:conf/cvpr/SchroffKP15} they discuss various online and offline approaches for the problem of triplet selection.
-Conceptually, sampling the `right' triples for fast network learning, as Schroff et al.
-point out requires sampling a set of \textit{hard positives} and a set of \textit{hard negatives}, where a hard positive is defined as $argmax^i \| x_{a} - x_{p}^i \|^2$, where $i$ ranges over all $x_p$ and a hard negative is defined as $argmin^i \| x_{a} - x{_n}^i \|^2$.
+\begin{figure}
+\includegraphics[width=1.0\linewidth]{triplet_selection}
+\caption{Batch based triplet selection}
+\label{triplet_selection}
+\end{figure}
 
-However, it is infeasible to compute these values for the entire dataset for selection.
-As a result, the triplets can be generated either offline, for every n steps, or online, by selecting the hard positive and negative exemplars within a batch of examples.
+In Schroff et al.'s work~\cite{DBLP:conf/cvpr/SchroffKP15} they discuss a sample or mini-batch based triplet selection mechanism for training.
+Conceptually, sampling the `right' triplets for fast network learning, as Schroff et al.
+point out requires sampling a set of \textit{hard positives} and a set of \textit{hard negatives}, where a hard positive is defined as $argmax^i \| x_{a} - x_{p}^i \|^2$, where $i$ ranges over all $x_p$ and a hard negative is defined as $argmin^i \| x_{a} - x{_n}^i \|^2$, where $i$ ranges over all $x_n$.
+
+However, it is infeasible to compute these values for the entire dataset.
+Calculating hard positives is easy because the number of \textit{positives} is small normally.
+Calculating hard negatives is not possible for all but small datasets.
+As a result, the triplets can be generated either offline, for every n steps, or online, by selecting positive and negative exemplars within a batch of examples.
 In Schroff et al.'s work, they focus on the online generation case.
 
-In practice, instead of focusing on finding \textit{hard positives}, they instead pair every possible positive in the sample with selected negatives, since the set of positives is usually quite small.
+Figure~\ref{triplet_selection} shows the triplet selection mechanism used in their work.
+In practice, instead of focusing on finding \textit{hard positives}, they instead pair every possible positive in the sample shown in the right panel in the figure with selected negatives, since the set of positives is usually quite small.
 Furthermore, for negative examples, they try to select what they term \textit{semi-hard negatives} instead of \textit{hard negatives}, where a \textit{semi-hard negative} has the property that $\|x_a - x_p \|^2 < \|x_a - x_n \|^2$.
-That is, \textit{semi-hard negative} is further from the \textit{anchor} than the \textit{positive}, but is not distant by the margin $\alpha$ that is used in the triplet-loss function.
+As shown in the figure~\ref{triplet_selection} a \textit{semi-hard negative} is further from the \textit{anchor} than the \textit{positive}, but is not distant enough.
+That is, the loss function still needs to move it closer to the margin $\alpha$ that is used in the triplet-loss function.
 Schroff et al.
-argue selecting \textit{hard negatives} may in practice lead to bad local minima early on in training, and lead to a collapsed model where the function always learns to return a value of 0, regardless of the pair being considered.
+further argue selecting \textit{hard negatives} such as $C$ in the figure may in fact lead to bad local minima early on in training, and lead to a collapsed model where the function always learns to return a value of 0, regardless of the pair being considered.
 
@@
 
-Approximate nearest neighbor indexes are highly efficient methods for selecting the top-K neighbors of a given vector by Euclidean distance or cosine similarity.
+Approximate nearest neighbor indexes are highly efficient methods for selecting the top-K neighbors of a given vector by Euclidean distance, cosine similarity or other distance metrics.
 They are based on space partitioning algorithms, such as \textit{k-d trees}, where the vector space is iteratively bisected into two disjoint regions.
 Finding the nearest neighbors of a vector involves traversal of the tree to a leaf by evaluating the queried vector at each split point in the tree.
-Depending on the position of the vector within the space bounded by a split point, it may need to traverse both points the split.
-However, large portions of the tree (and hence most vectors in the dataset) never get compared to each other.
-The average complexity to query the vectors of a neighbor is in fact $O(log N)$ where N is the number of vectors in the dataset.
+Depending on the position of the vector within the space bounded by a split point, it may need to traverse both points at a split node.
+However, large portions of the tree (and hence most vectors in the dataset) never get compared to the queried vector.
+The average complexity to query the vectors of a neighbor is $O(log N)$ where N is the number of vectors in the dataset.
 Implementations exist now for fast, memory-efficient ANN indexes that scale up to a billion vectors \cite{JDH17} using techniques to compress vectors in memory efficiently.
@@
 
+\begin{figure}
+\includegraphics[width=1.0\linewidth]{ANN_selection}
+\caption{ANN based triplet selection}
+\label{ANN_selection}
+\end{figure}
+
 Assuming one has the entire dataset indexed in an ANN index, the problem of triplet selection can be simplified by asking the ANN index for the top k-nearest neighbors of an \textit{anchor}, where k is given by the number of triplets that one desires to generate for each anchor.
-Selection of \textit{hard positives} is not really relevant because all positive data should be used to teach the network the right function, as Schroff et al.
-point out.
-\textit{Hard negatives} are simply the negatives that appear in the top-K.
+As in earlier work, selection of \textit{hard positives} is not really relevant because all positive data should be used to teach the network the right function.
+Selection of negatives is the set of all nearest neighbors that are \textit{negatives}.
+There is no explicit attempt to filter out\textit{hard negatives} in the approach.
+The overall idea is that teh set of negatives that appear in the nearest neighbor set at input are in fact the most important elements for the network to learn to discriminate from positives.
+Focusing on these elements, regardless of whether they are \textit{hard} or \textit{semi-hard} should lead to better learning.
 
-The selection of \textit{semi-hard negatives} is a bit more difficult and depends on the characteristics of the dataset.
-In some cases, there may be very few \textit{semi-hard negatives} because the positives are more distant than the negatives.
-This was a rather serious problem in our people's name matching dataset.
+An ANN-based strategy works better than the batch based triplet selection approach on two counts.
+First, the entire dataset is in fact used in the triplet selection process.
+Second, for certain types of datasets, the batch based triplet selection mechanism will actually fail if it is focused on finding \textit{semi-hard negatives}.
+In particular, anytime \textit{positive distances} are on average much greater than \textit{negative} distances, there are very few \textit{semi-hard negatives} because most positives are in fact more distant than the negatives.
+We observed this property in the people's name matching dataset.
 If we take the character embeddings of each of the names in our name matching dataset, index it in an ANN, and then ask for the top-k neighbors we find somewhat troubling properties for an approach that tries to select \textit{semi-hard} negatives.
@@
 Given that only 3.2\% of positives actually even appeared in the top-K nearest neighbors, selection of \textit{semi-hard} negatives is reduced to a very small fraction of the dataset.
-We therefore used a k-nearest neighbor approach to triplet selection instead, picking all positive triplets, and a set of \textit{hard negative} triplets based on the top-k nearest neighbors.
-As we show later this approach generalizes to datasets such as company names where it is less extreme in terms of reversal of \textit{positive} and \textit{negative} distances.
+A k-nearest neighbor approach to triplet selection on the other hand works on this difficult dataset as well, by picking all positive triplets, and a set of \textit{negatives} based on the top-k nearest neighbors.
+As we show later this approach generalizes to datasets such as company names where such a strong reversal of \textit{positive} and \textit{negative} distances does not exist.

### 2018-08-16 paper2018/introduction.tex
adding another section

@@
 
-Merging two datasets using joins is a key operation in data management.
-Data management systems have largely focussed solely on equi-joins, where equality of strings or numeric values of the two columns determines if rows should be joined.
-However, equality at a string level is inadequate because the same entity may in many cases be expressed with slight variations of the same name, as shown in Table~\ref{table-example} (e.g., \textit{Douglas Adams} and \textit{Douglas Noel Adams}).
-This problem occurs for many entity types such as company names, addresses, product descriptions, and conference venues.
+Merging datasets is a key operation for data analytics.
+A frequent requirement for merging datasets is a join between two columns that frequently have different surface representations for the same entity (e.g., the name of a person might be represented as \textit{Douglas Adams} or \textit{Douglas Noel Adams}, as shown in Table~\ref{table-example}.
+This problem occurs for many entity types such as people's names, company names, addresses, product descriptions, conference venues, or even people's faces.
+Data management systems have however, largely focussed solely on equi-joins, where string or numeric equality determines which rows should be joined, because such joins are efficient.
 
-A common technique to overcome this problem is to perform fuzzy joins using string similarity algorithms such as edit-distance, Jaro-Winkler and TF-IDF (e.g., \cite{Cohen2003}).
+Extensions in data management systems for handling `fuzzy' joins across different surface forms for the same entity typically use string similarity algorithms such as edit-distance, Jaro-Winkler and TF-IDF (e.g., \cite{Cohen2003}).
 In applying fuzzy joins, a key problem is to avoid quadratic comparisons between pairs of strings drawn from the two columns.
 A blocking strategy is used to reduce the number of pairs for fuzzy joins, such that only strings that share a common prefix, or suffix will be compared further.
-String matching algorithms often do not work because transformations of entity names in perfectly valid ways can yield very different strings (e.g., switching the last name and first name of a person, or providing acronyms for a company name).
+String matching algorithms often do not work however, because transformations of entity names in perfectly valid ways can yield very different strings.
+As shown in Table~\ref{table-example}, \textit{John Smith} is more similar by string similarity to \textit{John Adams} than \textit{Adams, John}, but of course \textit{Adams, John} is the valid alternate surface form for \textit{John Adams}.
 
@@
 
-In this paper, we propose a novel data driven approach to the problem of joining different representations of the same entity.
+In this paper, we propose a novel data driven approach to the problem of joining different surface representations of the same entity.
 Our approach relies on building supervised deep learning models to automatically learn the correct set of transformations needed to compute the equality of two cell values.
-For the closely related problem of face recognition and person re-identification, deep learning networks have been used successfully to discriminate pairs that represent the same entity from those that don't.
-However, we know of no work that has adapted these techniques to the problem of fuzzy joins for entity names.
-
 Because a deep learning model can learn the features necessary for matching from the data, it should in theory be able to generalize better to new datasets than the data driven approaches outlined in \cite{He:2015:SJS:2824032.2824036}.
 Conceptually, our approach is similar in spirit to the approach described in \cite{auto-join-joining-tables-leveraging-transformations}, but we use deep neural networks to learn the right function for the join operation instead of synthesizing different programs for different entity types.
-The advantage of building such a function over the approach described in \cite{auto-join-joining-tables-leveraging-transformations} is that we can use this function in novel ways to completely eliminate the blocking step that is typically needed to identify the set of potentially joinable rows, as we describe below.
+The advantage of building such a function compared to work described in \cite{auto-join-joining-tables-leveraging-transformations} is that (a) we can use this function in novel ways to completely eliminate the blocking step that is typically needed to identify the set of potentially joinable rows, as we describe below, and (b) we can use this function on arbitrary surface forms such as faces, where valid transformations of a face cannot be readily described in terms of a program.
 
-Our solution to the join problem involves building a system that performs deep metric learning.
-That is, the specific function the network learns is to map input vectors corresponding to same entity closer in vector space compared to vectors that correspond to different entities.
-As in face recognition, we do this by training a `triplet siamese network'.
-However, entity names have very different properties from faces, so we needed to adapt the approaches used in face recognition to the entity matching problem with a novel method to choose the sample for training, and novel loss functions as objectives for the metric learning problem.
+Specifically, our solution to the join problem involves building a system that performs deep metric learning.
+That is, the network learns is to map input vectors corresponding to same entity closer in vector space compared to vectors that correspond to different entities.
+For the closely related problem of face recognition and person re-identification, deep learning networks have been used successfully to discriminate pairs that represent the same entity from pairs that do not.
+However, simply building a model that discriminates pairs of entities is not sufficient; if used naively, this would mean a quadratic comparison between cell values in the two columns to be joined.
+We know of no work that has adapted these techniques to the problem of how to use such deep learning models to perform joins efficiently for different surface forms of the same entity.
 
+As in face recognition, our system for metric learning is built by training a `triplet siamese network' to learn to map different surface forms of the same entity closer in vector space than different forms of the same entity.
+Entity names have very different properties from faces, so we needed to adapt the approaches used in face recognition to the problem of matching entity names with a novel method to choose the sample for training, and novel loss functions as objectives for the metric learning problem.
 At training, the network is given a triplet consisting of an `anchor' (e.g.
@@
 Then, for each cell value in the first column to be joined, querying the k-nearest neighbors should provide the set of values in the second column that can be joined.
-Because approximate nearest neighbor algorithms have been applied successfully to billions of items \cite{JDH17}, this approach should scale just as well as join algorithms based on blocking, but has the added advantage that the blocking step is also data driven, and hence can adapt to different entity types very effectively.
+Because approximate nearest neighbor algorithms have been applied successfully to billions of items \cite{JDH17}, this approach should scale just as well as join algorithms based on blocking, but it has the added advantage that the blocking step is also data driven, and hence can adapt to different entity types very effectively.
 
 \begin{table}[!htb]
-    \caption{Example of a join problem}
+    \caption{Example of a merge problem}
     \begin{subtable}{.5\linewidth}
@@
 We compare the results for this loss function with the ones that have been used for face recognition, and show that this loss function can perform much better than the existing functions for deep learning in this domain.
+\item We demonstrate how such models can then be used to perform joins across different surface forms of the same entity efficiently, with a complexity of $\mathcal{O}(n\log{}n)$.  
 \end{itemize}
 
-The rest of the paper is organized as follows: Section~\ref{siamese networks} describes how we adapted siamese networks to the problem of entity matching, specifically the problem of triplet selection for entity names, and the need for a new type of loss function to improve metric learning for this problem, section ~\ref{dataset} describes characteristics of the datasets we used for training, as well as cleansing and data augmentation techniques we used to generate data, section ~\ref{results} provides the experimental results, section~\ref{related work} covers related work, and section~\ref{conclusions} describes future work and conclusions.
+The rest of the paper is organized as follows: Section~\ref{siamese networks} describes how we adapted siamese networks to the problem of entity matching, specifically the problem of triplet selection for entity names, and the need for a new type of loss function to improve metric learning for this problem, section ~\ref{joins} describes how to use these models for efficient joins across datasets, section ~\ref{dataset} describes characteristics of the datasets we used for training, as well as cleansing and data augmentation techniques we used to generate data, section ~\ref{results} provides the experimental results, section~\ref{related work} covers related work, and section~\ref{conclusions} describes future work and conclusions.

### 2018-08-16 paper2018/joins.tex
adding another section

\section{Merging datasets with siamese networks}
\label{joins}

Section~\ref{join_system} describes our overall system for using siamese networks for joins.  Section~\ref{join_complexity} provides a complexity analysis for this approach.

\section{Applying deep learning models to joins}
\label{join_system}
\begin{figure}
\includegraphics[width=1.0\linewidth]{joins}
\caption{Applying deep learning models to joins}
\label{join_fig}
\end{figure}

Figure~\ref{join_fig} provides an overview of how deep learning models can be used for merging datasets.  Panel (a) in the figure are the two datasets to be joined.  The datasets are labeled arbitrarily as a left table and a right table.  For each cell value in the two columns to be joined, we obtain vector embeddings from the siamese network that was used to estimate distance for same and different surface forms for the same entity.  Note that although the siamese network has three separate networks, each network within a triplet network is in fact identical to the other two networks because they share weights.  A single version of the network with learnt weights is used to generate the embeddings for the cell value as shown in panel (b). For the left table cell values, vector embeddings are inserted into an approximate nearest neighbors index, as shown in panel (c).  For each cell value in the right table, vector embeddings are used as `query vectors' to query the approximate nearest neighbors index as shown in panel (d).  In our context, merging the datasets would involve joining the top $k$ rows in the left table that are `closest' in distance to each cell value in the right table.  Note that the choice of $k$ clearly has a direct effect on the tradeoff between precision and recall, but this is true for any type of join algorithm that is not based on equality.

### 2018-08-16 paper2018/main.tex
changed notation for schroff loss
adding another section

@@
-\def\year{2018}\relax
+\def\year{2019}\relax
 %File: formatting-instruction.tex
 \documentclass[letterpaper]{article} %DO NOT CHANGE THIS
-\usepackage{aaai18}  %Required
+\usepackage{aaai19}  %Required
 \usepackage{times}  %Required
@@
   \pdfinfo{
-/Title (Fuzzy joins through deep learning)
+/Title (Merging datasets through deep learning)
 /Author (Kavitha Srinivas, Yehuda Gale, Julian Dolby)}
 \setcounter{secnumdepth}{0}  
+\usepackage{bm}
+
  \begin{document}
@@
 %
-\title{Fuzzy joins through deep learning}
+\title{Merging datasets through deep learning}
 
@@
 \begin{abstract}
-AAAI creates proceedings, working notes, and technical reports directly from electronic source furnished by the authors.
-To ensure that all papers in the publication have a uniform appearance, authors must adhere to the following instructions.
+Merging datasets is a key operation for data analytics.
+A frequent requirement for merging datasets is a join between two columns that frequently have different surface forms for the same entity (e.g., the name of a person might be represented as \textit{Douglas Adams} or \textit{Douglas Noel Adams}).
+Data management systems are currently limited to performing merges based on string equality, or at best use string similarity to allow so-called `fuzzy' joins.
+We explore a novel approach to performing merges based on recent advances in deep learning.
+Our approach builds a deep learning model that maps names into a set of vector embeddings such that names for the same entity are closer in vector space than names for a different entity.
+We then index these vector embeddings in an approximate nearest neighbors algorithm to find the names that can be potentially joined together.
+Our approach for merging datasets is efficient $\mathcal{O}(n\log{}n)$ and flexible because it can be applied to any data that can be mapped into vector space with the constraint that joinable surface forms are closer in vector space than disparate forms.
+We demonstrate the feasibility of the approach for people's names and company names drawn from Wikidata.
 \end{abstract}
@@
 \input{siamese_networks}
+\input{joins}
 

### 2018-08-17 TripletLossFacenetLSTM-hpo.py
fix tanh so-called improved loss

@@ -197,9 +197,9 @@ def triplet_tanh_loss(y_true, y_pred):
 
 
 def triplet_tanh_pn_loss(y_true, y_pred):
-    return K.mean((K.tanh(y_pred[:,0,0]) +
-                   K.tanh(y_pred[:,2,0]))/2 +
-                  (K.constant(1) - K.tanh(y_pred[:,1,0])))
+    return K.mean(K.tanh(y_pred[:,0,0]) +
+                  ((K.constant(1) - K.tanh(y_pred[:,1,0])) +
+                   (K.constant(1) - K.tanh(y_pred[:,2,0]))) / K.constant(2));
 
 
 # the following triplet loss function is from: Deep Metric Learning with Improved Triplet Loss for 

### 2018-08-17 paper2018/datasets.tex

\section{Datasets}
\label{datasets}
Our datasets were derived from Wikidata.  Specifically, we used the \textit{also known as} property from Wikidata to get alternate forms for the same entity name for people as well as companies.  For company names, we augmented the names and surface forms in Wikidata with data from the SEC \footnote{\url{https://www.sec.gov/dera/data/financial-statement-and-notes-data-set.html}}, which has former and more recent names for companies.  There were 213106 names for people from the specific dump we extracted, and 70946 names for companies.  The extracted files and the cleansing code are available on our repository \footnote{\url{https://github.com/yehudagale/fuzzyJoiner}}. The extracted files however contained noise that we cleaned up programmatically.  We describe the clean up rules for people and for companies separately because they were somewhat different.  In the case of people's names, we also augmented the data so the system could learn some common rules that define variants of a person's name.  This was not possible for company names.

\subsection{Cleansing people's names}
Wikidata has a number of historical figures which are not really names of people (e.g. Queen Elizabeth, Pope Leo).  If we detected a title in the name referring to royalty or qualifiers or Roman numerals which strongly indicated royalty, we dropped the name.  We also removed punctuations such as '...', and anything that was placed in parenthesese because they were irrelevant to the name (e.g. a qualification such as the son of Jacob might appear in parentheses after a name).  Although we got the extract for English, there were frequently names in Chinese, Korean, Cyrillic, etc.  We removed these and restricted ourselves to names in ISO-8859-1 unicode.  All punctuations such as ',', '-', '.' etc were retained for names because they are strong indicators of how a name needs to be parsed.  People in wikidata have the main name for the entity, with aliases for the person specified in a different property.  We made sure that every alternate form had at least one name part in common with the main name to rule out 'nicknames' (e.g. `Father of the Nation' for George Washington).  We also dropped cases where the last name of a person was different (usually because a woman's name changed after marriage).

\subsection{Cleansing company names}
As with people's names, we removed any text in parentheses because it usually was a qualification (e.g., IBM (company)).  We restricted ourselves to unicode ISO-8859-1.  The SEC data had a lot of strange company names that could be described with the regex pattern T[0-9]+ or [0-9]+, and we dropped these.  We tried to ensure we included names that shared some subset of characters with the main name, ensuring we would not drop acronyms when possible.

\subsection{Augmenting people's names}
In many cases, we had no alternate forms for a person's name even if we did have their main name.  We augmented the data with the following rules.  If the main name for the person in Wikidata had two parts, we created new source forms as follows: 
\begin{itemize}
\item Last Name, First Name
\item First Name Initial . Last Name
\item Last Name , First Name Initial
\end{itemize}
If the main name in Wikidata had three parts, we created these additional source forms in addition to the ones listed above:
\begin{itemize}
\item First Name Middle Name Initial Last Name
\item Last Name, First Name Middle Name
\item Last Name, First Name Middle Initial .
\end{itemize}

### 2018-08-17 TripletLossFacenetLSTM-hpo.py
remove seeds for runs

@@ -6,30 +6,6 @@ import json
 
 from keras import backend as K
 
-########################## FIX SEEDS ################################################
-import os
-os.environ['PYTHONHASHSEED'] = '0'
-# The below is necessary for starting Numpy generated random numbers
-# in a well-defined initial state.
-np.random.seed(42)
-# The below is necessary for starting core Python generated random numbers
-# in a well-defined state.
-random.seed(12345)
-# Force TensorFlow to use single thread.
-# Multiple threads are a potential source of
-# non-reproducible results.
-# For further details, see: https://stackoverflow.com/questions/42022950/which-seeds-have-to-be-set-where-to-realize-100-reproducibility-of-training-res
-session_conf = tf.ConfigProto(intra_op_parallelism_threads=1, inter_op_parallelism_threads=1)
-#
-# The below tf.set_random_seed() will make random number generation
-# in the TensorFlow backend have a well-defined initial state.
-# For further details, see: https://www.tensorflow.org/api_docs/python/tf/set_random_seed
-tf.set_random_seed(1234)
-sess = tf.Session(graph=tf.get_default_graph(), config=session_conf)
-K.set_session(sess)
-
-#########################################################################
-
 from keras.preprocessing.text import Tokenizer
 from keras.preprocessing.sequence import pad_sequences
 
@@ -59,7 +35,7 @@ MAX_NB_WORDS = 140000
 EMBEDDING_DIM = 100
 MAX_SEQUENCE_LENGTH = 10
 MARGIN=10
-ALPHA=30
+ALPHA=45
 
 DEBUG = False
 DEBUG_DATA_LENGTH = 100
@@ -185,16 +161,11 @@ def schroff_triplet_loss(y_true, y_pred):
     return K.mean(K.maximum(K.constant(0), K.square(y_pred[:,0,0]) - K.square(y_pred[:,1,0]) + margin))
 
 def triplet_loss(y_true, y_pred):
-
-    # margin = K.constant(MARGIN)
-    # return K.mean(K.square(y_pred[:,0,0]) + K.square(margin - y_pred[:,1,0]))
     margin = K.constant(MARGIN)
     return K.mean(K.square(y_pred[:,0,0]) + K.square(margin - y_pred[:,1,0]))
 
-
 def triplet_tanh_loss(y_true, y_pred):
[…]

### 2018-08-17 paper2018/introduction2.tex
intro reworked

--- 2018-08-16 paper2018/introduction.tex
@@
 Merging datasets is a key operation for data analytics.
-A frequent requirement for merging datasets is a join between two columns that frequently have different surface representations for the same entity (e.g., the name of a person might be represented as \textit{Douglas Adams} or \textit{Douglas Noel Adams}, as shown in Table~\ref{table-example}.
+A frequent requirement for merging is a join between two columns that frequently have different surface representations for the same entity (e.g., the name of a person might be represented as \textit{Douglas Adams} or \textit{Douglas Noel Adams}, as shown in Table~\ref{table-example}.
 This problem occurs for many entity types such as people's names, company names, addresses, product descriptions, conference venues, or even people's faces.
@@
 String matching algorithms often do not work however, because transformations of entity names in perfectly valid ways can yield very different strings.
-As shown in Table~\ref{table-example}, \textit{John Smith} is more similar by string similarity to \textit{John Adams} than \textit{Adams, John}, but of course \textit{Adams, John} is the valid alternate surface form for \textit{John Adams}.
+As shown in Table~\ref{table-example}, \textit{John Smith} is more similar to \textit{John Adams} than \textit{Adams, John}, but of course it is \textit{Adams, John} that is the valid alternate surface form for \textit{John Adams}.
 
@@
 
-In this paper, we propose a novel data driven approach to the problem of joining different surface representations of the same entity.
-Our approach relies on building supervised deep learning models to automatically learn the correct set of transformations needed to compute the equality of two cell values.
-Because a deep learning model can learn the features necessary for matching from the data, it should in theory be able to generalize better to new datasets than the data driven approaches outlined in \cite{He:2015:SJS:2824032.2824036}.
-Conceptually, our approach is similar in spirit to the approach described in \cite{auto-join-joining-tables-leveraging-transformations}, but we use deep neural networks to learn the right function for the join operation instead of synthesizing different programs for different entity types.
-The advantage of building such a function compared to work described in \cite{auto-join-joining-tables-leveraging-transformations} is that (a) we can use this function in novel ways to completely eliminate the blocking step that is typically needed to identify the set of potentially joinable rows, as we describe below, and (b) we can use this function on arbitrary surface forms such as faces, where valid transformations of a face cannot be readily described in terms of a program.
+In this paper, we propose a novel approach to the problem of joining different surface representations of the same entity, inspired in part by recent advances in deep learning.
+Our approach depends on (a) creating a function that maps surface forms into a set of vectors such that alternate forms for the same entity are closest in vector space, (b) indexing these vectors using a space partitioning algorithm to find the forms that can be potentially joined together.
+Our approach for merging datasets is much more flexible than prior data driven approaches (e.g., \cite{He:2015:SJS:2824032.2824036}, \cite{auto-join-joining-tables-leveraging-transformations}) because it can be applied to any data provided one can create a mapping function such that joinable surface forms of the entity are closer in vector space than disparate forms.
+For instance, in face recognition and person re-identification, there has been a significant research effort aimed at creating deep learning models that learn to map different surface forms of a face closer together in a vector space.
+In our proposed approach, we can now join two columns if they have alternate faces for the same entity, whereas in prior work, those faces needed to either have been joined before in some existing dataset, or the transforms of a face need to be discoverable as a program, which is near impossible for faces.
+Our approach for merging datasets is also efficient because it eliminates quadratic comparisons of cell values in each column by using a mechanism that is itself data-driven.
+Because we use space partitioning algorithms to find surface forms that are potentially joinable, the search process is efficiently eliminates large parts of the vector space from consideration for any given queried vector.
+Across all cell values that are considered for a join, the efficiency of the search is $\mathcal{O}(n\log{}n)$.
 
-Specifically, our solution to the join problem involves building a system that performs deep metric learning.
-That is, the network learns is to map input vectors corresponding to same entity closer in vector space compared to vectors that correspond to different entities.
-For the closely related problem of face recognition and person re-identification, deep learning networks have been used successfully to discriminate pairs that represent the same entity from pairs that do not.
-However, simply building a model that discriminates pairs of entities is not sufficient; if used naively, this would mean a quadratic comparison between cell values in the two columns to be joined.
-We know of no work that has adapted these techniques to the problem of how to use such deep learning models to perform joins efficiently for different surface forms of the same entity.
-
+Specifically, the first part of our solution to the join problem involves building a deep learning model that performs metric learning.
+For the closely related problem of face recognition and person re-identification, deep neural networks have been used successfully to build models that map faces of the same entity closer in vector space estimate relative to faces from other entities.
+To test the generality of our approach, we tried to build a deep learning model model for names of people and companies.
 As in face recognition, our system for metric learning is built by training a `triplet siamese network' to learn to map different surface forms of the same entity closer in vector space than different forms of the same entity.
@@
 Specifically, the last hidden layer of the siamese network is effectively a `vector embedding' that contains the critical features needed for computing the distance estimate.
-If such models are pre-built for a given entity type, we can then use the models to produce vector embeddings for all cell values in the two columns to be joined in a single linear pass, and index just the second column values in an approximate nearest neighbors index.
+If such models are pre-built for a given entity type, we can then use the models to produce vector embeddings for all cell values in the two columns to be joined in a single linear pass, and index just the second column values with a space partitioning algorithm that lays out vectors in n-dimensional space.
 Then, for each cell value in the first column to be joined, querying the k-nearest neighbors should provide the set of values in the second column that can be joined.
-Because approximate nearest neighbor algorithms have been applied successfully to billions of items \cite{JDH17}, this approach should scale just as well as join algorithms based on blocking, but it has the added advantage that the blocking step is also data driven, and hence can adapt to different entity types very effectively.
+In our work, we used approximate nearest neighbor algorithms, which have been applied successfully to billions of items \cite{JDH17}.
 
@@
            \hline
-           Douglas N. Adams & 2000 \\
+           Douglas Noel Adams & 2000 \\
            Adams, John & 3000 \\
@@
 \begin{itemize}
-\item We demonstrate that triplet loss based siamese networks can be used to learn a distance function that successfully discriminates same entity pairs from different pairs with an accuracy of 98\% and 97\% for about 200,000 people's names and 70,000 company names respectively, drawn from Wikidata.
-More importantly, we show that such a network has a high recall of 83\% and 79\%, finding the variants of an entity name in the top 20 neighbors for people and companies respectively.
+\item We outline a general approach to the problem of merging datasets for different surface forms of the same entity.
+Our approach consists of building a deep neural network model for specific entity types and using a space partitioning algorithm to find the nearest neighbors to join.
+To test the generality of our approach, we built triplet loss based siamese networks for ~200,000 people's names and ~70,000 company names respectively, drawn from Wikidata.
+We show that such networks did learn to map surface forms of the same entity closer in vector space.
+Specifically, if we 83\% and 79\% of variants of the entity name appeared in the top 20 neighbors for each entity.
 Moreover, within the 20 neighbors, 77\% and 75\% of the positive names were closer to the anchor than negative names for people and companies respectively.
@@
 We developed a new technique for triplet selection for entity names because the techniques from face recognition do not generalize well to entity names.
-\item We also developed a novel loss function to train the network to discriminate entity names from names of other entities.
+We also developed a novel loss function to train the network to discriminate entity names from names of other entities.
 We compare the results for this loss function with the ones that have been used for face recognition, and show that this loss function can perform much better than the existing functions for deep learning in this domain.
-\item We demonstrate how such models can then be used to perform joins across different surface forms of the same entity efficiently, with a complexity of $\mathcal{O}(n\log{}n)$.  
+\item We also perform a complexity analysis of how such models can then be used to perform joins across different surface forms of the same entity efficiently, with a complexity of $\mathcal{O}(n\log{}n)$.
 \end{itemize}

### 2018-08-19 TripletLossFacenetLSTM-hpo.py
actually use loss function

@@ -375,7 +375,7 @@ def build_model(embedder):
                     )([positive_dist, negative_dist, exemplar_negative_dist])
 
         model = Model([input_anchor, input_positive, input_negative], stacked_dists, name='triple_siamese')
-        model.compile(optimizer="rmsprop", loss=triplet_loss, metrics=[accuracy])
+        model.compile(optimizer="rmsprop", loss=LOSS_FUNCTION, metrics=[accuracy])
     test_positive_model = Model([input_anchor, input_positive, input_negative], positive_dist)
     test_negative_model = Model([input_anchor, input_positive, input_negative], negative_dist)
     inter_model = Model(input_anchor, net_anchor)

### 2018-08-19 TripletLossFacenetLSTM-hpo.py
kill hpo margin

@@ -428,15 +428,6 @@ if args.debug_sample_size:
     DEBUG_DATA_LENGTH=args.debug_sample_size
     print('Debug data length:' + str(DEBUG_DATA_LENGTH))
 
-try:
-    with open("config.json", "r") as f:
-        print(f)
-        json_obj = json.load(f)
-        print(json_obj)
-        MARGIN = json_obj["margin"]
-except:
-    MARGIN = args.margin
-    
 print('Margin:' + str(MARGIN))
 
 USE_L2_NORM = args.use_l2_norm.lower() in ("yes", "true", "t", "1")

### 2018-08-20 paper2018/introduction.tex

@@
 
-In this paper, we propose a novel data driven approach to the problem of joining different surface representations of the same entity.
+In this paper, we propose a novel approach to the problem of joining different surface representations of the same entity, inspired in part by recent advances in deep learning.
 Our approach relies on building supervised deep learning models to automatically learn the correct set of transformations needed to compute the equality of two cell values.

### 2018-08-20 paper2018/joins.tex

@@
 \label{join_system}
-\begin{figure}
-\includegraphics[width=1.0\linewidth]{joins}
-\caption{Applying deep learning models to joins}
+
+\begin{figure*}[htb]
+    \centering
+    \begin{subfigure}[t]{0.24\linewidth}
+        \centering
+        \includegraphics[width=.9\linewidth]{join1}
+        \caption{Columns to be merged}
+        \label{join1}
+    \end{subfigure}%
+    ~ 
+    \begin{subfigure}[t]{0.24\linewidth}
+        \centering 
+        \includegraphics[width=.9\linewidth]{join2}
+        \caption{Create embeddings for each cell value in each column using the siamese model}
+        \label{join2}
+    \end{subfigure}
+    ~ 
+    \begin{subfigure}[t]{0.24\linewidth}
+        \centering 
+        \includegraphics[width=.9\linewidth]{join3}
+        \caption{Index embeddings for left table's cell values in a nearest neighbors index}
+        \label{join3}
+    \end{subfigure}
+    ~ 
+    \begin{subfigure}[t]{0.24\linewidth}
+        \centering 
+        \includegraphics[width=.9\linewidth]{join4}
+        \caption{For each cell in right table, find closest neighbor(s) and merge these rows}
+        \label{join4}
+    \end{subfigure}
+    \caption{Overview of joins using deep learning}
     \label{join_fig}
-\end{figure}
+\end{figure*}
 
 Figure~\ref{join_fig} provides an overview of how deep learning models can be used for merging datasets.
-Panel (a) in the figure are the two datasets to be joined.
+Figure~\ref{join1} in the figure shows the two columns in the two datasets to be joined.
 The datasets are labeled arbitrarily as a left table and a right table.
@@
 Note that although the siamese network has three separate networks, each network within a triplet network is in fact identical to the other two networks because they share weights.
-A single version of the network with learnt weights is used to generate the embeddings for the cell value as shown in panel (b).
-For the left table cell values, vector embeddings are inserted into an approximate nearest neighbors index, as shown in panel (c).
-For each cell value in the right table, vector embeddings are used as `query vectors' to query the approximate nearest neighbors index as shown in panel (d).
+A single version of the network with learnt weights is used to generate the embeddings for the cell value as shown in figure ~\ref{join2}.
+For the left table cell values, vector embeddings are inserted into an approximate nearest neighbors index, as shown in figure ~\ref{join3}.
+For each cell value in the right table, vector embeddings are used as `query vectors' to query the approximate nearest neighbors index as shown in figure ~\ref{join4}.
 In our context, merging the datasets would involve joining the top $k$ rows in the left table that are `closest' in distance to each cell value in the right table.

### 2018-08-20 paper2018/main.tex

--- 2018-07-21 paper2018/main.tex
@@
 \begin{abstract}
-AAAI creates proceedings, working notes, and technical reports directly from electronic source furnished by the authors.
-To ensure that all papers in the publication have a uniform appearance, authors must adhere to the following instructions.
+Merging datasets is a key operation for data analytics.
+A frequent requirement for merging is a join between two columns that frequently have different surface forms for the same entity (e.g., the name of a person might be represented as \textit{Douglas Adams} or \textit{Douglas Noel Adams}).
+Data management systems are currently limited to performing merges based on string equality, or at best use string similarity to allow so-called `fuzzy' joins.
+We propose a novel approach to performing merges inspired in part by recent advances in deep learning.
+Our approach depends on (a) creating a function that maps surface forms into a set of vectors such that alternate forms for the same entity are closest in vector space, (b) indexing these vectors using a space partitioning algorithm to find the forms that can be potentially joined together.
+Our approach for merging datasets is efficient $\mathcal{O}(n\log{}n)$ and flexible because it can be applied to any data provided one can create a mapping function such that joinable surface forms of the entity are closer in vector space than disparate forms.
+We demonstrate the generality of this approach by creating such a mapping function using deep learning models for people's names and company names drawn from Wikidata, and show that such a function does in fact produce vector embeddings that can be used together with space partitioning algorithms to perfom efficient joins.
 \end{abstract}
 
-\input{introduction}
+\input{introduction2}
 \input{siamese_networks}
+\input{joins}
+\input{datasets}
 

### 2018-08-20 paper2018/triplet_selection.tex

@@
 Implementations exist now for fast, memory-efficient ANN indexes that scale up to a billion vectors \cite{JDH17} using techniques to compress vectors in memory efficiently.
-In our work, we used the Annoy ANN implementation \cite{annoy_git} in our work which is based on the refinements to \textit{k-d trees} ideas described in \cite{annoy-paper}.
+In our work, we used the Annoy ANN implementation \cite{annoy_git} in our work which is based on the refinements to \textit{k-d trees} ideas described in \cite{ann_paper}.
 

### 2018-08-23 paper2018/introduction2.tex
new version of intro

@@
 
-In this paper, we propose a novel approach to the problem of joining different surface representations of the same entity, inspired in part by recent advances in deep learning.
+In this paper, we propose a different approach to the problem of joining different surface representations of the same entity, inspired in part by recent advances in deep learning.
 Our approach depends on (a) creating a function that maps surface forms into a set of vectors such that alternate forms for the same entity are closest in vector space, (b) indexing these vectors using a space partitioning algorithm to find the forms that can be potentially joined together.
 Our approach for merging datasets is much more flexible than prior data driven approaches (e.g., \cite{He:2015:SJS:2824032.2824036}, \cite{auto-join-joining-tables-leveraging-transformations}) because it can be applied to any data provided one can create a mapping function such that joinable surface forms of the entity are closer in vector space than disparate forms.
-For instance, in face recognition and person re-identification, there has been a significant research effort aimed at creating deep learning models that learn to map different surface forms of a face closer together in a vector space.
+For instance, in face recognition and person re-identification, there has been a significant research effort aimed at creating deep learning models that learn to map different surface forms of a face closer together in a vector space (this technique is often referred to as deep metric learning).
 In our proposed approach, we can now join two columns if they have alternate faces for the same entity, whereas in prior work, those faces needed to either have been joined before in some existing dataset, or the transforms of a face need to be discoverable as a program, which is near impossible for faces.
 Our approach for merging datasets is also efficient because it eliminates quadratic comparisons of cell values in each column by using a mechanism that is itself data-driven.
-Because we use space partitioning algorithms to find surface forms that are potentially joinable, the search process is efficiently eliminates large parts of the vector space from consideration for any given queried vector.
+Because we use space partitioning algorithms (such as approximate nearest neighbor) to find surface forms that are potentially joinable, the search process is efficiently eliminates large parts of the vector space from consideration for any given queried vector.
 Across all cell values that are considered for a join, the efficiency of the search is $\mathcal{O}(n\log{}n)$.
+Implementations exist for nearest neighbor algorithms that have been applied to billions of vectors \cite{JDH17}, so the approach is practical for most datasets.
 
-Specifically, the first part of our solution to the join problem involves building a deep learning model that performs metric learning.
-For the closely related problem of face recognition and person re-identification, deep neural networks have been used successfully to build models that map faces of the same entity closer in vector space estimate relative to faces from other entities.
-To test the generality of our approach, we tried to build a deep learning model model for names of people and companies.
+The idea of building joint embeddings for merging followed by nearest neighbors search has been applied recently to a slightly different problem of linking relational tuple embeddings with embeddings of other relational tuples or unstructured text \cite{Bordawekar18}, \cite{IDEL18}).
+While our approach is conceptually similar to these two pieces of work, our contribution is that we developed general purpose embedding models for merging alternate surface forms of key entities such as people and companies leveraged from linked open data.
+Using Wikidata as our ground truth, we built models for datasets with ~1.1M people's names (~200K identities) and 130K company names (~70K identities).
+Deep metric learning is known to be a difficult problem in the closely related space of face recognition and person-re-identification \cite{DBLP:conf/cvpr/SchroffKP15}.
+To build these models for people and companies, we developed a novel approach for selecting samples for training, as well as developed a novel loss function, as we describe below.
+
 As in face recognition, our system for metric learning is built by training a `triplet siamese network' to learn to map different surface forms of the same entity closer in vector space than different forms of the same entity.
-Entity names have very different properties from faces, so we needed to adapt the approaches used in face recognition to the problem of matching entity names with a novel method to choose the sample for training, and novel loss functions as objectives for the metric learning problem.
 At training, the network is given a triplet consisting of an `anchor' (e.g.
@@
 \textit{Douglas Noel Adams}) and a negative element (e.g., John Adams), and it learns to produce a small distance estimate for the positive pair (close to 0), and a large distance estimate for the negative pair, using an objective function.
-A classification form of this function that simply learns whether two names belong to the same entity can be used to perform fuzzy joins, but then we would need a blocking strategy analogous to what has been used in the literature to identify the set of joinable pairs \cite{auto-join-joining-tables-leveraging-transformations}.
+The last hidden layer of the siamese network is effectively a `vector embedding' that contains the critical features needed for computing the distance estimate.
+There has been a significant amount of research in the problem of triplet selection, starting with the original Facenet work \cite{DBLP:conf/cvpr/SchroffKP15}.
+For any given training set, the key question is how to choose the set of negatives to teach the system the right mapping quickly.
+In prior work, for instance, various triplet mining techniques have been used to estimate which negatives might be good to pair with positives for training.
+As one example, \cite{DBLP:conf/cvpr/SchroffKP15} perform pairwise comparisons within a batch of training examples to identify \textit{semi-hard negatives} which are negatives that are slightly further away from the anchor than the positive example, but not distant enough from the anchor by a sufficient margin.
+One problem with this approach is that it relies on the existence of very large training sets and batches, so that one can find a sufficient number of negative examples for training in a batch.
+Our observation is that we can re-use the approximate nearest neighbors approach for triplet selection as well.
+Because our ultimate goal is to train the system to learn to map positives closer to the anchor and negatives further away from the anchor, we could select negatives that appear in the nearest neighbor set for input vectors, before any training has taken place.
+Depending on the nature of the dataset, these negatives could well be \textit{hard negatives}, i.e., negatives that are closer to the anchor than the positives.
+In fact, in our work, most of the triplets we selected had \textit{hard negatives}.
+\cite{DBLP:conf/cvpr/SchroffKP15} suggest that using only \textit{hard negatives} might be problematic for metric learning, but in our work, we used this approach successfully to train two separate models for people and companies respectively.
+Our observation is that triplet selection based on a nearest neighbors algorithm is a principled and efficient mechanism for selecting triples to train deep metric learning models.
 
-Our observation is that one can actually exploit what the siamese network produces to eliminate this blocking step altogether.
-Specifically, the last hidden layer of the siamese network is effectively a `vector embedding' that contains the critical features needed for computing the distance estimate.
-If such models are pre-built for a given entity type, we can then use the models to produce vector embeddings for all cell values in the two columns to be joined in a single linear pass, and index just the second column values with a space partitioning algorithm that lays out vectors in n-dimensional space.
-Then, for each cell value in the first column to be joined, querying the k-nearest neighbors should provide the set of values in the second column that can be joined.
-In our work, we used approximate nearest neighbor algorithms, which have been applied successfully to billions of items \cite{JDH17}.
+There have also been a number of different objective functions that have been proposed to build better models.
+For the problem of building models for people's names, we found that a modification to the objective function proposed in \cite{DBLP:conf/cvpr/SchroffKP15} was better than three other functions that have been proposed in the literature.
+We show the performance of the different functions for the two datasets we considered.
 
@@
 Our approach consists of building a deep neural network model for specific entity types and using a space partitioning algorithm to find the nearest neighbors to join.
-To test the generality of our approach, we built triplet loss based siamese networks for ~200,000 people's names and ~70,000 company names respectively, drawn from Wikidata.
-We show that such networks did learn to map surface forms of the same entity closer in vector space.
-Specifically, if we 83\% and 79\% of variants of the entity name appeared in the top 20 neighbors for each entity.
-Moreover, within the 20 neighbors, 77\% and 75\% of the positive names were closer to the anchor than negative names for people and companies respectively.
+To test the generality of our approach, we built triplet loss based siamese networks for 200K people's names and 70K company names respectively, drawn from Wikidata.
+We show that such networks did learn to map surface forms of the same entity closer in vector space, with a recall rate of 81\% and 75\% after training for 20 neighbors.
+Moreover, within the 20 neighbors, 93\% and 96\% of the positive names were closer to the anchor than negative names for people and companies respectively, suggesting good precision.
 Our results suggest that deep learning models can be used successfully for data driven joins, assuming that such models are built for common entity types.
@@
 In face recognition, a number of techniques exist for triplet selection, and methods for selecting triples is an active area of research.
-We developed a new technique for triplet selection for entity names because the techniques from face recognition do not generalize well to entity names.
-We also developed a novel loss function to train the network to discriminate entity names from names of other entities.
-We compare the results for this loss function with the ones that have been used for face recognition, and show that this loss function can perform much better than the existing functions for deep learning in this domain.
-\item We also perform a complexity analysis of how such models can then be used to perform joins across different surface forms of the same entity efficiently, with a complexity of $\mathcal{O}(n\log{}n)$.
+We developed a new technique for triplet selection for entity names based on an approximate nearest neighbors algorithm over input vectors.
+We also explored whether a modified loss function can be used to train the network more effectively, and found that it does in fact perform better for training on people's names.
+\item A key element of our argument is that once these embedding models have been built, they can be applied to perform joins efficiently for a new dataset.
+We test if this is true with previously built face recognition models, because of the paucity of large datasets for companies and people, and the wealth of datasets in the face recognition literature.
+For the most part, deep metric models for faces have been used with a classification layer have been used to identify a specific individual, or for clustering faces to measure goodness of the clustering algorithm.
+Because we use these existing models for a slightly different purpose, we calculated the same metrics of precision and recall that we calculated for people and companies.
+We compared the performance of the Facenet model that was trained on VGGFace2 \cite{DBLP:conf/fgr/CaoSXPZ18} on the Labeled Faces in the Wild dataset \cite{Huang_labeledfaces}.
+Our results show a recall of 80\%, and a precision of 93\%.
 \end{itemize}

### 2018-08-23 paper2018/main.tex
new version of intro

--- 2018-07-21 paper2018/main.tex
@@
 \begin{abstract}
-AAAI creates proceedings, working notes, and technical reports directly from electronic source furnished by the authors.
-To ensure that all papers in the publication have a uniform appearance, authors must adhere to the following instructions.
+Merging datasets is a key operation for data analytics.
+A frequent requirement for merging is joining across columns that have different surface forms for the same entity (e.g., the name of a person might be represented as \textit{Douglas Adams} or \textit{Douglas Noel Adams}).
+Data management systems are currently limited to performing merges based on string equality, or at best use string similarity to allow so-called `fuzzy' joins.
+We propose a novel approach to performing merges inspired in part by recent advances in deep learning.
+Our approach depends on (a) creating a function that maps surface forms into a set of vectors such that alternate forms for the same entity are closest in vector space, (b) indexing these vectors using a nearest neighbors algorithm to find the forms that can be potentially joined together.
+Using Wikidata as our ground truth, we built models for datasets with approximately 1.1M people's names (200K identities) and 130K company names (70K identities), where the vector embeddings allow joins with precision of .91-.93 and recall of .70-.81.
+To build these models, we developed novel techniques for the selection of samples to train on, as well as a loss function, which we describe in the paper.
+We also make the models available to the community for use in joining names or for aligning people or companies across multiple ontologies.
+
 \end{abstract}
 
-\input{introduction}
+\input{introduction2}
 \input{siamese_networks}
+\input{joins}
+\input{datasets}
 

### 2018-08-23 ContrastiveLossLSTM-8.20.18.py

@@ -1,0 +1,530 @@
+import numpy as np
+import pandas
+import tensorflow as tf
+import random as random
+import json
+
+from keras import backend as K
+
+from keras.preprocessing.text import Tokenizer
+from keras.preprocessing.sequence import pad_sequences
+
+from keras.layers import Dense, Input, Flatten, Dropout, Lambda, GRU, Activation
+from keras.layers.wrappers import Bidirectional
+
+from keras.layers import Conv1D, MaxPooling1D, Embedding
+
+from keras.models import Model, model_from_json, Sequential
+
+from embeddings import KazumaCharEmbedding
+
+from annoy import AnnoyIndex
+
+from keras.callbacks import ModelCheckpoint, EarlyStopping
+
+from names_cleanser import NameDataCleanser, CompanyDataCleanser
+
+import sys
+
+import statistics 
+
+import argparse
+
+#must fix
+MAX_NB_WORDS = 140000
+EMBEDDING_DIM = 100
+MAX_SEQUENCE_LENGTH = 10
+MARGIN=10
+ALPHA=45
+
+DEBUG = False
+DEBUG_DATA_LENGTH = 100
+DEBUG_ANN = False
+
+USE_ANGULAR_LOSS=False
+LOSS_FUNCTION=None
+TRAIN_NEIGHBOR_LEN=20
+TEST_NEIGHBOR_LEN=20
+EMBEDDING_TYPE = 'Kazuma'
+NUM_LAYERS = 3
+USE_L2_NORM = False
+
+output_file_name_for_hpo = "val_dict_list.json"
+
+def f1score(positive, negative):
+    #labels[predictions.ravel() < 0.5].sum()
+    fsocre = 0.0
+    true_positive = 0.0
+    false_positive = 0
+    false_negitive = 0
+    for i in range(len(positive)):
+        if positive[i] <= negative[i]:
+            true_positive += 1
+        else:
+            false_negitive += 1
+            false_positive += 1
+    print('tp' + str(true_positive))
+    print('fp' + str(false_positive))
+    print('fn' + str(false_negitive))
+    fscore = (2 * true_positive) / ((2 * true_positive) + false_negitive + false_positive)
+    return fscore 
+
+
+def get_embedding_layer(tokenizer):
+    word_index = tokenizer.word_index
+    num_words = len(word_index) + 1
+    embedding_matrix = np.zeros((num_words, EMBEDDING_DIM))
+    print('about to get kz')
[…]

### 2018-08-24 paper2018/evaluation.tex
draft of evaluation results

\section{Evaluation}
\label{results}

Table\ref{Characteristics} quantifies the difficulty of the metric problem for the people and company data in Wikidata.  After conversion to character embeddings, we computed the 20 nearest neighbors for each anchor, and computed what percentage of positives were found within the top 20 (recall), the average distance of positives and negatives from the anchor and their standard deviations respectively.  To compare it with metric learning for face recognition, which has been studied before, we also provide the same metrics for Labeled Faces in the Wild based on their input vector embeddings.  The table quantifies the difficulty of the metric learning problem across different data types, with positive distances for each being greater than negative distances.  Baseline recall rates are also poor, which is important if one needs to establish that the neural network did in fact learn after training.

\begin{table}[ht]
\caption{Dataset characteristics}
\label{Characteristics}
\begin{tabular}{l|r|r|r|r|r|r|r|}
\hline
Entity Type & Recall & Positives Avg. & Positives Std. & Max Positives & Negatives Avg. & Negatives Std. & Negatives Max \\
People & 0.03 & 9.07 & 3.05 & 28.30 & 3.16 & 1.17 & 16.97 \\
Companies & 0.20 & 4.67 & 2.29 & 19.21 & 3.18 & 1.40 & 12.77 \\
Faces & 0.037 & 39.82 & 9.17 & 79.15 & 25.05 & 3.72 & 43.19 \\
\end{tabular}
\end{table}

Table\ref{Evaluation} shows the same metrics after training.  Because we compared across different losses, the results are catagorized by each loss function for each dataset we tested.  For each value reported in the table, we conducted two runs to ensure the results were stable across runs, and we report the mean in the table.

\begin{table}[ht]
\caption{Results for people and companies by loss functions}
\label{Evaluation}
\begin{tabular}{l|l|r|r|r|r|r|r|r|r|}
\hline
Entity Type & Loss Function & Recall & Precision & Positives Avg. & Positives Std. & Max Positives & Negatives Avg. & Negatives Std. & Negatives Max \\
\hline
\multirow{4}{*}{People} & Our loss & .81 & .93 & .69 & .53 & 21.08 & 2.39 & 1.27 & 33.46 \\
\hline
& Triplet loss & .73 & .91 & .38 & .13 & .84 & .54 & .1 & .86 \\
\hline
& Improved loss & NA & NA & NA & NA & NA & NA & NA & NA \\
\hline
& Angular loss & NA & NA & NA & NA & NA & NA & NA & NA \\
\hline
\multirow{4}{*}{Companies} & Our loss & NA & NA & NA & NA & NA & NA & NA & NA \\
& Triplet loss & NA & NA & NA & NA & NA & NA & NA & NA \\
\hline
& Improved loss & NA & NA & NA & NA & NA & NA & NA & NA \\
\hline
& Angular loss & NA & NA & NA & NA & NA & NA & NA & NA \\
\hline
\end{tabular}
\end{table}

### 2018-08-28 paper2018/datasets.tex
cleaning up

@@
-\section{Datasets}
+\section{Benchmarks}
 \label{datasets}
-Our datasets were derived from Wikidata.
+Our benchmarks were derived from Wikidata.
 Specifically, we used the \textit{also known as} property from Wikidata to get alternate forms for the same entity name for people as well as companies.
@@
 There were 213106 names for people from the specific dump we extracted, and 70946 names for companies.
-The extracted files and the cleansing code are available on our repository \footnote{\url{https://github.com/yehudagale/fuzzyJoiner}}.
+The extracted files and the cleansing code are available on our repository.
 The extracted files however contained noise that we cleaned up programmatically.
@@
 We tried to ensure we included names that shared some subset of characters with the main name, ensuring we would not drop acronyms when possible.
+The check for acronyms tested if any of the initial letters of each name part occurred in the name.
 
@@
 \end{itemize}
+
+The data was then split with a 60-20-20 ratio to provide training, validation and test data respectively.  Each run was conducted with a different random split to ensure generalization of results.

### 2018-08-28 paper2018/evaluation.tex
cleaning up

@@
 
-Table\ref{Characteristics} quantifies the difficulty of the metric problem for the people and company data in Wikidata.
+Table \ref{Characteristics} quantifies the difficulty of the metric problem for the people and company data in Wikidata.
 After conversion to character embeddings, we computed the 20 nearest neighbors for each anchor, and computed what percentage of positives were found within the top 20 (recall), the average distance of positives and negatives from the anchor and their standard deviations respectively.
@@
 The table quantifies the difficulty of the metric learning problem across different data types, with positive distances for each being greater than negative distances.
-Baseline recall rates are also poor, which is important if one needs to establish that the neural network did in fact learn after training.
+Baseline recall rates are also poor, which is important because it suggests that a different mapping function learnt by a neural network is in fact needed for these entity types, just as it is for faces.
 
@@
 
-Table\ref{Evaluation} shows the same metrics after training.
+Table \ref{Evaluation} shows the same metrics after training.
 Because we compared across different losses, the results are catagorized by each loss function for each dataset we tested.

### 2018-08-28 paper2018/introduction2.tex
cleaning up

--- 2018-08-17 paper2018/introduction2.tex
@@
 
-Extensions in data management systems for handling `fuzzy' joins across different surface forms for the same entity typically use string similarity algorithms such as edit-distance, Jaro-Winkler and TF-IDF (e.g., \cite{Cohen2003}).
-In applying fuzzy joins, a key problem is to avoid quadratic comparisons between pairs of strings drawn from the two columns.
-A blocking strategy is used to reduce the number of pairs for fuzzy joins, such that only strings that share a common prefix, or suffix will be compared further.
-String matching algorithms often do not work however, because transformations of entity names in perfectly valid ways can yield very different strings.
-As shown in Table~\ref{table-example}, \textit{John Smith} is more similar to \textit{John Adams} than \textit{Adams, John}, but of course it is \textit{Adams, John} that is the valid alternate surface form for \textit{John Adams}.
+In this paper, we propose a different approach to the problem of joining different surface representations of the same entity, inspired in part by recent advances in deep learning.
+Our approach depends on (a) creating a function that maps surface forms into a set of vectors such that alternate forms for the same entity are closest in vector space, (b) indexing these vectors using a space partitioning algorithm to find the forms that can be potentially joined together.
+The approach is general, in the sense that once a model has been built for a specific semantic type (e.g.
+people, companies or faces) it can be used for joining any two datasets which share that semantic type.
+It is also efficient because it uses space partitioning algorithms (such as approximate nearest neighbor) to find surface forms that are potentially joinable, thus eliminating large parts of the vector space from consideration.
+Further, implementations exist for nearest neighbor algorithms that have been applied to billions of vectors \cite{JDH17}, so the approach is practical for most datasets.
 
-More recently, data driven approaches have emerged as a powerful alternative to string matching techniques for fuzzy joins.
-Data driven approaches mine patterns in the data to determine the `rules' for joining a given entity type.
-One example of such an approach is illustrated in \cite{He:2015:SJS:2824032.2824036}, which determines which cell values should be joined based on whether those cell values co-occur on the same row across disparate tables in a very large corpus of data.
-Another example of a data driven approach is work by \cite{auto-join-joining-tables-leveraging-transformations} where program synthesis techniques are used to learn the right set of transformations needed to perform the entity matching operation.
+To test the feasability of these ideas, we used Wikidata as ground truth to build models for datasets with 1.1M people's names (about 200K identities) and 130K company names (70K identities).
+The problem of mapping vectors for the same entity closer in vector space than vectors for other entities is known in the literature as deep metric learning.
+Deep metric learning is known to be a difficult problem as studied in the space of face recognition and person-re-identification \cite{DBLP:conf/cvpr/SchroffKP15}.
+As a result, there is a significant amount of research that has been targeted at two aspects of training these networks (a) how to choose samples for efficient learning, and (b) what constitutes a good loss function.
+In building models for entity names, we developed a novel method for sample selection, and a novel loss function, which was effective in building these models.
 
-In this paper, we propose a novel approach to the problem of joining different surface representations of the same entity, inspired in part by recent advances in deep learning.
-Our approach depends on (a) creating a function that maps surface forms into a set of vectors such that alternate forms for the same entity are closest in vector space, (b) indexing these vectors using a space partitioning algorithm to find the forms that can be potentially joined together.
-Our approach for merging datasets is much more flexible than prior data driven approaches (e.g., \cite{He:2015:SJS:2824032.2824036}, \cite{auto-join-joining-tables-leveraging-transformations}) because it can be applied to any data provided one can create a mapping function such that joinable surface forms of the entity are closer in vector space than disparate forms.
-For instance, in face recognition and person re-identification, there has been a significant research effort aimed at creating deep learning models that learn to map different surface forms of a face closer together in a vector space.
-In our proposed approach, we can now join two columns if they have alternate faces for the same entity, whereas in prior work, those faces needed to either have been joined before in some existing dataset, or the transforms of a face need to be discoverable as a program, which is near impossible for faces.
-Our approach for merging datasets is also efficient because it eliminates quadratic comparisons of cell values in each column by using a mechanism that is itself data-driven.
-Because we use space partitioning algorithms to find surface forms that are potentially joinable, the search process is efficiently eliminates large parts of the vector space from consideration for any given queried vector.
-Across all cell values that are considered for a join, the efficiency of the search is $\mathcal{O}(n\log{}n)$.
+As in face recognition, our system for metric learning is built by training a so-called `siamese triplet' network to learn to produce a small distance estimate for two surface forms for the same entity (positive pairs), and a large distance estimate for surface forms of different entities (negative pairs).
+A key problem in effective training of such networks is the problem of how to select negative pair for training, because one cannot exhaustively show all negative pairs to the network.
+In prior work for instance, this problem is solved by so-called `triplet mining' where negatives are gleaned after an all-pairs comparison of input vectors in a batch \cite{DBLP:conf/cvpr/SchroffKP15}.
+Our novel approach to this problem is to re-use the approximate nearest neighbors algorithm to choose negatives for training.
+Because our ultimate goal is to train the system to learn to map positives pairs closer and negative pairs further away from each other, we select negatives that appear in the nearest neighbor set for input vectors of a given entity, before any training has taken place.
+This approach has two key benefits.
+First, it lays out the entities based on their input vectors, and thus allows an efficient gathering of all nearest neighbors without a quadratic comparison of vectors to determine suitable negatives.
+Second, it provides a baseline against which one can objectively measure the effects if any of training.
+If for instance, the input vectors for surface forms of the same entity are already close together in vector space, little can be gained by a deep learning model.
 
-Specifically, the first part of our solution to the join problem involves building a deep learning model that performs metric learning.
-For the closely related problem of face recognition and person re-identification, deep neural networks have been used successfully to build models that map faces of the same entity closer in vector space estimate relative to faces from other entities.
-To test the generality of our approach, we tried to build a deep learning model model for names of people and companies.
-As in face recognition, our system for metric learning is built by training a `triplet siamese network' to learn to map different surface forms of the same entity closer in vector space than different forms of the same entity.
-Entity names have very different properties from faces, so we needed to adapt the approaches used in face recognition to the problem of matching entity names with a novel method to choose the sample for training, and novel loss functions as objectives for the metric learning problem.
-At training, the network is given a triplet consisting of an `anchor' (e.g.
-\textit{Douglas Adams}), a positive element (e.g.
-\textit{Douglas Noel Adams}) and a negative element (e.g., John Adams), and it learns to produce a small distance estimate for the positive pair (close to 0), and a large distance estimate for the negative pair, using an objective function.
-A classification form of this function that simply learns whether two names belong to the same entity can be used to perform fuzzy joins, but then we would need a blocking strategy analogous to what has been used in the literature to identify the set of joinable pairs \cite{auto-join-joining-tables-leveraging-transformations}.
-
-Our observation is that one can actually exploit what the siamese network produces to eliminate this blocking step altogether.
-Specifically, the last hidden layer of the siamese network is effectively a `vector embedding' that contains the critical features needed for computing the distance estimate.
-If such models are pre-built for a given entity type, we can then use the models to produce vector embeddings for all cell values in the two columns to be joined in a single linear pass, and index just the second column values with a space partitioning algorithm that lays out vectors in n-dimensional space.
-Then, for each cell value in the first column to be joined, querying the k-nearest neighbors should provide the set of values in the second column that can be joined.
-In our work, we used approximate nearest neighbor algorithms, which have been applied successfully to billions of items \cite{JDH17}.
+We also investigated the effect of manipulating multiple loss functions which have been proposed in the literature for improving deep metric learning, e.g., the triplet loss \cite{DBLP:conf/cvpr/SchroffKP15}, improved loss \cite{Zhang:2016:DML:3088616.3088665}, and angular loss \cite{DBLP:journals/corr/abs-1708-01682} functions.
+For the problem of building models for people's names, we found that a modification to the objective function proposed in \cite{DBLP:conf/cvpr/SchroffKP15} was better than three other functions that have been proposed in the literature.
 
@@
 
-Our key contributions are as follows:
-\begin{itemize}
-\item We outline a general approach to the problem of merging datasets for different surface forms of the same entity.
+%Our key contributions are as follows:
+%\begin{itemize}
+%\item We outline a general approach to the problem of merging datasets for different surface forms of the same entity.
 Our approach consists of building a deep neural network model for specific entity types and using a space partitioning algorithm to find the nearest neighbors to join.
-To test the generality of our approach, we built triplet loss based siamese networks for ~200,000 people's names and ~70,000 company names respectively, drawn from Wikidata.
-We show that such networks did learn to map surface forms of the same entity closer in vector space.
-Specifically, if we 83\% and 79\% of variants of the entity name appeared in the top 20 neighbors for each entity.
-Moreover, within the 20 neighbors, 77\% and 75\% of the positive names were closer to the anchor than negative names for people and companies respectively.
+To test the generality of our approach, we built triplet loss based siamese networks for 200K people's names and 70K company names respectively, drawn from Wikidata.
+We show that such networks did learn to map surface forms of the same entity closer in vector space, with a recall rate of 81\% and 75\% after training for 20 neighbors.
+Moreover, within the 20 neighbors, 93\% and 96\% of the positive names were closer to the anchor than negative names for people and companies respectively, suggesting good precision.
 Our results suggest that deep learning models can be used successfully for data driven joins, assuming that such models are built for common entity types.
-\item Training neural networks for deep metric learning is difficult because one cannot show quadratic combinations of the data to the system.
+%\item Training neural networks for deep metric learning is difficult because one cannot show quadratic combinations of the data to the system.
 In face recognition, a number of techniques exist for triplet selection, and methods for selecting triples is an active area of research.
-We developed a new technique for triplet selection for entity names because the techniques from face recognition do not generalize well to entity names.
-We also developed a novel loss function to train the network to discriminate entity names from names of other entities.
-We compare the results for this loss function with the ones that have been used for face recognition, and show that this loss function can perform much better than the existing functions for deep learning in this domain.
-\item We also perform a complexity analysis of how such models can then be used to perform joins across different surface forms of the same entity efficiently, with a complexity of $\mathcal{O}(n\log{}n)$.
-\end{itemize}
+We developed a new technique for triplet selection for entity names based on an approximate nearest neighbors algorithm over input vectors.
+We also explored whether a modified loss function can be used to train the network more effectively, and found that it does in fact perform better for training on people's names.
+%\item A key element of our argument is that once these embedding models have been built, they can be applied to perform joins efficiently for a new dataset.
+We test if this is true with previously built face recognition models, because of the paucity of large datasets for companies and people, and the wealth of datasets in the face recognition literature.
+For the most part, deep metric models for faces have been used with a classification layer have been used to identify a specific individual, or for clustering faces to measure goodness of the clustering algorithm.
+Because we use these existing models for a slightly different purpose, we calculated the same metrics of precision and recall that we calculated for people and companies.
+We compared the performance of the Facenet model that was trained on VGGFace2 \cite{DBLP:conf/fgr/CaoSXPZ18} on the Labeled Faces in the Wild dataset \cite{Huang_labeledfaces}.
+Our results show a recall of 80\%, and a precision of 93\%.
+%\end{itemize}
 
-The rest of the paper is organized as follows: Section~\ref{siamese networks} describes how we adapted siamese networks to the problem of entity matching, specifically the problem of triplet selection for entity names, and the need for a new type of loss function to improve metric learning for this problem, section ~\ref{joins} describes how to use these models for efficient joins across datasets, section ~\ref{dataset} describes characteristics of the datasets we used for training, as well as cleansing and data augmentation techniques we used to generate data, section ~\ref{results} provides the experimental results, section~\ref{related work} covers related work, and section~\ref{conclusions} describes future work and conclusions.
+%The rest of the paper is organized as follows: Section~\ref{siamese networks} describes how we adapted siamese networks to the problem of entity matching, specifically the problem of triplet selection for entity names, and the need for a new type of loss function to improve metric learning for this problem, section ~\ref{joins} describes how to use these models for efficient joins across datasets, section ~\ref{dataset} describes characteristics of the datasets we used for training, as well as cleansing and data augmentation techniques we used to generate data, section ~\ref{results} provides the experimental results, section~\ref{related work} covers related work, and section~\ref{conclusions} describes future work and conclusions.

### 2018-08-28 paper2018/main.tex
draft of evaluation results
cleaning up

@@
 \usepackage{subcaption}
+\usepackage{multirow}
 
@@
 %
-\title{Merging datasets through deep learning}
+\title{Merging Datasets Through Deep learning}
 
-\author{Kavitha Srinivas \\ IBM Research
-\And Yehuda Gale \\ Yeshiva University
-\And Julian Dolby \\ IBM Research}
+%\author{Kavitha Srinivas \\ IBM Research
+%\And Yehuda Gale \\ Yeshiva University
+%\And Julian Dolby \\ IBM Research}
 
@@
 A frequent requirement for merging is joining across columns that have different surface forms for the same entity (e.g., the name of a person might be represented as \textit{Douglas Adams} or \textit{Douglas Noel Adams}).
-Data management systems are currently limited to performing merges based on string equality, or at best use string similarity to allow so-called `fuzzy' joins.
-We propose a novel approach to performing merges inspired in part by recent advances in deep learning.
-Our approach depends on (a) creating a function that maps surface forms into a set of vectors such that alternate forms for the same entity are closest in vector space, (b) indexing these vectors using a nearest neighbors algorithm to find the forms that can be potentially joined together.
-Using Wikidata as our ground truth, we built models for datasets with approximately 1.1M people's names (200K identities) and 130K company names (70K identities), where the vector embeddings allow joins with precision of .91-.93 and recall of .70-.81.
+Data management systems are currently limited to performing merges based on string equality, or at best use string similarity.
+We propose a novel approach to performing merges based on deep learning models.
+Our approach depends on (a) creating a deep learning model that maps surface forms of an entity into a set of vectors such that alternate forms for the same entity are closest in vector space, (b) indexing these vectors using a nearest neighbors algorithm to find the forms that can be potentially joined together.
+Using Wikidata as our ground truth, we built models for datasets with approximately 1.1M people's names (200K identities) and 130K company names (70K identities), where the vector embeddings allow for joins with precision of .91-.93 and recall of .70-.81.
 To build these models, we developed novel techniques for the selection of samples to train on, as well as a loss function, which we describe in the paper.
-We also make the models available to the community for use in joining names or for aligning people or companies across multiple ontologies.
+We make the models available to the community for aligning people or companies across multiple datasets.
 
@@
 \input{introduction2}
+\input{relatedWork}
 \input{siamese_networks}
@@
 \input{datasets}
+\input{evaluation}
 

### 2018-08-28 paper2018/relatedWork.tex
cleaning up

\section{Related Work}
Extensions in data management systems for handling joins across different spellings for instance, typically use string similarity algorithms such as edit-distance, Jaro-Winkler and TF-IDF (e.g., \cite{Cohen2003}).  String matching algorithms often do not work for merging different forms of the same entity because valid transformations of entity names can yield very different strings (e.g., \textit{John Smith} is more similar to \textit{John Adams} than \textit{Adams, John}, but it is \textit{Adams, John} that is a valid alternate form).

More recently, data driven approaches have emerged as a powerful alternative to string matching techniques for merging data.  Data driven approaches mine patterns in the data to determine the `rules' for joining a given entity type.  One example of such an approach is illustrated in \cite{He:2015:SJS:2824032.2824036}, which determines which cell values should be joined based on whether those cell values co-occur on the same row across disparate tables in a very large corpus of data.  Another example of a data driven approach is work by \cite{auto-join-joining-tables-leveraging-transformations} where program synthesis techniques are used to learn the right set of transformations needed to perform the entity matching operation.  Our approach for merging datasets is much more general than either approach because the mapping function generalizes the set of transformations that are allowed across surface forms of an entity even when the explicit rules for identifying two surface forms as the same are not explicitly expressible as program transforms.

The idea of building joint embeddings for merging followed by nearest neighbors search has been applied recently to a slightly different problem of linking relational tuple embeddings with embeddings of other relational tuples or unstructured text \cite{Bordawekar18}, \cite{IDEL18}).  For the problem of linking tuples, each model that is learnt is specific to the database it was trained on.  Our contribution is that we developed general purpose embedding models for merging alternate surface forms of key entities such as people and companies leveraged from linked open data.  Once such models are built, they can be applied to joining any two datasets that share that semantic type.

TBD - related work on triplet selection and losses.

### 2018-08-28 paper2018/siamese_networks.tex
intro reworked
cleaning up

@@
-\section{Siamese networks}
-\label{siamese networks}
-
-Section~\ref{architecture} describes our overall network architecture for entity matching.
-Section~\ref{loss_functions} enumerates the different loss functions which have been used in prior work, and a new loss function which appears to do better in metric learning for entities.
-Section~\ref{triplet_selection} describes a novel triplet selection mechanisms for entity matching.
-
-\subsection{Network Architecture}
+\section{Network Architecture}
 \label{architecture}
@@
 
-Figure~\ref{siamese_nets} illustrates overall network architecture we used to build a system for fuzzy joins.
-Input is initially triples of a name (anchor), another name for the same entity (positive) and a name of another entity (negative).
+Figure~\ref{siamese_nets} illustrates the siamese network architecture \cite{DBLP:conf/cvpr/SchroffKP15} we used to build a system for merging data.
+Input is initially triples of a name (\textit{anchor}), another name for the same entity (\textit{positive}) and a name of another entity (\textit{negative}).
 For the network, input vectors are computed for each entity assuming a maximum name length of 10 for each entity (i.e., no entity could have a name that spanned more than 10 tokens).
-A 100 dimensional character embedding was computed for each token in the entity using pretrained embeddings \cite{hashimoto-jmt:2017:EMNLP2017}, which resulted in a 100 x 10 character encoding for each name used in a triplet.
+A 100 dimensional character embedding was computed for each token in the entity using pretrained character embeddings \cite{hashimoto-jmt:2017:EMNLP2017}, which resulted in a 100 x 10 character encoding for each name used in a triplet.
 These three input vectors from each triplet are fed to three identical networks that share the same weights.
@@
 Conceptually, there are two objectives in metric learning, one to minimize \textit{positive distances}, and the other to maximize \textit{negative distances}.
-As described below, this dual objective is achieved by different loss functions in the literature.
+As described below, this dual objective can be achieved by different loss functions.
 
-\subsection{Loss functions}
+\section{Loss functions}
 \label{loss_functions}
@@
 Let $\mathbf{x}$ represent an embedding for an entity name, and $\bf{x_{a}}$, $\bf{x_{p}}$, $\bf{x_{n}}$ reflect the vector embeddings of the \textit{anchor}, \textit{positive} and \textit{negative}, respectively.
-We investigated four different loss functions to explore their effectiveness for the entity metric learning problem.
+We investigated four different loss functions, three of which have been used in prior literature to explore their effectiveness for the entity metric learning problem.
 
@@
 
-\subsubsection{Triplet loss}
+\subsection{Triplet loss}
 
@@
 
-\subsubsection{Improved Loss}
+\subsection{Improved Loss}
 
@@
 As in Schroff et al.
-\cite{DBLP:conf/cvpr/SchroffKP15}, the embeddings are normalized to 1.
+\cite{DBLP:conf/cvpr/SchroffKP15}, the embeddings are normalized to 1 although the actual paper does not make it clear.
 
-\subsubsection{Angular Loss}
+\subsection{Angular Loss}
 
@@
 \begin{equation}
-\bf{x_{c}} = (\bf{x_{a}} + \bf{x_{c}}) / 2
+\bf{x_{c}} = (\bf{x_{a}} + \bf{x_{p}}) / 2
 \end{equation}
@@
 
-\subsubsection{Hyperbolic Tangent Loss}
+\subsection{Hyperbolic Tangent Loss}
 

### 2018-08-28 paper2018/triplet_selection.tex
cleaning up

@@
-\subsection{Triplet Selection}
+\section{Triplet Selection}
 Deep metric learning for faces is a difficult problem for neural networks to learn because improper sample selection can make it difficult for the network to converge.
@@
 
-\subsubsection{Batch Based Triple Selection}
+\subsection{Batch Based Triple Selection}
 \begin{figure}
@@
 
-\subsubsection{Metric Based Triplet Selection}
+\subsection{Metric Based Triplet Selection}
 Although the computation of there is $argmax^i \| x_{a} - x_{p}^i \|^2$ and $argmin^i \| x_{a} - x{_n}^i \|^2$ is infeasible because it involves quadratic comparisons within a dataset, we observe that the use of approximate nearest neighbor (ANN) indexes can actually make this problem tractable for the selection of triples.
@@
 There is no explicit attempt to filter out\textit{hard negatives} in the approach.
-The overall idea is that teh set of negatives that appear in the nearest neighbor set at input are in fact the most important elements for the network to learn to discriminate from positives.
+The overall idea is that the set of negatives that appear in the nearest neighbor set at input are in fact the most important elements for the network to learn to discriminate from positives.
 Focusing on these elements, regardless of whether they are \textit{hard} or \textit{semi-hard} should lead to better learning.
@@
 First, the entire dataset is in fact used in the triplet selection process.
-Second, for certain types of datasets, the batch based triplet selection mechanism will actually fail if it is focused on finding \textit{semi-hard negatives}.
-In particular, anytime \textit{positive distances} are on average much greater than \textit{negative} distances, there are very few \textit{semi-hard negatives} because most positives are in fact more distant than the negatives.
-We observed this property in the people's name matching dataset.
-If we take the character embeddings of each of the names in our name matching dataset, index it in an ANN, and then ask for the top-k neighbors we find somewhat troubling properties for an approach that tries to select \textit{semi-hard} negatives.
-First, \textit{positives} appeared in the top 20 neighbors only in 3.2\% of the dataset.
-Explicitly computing the distance between the \textit{anchor} and the \textit{positive} yielded a mean of 9.07, with a standard deviation of 3.07.
-The mean distances between the \textit{anchor} and the \textit{negatives} for those negatives in the top 20 was 3.16 with a standard deviation of 1.17.
-Given that only 3.2\% of positives actually even appeared in the top-K nearest neighbors, selection of \textit{semi-hard} negatives is reduced to a very small fraction of the dataset.
-A k-nearest neighbor approach to triplet selection on the other hand works on this difficult dataset as well, by picking all positive triplets, and a set of \textit{negatives} based on the top-k nearest neighbors.
-As we show later this approach generalizes to datasets such as company names where such a strong reversal of \textit{positive} and \textit{negative} distances does not exist.
+Second, it yields an important baseline to assess what if any learning was performed by the neural network in mapping input vectors to a different space.

### 2018-08-29 paper2018/introduction2.tex
adding more text

@@
 As a result, there is a significant amount of research that has been targeted at two aspects of training these networks (a) how to choose samples for efficient learning, and (b) what constitutes a good loss function.
-In building models for entity names, we developed a novel method for sample selection, and a novel loss function, which was effective in building these models.
+In building models for entity names, we had to adapt these techniques for triplet selection and loss functions because matching entity names have different properties than faces, as we describe below.
 
-As in face recognition, our system for metric learning is built by training a so-called `siamese triplet' network to learn to produce a small distance estimate for two surface forms for the same entity (positive pairs), and a large distance estimate for surface forms of different entities (negative pairs).
+As in face recognition, our system for metric learning is built by training a so-called triplet based `siamese triplet' network to learn to produce a small distance estimate for two surface forms for the same entity (between an arbitarily chosen anchor and positive), and a large distance estimate for surface forms of different entities (an anchor and a negative).
 A key problem in effective training of such networks is the problem of how to select negative pair for training, because one cannot exhaustively show all negative pairs to the network.
-In prior work for instance, this problem is solved by so-called `triplet mining' where negatives are gleaned after an all-pairs comparison of input vectors in a batch \cite{DBLP:conf/cvpr/SchroffKP15}.
-Our novel approach to this problem is to re-use the approximate nearest neighbors algorithm to choose negatives for training.
-Because our ultimate goal is to train the system to learn to map positives pairs closer and negative pairs further away from each other, we select negatives that appear in the nearest neighbor set for input vectors of a given entity, before any training has taken place.
-This approach has two key benefits.
-First, it lays out the entities based on their input vectors, and thus allows an efficient gathering of all nearest neighbors without a quadratic comparison of vectors to determine suitable negatives.
+In prior work for instance, this problem is solved by so-called `triplet mining' where so-called `semi-hard' negatives are gleaned after an all-pairs comparison of input vectors in a batch, e.g., \cite{DBLP:conf/cvpr/SchroffKP15}.
+`Semi-hard' negatives are negatives that are further away from the anchor than positives, but not by a sufficient margin.
+The idea of focusing on semi-hard negatives is to avoid mining poorly structured regions of the embedding space.
+For matching across entity names, most positive forms for the entity names are actually substantially further away from the anchor and from negatives, as we show empirically in this paper.
+Our approach to this problem is to use an approximate nearest neighbors algorithm to choose negatives for training in an efficient way, which means that most of the time, our negatives are `hard negatives', where the negative is closer to the anchor than positives.
+This approach has three key benefits.
+First, it lays out the entities based on their input vectors, and thus allows an efficient gathering of all nearest neighbors without a quadratic comparison of vectors in a batch to determine suitable negatives.
 Second, it provides a baseline against which one can objectively measure the effects if any of training.
 If for instance, the input vectors for surface forms of the same entity are already close together in vector space, little can be gained by a deep learning model.
+Third, it examines whether focusing on hard negatives is really detrimental to deep metric learning, at least for learning to map entity names in vector space.
 
-We also investigated the effect of manipulating multiple loss functions which have been proposed in the literature for improving deep metric learning, e.g., the triplet loss \cite{DBLP:conf/cvpr/SchroffKP15}, improved loss \cite{Zhang:2016:DML:3088616.3088665}, and angular loss \cite{DBLP:journals/corr/abs-1708-01682} functions.
+We also investigated the effect of manipulating multiple local loss functions which have been proposed in the literature for improving deep metric learning, e.g., the triplet loss \cite{DBLP:conf/cvpr/SchroffKP15}, improved loss \cite{Zhang:2016:DML:3088616.3088665}, and angular loss \cite{DBLP:journals/corr/abs-1708-01682} functions.
 For the problem of building models for people's names, we found that a modification to the objective function proposed in \cite{DBLP:conf/cvpr/SchroffKP15} was better than three other functions that have been proposed in the literature.

### 2018-08-29 paper2018/main.tex
adding more text

@@
 Using Wikidata as our ground truth, we built models for datasets with approximately 1.1M people's names (200K identities) and 130K company names (70K identities), where the vector embeddings allow for joins with precision of .91-.93 and recall of .70-.81.
-To build these models, we developed novel techniques for the selection of samples to train on, as well as a loss function, which we describe in the paper.
+To build these models, we adapted techniques for the selection of samples to train on, as well as a loss function, which we describe in the paper.
 We make the models available to the community for aligning people or companies across multiple datasets.

### 2018-08-29 paper2018/relatedWork.tex
adding more text

@@
 
+The use of nearest neighbors algorithms for triplet mining has been applied by \cite{DBLP:journals/corr/KumarHC0D17}, but their focus is on mining semi-hard negatives, that is focusing on negatives where at least one positive is closer to the anchor.
+In general, this means that one cannot look at fixed neighborhood sizes in building triplets.
+In other words, if all the positives are further away from the anchor than the negatives in a given neighborhood size of $k$, it means that $k$ needs to be expanded until a neighborhood size is found that has the right characteristics (i.e., at least one positive that is closer than the negattives which can be chosen).
+Our approach much more efficient because it relies on a fixed $k$ to generate samples.
 TBD - related work on triplet selection and losses.

### 2018-08-29 paper2018/main.tex
adding a new abstract

@@
 Using Wikidata as our ground truth, we built models for datasets with approximately 1.1M people's names (200K identities) and 130K company names (70K identities), where the vector embeddings allow for joins with precision of .91-.93 and recall of .70-.81.
-To build these models, we adapted techniques for the selection of samples to train on, as well as a loss function, which we describe in the paper.
+To build these models, we had to adapt techniques from metric learning due to the properties of the our domain.
+We demonstrate sample selection and loss functions, which work for this domain.
 We make the models available to the community for aligning people or companies across multiple datasets.

### 2018-08-29 TripletLossFacenetLSTM-8.29.18.py
latest code

@@ -1,0 +1,572 @@
+import numpy as np
+import pandas
+import tensorflow as tf
+import random as random
+import json
+
+from keras import backend as K
+
+from keras.preprocessing.text import Tokenizer
+from keras.preprocessing.sequence import pad_sequences
+
+from keras.layers import Dense, Input, Flatten, Dropout, Lambda, GRU, Activation
+from keras.layers.wrappers import Bidirectional
+
+from keras.layers import Conv1D, MaxPooling1D, Embedding
+
+from keras.models import Model, model_from_json, Sequential
+
+from embeddings import KazumaCharEmbedding
+
+from annoy import AnnoyIndex
+
+from keras.callbacks import ModelCheckpoint, EarlyStopping
+
+from names_cleanser import NameDataCleanser, CompanyDataCleanser
+
+import sys
+
+import statistics 
+from scipy.stats.mstats import gmean
+
+import argparse
+
+#must fix
+MAX_NB_WORDS = 140000
+EMBEDDING_DIM = 100
+MAX_SEQUENCE_LENGTH = 10
+MARGIN=10
+ALPHA=45
+
+DEBUG = False
+DEBUG_DATA_LENGTH = 100
+DEBUG_ANN = False
+
+USE_ANGULAR_LOSS=False
+LOSS_FUNCTION=None
+TRAIN_NEIGHBOR_LEN=20
+TEST_NEIGHBOR_LEN=20
+EMBEDDING_TYPE = 'Kazuma'
+NUM_LAYERS = 3
+USE_L2_NORM = False
+filepath="weights.best.hdf5"
+
+output_file_name_for_hpo = "val_dict_list.json"
+
+def f1score(positive, negative):
+    #labels[predictions.ravel() < 0.5].sum()
+    fsocre = 0.0
+    true_positive = 0.0
+    false_positive = 0
+    false_negitive = 0
+    for i in range(len(positive)):
+        if positive[i] <= negative[i]:
+            true_positive += 1
+        else:
+            false_negitive += 1
+            false_positive += 1
+    print('tp' + str(true_positive))
+    print('fp' + str(false_positive))
+    print('fn' + str(false_negitive))
+    fscore = (2 * true_positive) / ((2 * true_positive) + false_negitive + false_positive)
+    return fscore 
+
+
+def get_embedding_layer(tokenizer):
+    word_index = tokenizer.word_index
+    num_words = len(word_index) + 1
[…]

### 2018-08-29 paper2018/main.tex
ontology propaganda

@@
 \begin{abstract}
-Merging datasets is a key operation for data analytics.
-A frequent requirement for merging is joining across columns that have different surface forms for the same entity (e.g., the name of a person might be represented as \textit{Douglas Adams} or \textit{Douglas Noel Adams}).
-Data management systems are currently limited to performing merges based on string equality, or at best use string similarity.
-We propose a novel approach to performing merges based on deep learning models.
-Our approach depends on (a) creating a deep learning model that maps surface forms of an entity into a set of vectors such that alternate forms for the same entity are closest in vector space, (b) indexing these vectors using a nearest neighbors algorithm to find the forms that can be potentially joined together.
-Using Wikidata as our ground truth, we built models for datasets with approximately 1.1M people's names (200K identities) and 130K company names (70K identities), where the vector embeddings allow for joins with precision of .91-.93 and recall of .70-.81.
-To build these models, we had to adapt techniques from metric learning due to the properties of the our domain.
-We demonstrate sample selection and loss functions, which work for this domain.
-We make the models available to the community for aligning people or companies across multiple datasets.
-
+Merging datasets is a key operation for data analytics.  A frequent
+requirement for merging is joining across columns that have
+different surface forms for the same entity (e.g., the name of a
+person might be represented as \textit{Douglas Adams},
+\textit{Adams, Douglas} or \textit{Douglas Noel Adams}).  Similarly,
+ontology alignment can require recognizing distinct surface forms of
+the same entity, especially when ontologies are independently
+developed.  However, data management systems are currently limited
+to performing merges based on string equality, or at best using
+string similarity.  We propose a novel approach to performing merges
+based on deep learning models.  Our approach depends on (a) creating
+a deep learning model that maps surface forms of an entity into a
+set of vectors such that alternate forms for the same entity are
+closest in vector space, (b) indexing these vectors using a nearest
+neighbors algorithm to find the forms that can be potentially joined
+together.  To build these models, we had to adapt techniques from
+metric learning, due to the properties of entity names.  We
+demonstrate sample selection and loss functions, which work for this
+domain.  To evaluate our approach, we used Wikidata as ground truth
+and built models for datasets with approximately 1.1M people's names
+(200K identities) and 130K company names (70K identities).  We found
+that vector embeddings allow for joins with precision of .91-.93 and
+recall of .70-.81.  We make the models available to the community
+for aligning people or companies across multiple datasets.  
 \end{abstract}

### 2018-08-30 paper2018/introduction2.tex
add details from abstract

@@
 
-Merging datasets is a key operation for data analytics.
-A frequent requirement for merging is a join between two columns that frequently have different surface representations for the same entity (e.g., the name of a person might be represented as \textit{Douglas Adams} or \textit{Douglas Noel Adams}, as shown in Table~\ref{table-example}.
+Merging datasets is a key operation for data analytics.  A frequent
+requirement for merging is joining across columns that have
+different surface forms for the same entity  For instance, the name of a person might be represented as \textit{Douglas Adams} and \textit{Douglas Noel Adams} or \textit{John Adams} and \textit{Adams, John}, as shown in Table~\ref{table-example}.
+Similarly,
+ontology alignment can require recognizing distinct surface forms of
+the same entity, especially when ontologies are independently
+developed.
 This problem occurs for many entity types such as people's names, company names, addresses, product descriptions, conference venues, or even people's faces.
@@
 
-To test the feasability of these ideas, we used Wikidata as ground truth to build models for datasets with 1.1M people's names (about 200K identities) and 130K company names (70K identities).
+To test the feasibility of these ideas, we used Wikidata as ground truth to build models for datasets with 1.1M people's names (about 200K identities) and 130K company names (70K identities).
 The problem of mapping vectors for the same entity closer in vector space than vectors for other entities is known in the literature as deep metric learning.
 Deep metric learning is known to be a difficult problem as studied in the space of face recognition and person-re-identification \cite{DBLP:conf/cvpr/SchroffKP15}.
-As a result, there is a significant amount of research that has been targeted at two aspects of training these networks (a) how to choose samples for efficient learning, and (b) what constitutes a good loss function.
+As a result, there is a significant amount of research on two aspects of training these networks: (a) how to choose samples for efficient learning, and (b) what constitutes a good loss function.
 In building models for entity names, we had to adapt these techniques for triplet selection and loss functions because matching entity names have different properties than faces, as we describe below.
 
-As in face recognition, our system for metric learning is built by training a so-called triplet based `siamese triplet' network to learn to produce a small distance estimate for two surface forms for the same entity (between an arbitarily chosen anchor and positive), and a large distance estimate for surface forms of different entities (an anchor and a negative).
-A key problem in effective training of such networks is the problem of how to select negative pair for training, because one cannot exhaustively show all negative pairs to the network.
+As in face recognition, our system for metric learning is built by training a so-called triplet based `siamese triplet' network to learn to produce a small distance estimate for two surface forms for the same entity (between an arbitrarily chosen anchor and positive), and a large distance estimate for surface forms of different entities (an anchor and a negative).
+A key problem in effective training of such networks is the problem of how to select negative pairs for training, because one cannot exhaustively show all negative pairs to the network.
 In prior work for instance, this problem is solved by so-called `triplet mining' where so-called `semi-hard' negatives are gleaned after an all-pairs comparison of input vectors in a batch, e.g., \cite{DBLP:conf/cvpr/SchroffKP15}.
@@
 The idea of focusing on semi-hard negatives is to avoid mining poorly structured regions of the embedding space.
-For matching across entity names, most positive forms for the entity names are actually substantially further away from the anchor and from negatives, as we show empirically in this paper.
+For matching across entity names, most positive forms for the entity names are actually substantially further away from the anchor than are negatives, as we show empirically in this paper.
 Our approach to this problem is to use an approximate nearest neighbors algorithm to choose negatives for training in an efficient way, which means that most of the time, our negatives are `hard negatives', where the negative is closer to the anchor than positives.
@@
 First, it lays out the entities based on their input vectors, and thus allows an efficient gathering of all nearest neighbors without a quadratic comparison of vectors in a batch to determine suitable negatives.
-Second, it provides a baseline against which one can objectively measure the effects if any of training.
+Second, it provides a baseline against which one can objectively measure the effects of training.
 If for instance, the input vectors for surface forms of the same entity are already close together in vector space, little can be gained by a deep learning model.

### 2018-08-30 paper2018/relatedWork.tex
related work

--- 2018-08-28 paper2018/relatedWork.tex
@@
 
-The idea of building joint embeddings for merging followed by nearest neighbors search has been applied recently to a slightly different problem of linking relational tuple embeddings with embeddings of other relational tuples or unstructured text \cite{Bordawekar18}, \cite{IDEL18}).
+The idea of building joint embeddings for merging followed by nearest neighbors search has been applied recently to the problem of linking relational tuple embeddings with embeddings of other relational tuples or unstructured text \cite{Bordawekar18}, \cite{IDEL18}).
 For the problem of linking tuples, each model that is learnt is specific to the database it was trained on.
@@
 
-TBD - related work on triplet selection and losses.
+Metric learning is a well studied problem in the face recognition literature, e.g., \cite{DBLP:conf/cvpr/2014}, \cite{DBLP:conf/cvpr/SchroffKP15}, with a rich literature in triplet mining techniques.
+The closest approach to ours is the use of nearest neighbors algorithms for triplet mining has been applied by \cite{DBLP:journals/corr/KumarHC0D17}, but their focus is on a common practice in the literature which is focusing on mining semi-hard negatives, that is focusing on negatives where at least one positive is closer to the anchor.
+In general, this means that one cannot look at fixed neighborhood sizes in building triplets.
+In other words, if all the positives are further away from the anchor than the negatives in a given neighborhood size of $k$, it means that $k$ needs to be expanded until a neighborhood size is found that has the right characteristics (i.e., at least one positive that is closer than the negatives which can be chosen).
+Our approach much more efficient because it relies on a fixed $k$ to generate samples, and shows that at least in the names domain, learning with hard negatives is effective.
+
+The study of loss function effectiveness in metric learning is also a rich literature, with two basic types of loss functions that have been proposed: (a) local loss functions such as triplet loss \cite{DBLP:conf/cvpr/SchroffKP15}, angular loss \cite{Zhang:2016:DML:3088616.3088665} and improved loss \cite{DBLP:journals/corr/abs-1708-01682}, and (b) loss functions that operate on a more global level across a batch of training examples \cite{NIPS2016_6200}, \cite{songCVPR17}.
+Our focus in this paper is on local loss functions.

### 2018-08-30 paper2018/relatedWork.tex
edits

--- 2018-08-29 paper2018/relatedWork.tex
@@
 Extensions in data management systems for handling joins across different spellings for instance, typically use string similarity algorithms such as edit-distance, Jaro-Winkler and TF-IDF (e.g., \cite{Cohen2003}).
-String matching algorithms often do not work for merging different forms of the same entity because valid transformations of entity names can yield very different strings (e.g., \textit{John Smith} is more similar to \textit{John Adams} than \textit{Adams, John}, but it is \textit{Adams, John} that is a valid alternate form).
+String matching algorithms often do not work for merging different forms of the same entity because valid transformations of entity names can yield very different strings (e.g., \textit{John Smith} is more similar to \textit{John Adams} than to \textit{Adams, John}, but it is \textit{Adams, John} that is a valid alternate form).
 

### 2018-08-30 ANNCharacteristics.py
data characteristics

@@ -220,6 +220,63 @@ def build_unique_entities(entity2same):
     return unique_text, entity2index
 
 
+def characterize_dataset(model, sequences, entity2unique, entity2same, unique_text, nnlens):
+    predictions = model.predict(sequences)
+    t = AnnoyIndex(len(predictions[0]), metric='euclidean')  # Length of item vector that will be indexed
+    t.set_seed(123)
+    for i in range(len(predictions)):
+        # print(predictions[i])
+        v = predictions[i]
+        t.add_item(i, v)
+
+    t.build(100)  # 100 trees
+
+    for nnlen in nnlens:
+        print("Characteristics at neighborhood length:" + str(nnlen))
+        pos_distances = []
+        neg_distances = []
+        match = 0
+        no_match = 0
+
+        for key in entity2same:
+            index = entity2unique[key]
+            nearest = t.get_nns_by_vector(predictions[index], nnlen)
+            nearest_text = set([unique_text[i] for i in nearest])
+            expected_text = set(entity2same[key])
+            overlap = expected_text.intersection(nearest_text)
+
+            m = len(overlap)
+            match += m
+            # since we asked for only x nearest neighbors, and we get at most x-1 neighbors that are not the same as key (!)
+            # make sure we adjust our estimate of no match appropriately
+            no_match += min(len(expected_text), nnlen - 1) - m
+
+            # annoy has this annoying habit of returning the queried item back as a nearest neighbor.  Remove it.
+            if key in nearest_text:
+                nearest_text.remove(key)
+
+            # sample only the negatives that are true negatives
+            # that is, they are not in the expected set - sampling only 'semi-hard negatives is not defined here'
+            pos = expected_text
+            neg = nearest_text - expected_text
+
+            for i in pos:
+                dist_pos = t.get_distance(index, entity2unique[i])
+                pos_distances.append(dist_pos)
+            for i in neg:
+                dist_neg = t.get_distance(index, entity2unique[i])
+                neg_distances.append(dist_neg)
+
+        recall = match / (match + no_match)
+
+        print("mean positive distance:" + str(statistics.mean(pos_distances)))
+        print("stdev positive distance:" + str(statistics.stdev(pos_distances)))
+        print("max positive distance:" + str(max(pos_distances)))
[…]

### 2018-08-30 ANNCharacteristics.py
adding larger neighborhoods

@@ -534,4 +534,4 @@ sequences = pad_sequences(sequences, maxlen=MAX_SEQUENCE_LENGTH)
 embedder = get_embedding_layer(tokenizer)
 embedder_model = embedded_representation_model(embedder)
 
-characterize_dataset(embedder_model, sequences, entity2unique, entity2same, unique_text, [20, 100, 500])
+characterize_dataset(embedder_model, sequences, entity2unique, entity2same, unique_text, [20, 100, 500, 1000])

### 2018-08-31 paper2018/siamese_networks.tex

@@
 Figure~\ref{siamese_nets} illustrates the siamese network architecture \cite{DBLP:conf/cvpr/SchroffKP15} we used to build a system for merging data.
-Input is initially triples of a name (\textit{anchor}), another name for the same entity (\textit{positive}) and a name of another entity (\textit{negative}).
+As stated earlier, input is initially triples of a name (\textit{anchor}), another name for the same entity (\textit{positive}) and a name of another entity (\textit{negative}).
+During the tokenization process, we kept punctuation such as `-', `,', and `.' in the name because they are important signals in processing a name.
 For the network, input vectors are computed for each entity assuming a maximum name length of 10 for each entity (i.e., no entity could have a name that spanned more than 10 tokens).
 A 100 dimensional character embedding was computed for each token in the entity using pretrained character embeddings \cite{hashimoto-jmt:2017:EMNLP2017}, which resulted in a 100 x 10 character encoding for each name used in a triplet.
+We used a character encoding rather than a word based encoding primarily because many names were missing from word based vector embeddings.
+
 These three input vectors from each triplet are fed to three identical networks that share the same weights.
@@
 In our implementation, each of the three networks had 4 stacked layers of 128 unit Gated Recurrent Units (or GRUs) to capture the sequential nature of the input.
+For name and textual data, positional information is critical, so we used GRUs instead of the convolutional neural networks (CNNs) that have been traditionally used in metric learning for face and image recognition.
 
@@
 As described below, this dual objective can be achieved by different loss functions.
+We restrict ourselves to a discussion of the some of the more popular loss functions that are local in nature (i.e., they only look at a single triple).
 

### 2018-08-31 paper2018/evaluation.tex
start of eval

@@
 
-\begin{table}[ht]
+\begin{table*}[ht]
 \caption{Dataset characteristics}
@@
 \end{tabular}
-\end{table}
+\end{table*}
 
 Table \ref{Evaluation} shows the same metrics after training.
-Because we compared across different losses, the results are catagorized by each loss function for each dataset we tested.
+Because we compared across different losses, the results are categorized by each loss function for each dataset we tested.
 For each value reported in the table, we conducted two runs to ensure the results were stable across runs, and we report the mean in the table.
 
-\begin{table}[ht]
+\begin{table*}[ht]
 \caption{Results for people and companies by loss functions}
@@
 \end{tabular}
-\end{table}
+\end{table*}
+
+\subsection{Performance for Joins}
+
+ For fuzzy joins, we need both precision and recall to be high.
+Without good recall, a join will potentially miss names that should be joined.
+Without high precision, a join will mistakenly join many inappropriate names.
+To quantify recall, we measure, for each loss function, the fraction of positives---names of the same entity---that are found in our neighborhood.
+The numbers for our own loss function are 81\% for people and 72\% for companies, so a join could capture most similar names.
+
+ Precision is a little trickier to define, but one way is to measure how many true matches we get in the neighborhood before seeing a single mistake, i.e.
+a match that should not be there.
+That metric gives a picture of how many names would be correctly found, on average, by a join.
+Our loss function gives 62\% by this metric for people and 64\% for companies, so about two thirds of recalled names would be found before finding a single error.
+Since every name has at least one other name for the same entity, we also measure precision at 1, which is the probability that the very nearest neighbor is a true match.
+For that, our loss yields 81\% for people and 73\% for companies.
+Note that measuring precision for larger neighborhoods is tricky, since not every name has more than one name for the same entity.
+
+\subsection{Learning Performance}
+
+ We also assessed our learning mechanism more directly by examining how the nearest neighborhood changed from before to after training.
+As can be seen from Tables~\ref{Characteristics} and~\ref{Evaluation}, recall is improved greatly, with the bigger change for people, in which case it improves from 3\% to 80\%.
+For companies, it is from 17\% to 72\%.
+Thus training is clearly effective in moving actual names for the same entity into the nearest neighbors.
+For precision, the fraction of true matches found before the first error improves from 16\% to 73\% for people and 16\% to 64\% for companies.
+Precision at one improves from 10\% to 81\% for people and from 26\% to 73\% for companies.
+In both these cases, before training the results are basically noise even though embeddings are used for context, but training has made the results usable.

### 2018-08-31 TripletLossFacenetLSTM-8.20.18.py

@@ -27,6 +27,7 @@ from names_cleanser import NameDataCleanser, CompanyDataCleanser
 import sys
 
 import statistics 
+from scipy.stats.mstats import gmean
 
 import argparse
 
@@ -48,6 +49,7 @@ TEST_NEIGHBOR_LEN=20
 EMBEDDING_TYPE = 'Kazuma'
 NUM_LAYERS = 3
 USE_L2_NORM = False
+filepath="weights.best.hdf5"
 
 output_file_name_for_hpo = "val_dict_list.json"
 
@@ -235,11 +237,15 @@ def generate_triplets_from_ANN(model, sequences, entity2unique, entity2same, uni
     no_match = 0
     ann_accuracy = 0
     total = 0
-
+    precise = 0
+    
     triplets = {}
-
+    closest_positive_counts = []
+    
     pos_distances = []
     neg_distances = []
+    all_pos_distances = []
+    all_neg_distances = []
 
     triplets['anchor'] = []
     triplets['positive'] = []
@@ -255,6 +261,7 @@ def generate_triplets_from_ANN(model, sequences, entity2unique, entity2same, uni
         nearest = t.get_nns_by_vector(predictions[index], NNlen)
         nearest_text = set([unique_text[i] for i in nearest])
         expected_text = set(entity2same[key])
+            
         # annoy has this annoying habit of returning the queried item back as a nearest neighbor.  Remove it.
         if key in nearest_text:
             nearest_text.remove(key)
@@ -287,20 +294,52 @@ def generate_triplets_from_ANN(model, sequences, entity2unique, entity2same, uni
                 # print(dist_pos)
                 # print(dist_neg)               
 
+        min_neg_distance = 1000000        
+        for i in negatives:
+            dist_neg = t.get_distance(index, entity2unique[i])
+            all_neg_distances.append(dist_neg)
+            if dist_neg < min_neg_distance:
+                    min_neg_distance = dist_neg
+
+        for j in expected_text:
+            dist_pos = t.get_distance(index, entity2unique[j])
+            all_pos_distances.append(dist_pos)
+
+        closest_pos_count = 0
+        for p in overlap:
+            dist_pos = t.get_distance(index, entity2unique[p])
+            if dist_pos < min_neg_distance:
+                closest_pos_count+=1
+
+        if closest_pos_count > 0:
+            precise+=1
+
+        closest_positive_counts.append(closest_pos_count / min(len(expected_text), NNlen - 1))
+
+
+            
         for i in negatives:
[…]

### 2018-08-31 paper2018/evaluation.tex
faces

@@
 In both these cases, before training the results are basically noise even though embeddings are used for context, but training has made the results usable.
+
+\subsection{Generalization Test on Faces}
+
+ We have demonstrated that our strategy for joins could work well for textual names of people and companies, but the technique could potentially work for any kind of data for which a vector embedding can be made.
+To test how well that works, we evaluated an existing model for face recognition: we took the existing trained model at \url{https://github.com/davidsandberg/facenet}, and extracted the output embeddings for faces from the LFW test set at \url{http://vis-www.cs.umass.edu/lfw/}.
+We put these ooutput embeddings into an ANN structure, and computed our metrics on that.
+Recall of the same face was remarkably similar to our results for names, getting 76\%; however, we found precision at one was much lower at 21\%.
+
+ We hypothesize that one reason for lower precision at one is the nature of the training.
+Training on pre-built LFW model focused on what they call semi-hard negatives, which are triplets for which the negative is further from training anchor than the corresponding positive.
+Thus, negatives which are very close to an anchor may get less training to move them away from that anchor.
+Our training focuses on nearby negatives, which allows tem to be moved.
+
+\subsection{Discussion}
+
+ Our results and our comparison with faces seems to show that training on hard negatives does not compromise recall overall and can boost precision for near neighbors.
+Since joins will be most effective and efficient by focusing on a small, precise neighborhood, training on hard negatives may in fact be a useful addition.

### 2018-08-31 paper2018/datasets.tex
datasets added

@@
 The extracted files and the cleansing code are available on our repository.
-The extracted files however contained noise that we cleaned up programmatically.
+The extracted files however contained significant noise that we cleaned up programmatically.
 We describe the clean up rules for people and for companies separately because they were somewhat different.
@@
 
-The data was then split with a 60-20-20 ratio to provide training, validation and test data respectively.  Each run was conducted with a different random split to ensure generalization of results.
+After cleansing, if a name had no alternate surface forms, they were dropped.
+This resulted in 40555 company names with an average of 2.2 names each, and 195422 people's names with an average of 4.69 names each.
+Using the triplet selection algorithm we created a set of 10.9 million and 1.04 million triplets for people and companies at training.
+The data was then split with a 60-20-20 ratio to provide training, validation and test data respectively.
+Each run was conducted with a different random split to ensure generalization of results.
+
+\subsection{Dataset characteristics}
+As a baseline, we measured how the anchors, positives and negatives were laid out in vector space based on character embeddings alone.
+This gives us a measure of how difficult the problem is for the neural network to learn.
+We indexed all the vector embeddings (regardless of test or train) into a nearest neighbors algorithm using the Spotify ANNOY\footnote{\url{https://github.com/spotify/annoy}} implementation.
+We then queried the index for the $k$ nearest neighbors of this set, varying $k$ so it was either 20, 100, 500, or 1500 neighbors.
+Our primary interest was in recall rates of positives prior to any training, to establish the baseline prior to training.
+We also measured the nature of hard negatives as we varied the neighborhoods; i.e., what is the mean distance of negatives from the anchor while we increased neighborhoods, compared to the positive distances.
+Figure \ref{people_characteristics} shows the results for the people data.
+First, recall rate of positives in the nearest neighbor set was very low at 3\%, and it increased only to 6\%.
+The difficulty of the problem for reconciling people's names is further highlighted by the distance data.
+The mean distance of positives from anchor was 9.05, with a standard deviation of 3.08.
+The mean distances of negatives from anchor was 2.73, with a standard deviation of 0.99 for $k$ of 20.
+However even for $k$ of 1500, the mean negative distance was 3.64, well below the mean positive distance of 9.05.
+The company data show a similar trend, although companies seems to be an easier problem than reconciling people data, as shown in Figure \ref{company_characteristics}.
+Recall rate for companies starts at 16\% for a neighborhood size of 20, and is up to 25\% for a neighborhood size of 1500.
+Mean negative distance is at 3.05 compared to 4.64 at a neighborhood size of 20, with a standard deviation of 1.44.
+At a neighborhood size of 1500, mean negative sizes are slightly higher at 3.86.
+
+\begin{figure*}[htb]
+    \centering
+    \begin{subfigure}[t]{0.5\textwidth}
+        \centering
+        \includegraphics[width=.9\linewidth]{people_recall}
+        \caption{Recall rate as a function of neighborhood size}
+        \label{people_recall}
+    \end{subfigure}%
+    ~ 
+    \begin{subfigure}[t]{0.5\textwidth}
+        \centering 
+        \includegraphics[width=.9\linewidth]{people_distances}
+        \caption{Mean negative distance from anchor as a function of neighborhood size}
+        \label{modified_loss}
+    \end{subfigure}
+    \label{people_distances}
+    \caption{Characteristics of people data}
+\label{people_characteristics}
+\end{figure*}
+
+\begin{figure*}[htb]
+    \centering
+    \begin{subfigure}[t]{0.5\textwidth}
+        \centering
+        \includegraphics[width=.9\linewidth]{company_recall}
+        \caption{Recall rate as a function of neighborhood size}
+        \label{company_recall}
+    \end{subfigure}%                                                                                                   
+    ~
+    \begin{subfigure}[t]{0.5\textwidth}
+        \centering
+        \includegraphics[width=.9\linewidth]{company_distances}
+        \caption{Mean negative distance from anchor as a function of neighborhood size}
+        \label{modified_loss}
+    \end{subfigure}
+    \label{company_distances}
+    \caption{Characteristics of company data}
+\label{company_characteristics}
+\end{figure*}

### 2018-08-31 paper2018/siamese_networks.tex
loss function edits

@@
         \label{angular_loss}
-    \end{subfigure}
-    ~ 
-    \begin{subfigure}[t]{0.23\textwidth}
-        \centering 
-        \includegraphics[width=.9\linewidth]{tanh_triplet}
-        \caption{$Tanh$ loss}
-        \label{tanh_loss}
     \end{subfigure}
@@
 
-\subsection{Hyperbolic Tangent Loss}
+\subsection{Adapted Loss}
 
-The inspiration for our loss is that triplet loss, in effect, only
-pushes the negative distance as far as $\alpha$; if the negative
-distance is larger than that, the total loss can become negative,
-which is then forced to 0.  However, the further the negative point is
-from the anchor, the better, so we want to push it as far away as
-possible, without a limit like $\alpha$.  This is illustrated in
-Figure~\ref{tanh_loss} by pushing toward $\infty$.  To achieve this,
-we use hyperbolic tangent to compress all distances to the range 0 to
-1, and substract the negative distance from 1.  Then our loss function
-simply needs to minimize both positive and negative numbers:
+The inspiration for our loss is to separate the effect of the positive
+and negative distances as much as possible.  Rather than subtracting
+the negative distance from the positive one, we want to negate the
+negtive distance and then add the two.  To approximate this, we
+subtract the negative distance from a margin, and use 0 instead if
+that difference is negative.  We then combine the squared distances as
+usual, as how in Figure~\ref{adapted}.
 
 \begin{equation}
-  l_{triple} =  tanh\left(\|\bf{x_a} - \bf{x_p}\|\right) + \left(1-tanh\left(\|\bf{x_a} -\bf{x_n}\|\right)\right)
-\label{tanh}
+  l_{triple} =  \|\bf{x_a} - \bf{x_p}\|^2 + \left[ \alpha - \|\bf{x_a} -\bf{x_n} \right]_+^2
+\label{adapted}
 \end{equation}

### 2018-08-31 paper2018/evaluation.tex
evaluation.tex

@@
 \label{results}
+In building the models, we employed early stopping using the usual metric of accuracy of the validation data, and we performed hyper-parameter tuning using grid search varying margins for our loss function from 1-20.
+Accuracy was defined as the percentage of validation triples where positive distances from anchor were less than negative distances from anchor.
+For all our runs, test accuracy as measured by this metric ranged in the 9-- range.
+Table \ref{Evaluation} shows the results for the people and company datasets, run with a fixed $k$ of 20 neighbors.
+Because we compared across different losses, the results are categorized by each loss function for each dataset we tested.
+For all the results reported here, we ran multiple runs because of the stochastic nature of neural network models; the results here are representative of what we saw across runs.
 
-Table \ref{Characteristics} quantifies the difficulty of the metric problem for the people and company data in Wikidata.
-After conversion to character embeddings, we computed the 20 nearest neighbors for each anchor, and computed what percentage of positives were found within the top 20 (recall), the average distance of positives and negatives from the anchor and their standard deviations respectively.
-To compare it with metric learning for face recognition, which has been studied before, we also provide the same metrics for Labeled Faces in the Wild based on their input vector embeddings.
-The table quantifies the difficulty of the metric learning problem across different data types, with positive distances for each being greater than negative distances.
-Baseline recall rates are also poor, which is important because it suggests that a different mapping function learnt by a neural network is in fact needed for these entity types, just as it is for faces.
-
-\begin{table*}[ht]
-\caption{Dataset characteristics}
-\label{Characteristics}
-\begin{tabular}{l|r|r|r|r|r|r|r|}
-\hline
-Entity Type & Recall & Positives Avg. & Positives Std. & Max Positives & Negatives Avg. & Negatives Std. & Negatives Max \\
-People & 0.03 & 9.07 & 3.05 & 28.30 & 3.16 & 1.17 & 16.97 \\
-Companies & 0.20 & 4.67 & 2.29 & 19.21 & 3.18 & 1.40 & 12.77 \\
-Faces & 0.037 & 39.82 & 9.17 & 79.15 & 25.05 & 3.72 & 43.19 \\
-\end{tabular}
-\end{table*}
-
-Table \ref{Evaluation} shows the same metrics after training.
-Because we compared across different losses, the results are categorized by each loss function for each dataset we tested.
-For each value reported in the table, we conducted two runs to ensure the results were stable across runs, and we report the mean in the table.
+We report multiple metrics to measure the effectiveness of training, some of which are not standard because of the experimental setup, so we define them below:
+\begin{itemize}
+\item \textbf{Recall}.  Recall is measured by the percentage of positives in the nearest neighbor set of each anchor.
+\item \textbf{Precision@1}.  Precision@1 is measured by the percentage of anchors with the very nearest neighbor being a positive.
+\item \textbf{Precision}.  Precision is measured by the percentage of all positives for all anchors that were closer to the anchor than any other negative.
+\end{itemize}
 
@@
 \hline
-Entity Type & Loss Function & Recall & Precision & Positives Avg. & Positives Std. & Max Positives & Negatives Avg. & Negatives Std. & Negatives Max \\
+Entity Type & Loss Function & Recall & Precision@1 & Precision \\
 \hline
@@
 Without high precision, a join will mistakenly join many inappropriate names.
-To quantify recall, we measure, for each loss function, the fraction of positives---names of the same entity---that are found in our neighborhood.
-The numbers for our own loss function are 81\% for people and 72\% for companies, so a join could capture most similar names.
+To quantify recall, we measure, for each loss function.
+The numbers for our adapted loss function are 81\% for people and 72\% for companies, so a join could capture most similar names.
 
@@
  We also assessed our learning mechanism more directly by examining how the nearest neighborhood changed from before to after training.
-As can be seen from Tables~\ref{Characteristics} and~\ref{Evaluation}, recall is improved greatly, with the bigger change for people, in which case it improves from 3\% to 80\%.
+As can be seen from Table \ref{Evaluation}, recall is improved greatly, with the bigger change for people, in which case it improves from 3\% to 80\%.
 For companies, it is from 17\% to 72\%.
@@
  We have demonstrated that our strategy for joins could work well for textual names of people and companies, but the technique could potentially work for any kind of data for which a vector embedding can be made.
-To test how well that works, we evaluated an existing model for face recognition: we took the existing trained model at \url{https://github.com/davidsandberg/facenet}, and extracted the output embeddings for faces from the LFW test set at \url{http://vis-www.cs.umass.edu/lfw/}.
-We put these ooutput embeddings into an ANN structure, and computed our metrics on that.
-Recall of the same face was remarkably similar to our results for names, getting 76\%; however, we found precision at one was much lower at 21\%.
+To test how well that works, we evaluated two existing models for face recognition that were trained with the same approaches defined in the \cite{DBLP:conf/cvpr/SchroffKP15} on two different datasets, VGGFace2, and CasiaWebFace.
+We took the existing trained model at \url{https://github.com/davidsandberg/facenet}, and extracted the output embeddings for faces from the LFW test set at \url{http://vis-www.cs.umass.edu/lfw/} using these embeddings.
+We put these output embeddings into an ANN structure, and computed our metrics on that.
+Recall of the same face was remarkably similar to our results for names, getting 80\% on the VGGFace2 dataset, and 76\% for the Casia Web Face dataset.
+However, we found precision at one was much lower on both datasets at 23\% for VGGFace2 and 21\% for Casia Web faces.
 
@@
 Thus, negatives which are very close to an anchor may get less training to move them away from that anchor.
-Our training focuses on nearby negatives, which allows tem to be moved.
+Our training focuses on nearby negatives, which allows them to be moved.
+This is clearly a hypothesis that needs to be tested further.
 

### 2018-08-31 paper2018/evaluation.tex
adding references to face datasets

@@
  We have demonstrated that our strategy for joins could work well for textual names of people and companies, but the technique could potentially work for any kind of data for which a vector embedding can be made.
-To test how well that works, we evaluated two existing models for face recognition that were trained with the same approaches defined in the \cite{DBLP:conf/cvpr/SchroffKP15} on two different datasets, VGGFace2, and CasiaWebFace.
-We took the existing trained model at \url{https://github.com/davidsandberg/facenet}, and extracted the output embeddings for faces from the LFW test set at \url{http://vis-www.cs.umass.edu/lfw/} using these embeddings.
+To test how well that works, we evaluated two existing models for face recognition that were trained with the same approaches defined in the \cite{DBLP:conf/cvpr/SchroffKP15} on two different datasets, VGGFace2 \cite{DBLP:conf/fgr/CaoSXPZ18}, and CasiaWebFace \cite{DBLP:conf/cvpr/SchroffKP15}.
+We took the existing trained model at \url{https://github.com/davidsandberg/facenet}, and extracted the output embeddings for faces from the LFW test set \cite{Huang2012a} using these embeddings.
 We put these output embeddings into an ANN structure, and computed our metrics on that.

### 2018-08-31 TripletLossFacenetLSTM-8.31.18.py

@@ -1,0 +1,630 @@
+import numpy as np
+import pandas
+import tensorflow as tf
+import random as random
+import json
+
+from keras import backend as K
+
+from keras.preprocessing.text import Tokenizer
+from keras.preprocessing.sequence import pad_sequences
+
+from keras.layers import Dense, Input, Flatten, Dropout, Lambda, GRU, Activation
+from keras.layers.wrappers import Bidirectional
+
+from keras.layers import Conv1D, MaxPooling1D, Embedding
+
+from keras.models import Model, model_from_json, Sequential
+
+from embeddings import KazumaCharEmbedding
+
+from annoy import AnnoyIndex
+
+from keras.callbacks import ModelCheckpoint, EarlyStopping
+
+from names_cleanser import NameDataCleanser, CompanyDataCleanser
+
+import sys
+
+import statistics 
+from scipy.stats.mstats import gmean
+
+import argparse
+
+#must fix
+MAX_NB_WORDS = 140000
+EMBEDDING_DIM = 100
+MAX_SEQUENCE_LENGTH = 10
+MARGIN=10
+ALPHA=45
+
+DEBUG = False
+DEBUG_DATA_LENGTH = 100
+DEBUG_ANN = True
+
+USE_ANGULAR_LOSS=False
+LOSS_FUNCTION=None
+TRAIN_NEIGHBOR_LEN=20
+TEST_NEIGHBOR_LEN=20
+EMBEDDING_TYPE = 'Kazuma'
+NUM_LAYERS = 3
+USE_L2_NORM = False
+filepath="weights.best.hdf5"
+
+output_file_name_for_hpo = "val_dict_list.json"
+
+def f1score(positive, negative):
+    #labels[predictions.ravel() < 0.5].sum()
+    fsocre = 0.0
+    true_positive = 0.0
+    false_positive = 0
+    false_negitive = 0
+    for i in range(len(positive)):
+        if positive[i] <= negative[i]:
+            true_positive += 1
+        else:
+            false_negitive += 1
+            false_positive += 1
+    print('tp' + str(true_positive))
+    print('fp' + str(false_positive))
+    print('fn' + str(false_negitive))
+    fscore = (2 * true_positive) / ((2 * true_positive) + false_negitive + false_positive)
+    return fscore 
+
+
+def get_embedding_layer(tokenizer):
+    word_index = tokenizer.word_index
+    num_words = len(word_index) + 1
[…]

### 2018-08-31 TripletLossFacenetLSTM-8.31.18.py
added semi hard training

@@ -40,7 +40,7 @@ ALPHA=45
 
 DEBUG = False
 DEBUG_DATA_LENGTH = 100
-DEBUG_ANN = True
+DEBUG_ANN = False
 
 USE_ANGULAR_LOSS=False
 LOSS_FUNCTION=None
@@ -250,24 +250,21 @@ def generate_semi_hard_triplets_from_ANN(model, sequences, entity2unique, entity
         semi_hards = []
         expected_text = set(entity2same[key])
         expected_ids = [entity2unique[i] for i in expected_text]
-        print(key)
-        print(expected_text)
 
         for positive in expected_text:
             k = entity2unique[positive]
             nearest = t.get_nns_by_vector(predictions[k], NNlen)
             nearest_text = set([unique_text[i] for i in nearest])
-            print(positive)
-            print(nearest_text)
             dist_k = t.get_distance(index, k)
-            print(dist_k)
             for n in nearest:
                 if n == index or n in expected_ids or n == k:
                     continue
                 n_dist = t.get_distance(index, n)
-                print(n_dist)
                 if n_dist > dist_k:
                     semi_hards.append(unique_text[n])
+
+        shuffle(semi_hards)
+        semi_hards = semi_hards[0:20]
 
         for i in semi_hards:
             for j in expected_text:
@@ -595,8 +592,7 @@ counter = 0
 current_model = embedder_model
 prev_match_stats = 0
 
-train_data, match_stats = generate_triplets_from_ANN(current_model, sequences, entity2unique, entity2same_train, unique_text, False)
-print("Match stats:" + str(match_stats))
+train_data = generate_semi_hard_triplets_from_ANN(current_model, sequences, entity2unique, entity2same_train, unique_text, False)
 
 number_of_names = len(train_data['anchor'])
 # print(train_data['anchor'])

### 2018-09-01 TripletLossFacenetLSTM-8.31.18.py
fixes

@@ -1,3 +1,5 @@
+from random import shuffle
+
 import numpy as np
 import pandas
 import tensorflow as tf
@@ -87,7 +89,7 @@ def get_embedding_layer(tokenizer):
 
         if embedding_vector is not None:
             if sum(embedding_vector) == 0:
-                print("failed to find embedding for:" + word)
+                print(str("failed to find embedding for:" + word).encode('utf-8'))
             # words not found in embedding index will be all-zeros.
             embedding_matrix[i] = embedding_vector
     print("Number of words:" + str(num_words))
@@ -116,7 +118,7 @@ def get_sequences(texts, tokenizer):
 
 def read_entities(filepath):
     entities = []
-    with open(filepath) as fl:
+    with open(filepath, 'r', encoding='utf8') as fl:
         for line in fl:
             entities.append(line)
 
@@ -124,7 +126,7 @@ def read_entities(filepath):
 
 def read_file(file_path):
     texts = {'anchor':[], 'negative':[], 'positive':[]}
-    fl = open(file_path, 'r')
+    fl = open(file_path, 'r', encoding='utf8')
     i = 0
     for line in fl:
         line_array = line.split("|")
@@ -247,15 +249,15 @@ def generate_semi_hard_triplets_from_ANN(model, sequences, entity2unique, entity
     for key in entity2same:
         index = entity2unique[key]
 
-        semi_hards = []
         expected_text = set(entity2same[key])
         expected_ids = [entity2unique[i] for i in expected_text]
 
         for positive in expected_text:
             k = entity2unique[positive]
             nearest = t.get_nns_by_vector(predictions[k], NNlen)
-            nearest_text = set([unique_text[i] for i in nearest])
             dist_k = t.get_distance(index, k)
+
+            semi_hards = []
             for n in nearest:
                 if n == index or n in expected_ids or n == k:
                     continue
@@ -263,13 +265,12 @@ def generate_semi_hard_triplets_from_ANN(model, sequences, entity2unique, entity
                 if n_dist > dist_k:
                     semi_hards.append(unique_text[n])
 
-        shuffle(semi_hards)
-        semi_hards = semi_hards[0:20]
+            # shuffle(semi_hards)
+            # semi_hards = semi_hards[0:20]
 
-        for i in semi_hards:
-            for j in expected_text:
+            for i in semi_hards:
                 triplets['anchor'].append(key)
[…]

### 2018-09-02 paper2018/evaluation.tex
added latest numbers

@@
 \begin{table*}[ht]
-\caption{Results for people and companies by loss functions}
+\caption{Precision and Recall for people and companies by loss functions}
 \label{Evaluation}
-\begin{tabular}{l|l|r|r|r|r|r|r|r|r|}
+\begin{tabular}{l|l|r|r|r|}
 \hline
@@
 \hline
-\multirow{4}{*}{People} & Our loss & .81 & .93 & .69 & .53 & 21.08 & 2.39 & 1.27 & 33.46 \\
+\multirow{4}{*}{People} & Adapted loss & .81 & .81 & .63 \\
 \hline
-& Triplet loss & .73 & .91 & .38 & .13 & .84 & .54 & .1 & .86 \\
+& Triplet loss & .74 & .84 & .55 \\
 \hline
-& Improved loss & NA & NA & NA & NA & NA & NA & NA & NA \\
+& Improved loss & .71 & .52 & .45 \\
 \hline
-& Angular loss & NA & NA & NA & NA & NA & NA & NA & NA \\
+& Angular loss & .04 & .09 & .02 \\
 \hline
-\multirow{4}{*}{Companies} & Our loss & NA & NA & NA & NA & NA & NA & NA & NA \\
-& Triplet loss & NA & NA & NA & NA & NA & NA & NA & NA \\
+\multirow{4}{*}{Companies} & Adapted loss & .72 & .73 & .64 \\
+& Triplet loss & .75 & .76 & .67 \\
 \hline
-& Improved loss & NA & NA & NA & NA & NA & NA & NA & NA \\
+& Improved loss & .74 & .72 & .64 \\
 \hline
-& Angular loss & NA & NA & NA & NA & NA & NA & NA & NA \\
+& Angular loss & NA & NA & NA \\
+\hline
+\end{tabular}
+\end{table*}
+
+\begin{table*}[ht]
+\caption{Distance estimates for people and companies after training}
+\label{Evaluation}
+\begin{tabular}{l|l|r|r|r|r|}
+\hline
+Entity Type & Loss Function & Mean Pos & Std Pos & Mean Neg & Std Neg \\
+\hline
+\multirow{4}{*}{People} & Adapted loss & 1.59 & 4.04 & 2.44 & 2.45 \\
+\hline
+& Triplet loss & .46 & .18 & .55 & .10 \\
+\hline
+& Improved loss & .15 & .38 & .21 & .18 \\
+\hline
+& Angular loss & .51 & .25 & .06 & .02 \\
+\hline
+\multirow{4}{*}{Companies} & Adapted loss & 2.38 & 3.77 & 3.23 & 1.71 \\
+& Triplet loss & .39 & .28 & .55 & .09 \\
+\hline
+& Improved loss & .32 & .50 & .42 & 0.19 \\
+\hline
+& Angular loss & NA & NA & NA & NA \\
 \hline

### 2018-09-02 paper2018/main.tex
fixing abstract

@@
 to performing merges based on string equality, or at best using
-string similarity.  We propose a novel approach to performing merges
+string similarity.  We propose an approach to performing merges
 based on deep learning models.  Our approach depends on (a) creating
@@
 together.  To build these models, we had to adapt techniques from
-metric learning, due to the properties of entity names.  We
-demonstrate sample selection and loss functions, which work for this
+metric learning, due to the requirements of joins; specifically we describe 
+novel sample selection and loss functions that work for this
 domain.  To evaluate our approach, we used Wikidata as ground truth
@@
 (200K identities) and 130K company names (70K identities).  We found
-that vector embeddings allow for joins with precision of .91-.93 and
-recall of .70-.81.  We make the models available to the community
+that vector embeddings allow for joins with precision of .73-.81 and
+recall of .72-.81.  We make the models available to the community
 for aligning people or companies across multiple datasets.  

### 2018-09-02 paper2018/introduction2.tex
removing some equations

@@
 `Semi-hard' negatives are negatives that are further away from the anchor than positives, but not by a sufficient margin.
-The idea of focusing on semi-hard negatives is to avoid mining poorly structured regions of the embedding space.
+The idea of focusing on semi-hard negatives is to avoid mining noisy regions of the embedding space.
 For matching across entity names, most positive forms for the entity names are actually substantially further away from the anchor than are negatives, as we show empirically in this paper.
-Our approach to this problem is to use an approximate nearest neighbors algorithm to choose negatives for training in an efficient way, which means that most of the time, our negatives are `hard negatives', where the negative is closer to the anchor than positives.
+In other words, `hard negatives' dominate the space, and are the norm.
+Our approach to the problem of triplet mining for this problem was to use an approximate nearest neighbors algorithm to choose negatives for training that were in the nearest neighbor set, which means that most of the time, our negatives are `hard negatives', where the negative is closer to the anchor than positives.
 This approach has three key benefits.
@@
 Second, it provides a baseline against which one can objectively measure the effects of training.
-If for instance, the input vectors for surface forms of the same entity are already close together in vector space, little can be gained by a deep learning model.
 Third, it examines whether focusing on hard negatives is really detrimental to deep metric learning, at least for learning to map entity names in vector space.
@@
 We also investigated the effect of manipulating multiple local loss functions which have been proposed in the literature for improving deep metric learning, e.g., the triplet loss \cite{DBLP:conf/cvpr/SchroffKP15}, improved loss \cite{Zhang:2016:DML:3088616.3088665}, and angular loss \cite{DBLP:journals/corr/abs-1708-01682} functions.
-For the problem of building models for people's names, we found that a modification to the objective function proposed in \cite{DBLP:conf/cvpr/SchroffKP15} was better than three other functions that have been proposed in the literature.
+For the problem of building models for people's names, we found that an adaptation to the objective function proposed in \cite{DBLP:conf/cvpr/SchroffKP15} was better than three other functions that have been proposed in the literature.
 

### 2018-09-02 paper2018/relatedWork.tex
removing some equations

@@
 
-The idea of building joint embeddings for merging followed by nearest neighbors search has been applied recently to the problem of linking relational tuple embeddings with embeddings of other relational tuples or unstructured text \cite{Bordawekar18}, \cite{IDEL18}).
+The idea of building joint embeddings for merging datasets followed by nearest neighbors search has been applied recently to the problem of linking relational tuple embeddings with embeddings of other relational tuples or unstructured text \cite{Bordawekar18}, \cite{IDEL18}).
 For the problem of linking tuples, each model that is learnt is specific to the database it was trained on.
@@
 Metric learning is a well studied problem in the face recognition literature, e.g., \cite{DBLP:conf/cvpr/2014}, \cite{DBLP:conf/cvpr/SchroffKP15}, with a rich literature in triplet mining techniques.
-The closest approach to ours is the use of nearest neighbors algorithms for triplet mining has been applied by \cite{DBLP:journals/corr/KumarHC0D17}, but their focus is on a common practice in the literature which is focusing on mining semi-hard negatives, that is focusing on negatives where at least one positive is closer to the anchor.
-In general, this means that one cannot look at fixed neighborhood sizes in building triplets.
-In other words, if all the positives are further away from the anchor than the negatives in a given neighborhood size of $k$, it means that $k$ needs to be expanded until a neighborhood size is found that has the right characteristics (i.e., at least one positive that is closer than the negatives which can be chosen).
-Our approach much more efficient because it relies on a fixed $k$ to generate samples, and shows that at least in the names domain, learning with hard negatives is effective.
+The closest approach to ours is the use of nearest neighbors algorithms for triplet mining has been applied by \cite{DBLP:journals/corr/KumarHC0D17}, but their focus is on a common practice in the literature which is focusing on mining semi-hard negatives.
+This means that one cannot look at fixed neighborhood sizes in building triplets.
+If all the positives are further away from the anchor than the negatives in a given neighborhood size of $k$, it means that $k$ needs to be expanded until a neighborhood size is found that has the right characteristics (i.e., at least one positive that is closer than the negatives which can be chosen).
+Our focus on `hard negatives' means we can use a fixed $k$ to generate samples.
+At least in the names domain, metric learning with hard negatives is effective.
 
 The study of loss function effectiveness in metric learning is also a rich literature, with two basic types of loss functions that have been proposed: (a) local loss functions such as triplet loss \cite{DBLP:conf/cvpr/SchroffKP15}, angular loss \cite{Zhang:2016:DML:3088616.3088665} and improved loss \cite{DBLP:journals/corr/abs-1708-01682}, and (b) loss functions that operate on a more global level across a batch of training examples \cite{NIPS2016_6200}, \cite{songCVPR17}.
-Our focus in this paper is on local loss functions.
+Our focus in this paper is on local loss functions because many of the global loss functions seem to try and accomplish the same objective as hard triplet mining \cite{songCVPR17} using an indirect mechanism to do so.
+Our approach directly mines hard triplets, so there is no need to try to broaden the loss function to a batch.

### 2018-09-02 paper2018/siamese_networks.tex
type o
removing some equations

@@
 For name and textual data, positional information is critical, so we used GRUs instead of the convolutional neural networks (CNNs) that have been traditionally used in metric learning for face and image recognition.
+GRUs are a type of recurrent network \cite{cho-al-emnlp14} where each hidden unit updates its weights at a specific step in the sequence $t$ based on the current input $x_t$ and the value of the hidden unit from the prior step $h_{t-1}$.
 
-GRUs are a type of recurrent network \cite{cho-al-emnlp14} where each hidden unit updates its weights at a specific step in the sequence $t$ based on the current input $x_t$ and the value of the hidden unit from the prior step $h_{t-1}$.
-$r_t$ is a reset gate which determines whether the state from the previous step $h_{t-1}$ should be ignored.
+%$r_t$ is a reset gate which determines whether the state from the previous step $h_{t-1}$ should be ignored.
 $z_t$ is an update gate which determines whether the current hidden state should be updated with the new hidden state $\tilde{h_t}$.
 Equations~\ref{eq_1}-\ref{eq_4} that govern the update at $h_t$, as summarized by \cite{colah}.
-\begin{equation}
-z_t = \sigma(W_z . [h_{t-1}, x_t])
-\label{eq_1}
-\end{equation}
+%\begin{equation}
+%z_t = \sigma(W_z . [h_{t-1}, x_t])
+%@\label{eq_1}
+%\end{equation}
 
-\begin{equation}
-r_t = \sigma(W_r . [h_{t-1}, x_t])
-\label{eq_2}
-\end{equation}
+%\begin{equation}
+%r_t = \sigma(W_r . [h_{t-1}, x_t])
+%\label{eq_2}
+%\end{equation}
 
-\begin{equation}
-\tilde{h_t} = tanh (W . [r_t * h_{t-1}, x_t])
-\label{eq_3}
-\end{equation}
+%\begin{equation}
+%\tilde{h_t} = tanh (W . [r_t * h_{t-1}, x_t])
+%\label{eq_3}
+%\end{equation}
 
-\begin{equation}
-h_t = (1- z_t) * h_{t-1} + z_t * \tilde{h_t}
-\label{eq_4}
-\end{equation}
+%\begin{equation}
+%h_t = (1- z_t) * h_{t-1} + z_t * \tilde{h_t}
+%\label{eq_4}
+%\end{equation}
 
-The output of the last layer shown in the Figure~\ref{siamese_nets} as a dark gray layer produces an output vector embedding for the inputs.
+The output of the last layer shown in the Figure~\ref{siamese_nets} as a dark layer produces an output vector embedding for the inputs.
 These are fed to two layers which compute a euclidean distance between the \textit{anchor} and the \textit{positive} elements of a triplet (\textit{positive distance}), and the \textit{anchor} and the \textit{negative} elements of a triplet (\textit{negative distance}).
@@
 \begin{equation}
-  l_{triple} =  \|\bf{x_a} - \bf{x_p}\|^2 + \left[ \alpha - \|\bf{x_a} -\bf{x_n} \right]_+^2
+  l_{triple} =  \|\bf{x_a} - \bf{x_p}\|^2 + \left[ \alpha - \|\bf{x_a} -\bf{x_n}\| \right]_+^2
 \label{adapted}

### 2018-09-02 paper2018/triplet_selection.tex
removing some equations

@@
 \section{Triplet Selection}
-Deep metric learning for faces is a difficult problem for neural networks to learn because improper sample selection can make it difficult for the network to converge.
-We describe a popular approach from the face recognition literature first before we describe a new mechanism for triplet selection.
+As discussed earlier, deep metric learning for faces is a difficult problem for neural networks to learn because improper sample selection can make it difficult for the network to converge.
+We describe a popular approach batch based approach from the face recognition literature first to contrast it with our mechanism for triplet selection.
 
@@
 In practice, instead of focusing on finding \textit{hard positives}, they instead pair every possible positive in the sample shown in the right panel in the figure with selected negatives, since the set of positives is usually quite small.
-Furthermore, for negative examples, they try to select what they term \textit{semi-hard negatives} instead of \textit{hard negatives}, where a \textit{semi-hard negative} has the property that $\|x_a - x_p \|^2 < \|x_a - x_n \|^2$.
+Furthermore, for negative examples, they try to select \textit{semi-hard negatives} instead of \textit{hard negatives}, where a \textit{semi-hard negative} has the property that $\|x_a - x_p \|^2 < \|x_a - x_n \|^2$.
 As shown in the figure~\ref{triplet_selection} a \textit{semi-hard negative} is further from the \textit{anchor} than the \textit{positive}, but is not distant enough.
@@
 There is no explicit attempt to filter out\textit{hard negatives} in the approach.
-The overall idea is that the set of negatives that appear in the nearest neighbor set at input are in fact the most important elements for the network to learn to discriminate from positives.
-Focusing on these elements, regardless of whether they are \textit{hard} or \textit{semi-hard} should lead to better learning.
-
-An ANN-based strategy works better than the batch based triplet selection approach on two counts.
-First, the entire dataset is in fact used in the triplet selection process.
-Second, it yields an important baseline to assess what if any learning was performed by the neural network in mapping input vectors to a different space.
+The overall idea is that the set of negatives that appear in the nearest neighbor set at input are in fact the most important elements for the network to learn to discriminate from positives for a join.
+Focusing on these elements, regardless of whether they are \textit{hard} or \textit{semi-hard} should lead to better discrimination for joins.
+An ANN-based strategy also provides an important baseline to assess what if any learning was performed by the neural network in mapping input vectors to a different space.

### 2018-09-02 paper2018/evaluation.tex
semi hard results

@@
 \multirow{4}{*}{Companies} & Adapted loss & 2.38 & 3.77 & 3.23 & 1.71 \\
+\hline
 & Triplet loss & .39 & .28 & .55 & .09 \\
@@
 
+\subsection{Comparison with Semi-Hard Negatives}
+
+ We hypothesize that training against hard negatives can potentially benefit on datasets with characteristics like those of our people dataset, when compared to training against semi-hard negatives.
+Such datasets have large numbers of hard negatives, as suggested by Figure~\ref{people_characteristics}, which shows positive distances higher on average than negative ones.
+Our strategy of focusing on the hardest negatives, i.e.
+those in the nearest neighborhood, ought to learn a nearest neighborhood with fewer negatives.
+The common technique of using semi-hard negatives will focus more on negatives that are further than already-distant positives, and hence place less emphasis on the nearest neighborhood.
+
+We compare our results to those from training againt semi-hard negatives.
+To compute semi-hard negatives, we took, for each entity, all its positives, and found all negatives in the nearest neighborhood of that positive that are further from the entity than is the positive.
+We made triplets for each such pair of positive and negative.
+We thus chose the hardest semi-hard triplets: the negatives are as close to the positive as possible while still being further from the entity.
+We ran experiments again for adapted loss on our people dataset, changing only the training used; these results are in Table~\ref{hard-semi-hard}.
+
+\begin{table}[ht]
+\caption{Precision and Recall for hard and semi-hard training}
+\label{hard-semi-hard}
+\begin{center}
+\begin{tabular}{|l|r|r|r|}
+\hline
+Training & Recall & Precision@1 & Precision \\
+\hline
+hard & .81 & .81 & .63 \\
+\hline
+semi-hard & .63 & .61 & .43 \\
+\hline
+\end{tabular}
+\end{center}
+\end{table}
+
+ The results show training on hard negatives produces consistently better results, both for precision and recall.
+Hard negative training resulted in recall of 81\% of posiives in the nearest set versus 63\% for semi-hard negatives.
+Precision@1 is similar, with 81\% for hard negatives versus 61\% for semi-hard.
+Overall precision, defined as the fraction of positives closer than any negative is 63\% for hard negatives versus 43\% for semi hard.
+
 \subsection{Generalization Test on Faces}

### 2018-09-02 paper2018/introduction2.tex
massaged paper to add new results

@@
 different surface forms for the same entity  For instance, the name of a person might be represented as \textit{Douglas Adams} and \textit{Douglas Noel Adams} or \textit{John Adams} and \textit{Adams, John}, as shown in Table~\ref{table-example}.
-Similarly,
-ontology alignment can require recognizing distinct surface forms of
+Similarly, ontology alignment can require recognizing distinct surface forms of
 the same entity, especially when ontologies are independently
@@
 As a result, there is a significant amount of research on two aspects of training these networks: (a) how to choose samples for efficient learning, and (b) what constitutes a good loss function.
-In building models for entity names, we had to adapt these techniques for triplet selection and loss functions because matching entity names have different properties than faces, as we describe below.
+In building models for entity names, we had to adapt these techniques for triplet selection and loss functions because matching entity names have more stringent requirements for a join, as we describe below.
 
@@
 Third, it examines whether focusing on hard negatives is really detrimental to deep metric learning, at least for learning to map entity names in vector space.
+As we show empirically in this paper, this technique is better for building models that suitable for use in joins than semi-hard triplet mining.
 
 We also investigated the effect of manipulating multiple local loss functions which have been proposed in the literature for improving deep metric learning, e.g., the triplet loss \cite{DBLP:conf/cvpr/SchroffKP15}, improved loss \cite{Zhang:2016:DML:3088616.3088665}, and angular loss \cite{DBLP:journals/corr/abs-1708-01682} functions.
-For the problem of building models for people's names, we found that an adaptation to the objective function proposed in \cite{DBLP:conf/cvpr/SchroffKP15} was better than three other functions that have been proposed in the literature.
+For the problem of building models for datasets dominated by hard negatives, we found that an adaptation to the objective function proposed in \cite{DBLP:conf/cvpr/SchroffKP15} was better than three other functions that have been proposed in the literature.
 

### 2018-09-02 paper2018/main.tex
removing some equations
massaged paper to add new results

@@
 metric learning, due to the requirements of joins; specifically we describe 
-novel sample selection and loss functions that work for this
-domain.  To evaluate our approach, we used Wikidata as ground truth
+novel sample selection techniques and loss functions that work for this problem.  
+To evaluate our approach, we used Wikidata as ground truth
 and built models for datasets with approximately 1.1M people's names
-(200K identities) and 130K company names (70K identities).  We found
-that vector embeddings allow for joins with precision of .73-.81 and
+(200K identities) and 130K company names (70K identities).  We found developed models that 
+allow for joins with precision@1 of .73-.81 and
 recall of .72-.81.  We make the models available to the community

### 2018-09-02 paper2018/datasets.tex
cutting to size

@@
 The extracted files however contained significant noise that we cleaned up programmatically.
-We describe the clean up rules for people and for companies separately because they were somewhat different.
+We describe the cleansing rules for people and for companies separately because they were somewhat different.
 In the case of people's names, we also augmented the data so the system could learn some common rules that define variants of a person's name.
@@
 We augmented the data with the following rules.
-If the main name for the person in Wikidata had two parts, we created new source forms as follows:
-\begin{itemize}
-\item Last Name, First Name
-\item First Name Initial . Last Name
-\item Last Name , First Name Initial
-\end{itemize}
-If the main name in Wikidata had three parts, we created these additional source forms in addition to the ones listed above:
-\begin{itemize}
-\item First Name Middle Name Initial Last Name
-\item Last Name, First Name Middle Name
-\item Last Name, First Name Middle Initial .
-\end{itemize}
+If the main name for the person in Wikidata had two parts, we created new source forms as follows: (a) Last Name, First Name, (b) First Name Initial .
+Last Name, and (c) Last Name , First Name Initial.
+
+If the main name in Wikidata had three parts, we created these additional source forms in addition to the ones listed above: (a) First Name Middle Name Initial Last Name (b) Last Name, First Name Middle Name (c) Last Name, First Name Middle Initial .
 

### 2018-09-02 paper2018/joins.tex
cleaning up
cutting to size

--- 2018-08-16 paper2018/joins.tex
@@
-\section{Merging datasets with siamese networks}
-\label{joins}
+%\section{Applying deep learning models to joins}
+%\label{join_system}
 
-Section~\ref{join_system} describes our overall system for using siamese networks for joins.  Section~\ref{join_complexity} provides a complexity analysis for this approach.
+%\begin{figure*}[htb]
+%    \centering
+%    \begin{subfigure}[t]{0.24\linewidth}
+%        \centering
+%        \includegraphics[width=.9\linewidth]{join1}
+%        \caption{Columns to be merged}
+%        \label{join1}
+%    \end{subfigure}%
+%    ~ 
+%    \begin{subfigure}[t]{0.24\linewidth}
+%        \centering 
+%        \includegraphics[width=.9\linewidth]{join2}
+%        \caption{Create embeddings for each cell value in each column using the siamese model}
+%        \label{join2}
+%    \end{subfigure}
+%    ~ 
+%    \begin{subfigure}[t]{0.24\linewidth}
+%        \centering 
+%        \includegraphics[width=.9\linewidth]{join3}
+%        \caption{Index embeddings for left table's cell values in a nearest neighbors index}
+%        \label{join3}
+%    \end{subfigure}
+%    ~ 
+%    \begin{subfigure}[t]{0.24\linewidth}
+%        \centering 
+%        \includegraphics[width=.9\linewidth]{join4}
+%        \caption{For each cell in right table, find closest neighbor(s) and merge these rows}
+%        \label{join4}
+%    \end{subfigure}
+%    \caption{Overview of joins using deep learning}
+%    \label{join_fig}
+%\end{figure*}
 
-\section{Applying deep learning models to joins}
-\label{join_system}
-\begin{figure}
-\includegraphics[width=1.0\linewidth]{joins}
-\caption{Applying deep learning models to joins}
-\label{join_fig}
-\end{figure}
-
-Figure~\ref{join_fig} provides an overview of how deep learning models can be used for merging datasets.
-Panel (a) in the figure are the two datasets to be joined.
-The datasets are labeled arbitrarily as a left table and a right table.
-For each cell value in the two columns to be joined, we obtain vector embeddings from the siamese network that was used to estimate distance for same and different surface forms for the same entity.
-Note that although the siamese network has three separate networks, each network within a triplet network is in fact identical to the other two networks because they share weights.
-A single version of the network with learnt weights is used to generate the embeddings for the cell value as shown in panel (b).
-For the left table cell values, vector embeddings are inserted into an approximate nearest neighbors index, as shown in panel (c).
-For each cell value in the right table, vector embeddings are used as `query vectors' to query the approximate nearest neighbors index as shown in panel (d).
+Assuming we have deep learning models that are trained to produce the right distance estimates for alternate surface forms for an entity, the models can be used for a join as follows.
+For each cell value in the two columns to be joined, obtain vector embeddings from the last layer of the network.
+Note that although the siamese network has three separate networks, each network is in fact identical to the other two networks because they share weights.
+For the column cell values, vector embeddings are inserted into an approximate nearest neighbors index.
+For each cell value in the right column, vector embeddings are used as `query vectors' to query the approximate nearest neighbors index.
 In our context, merging the datasets would involve joining the top $k$ rows in the left table that are `closest' in distance to each cell value in the right table.
-Note that the choice of $k$ clearly has a direct effect on the tradeoff between precision and recall, but this is true for any type of join algorithm that is not based on equality.
+Note that the choice of $k$ clearly has a direct effect on the tradeoff between precision and recall, but for most practical uses of join, $k$ is usually very small (typically 1).
+This has implications on what metrics we can use to evaluate joins, as we describe in section \ref{results}.

### 2018-09-02 paper2018/evaluation.tex
hacked tables

@@
 
-\begin{table*}[ht]
-\caption{Precision and Recall for people and companies by loss functions}
+\begin{table}[ht]
+\caption{Precision and Recall by loss functions}
 \label{Evaluation}
+\begin{center}
 \begin{tabular}{l|l|r|r|r|}
 \hline
-Entity Type & Loss Function & Recall & Precision@1 & Precision \\
+Entities & Loss & Recall & \multicolumn{2}{|c|}{Precision} \\
+ & & & @1 & All \\
 \hline
-\multirow{4}{*}{People} & Adapted loss & .81 & .81 & .63 \\
+\multirow{4}{*}{People} & Adapted & .81 & .81 & .63 \\
+\cline{2-5}
+& Triplet & .74 & .84 & .55 \\
+\cline{2-5}
+& Improved & .71 & .52 & .45 \\
+\cline{2-5}
+& Angular & .04 & .09 & .02 \\
 \hline
-& Triplet loss & .74 & .84 & .55 \\
-\hline
-& Improved loss & .71 & .52 & .45 \\
-\hline
-& Angular loss & .04 & .09 & .02 \\
-\hline
-\multirow{4}{*}{Companies} & Adapted loss & .72 & .73 & .64 \\
-& Triplet loss & .75 & .76 & .67 \\
-\hline
-& Improved loss & .74 & .72 & .64 \\
-\hline
-& Angular loss & NA & NA & NA \\
+\multirow{4}{*}{Corps} & Adapted & .72 & .73 & .64 \\
+\cline{2-5}
+& Triplet & .75 & .76 & .67 \\
+\cline{2-5}
+& Improved & .74 & .72 & .64 \\
+\cline{2-5}
+& Angular & NA & NA & NA \\
 \hline
 \end{tabular}
-\end{table*}
+\end{center}
+\end{table}
 
-\begin{table*}[ht]
-\caption{Distance estimates for people and companies after training}
+\begin{table}[ht]
+\caption{Distance estimates after training}
 \label{Evaluation}
+\begin{center}
 \begin{tabular}{l|l|r|r|r|r|}
 \hline
-Entity Type & Loss Function & Mean Pos & Std Pos & Mean Neg & Std Neg \\
+Entities & Loss & \multicolumn{2}{|c|}{Pos} & \multicolumn{2}{|c}{Neg} \\
+& & Mean & Std & Mean & Std \\
 \hline
-\multirow{4}{*}{People} & Adapted loss & 1.59 & 4.04 & 2.44 & 2.45 \\
+\multirow{4}{*}{People} & Adapted & 1.59 & 4.04 & 2.44 & 2.45 \\
+\cline{2-6}
+& Triplet & .46 & .18 & .55 & .10 \\
+\cline{2-6}
+& Improved & .15 & .38 & .21 & .18 \\
+\cline{2-6}
+& Angular & .51 & .25 & .06 & .02 \\
 \hline
-& Triplet loss & .46 & .18 & .55 & .10 \\
-\hline
-& Improved loss & .15 & .38 & .21 & .18 \\
-\hline
-& Angular loss & .51 & .25 & .06 & .02 \\
-\hline
-\multirow{4}{*}{Companies} & Adapted loss & 2.38 & 3.77 & 3.23 & 1.71 \\
-\hline
-& Triplet loss & .39 & .28 & .55 & .09 \\
-\hline
-& Improved loss & .32 & .50 & .42 & 0.19 \\
-\hline
-& Angular loss & NA & NA & NA & NA \\
+\multirow{4}{*}{Corps} & Adapted & 2.38 & 3.77 & 3.23 & 1.71 \\
+\cline{2-6}
+& Triplet & .39 & .28 & .55 & .09 \\
+\cline{2-6}
+& Improved & .32 & .50 & .42 & 0.19 \\
+\cline{2-6}
+& Angular & NA & NA & NA & NA \\
 \hline
 \end{tabular}
-\end{table*}
+\end{center}
+\end{table}
 

### 2018-09-02 paper2018/relatedWork.tex
cutting to size
more cutting

@@
 \section{Related Work}
-Extensions in data management systems for handling joins across different spellings for instance, typically use string similarity algorithms such as edit-distance, Jaro-Winkler and TF-IDF (e.g., \cite{Cohen2003}).
-String matching algorithms often do not work for merging different forms of the same entity because valid transformations of entity names can yield very different strings (e.g., \textit{John Smith} is more similar to \textit{John Adams} than to \textit{Adams, John}, but it is \textit{Adams, John} that is a valid alternate form).
-
-More recently, data driven approaches have emerged as a powerful alternative to string matching techniques for merging data.
-Data driven approaches mine patterns in the data to determine the `rules' for joining a given entity type.
+Extensions in data management systems for handling joins typically use string similarity algorithms such as edit-distance, Jaro-Winkler and TF-IDF (e.g., \cite{Cohen2003}).
+String matching algorithms often do not work for merging different forms of the same entity because valid transformations of entity names can yield very different strings.
+More recently, data driven approaches have emerged as a powerful alternative for merging data.
+Data driven approaches mine patterns to determine the `rules' for joining a given entity type.
 One example of such an approach is illustrated in \cite{He:2015:SJS:2824032.2824036}, which determines which cell values should be joined based on whether those cell values co-occur on the same row across disparate tables in a very large corpus of data.
-Another example of a data driven approach is work by \cite{auto-join-joining-tables-leveraging-transformations} where program synthesis techniques are used to learn the right set of transformations needed to perform the entity matching operation.
-Our approach for merging datasets is much more general than either approach because the mapping function generalizes the set of transformations that are allowed across surface forms of an entity even when the explicit rules for identifying two surface forms as the same are not explicitly expressible as program transforms.
+Another example is work by \cite{auto-join-joining-tables-leveraging-transformations} where program synthesis techniques are used to learn the right set of transformations needed to perform the entity matching operation.
+Our approach for merging datasets is much more general than either approach because the mapping function generalizes the set of transformations that are allowed across surface forms of an entity, even if they cannot be expressed as program transforms.
 
@@
 For the problem of linking tuples, each model that is learnt is specific to the database it was trained on.
-Our contribution is that we developed general purpose embedding models for merging alternate surface forms of key entities such as people and companies leveraged from linked open data.
+Our focus is on techniques that can be used to develop general purpose embedding models for merging alternate surface forms of key entities.
 Once such models are built, they can be applied to joining any two datasets that share that semantic type.
@@
 Metric learning is a well studied problem in the face recognition literature, e.g., \cite{DBLP:conf/cvpr/2014}, \cite{DBLP:conf/cvpr/SchroffKP15}, with a rich literature in triplet mining techniques.
-The closest approach to ours is the use of nearest neighbors algorithms for triplet mining has been applied by \cite{DBLP:journals/corr/KumarHC0D17}, but their focus is on a common practice in the literature which is focusing on mining semi-hard negatives.
-This means that one cannot look at fixed neighborhood sizes in building triplets.
-If all the positives are further away from the anchor than the negatives in a given neighborhood size of $k$, it means that $k$ needs to be expanded until a neighborhood size is found that has the right characteristics (i.e., at least one positive that is closer than the negatives which can be chosen).
+The closest approach to ours is the use of nearest neighbors algorithms for semi-hard triplet mining \cite{DBLP:journals/corr/KumarHC0D17}.
+For semi-hard triplet mining, one cannot look at fixed neighborhood sizes in building triplets.
+If all the positives are further away from the anchor than the negatives in a given neighborhood size of $k$, it means that $k$ needs to be expanded until a neighborhood size is found that has the right characteristics.
 Our focus on `hard negatives' means we can use a fixed $k$ to generate samples.
-At least in the names domain, metric learning with hard negatives is effective.
+An additional benefit is that at least in the names domain, we show that metric learning with hard negatives is more effective than semi-hard mining.
 
 The study of loss function effectiveness in metric learning is also a rich literature, with two basic types of loss functions that have been proposed: (a) local loss functions such as triplet loss \cite{DBLP:conf/cvpr/SchroffKP15}, angular loss \cite{Zhang:2016:DML:3088616.3088665} and improved loss \cite{DBLP:journals/corr/abs-1708-01682}, and (b) loss functions that operate on a more global level across a batch of training examples \cite{NIPS2016_6200}, \cite{songCVPR17}.
-Our focus in this paper is on local loss functions because many of the global loss functions seem to try and accomplish the same objective as hard triplet mining \cite{songCVPR17} using an indirect mechanism to do so.
-Our approach directly mines hard triplets, so there is no need to try to broaden the loss function to a batch.
+Our focus in this paper is on local loss functions because many of the global loss functions seem to try and accomplish the same objective as hard negative triplet mining \cite{songCVPR17} using an indirect mechanism to do so.
+Our approach directly mines hard negative triplets, so there is no need to try to broaden the loss function to a batch.

### 2018-09-02 paper2018/siamese_networks.tex
more cuts

@@
 
-Figure~\ref{siamese_nets} illustrates the siamese network architecture \cite{DBLP:conf/cvpr/SchroffKP15} we used to build a system for merging data.
-As stated earlier, input is initially triples of a name (\textit{anchor}), another name for the same entity (\textit{positive}) and a name of another entity (\textit{negative}).
+Figure~\ref{siamese_nets} illustrates the siamese network architecture \cite{DBLP:conf/cvpr/SchroffKP15} we used to build a system for merging data using Keras and Tensorflow.
+As stated earlier, input is initially triples of a name, i.e., an \textit{anchor}, a \textit{positive} and a \textit{negative}.
 During the tokenization process, we kept punctuation such as `-', `,', and `.' in the name because they are important signals in processing a name.
-For the network, input vectors are computed for each entity assuming a maximum name length of 10 for each entity (i.e., no entity could have a name that spanned more than 10 tokens).
+For the network, input vectors are computed for each entity assuming a maximum name length of 10 for each entity.
 A 100 dimensional character embedding was computed for each token in the entity using pretrained character embeddings \cite{hashimoto-jmt:2017:EMNLP2017}, which resulted in a 100 x 10 character encoding for each name used in a triplet.
-We used a character encoding rather than a word based encoding primarily because many names were missing from word based vector embeddings.
+We used character rather than word embeddings primarily because many names were missing from word based vector embeddings.
 
-These three input vectors from each triplet are fed to three identical networks that share the same weights.
-Weight sharing ensures that the networks learn the same mapping function for any given input vector.
+These three input character embedding vectors were fed to three identical networks that share the same weights.
+Weight sharing ensures that the networks learn the same mapping function.
 In our implementation, each of the three networks had 4 stacked layers of 128 unit Gated Recurrent Units (or GRUs) to capture the sequential nature of the input.
@@
 
-The output of the last layer shown in the Figure~\ref{siamese_nets} as a dark layer produces an output vector embedding for the inputs.
-These are fed to two layers which compute a euclidean distance between the \textit{anchor} and the \textit{positive} elements of a triplet (\textit{positive distance}), and the \textit{anchor} and the \textit{negative} elements of a triplet (\textit{negative distance}).
+The output of the last layer shown in the Figure~\ref{siamese_nets} as a dark layer is the vector embedding for the inputs.
+These are fed to two layers which compute a euclidean distance between the \textit{anchor} and the \textit{positive} (\textit{positive distance}), and the \textit{anchor} and the \textit{negative} (\textit{negative distance}).
 Conceptually, there are two objectives in metric learning, one to minimize \textit{positive distances}, and the other to maximize \textit{negative distances}.
@@
  function that we refer to as `improved loss' in the paper considers
- the distances from the \textit{positive} element of the triplet to
- the \textit{negative} element, and tries to push that
+ the distances from the \textit{positive} to the \textit{negative}, and tries to push that
  difference toward $\alpha$ as well as the distance from
@@
 equations below.  The rough idea is that moving the positive nearer
-and the negative further away each reduce the angle, which we
+and the \textit{negative} further away each reduce the angle, which we
 illustrate in Figure~\ref{angular_loss} with the angle to shrink.
@@
 
-The inspiration for our loss is to separate the effect of the positive
+The inspiration for adapting the original triplet loss is to separate the effect of the positive
 and negative distances as much as possible.  Rather than subtracting
 the negative distance from the positive one, we want to negate the
-negtive distance and then add the two.  To approximate this, we
+negative distance and then add the two.  To approximate this, we
 subtract the negative distance from a margin, and use 0 instead if

### 2018-09-02 paper2018/triplet_selection.tex
more cuts

@@
 \section{Triplet Selection}
-As discussed earlier, deep metric learning for faces is a difficult problem for neural networks to learn because improper sample selection can make it difficult for the network to converge.
+As discussed earlier, deep metric learning for joins is a difficult problem for neural networks to learn because it requires that the discrimination of each anchor from all the other hard negatives.
 We describe a popular approach batch based approach from the face recognition literature first to contrast it with our mechanism for triplet selection.
@@
 
-In Schroff et al.'s work~\cite{DBLP:conf/cvpr/SchroffKP15} they discuss a sample or mini-batch based triplet selection mechanism for training.
-Conceptually, sampling the `right' triplets for fast network learning, as Schroff et al.
-point out requires sampling a set of \textit{hard positives} and a set of \textit{hard negatives}, where a hard positive is defined as $argmax^i \| x_{a} - x_{p}^i \|^2$, where $i$ ranges over all $x_p$ and a hard negative is defined as $argmin^i \| x_{a} - x{_n}^i \|^2$, where $i$ ranges over all $x_n$.
+In Schroff et al.'s work~\cite{DBLP:conf/cvpr/SchroffKP15} they described a mini-batch based triplet selection mechanism for training that has dominated the literature.
+Conceptually, sampling the right triplets for fast network learning requires sampling a set of \textit{hard positives} and a set of \textit{hard negatives}, where a hard positive is defined as $argmax^i \| x_{a} - x_{p}^i \|^2$, where $i$ ranges over all $x_p$ and a hard negative is defined as $argmin^i \| x_{a} - x{_n}^i \|^2$, where $i$ ranges over all $x_n$.
 
@@
 Calculating hard negatives is not possible for all but small datasets.
-As a result, the triplets can be generated either offline, for every n steps, or online, by selecting positive and negative exemplars within a batch of examples.
-In Schroff et al.'s work, they focus on the online generation case.
+As a result, the triplets can be generated by a mechanism illustrated in Figure~\ref{triplet_selection}.
+Instead of focusing on finding \textit{hard positives}, they instead pair every possible positive in the sample shown in the right panel in the figure with selected negatives, since the set of positives is usually quite small.
+Furthermore, for negative examples, they try to select \textit{semi-hard negatives} instead of \textit{hard negatives}, where a \textit{semi-hard negative} has the property that $\|x_a - x_p \|^2 < \|x_a - x_n \|^2$ but by a margin smaller than $\alpha$, as shown in figure ~\ref{triplet_selection}.
 
-Figure~\ref{triplet_selection} shows the triplet selection mechanism used in their work.
-In practice, instead of focusing on finding \textit{hard positives}, they instead pair every possible positive in the sample shown in the right panel in the figure with selected negatives, since the set of positives is usually quite small.
-Furthermore, for negative examples, they try to select \textit{semi-hard negatives} instead of \textit{hard negatives}, where a \textit{semi-hard negative} has the property that $\|x_a - x_p \|^2 < \|x_a - x_n \|^2$.
-As shown in the figure~\ref{triplet_selection} a \textit{semi-hard negative} is further from the \textit{anchor} than the \textit{positive}, but is not distant enough.
+%As shown in the figure~\ref{triplet_selection} a \textit{semi-hard negative} is further from the \textit{anchor} than the \textit{positive}, but is not distant enough.
 That is, the loss function still needs to move it closer to the margin $\alpha$ that is used in the triplet-loss function.

### 2018-09-02 paper2018/introduction2.tex
removing table

@@
 requirement for merging is joining across columns that have
-different surface forms for the same entity  For instance, the name of a person might be represented as \textit{Douglas Adams} and \textit{Douglas Noel Adams} or \textit{John Adams} and \textit{Adams, John}, as shown in Table~\ref{table-example}.
+different surface forms for the same entity  For instance, the name of a person might be represented as \textit{Douglas Adams} and \textit{Douglas Noel Adams} or \textit{John Adams} and \textit{Adams, John}.
 Similarly, ontology alignment can require recognizing distinct surface forms of
@@
 For the problem of building models for datasets dominated by hard negatives, we found that an adaptation to the objective function proposed in \cite{DBLP:conf/cvpr/SchroffKP15} was better than three other functions that have been proposed in the literature.
-
-\begin{table}[!htb]
-    \caption{Example of a merge problem}
-    \begin{subtable}{.5\linewidth}
-      \centering
-        \caption{Table A}
-        \begin{tabular}{|l|l|}
-          \hline
-           Dept & Name \\
-           \hline
-           1    & Douglas Adams \\
-           2    & John Adams \\
-           3  & Douglas Bard \\
-           \hline
-        \end{tabular}
-    \end{subtable}%
-    \begin{subtable}{.5\linewidth}
-      \centering
-        \caption{Table B}
-        \begin{tabular}{|l|l|}
-          \hline
-           Name & Salary \\
-           \hline
-           Douglas Noel Adams & 2000 \\
-           Adams, John & 3000 \\
-           John Smith & 3000 \\
-           \hline
-        \end{tabular}
-    \end{subtable}
-    \label{table-example}
-\end{table}
+%
+%\begin{table}[!htb]
+%    \caption{Example of a merge problem}
+%    \begin{subtable}{.5\linewidth}
+%      \centering
+%        \caption{Table A}
+%        \begin{tabular}{|l|l|}
+%          \hline
+%           Dept & Name \\
+%           \hline
+%           1    & Douglas Adams \\
+%           2    & John Adams \\
+%           3  & Douglas Bard \\
+%           \hline
+%        \end{tabular}
+%    \end{subtable}%
+%    \begin{subtable}{.5\linewidth}
+%      \centering
+%        \caption{Table B}
+%        \begin{tabular}{|l|l|}
+%          \hline
+%           Name & Salary \\
+%           \hline
+%           Douglas Noel Adams & 2000 \\
+%           Adams, John & 3000 \\
+%           John Smith & 3000 \\
+%           \hline
+%        \end{tabular}
+%    \end{subtable}
+%    \label{table-example}
+% \end{table}
 

### 2018-09-02 paper2018/triplet_selection.tex
adding minor changes

@@
 \subsection{Metric Based Triplet Selection}
-Although the computation of there is $argmax^i \| x_{a} - x_{p}^i \|^2$ and $argmin^i \| x_{a} - x{_n}^i \|^2$ is infeasible because it involves quadratic comparisons within a dataset, we observe that the use of approximate nearest neighbor (ANN) indexes can actually make this problem tractable for the selection of triples.
-
+For the problem of joins, we ideally want the anchor and all of its positives to be clustered closest together and separated from the nearest negatives as clearly as possible.
 Approximate nearest neighbor indexes are highly efficient methods for selecting the top-K neighbors of a given vector by Euclidean distance, cosine similarity or other distance metrics.
 They are based on space partitioning algorithms, such as \textit{k-d trees}, where the vector space is iteratively bisected into two disjoint regions.
-Finding the nearest neighbors of a vector involves traversal of the tree to a leaf by evaluating the queried vector at each split point in the tree.
-Depending on the position of the vector within the space bounded by a split point, it may need to traverse both points at a split node.
-However, large portions of the tree (and hence most vectors in the dataset) never get compared to the queried vector.
 The average complexity to query the vectors of a neighbor is $O(log N)$ where N is the number of vectors in the dataset.
@@
 Assuming one has the entire dataset indexed in an ANN index, the problem of triplet selection can be simplified by asking the ANN index for the top k-nearest neighbors of an \textit{anchor}, where k is given by the number of triplets that one desires to generate for each anchor.
-As in earlier work, selection of \textit{hard positives} is not really relevant because all positive data should be used to teach the network the right function.
+As in earlier work, selection of \textit{hard positives} is not relevant because all positive data should be used to teach the network the right function.
 Selection of negatives is the set of all nearest neighbors that are \textit{negatives}.

### 2018-09-02 paper2018/evaluation.tex
scriptsize tables
adding minor changes
fixed typo

@@
-\section{Evaluation}
+\section{Experiments}
 \label{results}
@@
 \begin{center}
-\begin{tabular}{l|l|r|r|r|}
+%{\scriptsize
+\begin{tabular}{|l|l|r|r|r|}
 \hline
@@
 \cline{2-5}
-& Angular & NA & NA & NA \\
+& Angular & .26 & .32 & .22 \\
 \hline
-\end{tabular}
+\end{tabular} %}
 \end{center}
@@
 \begin{center}
-\begin{tabular}{l|l|r|r|r|r|}
+%{\scriptsize 
+\begin{tabular}{|l|l|r|r|r|r|}
 \hline
-Entities & Loss & \multicolumn{2}{|c|}{Pos} & \multicolumn{2}{|c}{Neg} \\
+Entities & Loss & \multicolumn{2}{|c|}{Pos} & \multicolumn{2}{|c|}{Neg} \\
 & & Mean & Std & Mean & Std \\
@@
 \cline{2-6}
-& Improved & .32 & .50 & .42 & 0.19 \\
+& Improved & .32 & .50 & .42 & .19 \\
 \cline{2-6}
-& Angular & NA & NA & NA & NA \\
+& Angular & .07 & .04 & .04 & .01 \\
 \hline
-\end{tabular}
+\end{tabular}%}
 \end{center}
@@
 
-We compare our results to those from training againt semi-hard negatives.
+We compare our results to those from training against semi-hard negatives.
 To compute semi-hard negatives, we took, for each entity, all its positives, and found all negatives in the nearest neighborhood of that positive that are further from the entity than is the positive.
@@
 \begin{center}
+%{\scriptsize
 \begin{tabular}{|l|r|r|r|}
@@
 \hline
-\end{tabular}
+\end{tabular}%}
 \end{center}

### 2018-09-03 paper2018/evaluation.tex
adding eval

@@
 \label{results}
-In building the models, we employed early stopping using the usual metric of accuracy of the validation data, and we performed hyper-parameter tuning using grid search varying margins for our loss function from 1-20.
+In building the models, we employed early stopping using the usual metric of accuracy of the validation data, and we performed hyper-parameter tuning using grid search varying margins for the adapted loss function from 1-20.
 Accuracy was defined as the percentage of validation triples where positive distances from anchor were less than negative distances from anchor.
-For all our runs, test accuracy as measured by this metric ranged in the 9-- range.
+For all our runs, test accuracy as measured by this metric ranged in the 96-97\% range (CAN WE CONFIRM THIS ON OUR RUNS?).
 Table \ref{Evaluation} shows the results for the people and company datasets, run with a fixed $k$ of 20 neighbors.
 Because we compared across different losses, the results are categorized by each loss function for each dataset we tested.
-For all the results reported here, we ran multiple runs because of the stochastic nature of neural network models; the results here are representative of what we saw across runs.
+For all the results reported here, we ran multiple runs because of the stochastic nature of neural network models; the results here are means across two runs.
 
@@
 \item \textbf{Recall}.  Recall is measured by the percentage of positives in the nearest neighbor set of each anchor.
-\item \textbf{Precision@1}.  Precision@1 is measured by the percentage of anchors with the very nearest neighbor being a positive.
-\item \textbf{Precision}.  Precision is measured by the percentage of all positives for all anchors that were closer to the anchor than any other negative.
+\item \textbf{Precision@1}.
+Precision@1 is measured by the percentage of anchors with the very nearest neighbor being a positive.
+As pointed out earlier, this is an important metric for assessing join performance in a majority of cases.
+\item \textbf{Precision}.  Precision is measured by the percentage of all positives for each anchor that were closer to the anchor than any other negative relative to the size of the positive set.
 \end{itemize}
@@
 \caption{Precision and Recall by loss functions}
-\label{Evaluation}
+\label{precision_recall}
 \begin{center}
@@
 \caption{Distance estimates after training}
-\label{Evaluation}
+\label{distance}
 \begin{center}
@@
 \subsection{Performance for Joins}
-
 For fuzzy joins, we need both precision and recall to be high.
@@
 Without high precision, a join will mistakenly join many inappropriate names.
-To quantify recall, we measure, for each loss function.
-The numbers for our adapted loss function are 81\% for people and 72\% for companies, so a join could capture most similar names.
+To quantify recall, we measured, for each loss function.
+The numbers for our adapted loss function were 81\% for people and 72\% for companies, so a join could capture most similar names.
+Furthermore, the adapted loss function showed better performance on the harder people dataset, but there was a small advantage for the triplet loss function in the easier company data, see Table \ref{precision_recall}.
+Furthermore, it appears that triplet loss and its variants are better than angular loss for learning this problem.
 
- Precision is a little trickier to define, but one way is to measure how many true matches we get in the neighborhood before seeing a single mistake, i.e.
+ Precision is a little trickier to define, but one way is to measure it is to examine how many true matches we get in the neighborhood of each anchor before seeing a single mistake, i.e.
 a match that should not be there.
@@
 For that, our loss yields 81\% for people and 73\% for companies.
-Note that measuring precision for larger neighborhoods is tricky, since not every name has more than one name for the same entity.
+Note that measuring precision for larger neighborhoods is tricky, since not every name has more than one name for the same entity (JULIAN I DONT UNDERSTAND WHAT THIS MEANS).
 
@@
  We also assessed our learning mechanism more directly by examining how the nearest neighborhood changed from before to after training.
-As can be seen from Table \ref{Evaluation}, recall is improved greatly, with the bigger change for people, in which case it improves from 3\% to 80\%.
+As can be seen from Table \ref{distance}, recall is improved greatly, with the bigger change for people, in which case it improves from 3\% to 80\%.
 For companies, it is from 17\% to 72\%.
@@
 Precision at one improves from 10\% to 81\% for people and from 26\% to 73\% for companies.
-In both these cases, before training the results are basically noise even though embeddings are used for context, but training has made the results usable.
+In both these cases, demonstrable training occurred.
 
 \subsection{Comparison with Semi-Hard Negatives}
-
- We hypothesize that training against hard negatives can potentially benefit on datasets with characteristics like those of our people dataset, when compared to training against semi-hard negatives.
+We hypothesized that training against hard negatives can potentially benefit on datasets with characteristics like those of our people dataset, when compared to training against semi-hard negatives.
 Such datasets have large numbers of hard negatives, as suggested by Figure~\ref{people_characteristics}, which shows positive distances higher on average than negative ones.
-Our strategy of focusing on the hardest negatives, i.e.
+%Our strategy of focusing on the hardest negatives, i.e.
 those in the nearest neighborhood, ought to learn a nearest neighborhood with fewer negatives.
@@
 
-We compare our results to those from training against semi-hard negatives.
-To compute semi-hard negatives, we took, for each entity, all its positives, and found all negatives in the nearest neighborhood of that positive that are further from the entity than is the positive.
+We therefore compared the hard negative triplet selection mechanism directly to training against semi-hard negatives.
+To compute semi-hard negatives, we took, for each entity, all its positives, and found all negatives in the nearest neighborhood of that positive that were further from the entity than is the positive.
 We made triplets for each such pair of positive and negative.
@@
 \subsection{Generalization Test on Faces}
-
 We have demonstrated that our strategy for joins could work well for textual names of people and companies, but the technique could potentially work for any kind of data for which a vector embedding can be made.
 To test how well that works, we evaluated two existing models for face recognition that were trained with the same approaches defined in the \cite{DBLP:conf/cvpr/SchroffKP15} on two different datasets, VGGFace2 \cite{DBLP:conf/fgr/CaoSXPZ18}, and CasiaWebFace \cite{DBLP:conf/cvpr/SchroffKP15}.
-We took the existing trained model at \url{https://github.com/davidsandberg/facenet}, and extracted the output embeddings for faces from the LFW test set \cite{Huang2012a} using these embeddings.
+We took the two open sourced models \footnote{\url{https://github.com/davidsandberg/facenet}}, and extracted the output embeddings for faces from the LFW test set \cite{Huang2012a} using these embeddings.
 We put these output embeddings into an ANN structure, and computed our metrics on that.
-Recall of the same face was remarkably similar to our results for names, getting 80\% on the VGGFace2 dataset, and 76\% for the Casia Web Face dataset.
+Recall of the same face was remarkably similar to our results for names, getting 80\% on the VGGFace2 dataset, and 76\% for the Casia Web Face dataset, as was precision (62\% for Casia Web faces, 68\% for VGGFace2).
 However, we found precision at one was much lower on both datasets at 23\% for VGGFace2 and 21\% for Casia Web faces.
 
-We hypothesize that one reason for lower precision at one is the nature of the training.
-Training on pre-built LFW model focused on what they call semi-hard negatives, which are triplets for which the negative is further from training anchor than the corresponding positive.
-Thus, negatives which are very close to an anchor may get less training to move them away from that anchor.
-Our training focuses on nearby negatives, which allows them to be moved.
-This is clearly a hypothesis that needs to be tested further.
+Our results contrasting hard versus semi-hard training suggest that one reason for lower precision at one could be the nature of the training.
+However, the dataset is sufficiently different that this hypothesis that needs to be tested further empirically.
 
-\subsection{Discussion}
+\subsection{Conclusion and Future Work}
+We have described techniques that are useful to build deep learning models that can be used effectively for joins, and we will provide these models to the community for use.
+Being able to build generic models that can be used for merging datasets seems to be a plausible idea, with caveats in terms of how one builds these models.
 
- Our results and our comparison with faces seems to show that training on hard negatives does not compromise recall overall and can boost precision for near neighbors.
+%Our results and our comparison with faces seems to show that training on hard negatives does not compromise recall overall and can boost precision for near neighbors.
 Since joins will be most effective and efficient by focusing on a small, precise neighborhood, training on hard negatives may in fact be a useful addition.

### 2018-09-03 paper2018/introduction2.tex
minor fixes

@@
 requirement for merging is joining across columns that have
-different surface forms for the same entity  For instance, the name of a person might be represented as \textit{Douglas Adams} and \textit{Douglas Noel Adams} or \textit{John Adams} and \textit{Adams, John}.
+different surface forms for the same entity.
+For instance, the name of a person might be represented as \textit{Douglas Adams} and \textit{Douglas Noel Adams} or \textit{D.
+Adams} and \textit{Adams, Douglas}.
 Similarly, ontology alignment can require recognizing distinct surface forms of
@@
 The idea of focusing on semi-hard negatives is to avoid mining noisy regions of the embedding space.
-For matching across entity names, most positive forms for the entity names are actually substantially further away from the anchor than are negatives, as we show empirically in this paper.
+However, for matching across entity names, most positive forms for the entity names are actually substantially further away from the anchor than are negatives, as we show empirically in this paper.
 In other words, `hard negatives' dominate the space, and are the norm.
-Our approach to the problem of triplet mining for this problem was to use an approximate nearest neighbors algorithm to choose negatives for training that were in the nearest neighbor set, which means that most of the time, our negatives are `hard negatives', where the negative is closer to the anchor than positives.
+Our approach to the problem of triplet mining was therefore to use an approximate nearest neighbors algorithm to choose negatives for training that were in the nearest neighbor set, which means that most of the time, our negatives are `hard negatives', where the negative is closer to the anchor than positives.
 This approach has three key benefits.
@@
 
-We also investigated the effect of manipulating multiple local loss functions which have been proposed in the literature for improving deep metric learning, e.g., the triplet loss \cite{DBLP:conf/cvpr/SchroffKP15}, improved loss \cite{Zhang:2016:DML:3088616.3088665}, and angular loss \cite{DBLP:journals/corr/abs-1708-01682} functions.
-For the problem of building models for datasets dominated by hard negatives, we found that an adaptation to the objective function proposed in \cite{DBLP:conf/cvpr/SchroffKP15} was better than three other functions that have been proposed in the literature.
+We also investigated the effect of using multiple local loss functions which have been proposed in the literature for improving deep metric learning, e.g., the triplet loss \cite{DBLP:conf/cvpr/SchroffKP15}, improved loss \cite{Zhang:2016:DML:3088616.3088665}, and angular loss \cite{DBLP:journals/corr/abs-1708-01682} functions.
+For the problem of building models for datasets dominated by hard negatives, we found that an adaptation to the triplet loss function proposed in \cite{DBLP:conf/cvpr/SchroffKP15} was better than three other functions that have been proposed in the literature.
 %

### 2018-09-03 paper2018/main.tex
minor fixes

@@
 together.  To build these models, we had to adapt techniques from
-metric learning, due to the requirements of joins; specifically we describe 
+metric learning due to the requirements of joins; specifically we describe 
 novel sample selection techniques and loss functions that work for this problem.  

### 2018-09-03 paper2018/siamese_networks.tex
mess with figures
figures
minor changes

@@
 
-Figure~\ref{siamese_nets} illustrates the siamese network architecture \cite{DBLP:conf/cvpr/SchroffKP15} we used to build a system for merging data using Keras and Tensorflow.
+Figure~\ref{siamese_nets} illustrates the siamese network architecture \cite{DBLP:conf/cvpr/SchroffKP15} we implemented to build the models using Keras and Tensorflow.
 As stated earlier, input is initially triples of a name, i.e., an \textit{anchor}, a \textit{positive} and a \textit{negative}.
@@
 
-\begin{figure*}[htb]
+\begin{figure}[htb]
     \centering
-    \begin{subfigure}[t]{0.23\textwidth}
+    \begin{subfigure}[t]{0.3\linewidth}
         \centering
-        \includegraphics[width=.9\linewidth]{schroff_triplet}
+        \includegraphics[width=\linewidth]{schroff_triplet}
         \caption{Triplet loss}
@@
     ~ 
-    \begin{subfigure}[t]{0.23\textwidth}
+    \begin{subfigure}[t]{0.3\linewidth}
         \centering 
-        \includegraphics[width=.9\linewidth]{modified_loss}
+        \includegraphics[width=\linewidth]{modified_loss}
         \caption{Modified loss}
@@
     ~ 
-    \begin{subfigure}[t]{0.23\textwidth}
+    \begin{subfigure}[t]{0.3\linewidth}
         \centering 
-        \includegraphics[width=.9\linewidth]{angular_loss}
+        \includegraphics[width=\linewidth]{angular_loss}
         \caption{Angular loss}
@@
     \caption{Loss functions}
-\end{figure*}
+\end{figure}
 

### 2018-09-04 paper2018/evaluation.tex

@@
 Accuracy was defined as the percentage of validation triples where positive distances from anchor were less than negative distances from anchor.
-For all our runs, test accuracy as measured by this metric ranged in the 96-97\% range (CAN WE CONFIRM THIS ON OUR RUNS?).
+For all our runs, test accuracy as measured by this metric ranged in the 97-99\% range for the people dataset and 92-94\% companies dataset for all losses except angular loss which was poor throughout.
 Table \ref{Evaluation} shows the results for the people and company datasets, run with a fixed $k$ of 20 neighbors.
@@
 We put these output embeddings into an ANN structure, and computed our metrics on that.
-Recall of the same face was remarkably similar to our results for names, getting 80\% on the VGGFace2 dataset, and 76\% for the Casia Web Face dataset, as was precision (62\% for Casia Web faces, 68\% for VGGFace2).
-However, we found precision at one was much lower on both datasets at 23\% for VGGFace2 and 21\% for Casia Web faces.
-
-Our results contrasting hard versus semi-hard training suggest that one reason for lower precision at one could be the nature of the training.
-However, the dataset is sufficiently different that this hypothesis that needs to be tested further empirically.
+Note that for face datasets there is a greater number of variability of faces per identity with a maximum of 529 faces for a single identity.
+We adjusted neighborhood length to a maximum of 20 or the number of expected neighbors in our experiments for each face.
+Recall was 91\% on the VGGFace2 dataset, and 87\% for the Casia Web Face dataset.
+Precision@1 was 95\% for VGGFace2 and 93\% for Casia Web faces.
+Overall precision was 91\% for VGGFace2 and Casia Web faces was 87\%.
+These results suggest that existing models can in fact be re-purposed for joins.
+We point out that the face models seem better in terms of performance compared to our model for names but there are significant differences in the data characteristics for training.
+The names data had a lot fewer positives per identity (mostly 2.2 for companies, and 4.69 for people).
+VGGFace2 has 362.6 faces per identity, and 500,000 images for 10,000 identities in CasiaWebFace.
 

### 2018-09-04 paper2018/evaluation.tex
added a line about company data

@@
 For that, our loss yields 81\% for people and 73\% for companies.
-Note that measuring precision for larger neighborhoods is tricky, since not every name has more than one name for the same entity (JULIAN I DONT UNDERSTAND WHAT THIS MEANS).
 
@@
 We ran experiments again for adapted loss on our people dataset, changing only the training used; these results are in Table~\ref{hard-semi-hard}.
+The same comparison on the company dataset showed no difference, mostly because company data seems easier and seems more immune to differences in loss functions or training regimens.
 

### 2018-09-04 paper2018/main.tex
fixes
fixing numbers

@@
 To evaluate our approach, we used Wikidata as ground truth
-and built models for datasets with approximately 1.1M people's names
+and built models from datasets with approximately 1.1M people's names
 (200K identities) and 130K company names (70K identities).  We found developed models that 
-allow for joins with precision@1 of .73-.81 and
-recall of .72-.81.  We make the models available to the community
+allow for joins with precision@1 of .75-.81 and
+recall of .74-.81.  We make the models available to the community
 for aligning people or companies across multiple datasets.  

### 2018-09-04 paper2018/evaluation.tex
wording

@@
 \hline
-\multirow{4}{*}{Corps} & Adapted & .72 & .73 & .64 \\
+\multirow{4}{*}{Corps} & Adapted & .74 & .73 & .66 \\
 \cline{2-5}
-& Triplet & .75 & .76 & .67 \\
+& Triplet & .74 & .75 & .67 \\
 \cline{2-5}
-& Improved & .74 & .72 & .64 \\
+& Improved & .74 & .72 & .65 \\
 \cline{2-5}
@@
 \hline
-\multirow{4}{*}{People} & Adapted & 1.59 & 4.04 & 2.44 & 2.45 \\
+\multirow{4}{*}{People} & Adapted & 1.59 & 4.05 & 2.44 & 2.45 \\
 \cline{2-6}
@@
 \hline
-\multirow{4}{*}{Corps} & Adapted & 2.38 & 3.77 & 3.23 & 1.71 \\
+\multirow{4}{*}{Corps} & Adapted & 2.39 & 3.62 & 3.59 & 2.72 \\
 \cline{2-6}
-& Triplet & .39 & .28 & .55 & .09 \\
+& Triplet & .43 & .31 & .59 & .09 \\
 \cline{2-6}
@@
 Without high precision, a join will mistakenly join many inappropriate names.
-To quantify recall, we measured, for each loss function.
 The numbers for our adapted loss function were 81\% for people and 72\% for companies, so a join could capture most similar names.
-Furthermore, the adapted loss function showed better performance on the harder people dataset, but there was a small advantage for the triplet loss function in the easier company data, see Table \ref{precision_recall}.
-Furthermore, it appears that triplet loss and its variants are better than angular loss for learning this problem.
+For people, the adapted loss function showed overall better performance than triplet loss (see Table \ref{precision_recall}).
+Furthermore, it appears that triplet loss outperformed improved loss, which in turn is better than angular loss for learning this problem.
+On the other hand, for companies the only significant difference was that angular was worse.
 

### 2018-09-04 paper2018/evaluation.tex
conclusions

@@
 
-\subsection{Conclusion and Future Work}
-We have described techniques that are useful to build deep learning models that can be used effectively for joins, and we will provide these models to the community for use.
-Being able to build generic models that can be used for merging datasets seems to be a plausible idea, with caveats in terms of how one builds these models.
-
-%Our results and our comparison with faces seems to show that training on hard negatives does not compromise recall overall and can boost precision for near neighbors.
-Since joins will be most effective and efficient by focusing on a small, precise neighborhood, training on hard negatives may in fact be a useful addition.
+\section{Conclusion and Future Work}
+We show that deep learning models can be used effectively for joins, and we will provide these models to the community for use.
+In the future, we will evaluate our work on other entity types and continue to explore refinements of both loss functions and triplet selection.

### 2018-09-04 paper2018/relatedWork.tex
global loss wording

@@
 The study of loss function effectiveness in metric learning is also a rich literature, with two basic types of loss functions that have been proposed: (a) local loss functions such as triplet loss \cite{DBLP:conf/cvpr/SchroffKP15}, angular loss \cite{Zhang:2016:DML:3088616.3088665} and improved loss \cite{DBLP:journals/corr/abs-1708-01682}, and (b) loss functions that operate on a more global level across a batch of training examples \cite{NIPS2016_6200}, \cite{songCVPR17}.
-Our focus in this paper is on local loss functions because many of the global loss functions seem to try and accomplish the same objective as hard negative triplet mining \cite{songCVPR17} using an indirect mechanism to do so.
-Our approach directly mines hard negative triplets, so there is no need to try to broaden the loss function to a batch.
+Since we do not use batches in triplet selection, but rather neighborhoods, our loss function also operates with a global perspective.

### 2018-09-04 paper2018/evaluation.tex
wording
stuff

@@
 As pointed out earlier, this is an important metric for assessing join performance in a majority of cases.
-\item \textbf{Precision}.  Precision is measured by the percentage of all positives for each anchor that were closer to the anchor than any other negative relative to the size of the positive set.
+\item \textbf{Precision}.  Precision is measured by the fractions of all positives for each anchor that were closer to that anchor than was any negative.
 \end{itemize}
@@
 We point out that the face models seem better in terms of performance compared to our model for names but there are significant differences in the data characteristics for training.
-The names data had a lot fewer positives per identity (mostly 2.2 for companies, and 4.69 for people).
+The names data had a lot fewer positives per identity.
 VGGFace2 has 362.6 faces per identity, and 500,000 images for 10,000 identities in CasiaWebFace.

### 2018-09-04 paper2018/relatedWork.tex
stuff

@@
 
-The study of loss function effectiveness in metric learning is also a rich literature, with two basic types of loss functions that have been proposed: (a) local loss functions such as triplet loss \cite{DBLP:conf/cvpr/SchroffKP15}, angular loss \cite{Zhang:2016:DML:3088616.3088665} and improved loss \cite{DBLP:journals/corr/abs-1708-01682}, and (b) loss functions that operate on a more global level across a batch of training examples \cite{NIPS2016_6200}, \cite{songCVPR17}.
+The study of loss function effectiveness in metric learning is also a rich literature, with two basic types of loss functions that have been proposed: (a) local loss functions such as triplet loss \cite{DBLP:conf/cvpr/SchroffKP15}, angular loss \cite{Zhang:2016:DML:3088616.3088665} and improved loss \cite{DBLP:journals/corr/abs-1708-01682}, and (b) loss functions that operate on a more global level across a batch of training examples \cite{NIPS2016_6200}, \cite{DBLP:conf/cvpr/SongXJS16}, \cite{songCVPR17}.
 Since we do not use batches in triplet selection, but rather neighborhoods, our loss function also operates with a global perspective.

### 2018-09-04 paper2018/triplet_selection.tex
stuff

@@
 Implementations exist now for fast, memory-efficient ANN indexes that scale up to a billion vectors \cite{JDH17} using techniques to compress vectors in memory efficiently.
-In our work, we used the Annoy ANN implementation \cite{annoy_git} in our work which is based on the refinements to \textit{k-d trees} ideas described in \cite{ann_paper}.
+In our work, we used the Annoy ANN implementation \footnote{\url{https://github.com/spotify/annoy}} in our work which is based on the refinements to \textit{k-d trees} ideas described in \cite{ann_paper}.
 

### 2018-09-04 paper2018/evaluation.tex
spelling
fixed table ref

@@
 For all our runs, test accuracy as measured by this metric ranged in the 97-99\% range for the people dataset and 92-94\% companies dataset for all losses except angular loss which was poor throughout.
-Table \ref{Evaluation} shows the results for the people and company datasets, run with a fixed $k$ of 20 neighbors.
+Table \ref{precision_recall} shows the results for the people and company datasets, run with a fixed $k$ of 20 neighbors.
 Because we compared across different losses, the results are categorized by each loss function for each dataset we tested.
@@
  The results show training on hard negatives produces consistently better results, both for precision and recall.
-Hard negative training resulted in recall of 81\% of posiives in the nearest set versus 63\% for semi-hard negatives.
+Hard negative training resulted in recall of 81\% of positives in the nearest set versus 63\% for semi-hard negatives.
 Precision@1 is similar, with 81\% for hard negatives versus 61\% for semi-hard.

### 2018-09-04 paper2018/datasets.tex
new figures
yehuda's edits

@@
 If we detected a title in the name referring to royalty or qualifiers or Roman numerals which strongly indicated royalty, we dropped the name.
-We also removed punctuations such as '...', and anything that was placed in parenthesese because they were irrelevant to the name (e.g.
+We also removed punctuations such as '...', and anything that was placed in parenthesese because they were not part of the name (e.g.
 a qualification such as the son of Jacob might appear in parentheses after a name).
@@
 We augmented the data with the following rules.
-If the main name for the person in Wikidata had two parts, we created new source forms as follows: (a) Last Name, First Name, (b) First Name Initial .
+If the main name for the person in Wikidata had two parts, we created new source forms as follows: (a) Last Name , First Name, (b) First Name Initial .
 Last Name, and (c) Last Name , First Name Initial.
 
-If the main name in Wikidata had three parts, we created these additional source forms in addition to the ones listed above: (a) First Name Middle Name Initial Last Name (b) Last Name, First Name Middle Name (c) Last Name, First Name Middle Initial .
+If the main name in Wikidata had three parts, we created these additional source forms in addition to the ones listed above: (a) First Name Middle Name Initial Last Name (b) Last Name , First Name Middle Name (c) Last Name , First Name Middle Initial .
 
@@
 
-\begin{figure*}[htb]
+\begin{figure}[htb]
     \centering
-    \begin{subfigure}[t]{0.5\textwidth}
+    \begin{subfigure}[t]{0.23\textwidth}
         \centering
-        \includegraphics[width=.9\linewidth]{people_recall}
+        \includegraphics[width=.95\linewidth]{people_recall}
         \caption{Recall rate as a function of neighborhood size}
@@
     ~ 
-    \begin{subfigure}[t]{0.5\textwidth}
+    \begin{subfigure}[t]{0.23\textwidth}
         \centering 
-        \includegraphics[width=.9\linewidth]{people_distances}
-        \caption{Mean negative distance from anchor as a function of neighborhood size}
+        \includegraphics[width=.95\linewidth]{people_distances}
+        \caption{Mean negative distance as a function of neighborhood size}
         \label{modified_loss}
@@
 \label{people_characteristics}
-\end{figure*}
+\end{figure}
 
-\begin{figure*}[htb]
+\begin{figure}[htb]
     \centering
-    \begin{subfigure}[t]{0.5\textwidth}
+    \begin{subfigure}[t]{0.23\textwidth}
         \centering
-        \includegraphics[width=.9\linewidth]{company_recall}
+        \includegraphics[width=.99\linewidth]{company_recall}
         \caption{Recall rate as a function of neighborhood size}
@@
     ~
-    \begin{subfigure}[t]{0.5\textwidth}
+    \begin{subfigure}[t]{0.23\textwidth}
         \centering
-        \includegraphics[width=.9\linewidth]{company_distances}
+        \includegraphics[width=.99\linewidth]{company_distances}
         \caption{Mean negative distance from anchor as a function of neighborhood size}
@@
 \label{company_characteristics}
-\end{figure*}
+\end{figure}

### 2018-09-05 paper2018/datasets.tex
fixing stuff

@@
 Specifically, we used the \textit{also known as} property from Wikidata to get alternate forms for the same entity name for people as well as companies.
-For company names, we augmented the names and surface forms in Wikidata with data from the SEC \footnote{\url{https://www.sec.gov/dera/data/financial-statement-and-notes-data-set.html}}, which has former and more recent names for companies.
-There were 213106 names for people from the specific dump we extracted, and 70946 names for companies.
+For company names, we augmented the names and surface forms in Wikidata with data from the SEC\footnote{\url{https://www.sec.gov/dera/data/financial-statement-and-notes-data-set.html}}, which has former and more recent names for companies.
+There were 213,106 names for people from the specific dump we extracted, and 70,946 names for companies.
 The extracted files and the cleansing code are available on our repository.
@@
 After cleansing, if a name had no alternate surface forms, they were dropped.
-This resulted in 40555 company names with an average of 2.2 names each, and 195422 people's names with an average of 4.69 names each.
+This resulted in 40,555 company names with an average of 2.2 names each, and 195,422 people's names with an average of 4.69 names each.
 Using the triplet selection algorithm we created a set of 10.9 million and 1.04 million triplets for people and companies at training.
@@
 Figure \ref{people_characteristics} shows the results for the people data.
-First, recall rate of positives in the nearest neighbor set was very low at 3\%, and it increased only to 6\%.
+First, recall rate of positives in the nearest neighbor set was very low at 3\%, and it increased only to 6\% at a neighborhood size of 1500.
 The difficulty of the problem for reconciling people's names is further highlighted by the distance data.

### 2018-09-05 paper2018/evaluation.tex
fixing stuff

@@
 Without high precision, a join will mistakenly join many inappropriate names.
-The numbers for our adapted loss function were 81\% for people and 72\% for companies, so a join could capture most similar names.
+The numbers for the adapted loss function were 81\% for people and 74\% for companies, so a join could capture most similar names.
 For people, the adapted loss function showed overall better performance than triplet loss (see Table \ref{precision_recall}).
@@
 That metric gives a picture of how many names would be correctly found, on average, by a join.
-Our loss function gives 62\% by this metric for people and 64\% for companies, so about two thirds of recalled names would be found before finding a single error.
+Adapted loss is at 63\% by this metric for people and 66\% for companies, so about two thirds of recalled names would be found before finding a single error.
 Since every name has at least one other name for the same entity, we also measure precision at 1, which is the probability that the very nearest neighbor is a true match.
-For that, our loss yields 81\% for people and 73\% for companies.
+For that, the very best performance we get is 84\% for people and 75\% for companies.
 
@@
  We also assessed our learning mechanism more directly by examining how the nearest neighborhood changed from before to after training.
-As can be seen from Table \ref{distance}, recall is improved greatly, with the bigger change for people, in which case it improves from 3\% to 80\%.
-For companies, it is from 17\% to 72\%.
+As can be seen from Table \ref{distance}, recall is improved greatly, with the bigger change for people, in which case it improves from 3\% to 81\%.
+For companies, it is from 16\% to 74\%.
 Thus training is clearly effective in moving actual names for the same entity into the nearest neighbors.
 For precision, the fraction of true matches found before the first error improves from 16\% to 73\% for people and 16\% to 64\% for companies.
-Precision at one improves from 10\% to 81\% for people and from 26\% to 73\% for companies.
+Precision@1 improves from 10\% to 81\% for people and from 26\% to 75\% for companies.
 In both these cases, demonstrable training occurred.

### 2018-09-05 paper2018/introduction2.tex
fixing stuff

@@
 different surface forms for the same entity.
-For instance, the name of a person might be represented as \textit{Douglas Adams} and \textit{Douglas Noel Adams} or \textit{D.
-Adams} and \textit{Adams, Douglas}.
+For instance, the name of a person might be represented as \textit{Douglas Adams}, \textit{Douglas Noel Adams}, \textit{D.
+Adams} or \textit{Adams, Douglas}.
 Similarly, ontology alignment can require recognizing distinct surface forms of
@@
 The problem of mapping vectors for the same entity closer in vector space than vectors for other entities is known in the literature as deep metric learning.
-Deep metric learning is known to be a difficult problem as studied in the space of face recognition and person-re-identification \cite{DBLP:conf/cvpr/SchroffKP15}.
+Deep metric learning is known to be a difficult problem as studied in the space of face recognition and person-re-identification \cite{DBLP:conf/cvpr/SchroffKP15}, \cite{8445716}, \cite{DBLP:journals/corr/abs-1802-03170}.
 As a result, there is a significant amount of research on two aspects of training these networks: (a) how to choose samples for efficient learning, and (b) what constitutes a good loss function.
-In building models for entity names, we had to adapt these techniques for triplet selection and loss functions because matching entity names have more stringent requirements for a join, as we describe below.
+In building models for entity names, we had to adapt these techniques for triplet selection and loss functions because matching entity names has different characteristics, as we describe below.
 
-As in face recognition, our system for metric learning is built by training a so-called triplet based `siamese triplet' network to learn to produce a small distance estimate for two surface forms for the same entity (between an arbitrarily chosen anchor and positive), and a large distance estimate for surface forms of different entities (an anchor and a negative).
+As in face recognition, our system for metric learning is built by training a so-called triplet based `siamese triplet' network to learn to produce a small distance estimate for two surface forms for the same entity (between an arbitrarily chosen \textit{anchor} and \textit{positive}), and a large distance estimate for surface forms of different entities (an \textit{anchor} and a \textit{negative}).
 A key problem in effective training of such networks is the problem of how to select negative pairs for training, because one cannot exhaustively show all negative pairs to the network.
@@
 Third, it examines whether focusing on hard negatives is really detrimental to deep metric learning, at least for learning to map entity names in vector space.
-As we show empirically in this paper, this technique is better for building models that suitable for use in joins than semi-hard triplet mining.
+As we show empirically in this paper, this technique is better for building models that are suitable for use in joins than semi-hard triplet mining when the dataset is dominated by hard negatives.
+For easier datasets, the nearest neighbors approach was just as good as semi-hard training.
 
 We also investigated the effect of using multiple local loss functions which have been proposed in the literature for improving deep metric learning, e.g., the triplet loss \cite{DBLP:conf/cvpr/SchroffKP15}, improved loss \cite{Zhang:2016:DML:3088616.3088665}, and angular loss \cite{DBLP:journals/corr/abs-1708-01682} functions.
-For the problem of building models for datasets dominated by hard negatives, we found that an adaptation to the triplet loss function proposed in \cite{DBLP:conf/cvpr/SchroffKP15} was better than three other functions that have been proposed in the literature.
+For the problem of building models for datasets dominated by hard negatives, we found that an adaptation to the triplet loss function proposed in \cite{DBLP:conf/cvpr/SchroffKP15} was better than three other functions that have been used in the literature.
 %

### 2018-09-05 paper2018/joins.tex
adding minor changes
fixing stuff

@@
-%\section{Applying deep learning models to joins}
-%\label{join_system}
+\section{Applying deep learning models to joins}
+\label{join_system}
 
@@
 Note that although the siamese network has three separate networks, each network is in fact identical to the other two networks because they share weights.
-For the column cell values, vector embeddings are inserted into an approximate nearest neighbors index.
+For the left column cell values, vector embeddings are inserted into an approximate nearest neighbors index.
 For each cell value in the right column, vector embeddings are used as `query vectors' to query the approximate nearest neighbors index.
@@
 Note that the choice of $k$ clearly has a direct effect on the tradeoff between precision and recall, but for most practical uses of join, $k$ is usually very small (typically 1).
-This has implications on what metrics we can use to evaluate joins, as we describe in section \ref{results}.
+This has implications on what metrics we can use to evaluate joins, as we describe in the section \ref{results}.

### 2018-09-05 paper2018/main.tex
stuff
id
fixing stuff

@@
 
+\author{Paper \#3597}
+
 %\author{Kavitha Srinivas \\ IBM Research
@@
 together.  To build these models, we had to adapt techniques from
-metric learning due to the requirements of joins; specifically we describe 
+metric learning due to the characteristics of the data; specifically we describe 
 novel sample selection techniques and loss functions that work for this problem.  
@@
 and built models from datasets with approximately 1.1M people's names
-(200K identities) and 130K company names (70K identities).  We found developed models that 
+(200K identities) and 130K company names (70K identities).  We developed models that 
 allow for joins with precision@1 of .75-.81 and
-recall of .74-.81.  We make the models available to the community
-for aligning people or companies across multiple datasets.  
+recall of .74-.81.  We make the models available for aligning people or companies across multiple datasets.  
 \end{abstract}

### 2018-09-05 paper2018/relatedWork.tex
fixing stuff

@@
 \section{Related Work}
-Extensions in data management systems for handling joins typically use string similarity algorithms such as edit-distance, Jaro-Winkler and TF-IDF (e.g., \cite{Cohen2003}).
+Extensions in data management systems for handling joins typically use string similarity algorithms such as edit-distance, Jaro-Winkler and TF-IDF; e.g., \cite{Cohen2003}.
 String matching algorithms often do not work for merging different forms of the same entity because valid transformations of entity names can yield very different strings.
@@
 Another example is work by \cite{auto-join-joining-tables-leveraging-transformations} where program synthesis techniques are used to learn the right set of transformations needed to perform the entity matching operation.
-Our approach for merging datasets is much more general than either approach because the mapping function generalizes the set of transformations that are allowed across surface forms of an entity, even if they cannot be expressed as program transforms.
+Our approach for merging datasets is much more general than either approach because the mapping function generalizes the set of transformations that are allowed across surface forms of an entity, even if they cannot be directly expressed as program transforms.
 
@@
 
-Metric learning is a well studied problem in the face recognition literature, e.g., \cite{DBLP:conf/cvpr/2014}, \cite{DBLP:conf/cvpr/SchroffKP15}, with a rich literature in triplet mining techniques.
+Metric learning is a well studied problem in the face recognition literature, e.g., \cite{DBLP:conf/cvpr/SchroffKP15}, with a rich literature in triplet mining techniques.
 The closest approach to ours is the use of nearest neighbors algorithms for semi-hard triplet mining \cite{DBLP:journals/corr/KumarHC0D17}.
@@
 If all the positives are further away from the anchor than the negatives in a given neighborhood size of $k$, it means that $k$ needs to be expanded until a neighborhood size is found that has the right characteristics.
-Our focus on `hard negatives' means we can use a fixed $k$ to generate samples.
-An additional benefit is that at least in the names domain, we show that metric learning with hard negatives is more effective than semi-hard mining.
+Our approach in including `hard negatives' means we can use a fixed $k$ to generate samples.
+An additional benefit is that at least for certain types of datasets, we show that metric learning with hard negatives is more effective than semi-hard mining.
 
 The study of loss function effectiveness in metric learning is also a rich literature, with two basic types of loss functions that have been proposed: (a) local loss functions such as triplet loss \cite{DBLP:conf/cvpr/SchroffKP15}, angular loss \cite{Zhang:2016:DML:3088616.3088665} and improved loss \cite{DBLP:journals/corr/abs-1708-01682}, and (b) loss functions that operate on a more global level across a batch of training examples \cite{NIPS2016_6200}, \cite{DBLP:conf/cvpr/SongXJS16}, \cite{songCVPR17}.
-Since we do not use batches in triplet selection, but rather neighborhoods, our loss function also operates with a global perspective.
+Since our triplet selection is global, rather than batch based, we did not see the value of using global loss functions.

### 2018-09-05 paper2018/siamese_networks.tex
figures
fixing stuff

@@
 In our implementation, each of the three networks had 4 stacked layers of 128 unit Gated Recurrent Units (or GRUs) to capture the sequential nature of the input.
+GRUs are a type of recurrent network \cite{cho-al-emnlp14} where each hidden unit updates its weights at a specific step in the sequence $t$ based on the current input $x_t$ and the value of the hidden unit from the prior step $h_{t-1}$.
 For name and textual data, positional information is critical, so we used GRUs instead of the convolutional neural networks (CNNs) that have been traditionally used in metric learning for face and image recognition.
-GRUs are a type of recurrent network \cite{cho-al-emnlp14} where each hidden unit updates its weights at a specific step in the sequence $t$ based on the current input $x_t$ and the value of the hidden unit from the prior step $h_{t-1}$.
 
@@
 Let $\mathbf{x}$ represent an embedding for an entity name, and $\bf{x_{a}}$, $\bf{x_{p}}$, $\bf{x_{n}}$ reflect the vector embeddings of the \textit{anchor}, \textit{positive} and \textit{negative}, respectively.
-We investigated four different loss functions, three of which have been used in prior literature to explore their effectiveness for the entity metric learning problem.
+We investigated four different loss functions, three of which have been used in prior face recognition literature to explore their effectiveness for the entity metric learning problem.
 
@@
     \centering
-    \begin{subfigure}[t]{0.3\linewidth}
+    \begin{subfigure}[t]{0.31\linewidth}
         \centering
@@
     ~ 
-    \begin{subfigure}[t]{0.3\linewidth}
+    \begin{subfigure}[t]{0.31\linewidth}
         \centering 
@@
 function is an attempt to minimize this angle, as defined in the
-equations below.  The rough idea is that moving the positive nearer
+equations below.  The rough idea is that moving the \textit{positive} nearer
 and the \textit{negative} further away each reduce the angle, which we
@@
 that difference is negative.  We then combine the squared distances as
-usual, as how in Figure~\ref{adapted}.
+usual, as shown in Figure~\ref{adapted}.  Note that we did not normalize $\|\bf{x} \| = 1$ because learning was worse with normalization.
 

### 2018-09-05 paper2018/evaluation.tex
adding ref

@@
 We thus chose the hardest semi-hard triplets: the negatives are as close to the positive as possible while still being further from the entity.
-We ran experiments again for adapted loss on our people dataset, changing only the training used; these results are in Table~\ref{hard-semi-hard}.
+We ran experiments again for adapted loss on our people dataset, changing only the triplets used; these results are in Table~\ref{hard-semi-hard}.
 The same comparison on the company dataset showed no difference, mostly because company data seems easier and seems more immune to differences in loss functions or training regimens.
@@
 Precision@1 is similar, with 81\% for hard negatives versus 61\% for semi-hard.
-Overall precision, defined as the fraction of positives closer than any negative is 63\% for hard negatives versus 43\% for semi hard.
+Overall precision, defined as the fraction of positives closer than any negative is 63\% for hard negatives versus 43\% for semi-hard.
 
@@
 We have demonstrated that our strategy for joins could work well for textual names of people and companies, but the technique could potentially work for any kind of data for which a vector embedding can be made.
-To test how well that works, we evaluated two existing models for face recognition that were trained with the same approaches defined in the \cite{DBLP:conf/cvpr/SchroffKP15} on two different datasets, VGGFace2 \cite{DBLP:conf/fgr/CaoSXPZ18}, and CasiaWebFace \cite{DBLP:conf/cvpr/SchroffKP15}.
-We took the two open sourced models \footnote{\url{https://github.com/davidsandberg/facenet}}, and extracted the output embeddings for faces from the LFW test set \cite{Huang2012a} using these embeddings.
+To test how well that works, we evaluated two existing models for face recognition that were trained with the same approaches defined in \cite{DBLP:conf/cvpr/SchroffKP15} on two different datasets, VGGFace2 \cite{DBLP:conf/fgr/CaoSXPZ18}, and CasiaWebFace \cite{DBLP:journals/corr/YiLLL14a}.
+We took the two open sourced models\footnote{\url{https://github.com/davidsandberg/facenet}}, and extracted the output embeddings for faces from the LFW test set \cite{Huang2012a} using these embeddings.
 We put these output embeddings into an ANN structure, and computed our metrics on that.
@@
 The names data had a lot fewer positives per identity.
-VGGFace2 has 362.6 faces per identity, and 500,000 images for 10,000 identities in CasiaWebFace.
+VGGFace2 has 362.6 faces per identity, and in CasiaWebFace, 500,000 images exist for 10,000 identities.
 
 \section{Conclusion and Future Work}
-We show that deep learning models can be used effectively for joins, and we will provide these models to the community for use.
+We show that deep learning models can be used effectively for joins, and we provide these models to the community for use.
 In the future, we will evaluate our work on other entity types and continue to explore refinements of both loss functions and triplet selection.

### 2018-09-05 arxiv2018/formatting-instructions-latex-2018.tex
prep paper for arxiv

\def\year{2018}\relax
%File: formatting-instruction.tex
\documentclass[letterpaper]{article} %DO NOT CHANGE THIS
\usepackage{aaai18}  %Required
\usepackage{times}  %Required
\usepackage{helvet}  %Required
\usepackage{courier}  %Required
\usepackage{url}  %Required
\usepackage{graphicx}  %Required
\frenchspacing  %Required
\setlength{\pdfpagewidth}{8.5in}  %Required
\setlength{\pdfpageheight}{11in}  %Required
%PDF Info Is Required:
  \pdfinfo{
/Title (Matching entity names using deep learning)
/Author (Kavitha Srinivas, Yehuda Gale, Julian Dolby)}
\setcounter{secnumdepth}{0}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Matching entity names using deep learning}
\author{Kavitha Srinivas\\
IBM Research\\
3601 Kitchawan Rd \\
Yorktown Heights NY 10532
}
\author{Abraham Yehuda Gale\\
Yeshiva University
}

\author{Julian Dolby\\
IBM Research\\
3601 Kitchawan Rd \\
Yorktown Heights NY 10532
}
\maketitle
\begin{abstract}
AAAI creates proceedings, working notes, and technical reports directly from electronic source furnished by the authors. To ensure that all papers in the publication have a uniform appearance, authors must adhere to the following instructions. 
\end{abstract}

\noindent Congratulations on having a paper selected for inclusion in an AAAI Press proceedings or technical report! This document details the requirements necessary to get your accepted paper published using \LaTeX{}. If you are using Microsoft Word, instructions are provided in a different document. If you want to use some other formatting software, you must obtain permission from AAAI Press first.

The instructions herein are provided as a general guide for experienced \LaTeX{} users. If you do not know how to use \LaTeX{}, do not use it to format your paper. AAAI cannot provide you with support and the accompanying style files are \textbf{not} guaranteed to work. If the results you obtain are not in accordance with the specifications you received, you must correct your source file to achieve the correct result.

These instructions are generic. Consequently, they do not include specific dates, page charges, and so forth. Please consult your specific written conference instructions for details regarding your submission. Please review the entire document for specific instructions that might apply to your particular situation. All authors must comply with the following:

\begin{itemize}
\item You must use the 2018 AAAI Press \LaTeX{} style file and bib file, which are located in the 2018 author kit.
\item You must complete, sign, and return by the deadline the AAAI copyright form (proceedings authors) or distribution license (technical report authors).
\item You must read and format your paper source and PDF according to the formatting instructions for authors.
\item You must submit your electronic files and abstract using our electronic submission form \textbf{on time.}
\item You must pay any required page or formatting charges to AAAI Press so that they are received by the deadline.
\item You must check your paper before submitting it, ensuring that it compiles without error, and complies with the guidelines found in the author kit.
\end{itemize}

\section{Copyright}
All papers submitted for publication by AAAI Press must be accompanied by a valid signed copyright form or, in the case of technical reports, by a valid signed permission to distribute form. There are no exceptions to this requirement. You must send us the original version of this form. However, to meet the deadline, you may fax (1-650-321-4457) or scan and e-mail the form (pubforms18@aaai.org) to AAAI by the submission deadline, and then mail the original via postal mail to the AAAI office. \textbf{If you fail to send in a signed copyright or permission form, we will be unable to publish your paper. There are no exceptions to this policy.} You will find PDF versions of the AAAI copyright and permission to distribute forms in the author kit.

\section{Formatting Requirements in Brief}
We need source and PDF files that can be used in a variety of ways and can be output on a variety of devices. The design and appearance of the paper is governed by the aaai style file. 
\textbf{You must not make any changes to the aaai style file, nor use any commands, packages, style files, or macros within your own paper that alter that design, including, but not limited to spacing, floats, margins, fonts, font size, and appearance.} AAAI imposes  requirements on your source and PDF files that must be followed. Most of these requirements are based on our efforts to standardize conference manuscript properties and layout. All papers submitted to AAAI for publication will be recompiled for standardization purposes. Consequently, every paper submission must comply with the following requirements:

\begin{itemize}
\item Your .tex file must compile in PDF\LaTeX{} --- \textbf{ no .ps or .eps figure files.}
\item All fonts must be embedded in the PDF file --- \textbf{ this includes your figures.}
\item Modifications to the style file, whether directly or via commands in your document may not be made, most especially when made in an effort to avoid extra page charges or make your paper fit in a specific number of pages.
\item No type 3 fonts may be used (even in illustrations).
\item You may not alter the spacing above and below captions, figures, headings, and subheadings.
\item You may not alter the font sizes of text elements, footnotes, heading elements, captions, or title information (for references and tables and mathematics, please see the the limited exceptions provided herein).
\item You may not alter the line spacing of text.
\item Your title must follow Title Case capitalization rules (not sentence case).
\item Your .tex file must include completed metadata to pass-through to the PDF (see PDFINFO below)
\item \LaTeX{} documents must use the Times or Nimbus font package (do not use Computer Modern for the text of your paper).
\item No \LaTeX{} 209 documents may be used or submitted.
\item Your source must not require use of fonts for non-Roman alphabets within the text itself. If your paper includes symbols in other languages (such as, but not limited to, Arabic, Chinese, Hebrew, Japanese, Thai, Russian and other Cyrillic languages), you must restrict their use to bit-mapped figures.
\item Fonts that require non-English language support (CID and Identity-H) must be converted to outlines or 300 dpi bitmap or removed from the document (even if they are in a graphics file embedded in the document). 
\item Two-column format in AAAI style is required for all papers.
\item The paper size for final submission must be US letter without exception.
\item The source file must exactly match the PDF.
\item The document margins must be as specified in the formatting instructions.
\item The number of pages and the file size must be as specified for your event.
\item No document may be password protected.
\item Neither the PDFs nor the source may contain any embedded links or bookmarks.
\item Your source and PDF must not have any page numbers, footers, or headers.
\item Your PDF must be compatible with Acrobat 5 or higher.
\item Your \LaTeX{} source file (excluding references) must consist of a \textbf{single} file (use of the ``input" command is not allowed.
\item Your graphics must be sized appropriately outside of \LaTeX{} (do not use the ``clip" command) .
\end{itemize}

If you do not follow the above requirements, your submission will be subject to reformatting and special handling fees that can easily exceed the extra page fee.

\section{What Files to Submit}
You must submit the following items to ensure that your paper is published:
\begin{itemize}
\item A fully-compliant PDF file.
\item Your  \LaTeX{}  source file submitted as a \textbf{single} .tex file (do not use the ``input" command to include sections of your paper --- every section must be in the single source file). The only exception is the reference list, which you should include separately. Your source must compile on our system, which includes the standard \LaTeX{} support files.
\item Only the graphics files used in compiling paper.
\item The \LaTeX{}-generated files (e.g. .aux and .bib file, etc.) for your compiled source.
\item If you have used an old installation of \LaTeX{}, you should include algorithm style files). If in doubt, include it.
\end{itemize}

Your \LaTeX{} source will be reviewed and recompiled on our system (if it does not compile, you may incur late fees).   \textbf{Do not submit your source in multiple text files.} Your single \LaTeX{} source file must include all your text, your bibliography (formatted using aaai.bst), and any custom macros. Accompanying this source file, you must also supply any nonstandard (or older) referenced style files and all your referenced graphics files.

Your files should work without any supporting files (other than the program itself) on any computer with a standard \LaTeX{} distribution. Place your PDF and source files in a single tar, zipped, gzipped, stuffed, or compressed archive. Name your source file with your last (family) name.

\textbf{Do not send files that are not actually used in the paper.} We don't want you to send us any files not needed for compiling your paper, including, for example, this instructions file, unused graphics files, standard style files, additional material sent for the purpose of the paper review, and so forth.

\textbf{Obsolete style files.}  The commands for some common packages (such as some used for algorithms), may have changed. Please be certain that you are not compiling your paper using old or obsolete style files.

\section{Using \LaTeX{} to Format Your Paper}

The latest version of the AAAI style file is available on AAAI's website. Download this file and place it in  the \TeX\ search path. Placing it in the same directory as the paper should also work. You must download the latest version of the complete author kit so that you will have the latest instruction set and style file.

\subsection{Document Preamble}

In the \LaTeX{} source for your paper, you \textbf{must} place the following lines as shown in the example in this subsection. This command set-up is for three authors. Add or subtract author and address lines as necessary, and uncomment the portions that apply to you. In most instances, this is all you need to do to format your paper in the Times font. The helvet package will cause Helvetica to be used for sans serif. These files are part of the PSNFSS2e package, which is freely available from many Internet sites (and is often part of a standard installation).

Leave the setcounter for section number depth commented out and set at 0 unless you want to add section numbers to your paper. If you do add section numbers, you must uncomment this line and change the number to 1 (for section numbers), or 2 (for section and subsection numbers). The style file will not work properly with numbering of subsubsections, so do not use a number higher than 2.

If (and only if) your author title information will not fit within the specified  height allowed, put \textbackslash setlength \textbackslash titlebox{2.5in} in your preamble. Increase the height until the height error disappears from your log. You may not use the  \textbackslash setlength command elsewhere in your paper, and it may not be used to reduce the height of the author-title box.

\subsubsection{The Following Must Appear in Your Preamble}
\begin{quote}
\begin{scriptsize}\begin{verbatim}
\documentclass[letterpaper]{article}
\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{url}
\usepackage{graphicx}
\frenchspacing
% Add additional packages here. The following
% packages may NOT be used  (this list
% is not exhaustive:
% authblk, caption, CJK, float, fullpage, geometry, 
%hyperref, layout, nameref, natbib, savetrees, 
%setspace, titlesec, tocbibind, ulem
%
%US Lettersize Paper Is Required
\setlength{pdfpagewidth}{8.5in}
\setlength{pdfpageheight}{11in}\\
%
%
% PDFINFO
% You are required to complete the following
% for pass-through to the PDF. 
% No LaTeX commands of any kind may be
% entered. The parentheses and spaces 
% are an integral part of the 
% pdfinfo script and must not be removed.
%
\pdfinfo{
/Title (Input Your Paper Title Here)
/Author (John Doe, Jane Doe)
/Keywords (Input your keywords in this optional area)
}
%
%Section Numbers
% Uncomment if you want to use section numbers
% and change the 0 to a 1 or 2
% \setcounter{secnumdepth}{0}

% Title and Author Information Must Immediately Follow
% the pdfinfo within the preamble
%
\title{Title}\\
\author\{Author 1 \ and Author 2\\
Address line\\
Address line\\
\ And\\
Author 3\\
Address line\\
Address line
}\\
%
\end{verbatim}\end{scriptsize}
\end{quote}

\subsection{Preparing Your Paper}

After the preamble above, you should prepare your paper as follows:
\begin{quote}
\begin{scriptsize}\begin{verbatim}
%
\begin{document}
\maketitle
\begin{abstract}
%...
\end{abstract}\end{verbatim}\end{scriptsize}
\end{quote}

\subsubsection{The Following Must Conclude Your Document}
\begin{quote}
\begin{scriptsize}\begin{verbatim}
%References and End of Paper
%These lines must be placed at the end of your paper
\bibliography{Bibliography-File}
\bibliographystyle{aaai}
\end{document}
\end{verbatim}\end{scriptsize}
\end{quote}

\subsection{Inserting Document Metadata with \LaTeX{}}
PDF files contain document summary information that enables us to create an Acrobat index (pdx) file, and also allows search engines to locate and present your paper more accurately. \textit{Document metadata for author and title are REQUIRED.} You may not apply any script or macro to implementation of the title, author, and metadata information in your paper.

\textit{Important:} Do not include \textit{any} \LaTeX{} code or nonascii characters (including accented characters) in the metadata. The data in the metadata must be completely plain ascii. It may not include slashes, accents, linebreaks, unicode, or any \LaTeX{} commands. Type the title exactly as it appears on the paper (minus all formatting). Input the author names in the order in which they appear on the paper (minus all accents), separating each author by a comma. You may also include keywords in the Keywords field.

\begin{quote}
\begin{scriptsize}\begin{verbatim}
\begin{document}\\
\maketitle\\
...\\
\bibliography{Bibliography-File}\\
\bibliographystyle{aaai}\\
\end{document}\\
\end{verbatim}\end{scriptsize}
\end{quote}

\subsection{Illegal Commands}
There are a number of packages, commands, scripts, and macros that are incompatable with aaai18.sty. The common ones are provided later on in this document (See some Common  Errors to Avoid).  Generally, if a command, package, script, or macro alters floats, margins, fonts, sizing, linespacing, or the presentation of the references and citations, it is unacceptable. The following commands are some of the more common ones that may not be used in your paper (this list is not exhaustive --- there are others):
\begin{itemize}
\item \textbackslash renewcommand (in almost all instances)
\item \textbackslash baselinestretch
\item \textbackslash setlength (except for titlebox)
\item \textbackslash input
\item \textbackslash vspace or vskip (when used before or after a section or subsection or figure or table)
\item \textbackslash addtolength 
\item \textbackslash columnsep
\item \textbackslash top margin (or text height or addsidemargin or even side margin)
\item trim or clip (used to crop figures)
\item any command that globally alters floats, space above and below figures and tables
\end{itemize}

\subsection{Removing Certain Commands in Your Final Paper}
For your final camera ready copy, you must not use any page break commands, including, but not limited to:
\begin{itemize}
\item \textbackslash newpage
\item \textbackslash break
\item \textbackslash clearpage
\item \textbackslash pagebreak
\end{itemize}
(References must flow directly after the text without breaks.) Note that this may \textit{not} the case when submitting a paper for review. Some conferences require references to be on a separate page during the review process. AAAI Press, however, does not require this condition for the final paper. You must also be certain that your \textbackslash pdfino author field includes all your authors. The latter step is often forgotten.

\subsection{Paper Size, Margins, and Column Width}
Papers must be formatted to print in two-column format on 8.5 x 11 inch US letter-sized paper. The margins must be exactly as follows: 
\begin{itemize}
\item Top margin: .75 inches
\item Left margin: .75 inches
\item Right margin: .75 inches
\item Bottom margin: 1.25 inches
\end{itemize}

The default paper size in most installations of \LaTeX{} is A4. However, because we require that your electronic paper be formatted in US letter size, the preamble we have provided includes commands that alter the default to US letter size. Please note that using any other package to alter page size (such as, but not limited to the Geometry package) will result in your final paper being rejected.

\subsubsection{Column Width and Margins.}
To ensure maximum readability, your paper must include two columns. Each column should be 3.3 inches wide (slightly more than 3.25 inches), with a .375 inch (.952 cm) gutter of white space between the two columns. The aaai18.sty file will automatically create these columns for you.

\subsection{Overlength Papers}
If your paper is too long, turn on \textbackslash frenchspacing, which will reduce the space after periods. Next,  shrink the size of your graphics. Use \textbackslash centering instead of \textbackslash begin\{center\} in your figure environment. For mathematical environments, you may reduce fontsize {\bf but not below 6.5 point}. You may also alter the size of your bibliography by inserting \textbackslash fontsize\{9.5pt\}\{10.5pt\} \textbackslash selectfont
right before the bibliography (the minimum size is \textbackslash fontsize\{9.0pt\}\{10.0pt\}.

Commands that alter page layout are forbidden. These include \textbackslash columnsep, \textbackslash topmargin, \textbackslash topskip, \textbackslash textheight, \textbackslash textwidth, \textbackslash oddsidemargin, and \textbackslash evensizemargin (this list is not exhaustive). If you alter page layout, you will be required to pay the page fee \textit{plus} a reformatting fee. Other commands that are questionable and may cause your paper to be rejected include  \textbackslash parindent, and \textbackslash parskip. Commands that alter the space between sections are forbidden. The title sec package is not allowed. Regardless of the above, if your paper is obviously ``squeezed" it is not going to to be accepted. Options for reducing the length of a paper include reducing the size of your graphics, cutting text, or paying the extra page charge (if it is offered).

\subsection{Figures}
Your paper must compile in PDF\LaTeX{}. Consequently, all your figures must be .jpg, .png, or .pdf. You may not use  the .gif (the resolution is too low), .ps, or .eps file format for your figures.

When you include your figures, you must crop them \textbf{outside} of \LaTeX{}. The command \textbackslash includegraphics*[clip=true, viewport 0 0 10 10]{...} might result in a PDF that looks great, but the image is \textbf{not really cropped.} The full image can reappear (and obscure whatever it is overlapping) when page numbers are applied or color space is standardized.

\subsection{Type Font and Size}
Your paper must be formatted in Times Roman or Nimbus. We will not accept papers formatted using Computer Modern or Palatino or some other font as the text or heading typeface. Sans serif, when used, should be Courier. Use Symbol or Lucida or Computer Modern for \textit{mathematics only. }

Do not use type 3 fonts for any portion of your paper, including graphics. Type 3 bitmapped fonts are designed for fixed resolution printers. Most print at 300 dpi even if the printer resolution is 1200 dpi or higher. They also often cause high resolution imagesetter devices and our PDF indexing software to crash. Consequently, AAAI will not accept electronic files containing obsolete type 3 fonts. Files containing those fonts (even in graphics) will be rejected.

Fortunately, there are effective workarounds that will prevent your file from embedding type 3 bitmapped fonts. The easiest workaround is to use the required times, helvet, and courier packages with \LaTeX{}2e. (Note that papers formatted in this way will still use Computer Modern for the mathematics. To make the math look good, you'll either have to use Symbol or Lucida, or you will need to install type 1 Computer Modern fonts --- for more on these fonts, see the section ``Obtaining Type 1 Computer Modern.")

If you are unsure if your paper contains type 3 fonts, view the PDF in Acrobat Reader. The Properties/Fonts window will display the font name, font type, and encoding properties of all the fonts in the document. If you are unsure if your graphics contain type 3 fonts (and they are PostScript or encapsulated PostScript documents), create PDF versions of them, and consult the properties window in Acrobat Reader.

The default size for your type should be ten-point with twelve-point leading (line spacing). Start all pages (except the first) directly under the top margin. (See the next section for instructions on formatting the title page.) Indent ten points when beginning a new paragraph, unless the paragraph begins directly below a heading or subheading.

\subsubsection{Obtaining Type 1 Computer Modern for \LaTeX{}.}

If you use Computer Modern for the mathematics in your paper (you cannot use it for the text) you may need to download type 1 Computer fonts. They are available without charge from the American Mathematical Society:
http://www.ams.org/tex/type1-fonts.html.

\subsection{Title and Authors}
Your title must appear in mixed case (nouns, pronouns, and verbs are capitalized) near the top of the first page, centered over both columns in sixteen-point bold type (twenty-four point leading). This style is called ``mixed case." Author's names should appear below the title of the paper, centered in twelve-point type (with fifteen point leading), along with affiliation(s) and complete address(es) (including electronic mail address if available) in nine-point roman type (the twelve point leading). (If the title is long, or you have many authors, you may reduce the specified point sizes by up to two points.) You should begin the two-column format when you come to the abstract.

\subsubsection{Formatting Author Information}
Author information can be set in a number of different styles, depending on the number of authors and the number of affiliations you need to display. In formatting your author information, however, you may not use a table nor may you employ the \textbackslash authorblk.sty package. For several authors from the same institution, use \textbackslash and:

\begin{quote}\begin{scriptsize}\begin{verbatim}
\author{Author 1 \and ... \and Author n\\ 
Address line \\ ... \\ Address line}
\end{verbatim}\end{scriptsize}\end{quote}

\noindent If the names do not fit well on one line use:

\begin{quote}\begin{scriptsize}\begin{verbatim}
\author{Author 1} ... \\
{\bf \Large Author  ...  Author}\\ 
Address line \\ ... \\ Address line
}
\end{verbatim}\end{scriptsize}\end{quote}

\noindent For authors from different institutions, use \textbackslash And:

\begin{quote}\begin{scriptsize}\begin{verbatim}
\author{Author 1\\ Address line \\ ... \\ Address line 
\And ... \And Author n\\
Address line\\ ... \\ Address line}
\end{verbatim}\end{scriptsize}\end{quote}

\noindent To start a separate ``row" of authors, use \textbackslash AND:

\noindent If the title and author information does not fit in the area allocated, place
\textbackslash setlength\textbackslash titlebox\{\textit{height}\}
after the \textbackslash documentclass line where \{\textit{height}\} is  2.5in or greater.

\subsubsection{Formatting Author Information --- Alternative Method}
If your paper has a large number of authors from different institutions, you may use the following alternative method for displaying the author information.

\begin{quote}\begin{scriptsize}\begin{verbatim}
\author{AuthorOne},\textsuperscript{1}
\author{AuthorTwo},\textsuperscript{2}
\author{AuthorThree},\textsuperscript{3}
\author{AuthorFour},\textsuperscript{4}
\author{AuthorFive}, \textsuperscript{5}\\
\textsuperscript{1}AffiliationOne}\\
\textsuperscript{2}AffiliationTwo}\\
\textsuperscript{3}AffiliationThree}\\
\textsuperscript{4}AffiliationFour}\\
\textsuperscript{5}AffiliationFive}\\
\{email, email\}@affiliation.com,
email@affiliation.com,
email@affiliation.com, 
email@affiliation.com
\end{verbatim}\end{scriptsize}\end{quote}

\subsection{\LaTeX{} Copyright Notice}
The copyright notice automatically appears if you use aaai.sty. If you are creating a technical report, it is not necessary to include this notice. You may disable the copyright line using the \verb+\+nocopyrightcommand. To change the entire text of the copyright slug, use:
\textbackslash copyrighttext \{\emph{text}\}.
Either of these must appear before \textbackslash maketitle. Please be advised, however, that \textit{if you disable or change the copyright line and transfer of copyright is required, your paper will not be published.}

\subsection{Credits}
Any credits to a sponsoring agency should appear in the acknowledgments section, unless the agency requires different placement. If it is necessary to include this information on the front page, use
\textbackslash thanks in either the \textbackslash author or \textbackslash title commands.
For example:
\begin{quote}
\begin{small}
\textbackslash title\{Very Important Results in AI\textbackslash thanks\{This work is
 supported by everybody.\}\}
\end{small}
\end{quote}
Multiple \textbackslash thanks commands can be given. Each will result in a separate footnote indication in the author or title with the corresponding text at the botton of the first column of the document. Note that the \textbackslash thanks command is fragile. You will need to use \textbackslash protect.

Please do not include \textbackslash pubnote commands in your document.

\subsection{Abstract}
Follow the example commands in this document for creation of your abstract. Further indentation is not required. {Do not include references in your abstract!}

\subsection{Page Numbers}

Do not \textbf{ever} print any page numbers on your paper.

\subsection{Text }
The main body of the paper must be formatted in ten-point with twelve-point leading (line spacing).

\subsection{Citations}
Citations within the text should include the author's last name and year, for example (Newell 1980). Append lower-case letters to the year in cases of ambiguity. Multiple authors should be treated as follows: (Feigenbaum and Engelmore 1988) or (Ford, Hayes, and Glymour 1992). In the case of four or more authors, list only the first author, followed by et al. (Ford et al. 1997).

\subsection{Extracts}
Long quotations and extracts should be indented ten points from the left and right margins.

\begin{quote}
This is an example of an extract or quotation. Note the indent on both sides. Quotation marks are not necessary if you offset the text in a block like this, and properly identify and cite the quotation in the text.

\end{quote}

\subsection{Footnotes}
Avoid footnotes as much as possible; they interrupt the reading of the text. When essential, they should be consecutively numbered throughout with superscript Arabic numbers. Footnotes should appear at the bottom of the page, separated from the text by a blank line space and a thin, half-point rule.

\subsection{Headings and Sections}
When necessary, headings should be used to separate major sections of your paper. Remember, you are writing a short paper, not a lengthy book! An overabundance of headings will tend to make your paper look more like an outline than a paper. The aaai.sty package will create headings for you. Do not alter their size nor their spacing above or below.

\subsubsection{Section Numbers}
The use of section numbers in AAAI Press papers is optional. To use section numbers in \LaTeX{}, uncomment the setcounter line in your document preamble and change the 0 to a 1 or 2. Section numbers should not be used in short poster papers.

\subsubsection{Section Headings.}
Sections should be arranged and headed as follows:

\subsubsection{Acknowledgments.}
The acknowledgments section, if included, appears after the main body of text and is headed ``Acknowledgments." This section includes acknowledgments of help from associates and colleagues, credits to sponsoring agencies, financial support, and permission to publish. Please acknowledge other contributors, grant support, and so forth, in this section. Do not put acknowledgments in a footnote on the first page. If your grant agency requires acknowledgment of the grant on page 1, limit the footnote to the required statement, and put the remaining acknowledgments at the back. Please try to limit acknowledgments to no more than three sentences.

\subsubsection{Appendices.}
Any appendices follow the acknowledgments, if included, or after the main body of text if no acknowledgments appear.

\subsubsection{References}
The references section should be labeled ``References" and should appear at the very end of the paper (don't end the paper with references, and then put a figure by itself on the last page). A sample list of references is given later on in these instructions. Please use a consistent format for references. Poorly prepared or sloppy references reflect badly on the quality of your paper and your research. Please prepare complete and accurate citations.

\subsection{Illustrations and Figures}
Figures, drawings, tables, and photographs should be placed throughout the paper near the place where they are first discussed. Do not group them together at the end of the paper. If placed at the top or bottom of the paper, illustrations may run across both columns. Figures must not invade the top, bottom, or side margin areas. Figures must be inserted using the \textbackslash usepackage\{graphicx\}. Number figures sequentially, for example, figure 1, and so on.

The illustration number and caption should appear under the illustration. Labels, and other text with the actual illustration must be at least nine-point type.

If your paper includes illustrations that are not compatible with PDF\TeX{} (such as .eps or .ps documents), you will need to convert them. The epstopdf package will usually work for eps files. You will need to convert your ps files to PDF however.

\subsubsection{Low-Resolution Bitmaps.}
You may not use low-resolution (such as 72 dpi) screen-dumps and GIF files---these files contain so few pixels that they are always blurry, and illegible when printed. If they are color, they will become an indecipherable mess when converted to black and white. This is always the case with gif files, which should never be used. The resolution of screen dumps can be increased by reducing the print size of the original file while retaining the same number of pixels. You can also enlarge files by manipulating them in software such as PhotoShop. Your figures should be 300 dpi when incorporated into your document.

\subsubsection{\LaTeX{} Overflow.}
\LaTeX{} users please beware: \LaTeX{} will sometimes put portions of the figure or table or an equation in the margin. If this happens, you need to scale the figure or table down, or reformat the equation.{ \bf Check your log file!} You must fix any overflow into the margin (that means no overfull boxes in \LaTeX{}). If you don't, the overflow text will simply be eliminated. \textbf{Nothing is permitted to intrude into the margin or gutter.}

\subsubsection{Using Color.}
Use of color is restricted to figures only. It may never be used for any portion of the text of your paper. The archival version of your paper will be printed in black and white and grayscale. Consequently, because conversion to grayscale can cause undesirable effects (red changes to black, yellow can disappear, and so forth), we strongly suggest you avoid placing color figures in your document. If you do include color figures, you must (1) use the CMYK (not RGB) colorspace and (2)  be mindful of readers who may happen to have a color deficiency. Your paper must be decipherable without using color for distinction.

\subsubsection{Drawings.}
We suggest you use computer drawing software (such as Adobe Illustrator or, (if unavoidable), the drawing tools in Microsoft Word) to create your illustrations. Do not use Microsoft Publisher. These illustrations will look best if all line widths are uniform (half- to two-point in size), and you do not create labels over shaded areas. Shading should be 133 lines per inch if possible. Use Times Roman or Helvetica for all figure call-outs. \textbf{Do not use hairline width lines} --- be sure that the stroke width of all lines is at least .5 pt. Zero point lines will print on a laser printer, but will completely disappear on the high-resolution devices used by our printers.

\subsubsection{Photographs and Images.}
Photographs and other images should be in grayscale (color photographs will not reproduce well; for example, red tones will reproduce as black, yellow may turn to white, and so forth) and set to a minimum of 300 dpi. Do not prescreen images.

\subsubsection{Resizing Graphics.}
Resize your graphics \textbf{before} you include them with LaTeX. You may \textbf{not} use trim or clip options as part of your \textbackslash includegraphics command. Resize the media box of your PDF using a graphics program instead.

\subsubsection{Fonts in Your Illustrations}
You must embed all fonts in your graphics before including them in your LaTeX document.

\subsection{References} 
The AAAI style includes a set of definitions for use in formatting references with BibTeX. These definitions make the bibliography style fairly close to the one specified below. To use these definitions, you also need the BibTeX style file ``aaai.bst," available in the author kit on the AAAI web site. Then, at the end of your paper but before \textbackslash end{document}, you need to put the following lines:

\begin{quote}
\begin{small}
\textbackslash bibliographystyle\{aaai\}
\textbackslash bibliography\{bibfile1,bibfile2,...\}
\end{small}
\end{quote}

Please note that you are required to use \textbackslash bibliographystyle\{aaai\} for your references. You may not use named, plain, apalike, acm, ieeetr, siam, chicago, or any other style. Use of natbib is also not acceptable.

The list of files in the \textbackslash  bibliography command should be the names of your BibTeX source files (that is, the .bib files referenced in your paper).

The following commands are available for your use in citing references:
\begin{quote}
\begin{small}
\textbackslash cite: Cites the given reference(s) with a full citation. This appears as ``(Author Year)'' for one reference, or ``(Author Year; Author Year)'' for multiple references.\\
\textbackslash shortcite: Cites the given reference(s) with just the year. This appears as ``(Year)'' for one reference, or ``(Year; Year)'' for multiple references.\\
\textbackslash citeauthor: Cites the given reference(s) with just the author name(s) and no parentheses.\\
\textbackslash citeyear: Cites the given reference(s) with just the date(s) and no parentheses.
\end{small}
\end{quote}

\textbf{Warning:} The aaai.sty file is incompatible with the hyperref and natbib packages. If you use either, your references will be garbled and your paper will not be published.

Formatted bibliographies should look like the following examples.

\smallskip \noindent \textit{Book with Multiple Authors}\\
Engelmore, R., and Morgan, A. eds. 1986. \textit{Blackboard Systems.} Reading, Mass.: Addison-Wesley.

\smallskip \noindent \textit{Journal Article}\\
Robinson, A. L. 1980a. New Ways to Make Microcircuits Smaller. \textit{Science} 208: 1019--1026.

\smallskip \noindent \textit{Magazine Article}\\
Hasling, D. W.; Clancey, W. J.; and Rennels, G. R. 1983. Strategic Explanations in Consultation. \textit{The International Journal of Man-Machine Studies} 20(1): 3--19.

\smallskip \noindent \textit{Proceedings Paper Published by a Society}\\
Clancey, W. J. 1983. Communication, Simulation, and Intelligent Agents: Implications of Personal Intelligent Machines for Medical Education. In \textit{Proceedings of the Eighth International Joint Conference on Artificial Intelligence,} 556--560. Menlo Park, Calif.: International Joint Conferences on Artificial Intelligence, Inc.

\smallskip \noindent \textit{Proceedings Paper Published by a Press or Publisher}\\
Clancey, W. J. 1984. Classification Problem Solving. In \textit{Proceedings of the Fourth National Conference on Artificial Intelligence,} 49--54. Menlo Park, Calif.: AAAI Press.

\smallskip \noindent \textit{University Technical Report}\\
Rice, J. 1986. Poligon: A System for Parallel Problem Solving, Technical Report, KSL-86-19, Dept. of Computer Science, Stanford Univ.

\smallskip \noindent \textit{Dissertation or Thesis}\\
Clancey, W. J. 1979. Transfer of Rule-Based Expertise through a Tutorial Dialogue. Ph.D. diss., Dept. of Computer Science, Stanford Univ., Stanford, Calif.

\smallskip \noindent \textit{Forthcoming Publication}\\
Clancey, W. J. 1986. The Engineering of Qualitative Models. Forthcoming.

\section{Some Common Errors to Avoid}

The following list includes a number of the most common mistakes made by authors when formatting their paper and the reponses that have been sent to the author regarding them:

\begin{small}
\begin{quote}
PDFINFO\\
The following required elements are missing from the preamble to your LaTeX source (or are malformed):
\begin{small}\begin{verbatim}
\pdfinfo{ 
/Title () 
/Author () 
}
\end{verbatim}\end{small}

A4\\
The PDF you submitted is A4. All PDFs must be US Letter sized. Submissions that do not conform to this requirement cannot be published. 
\smallskip

ABOVEDISPLAY\\
You've used \textbackslash abovedisplay, \textbackslash belowdisplay, \textbackslash above caption, and \textbackslash belowcaption to alter aaai18.sty. These commands are illegal and must be stripped from your source.
\smallskip

ABSTRACT INDENTATION\\
Remove the \textbackslash begin\{quote\} and \textbackslash \{endquote\} around your abstract. It might buy you some space.
\smallskip

ASPECT RATIO OF FIGURES CHANGED\\
You may scale the height OR the width of your figures, but not both.
\smallskip

AUTHOR LIST MALFORMED (AUTHBLK)\\
The authblk.sty package cannot be used. 
\smallskip

AUTHOR LIST MALFORMED\\
You did not use the built-in commands in aaai18.sty to format your authors. You need to follow the formatting instructions for authors using LaTeX. 
\smallskip

AUTHOR LIST TOO WIDE\\
Your author list goes beyond the accepted page width. Please break the line and insert \{\textbackslash bf \textbackslash Large\} around the authors on the second line. The author and title information must be presented as specified in the author instructions.
\smallskip

AUTHOR AFFLIATIONS TOO WIDE\\
Your author's affiliations go beyond the accepted page width. Please break the line.
\smallskip

BASELINESTRETCH\\
You've used \textbackslash baselinestretch --- a command specifically prohibited in the author formatting instructions. Please remove it.
\smallskip

CAPTION STYLE ALTERED (CAPTION.STY)\\
You've altered the font and style of captions. Captions must be rendered as specified by aaai.sty. They cannot be altered by changing the font, fontsize, or position, whether manually or by using caption.sty. Such revisions must be removed.
\smallskip

CJK\\
The CJK package cannot be used. Restrict use of non-roman alphabets to figures and tables, which must be compiled and converted to PDF, then imported as a figure into LaTeX.
\smallskip

CLIP\\
You may not use the clip to import only a portion of a graphic. It only places a fragile layer that screens the remained of the figure from view, but imports the entire figure into the PDF. The layer is fragile, and often fails when flattened. The full content of all figures must be imported. In addition and for the same reason, you may not use vspace to reposition a figure. All figures must be completely cropped and adjusted outside of LaTeX before being imported. 
\smallskip

COLUMN WIDTH\\
Unfortunately, your paper contains material that exceeds the column width. Please review your LaTeX log file and correct all the overfull boxes.
\smallskip

COMPILE ERRORS\\
Unfortunately, the source file you submitted will not compile. We are getting undefined control sequence errors. There are either missing packages in your preamble, or missing definitions, or perhaps you are using an old or modified style. For your information, we are using a complete 2017 install of TeXLive, complete with all updates as of September 1. The packages listed in your preamble are all installed on all our systems. If you are using a style file that is not in that package, you will need to include it. Whatever the reason, we need you to correct your LaTeX and resubmit your source files. (If your paper contains graphics, be certain that the fonts are embedded.) 
\smallskip

EPSF / EPSFIG / PSFIG\\
The epsf, epsfig, and psfig packages are obsolete. Use the graphicx package instead.
\smallskip

EULER\\
The euler package is obsolte
\smallskip

FIGURES HAVE BEEN CROPPED WITH LATEX\\
You have used trim and clip commands in your \textbackslash includegraphics statement. Please crop your graphics appropriately using a standard graphics program (not Preview). The masks created by LaTeX are fragile, and disappear when PDFs are combined together. This will result in text in your paper becoming obscured by the fully restored graphic you have imported.
\smallskip

FIGURES MISSING\\
Unfortunately, the source file you submitted are incomplete. You did not include the graphics files. As a result, your paper will not compile. You must upload a new compressed archive that contains all the files required to compile your paper on a different computer and network. (If your paper contains graphics, be certain that the fonts are embedded.) 
\smallskip

FLOATS ALTERED\\
You've altered floats.  The \textbackslash renewcommand cannot be used. The float package cannot be used. Please remove them.
\smallskip

FOOTNOTE STYLE ALTERED\\
Footnotes must follow the built-in style.
\smallskip

FONTS (EMBEDDING)\\
Unfortunately, one or more of the fonts in your paper (most likely the figures) were not embedded in your PDF. This can cause hidden and silent changes to characters once the paper is published, especially when it is combined with other PDFs in the proceedings. If you need to know how to verify the fonts in your figures, please search for ``font embedding pdf." You will find a number of methods, one or more of which may be suitable for your operating system and available software. We recommend using Acrobat Reader to check document properties in your PDF, as it is standards-based software. Consequently, you must embed all the fonts in all your graphics files. If you do not know how to do this, change them to png or jpg. 
\smallskip

FONTS (LANGUAGE)\\
We cannot accept files that require custom installation of non-roman font sets, including CJK and arabic.
 \smallskip

FONTS (TYPE 3)\\
Unfortunately, one or more of the fonts in your paper (most likely the figures) are type 3 PDF. If in your figures, you must either change them to type 1 embedded fonts or change them to png or jpg. If the problem is in your text, you will need to switch the package you are using that is calling type 3 fonts to one that uses type 1 fonts. (Blackboard fonts are often the problem in these cases.)
\smallskip

FULL PAGE USED\\
You used \textbackslash usepackage\{full page\}, which is a package specifically disallowed. You must remove it.
\smallskip

GEOMETRY USED\\
You used \textbackslash usepackage\{geometry\}, which is a package specifically disallowed. You must remove it.
\smallskip

GRAPHICS\\
The graphics package is obsolete. Use the graphicx package instead.
\smallskip

HYPERREF\\
The hyperref package may never be used. If you are using it for URLs, use url.sty instead
\smallskip

INCOMPATIBLE SCRIPT OR MACRO\\
You've used an incompatible script (such as \textbackslash maltepaper.sty) to automate completion of the title and author information on your paper and in the metadata. Such scripts impede correction of your paper and often are incompatible with Acrobat (producing corrupted metadata fields). Scripts and macros cannot be used to automate population of metadata, author or title information, or insertion of figures or tables.
\smallskip

LAYOUT\\
The layout package cannot be used. Use url.sty instead.
\smallskip

LINESPREAD\\
\textbackslash linespread alters aaai.sty. This command (along with \textbackslash baselineshift and others that alter aaai.sty) cannot be used. You must remove it.
\smallskip

LMODERN\\
You used \textbackslash usepackage\{lmodern\}, which is a package specifically disallowed. You must remove it.
\smallskip

LAYOUT USED\\
You used \textbackslash usepackage\{layout\}, which is a package specifically disallowed. You must remove it.
\smallskip

MBOX USED FOR FIGURES\\
You cannot use mboxes to insert figures. They circumvent the spacing requirements for aaai.sty. Use subfigures instead.
\smallskip

MULTIPLE TEX FILES\\
You did not submit a single .tex file as specified in the instructions. We require this to avoid production errors and to facilitate debugging. The \textbackslash input command is not allowed in your source. Please combine all your tex files into a single .tex file (references can remain in .bbl or .bib file).
\smallskip

NAMEREF\\
The nameref package cannot be used.
\smallskip

NATBIB\\
Natbib is incompatible with aaai18.sty and aaai.bst. It must be removed. See References Malformed below.
\smallskip
\smallskip

PAGE BREAKS \\
You've included pagebreaks in your final submission. (They are not required before your references accepted final papers and must be removed).
\smallskip

PAGE NUMBERS\\
Your paper contains page numbers. You need to remove them.
\smallskip

PDFLaTeX NOT USED\\
Your source will not compile in PDFLaTeX. You must convert your eps graphics to PDF.
\smallskip

PDFCOMMENT\\
You used pdfcomment, which is a disallowed package. You must remove it.
\smallskip

PSTRICKS\\
You used pstricks, which is a package specifically disallowed. You must remove it. (Use Tikz instead). If you are simply adding labels, use pinlabel.sty.
\smallskip

REFERENCES ARE INDENTED\\
You've indented your references. Remove the \textbackslash begin\{quote\} and \textbackslash end{quote}
\smallskip

REFERENCES MALFORMED\\
You've used natbib, which is incompatible with aaai.bst.

As an alternate to this, try this workaround:

\begin{quote}\begin{scriptsize}\begin{verbatim}% \usepackage{natbib}
\newcommand{\citet}[1]
{\citeauthor{#1}~\shortcite{#1}}
\newcommand{\citep}{\cite}
\newcommand{\citealp}[1]
{\citeauthor{#1}~\citeyear{#1}}\end{verbatim}\end{scriptsize}\end{quote}
\smallskip

REFERENCES TOO SMALL\\
Your references are too small. They cannot be any smaller than 9 pt (\textbackslash small). Please correct this.
 \smallskip

SAVETREES\\
The savetrees may not be used.
\smallskip

SETLENGTH\\
You've used \textbackslash setlength to alter textfloats. This command is specifically disallowed. Please strip it from your source and recompile.
\smallskip

SETSPACE\\
The setspace package may not be used.
\smallskip

SPACE ABOVE, BELOW ELEMENTS ALTERED\\
You've adjusted the space above or below tables, figures, captions, floats, and/or section/subsection/subsubsections. These changes alter aaai.sty and are not allowed. Please remove them and either edit your text or resize figures or both.
\smallskip

SOURCE FILES MISSING\\
Your compressed archive does not contain *ALL* your source files (a stand-alone archive containing all the files necessary to recompile your paper in LaTeX). Consequently, your LaTeX file will not compile. You must create another compressed archive in which you have included all the files necessary to compile your paper on a separate computer. We cannot publish your paper without these files.
\smallskip

SPACE ALTERED ABOVE, BELOW FLOATS AND SECTIONS\\
You've adjusted the space above or below tables, figures, captions, and/or section/subsection/subsubsections. These changes alter aaai.sty and have resulted in a paper that is more difficult to read. Please remove them and either edit your text or resize figures or both.
\smallskip

STYLE FILE OF BIBLIOGRAPHY IS INCORRECT\\
You did not use aaai.bst (you used named.bst instead). This is not an IJCAI conference. You need to recompile your bibliography using the correct style for AAAI-18.
\smallskip

STYLE FILE IS INCORRECT\\
You did not use aaai18.sty. This style file is required. No other style file (including previous versions of aaai.sty) may be used.
\smallskip

STYLE FILE NOT IN CTAN\\
All styles must be available in the CTAN archive. If they are custom, you need to remove them and put the contents of the custom style directly in your preamble so that our source checker will allow compilation of your file.
\smallskip

TIMES PACKAGE NOT USED\\
Your paper is not formatted using the Times package, either because it is missing completely from your preamble, or because you are using another package that is cancelling use of times. This package is required.
\smallskip

TITLESEC\\
The title sec package may not be used.
\smallskip

VSPACE USED\\
You've used negative vspace around section / subsections. These must be removed.
\smallskip

TIMES PACKAGE MISSING\\
You neglected to use \textbackslash usepackage\{times\}. This font is required.
\smallskip

TITLE AND AUTHOR INFORMATION MALFORMED\\
You need to remove the formatting commands from your title and author information. The style for this information is governed by the conference style file. It cannot be altered.
\smallskip

TITLE BOX TOO SMALL\\
Your author-title-affiliation data exceeds the limit of the title box. To
fix this, you need to increase the size of the title box. You can do this by
placing
\textbackslash setlength\textbackslash titlebox\{2.5in\} in your preamble. You may need to increase the measurement until
the log file error goes away. (Please note: This command cannot be used elsewhere
in the paper, and cannot be used to shrink the size of the title box.)
\smallskip

TITLE IN SENTENCE CASE\\
Your title is formatted in sentence case. Title Case (Mixed Case) is required. Please capitalize the initial letters of all words in your title except for conjunctions and prepositions. You need to do this in your source, in the \textbackslash pdfinfo in your source, and on the submission website.
\smallskip

TITLE MALFORMED (TITLESEC)\\
You've used titlesec.sty, which alters the AAAI style. It must be removed.
\smallskip

TOCBIBIND\\
The tocbibind package may not be used.
\smallskip

ULEM\\
The ulem package may not be used.
\smallskip

T1ENC\\
The T1enc package is obsolete. Us the CM Super Fonts package instead.

\end{quote}
\end{small}

\section{Producing Reliable PDF\\Documents with \LaTeX{}}
Generally speaking, PDF files are platform independent and accessible to everyone. When creating a paper for a proceedings or publication in which many PDF documents must be merged and then printed on high-resolution PostScript RIPs, several requirements must be met that are not normally of concern. Thus to ensure that your paper will look like it does when printed on your own machine, you must take several precautions:
\begin{itemize}
\item Use type 1 fonts (not type 3 fonts)
\item Use only standard Times, Nimbus, and CMR font packages (not fonts like F3 or fonts with tildes in the names or fonts---other than Computer Modern---that are created for specific point sizes, like Times\~{}19) or fonts with strange combinations of numbers and letters
\item Embed all fonts when producing the PDF
\item Do not use the [T1]{fontenc} package (install the CM super fonts package instead)
\end{itemize}

\subsection{Creating Output Using PDF\LaTeX{} Is Required}
By using the PDF\TeX{} program instead of straight \LaTeX{} or \TeX{}, you will probably avoid the type 3 font problem altogether (unless you use a package that calls for metafont). PDF\LaTeX{} enables you to create a PDF document directly from \LaTeX{} source. The one requirement of this software is that all your graphics and images must be available in a format that PDF\LaTeX{} understands (normally PDF, jpg, or png).

PDF\LaTeX{}'s default is to create documents with type 1 fonts. If you find that it is not doing so in your case, it is likely that one or more fonts are missing from your system or are not in a path that is known to PDF\LaTeX{}.

\subsubsection{dvipdf Script}
Scripts such as dvipdf which ostensibly bypass the Postscript intermediary should not be used since they generally do not instruct dvips to use the config.pdf file.

\subsubsection{dvipdfm}
Do not use this dvi-PDF conversion package.

\subsection{Ghostscript}
\LaTeX{} users should not use GhostScript to create their PDFs.

\subsection{Graphics}
If you are still finding type 3 fonts in your PDF file, look at your graphics! \LaTeX{} users should check all their imported graphics files as well for font problems.

\section{Proofreading Your PDF}
Please check all the pages of your PDF file. Is the page size A4? Are there any type 3, Identity-H, or CID fonts? Are all the fonts embedded? Are there any areas where equations or figures run into the margins? Did you include all your figures? Did you follow mixed case capitalization rules for your title? Did you include a copyright notice? Do any of the pages scroll slowly (because the graphics draw slowly on the page)? Are URLs underlined and in color? You will need to fix these common errors before submitting your file.

\section{Improperly Formatted Files }
In the past, AAAI has corrected improperly formatted files submitted by the authors. Unfortunately, this has become an increasingly burdensome expense that we can no longer absorb. Consequently, if your file is improperly formatted, it will not be included in the publication. If time allows, however, you will be notified via e-mail of the problems with your file and given the option of correcting the file yourself. A resubmission fee (minimum \$50.00, and likely higher) will be required for this service). Optionally, you may ask that AAAI have the file corrected for you, for an additional fee. If you opt to correct the file yourself, please note that we cannot provide you with any additional advice beyond that given in your packet. Files that are not corrected after a second attempt will not be included in the publication.

\subsection{\LaTeX{} 209 Warning}
If you use \LaTeX{} 209 we will not be able to publish your paper. Convert your paper to \LaTeX{}2e.

\section{Naming Your Electronic File}
We request that you name your \LaTeX{} source file with your last name (family name) so that it can easily be differentiated from other submissions. If you name your files with the name of the event or ``aaai" or ``paper" or ``camera-ready" or some other generic or indecipherable name, you bear all risks of loss --- it is extremely likely that your file may be overwritten.

\section{Submitting Your Electronic Files to AAAI}
Submitting your files to AAAI is a two-step process. It is explained fully in the author registration and submission instructions. Please consult this document for details on how to submit your paper.

\section{Inquiries} 
If you have any questions about the preparation or submission of your paper as instructed in this document, please contact AAAI Press at the address given below. If you have technical questions about implementation of the aaai style file, please contact an expert at your site. We do not provide technical support for \LaTeX{} or any other software package. To avoid problems, please keep your paper simple, and do not incorporate complicated macros and style files.

\begin{quote}
\noindent AAAI Press\\
2275 East Bayshore Road, Suite 160\\
Palo Alto, California 94303\\ 
\textit{Telephone:} (650) 328-3123\\ 
\textit{E-mail:} See the submission instructions for your particular conference or event.
\end{quote}

\section{Additional Resources}
\LaTeX{} is a difficult program to master. If you've used that software, and this document didn't help or some items were not explained clearly, we recommend you read Michael Shell's excellent document (testflow doc.txt V1.0a 2002/08/13) about obtaining correct PS/PDF output on \LaTeX{} systems. (It was written for another purpose, but it has general application as well). It is available at www.ctan.org in the tex-archive.

\section{ Acknowledgments}
AAAI is especially grateful to Peter Patel Schneider for his work in implementing the aaai.sty file, liberally using the ideas of other style hackers, including Barbara Beeton. We also acknowledge with thanks the work of George Ferguson for his guide to using the style and BibTeX files --- which has been incorporated into this document  --- and Hans Guesgen, who provided several timely modifications, as well as the many others who have, from time to time, sent in suggestions on improvements to the AAAI style.

The preparation of the \LaTeX{} and Bib\TeX{} files that implement these instructions was supported by Schlumberger Palo Alto Research, AT\&T Bell Laboratories, Morgan Kaufmann Publishers, The Live Oak Press, LLC, and AAAI Press. Bibliography style changes were added by Sunil Issar. \verb+\+pubnote was added by J. Scott Penberthy. George Ferguson added support for printing the AAAI copyright slug. Additional changes to aaai.sty and aaai.bst have been made by the AAAI staff.

\bigskip
\noindent Thank you for reading these instructions carefully. We look forward to receiving your electronic files!

\end{document}

### 2018-09-05 arxiv2018/main.tex
prep paper for arxiv

--- 2018-09-05 paper2018/main.tex
@@
 \documentclass[letterpaper]{article} %DO NOT CHANGE THIS
-\usepackage{aaai19}  %Required
+\usepackage{aaai19}
 \usepackage{times}  %Required
@@
 
-\author{Paper \#3597}
-
-%\author{Kavitha Srinivas \\ IBM Research
-%\And Yehuda Gale \\ Yeshiva University
-%\And Julian Dolby \\ IBM Research}
+\author{Kavitha Srinivas \\ IBM Research
+\And Yehuda Gale \\ Yeshiva University
+\And Julian Dolby \\ IBM Research}
 
@@
 different surface forms for the same entity (e.g., the name of a
-person might be represented as \textit{Douglas Adams},
-\textit{Adams, Douglas} or \textit{Douglas Noel Adams}).  Similarly,
+person might be represented as \textit{Douglas Adams} or
+\textit{Adams, Douglas}).  Similarly,
 ontology alignment can require recognizing distinct surface forms of

### 2018-09-05 ANNCharacteristics.py
adding code for dataset char

@@ -534,4 +534,4 @@ sequences = pad_sequences(sequences, maxlen=MAX_SEQUENCE_LENGTH)
 embedder = get_embedding_layer(tokenizer)
 embedder_model = embedded_representation_model(embedder)
 
-characterize_dataset(embedder_model, sequences, entity2unique, entity2same, unique_text, [20, 100, 500, 1000])
+characterize_dataset(embedder_model, sequences, entity2unique, entity2same, unique_text, [20, 100, 500, 1500])

### 2018-09-05 arxiv2018/introduction2.tex
fixing urls

--- 2018-09-05 paper2018/introduction2.tex
@@
 
-In this paper, we propose a different approach to the problem of joining different surface representations of the same entity, inspired in part by recent advances in deep learning.
-Our approach depends on (a) creating a function that maps surface forms into a set of vectors such that alternate forms for the same entity are closest in vector space, (b) indexing these vectors using a space partitioning algorithm to find the forms that can be potentially joined together.
+We propose a different approach to joining different surface representations of the same entity, inspired by recent advances in deep learning.
+Our approach depends on (a) mapping surface forms into sets of vectors such that forms for the same entity are closest in vector space, (b) indexing these vectors to find the forms that can be potentially joined together.
 The approach is general, in the sense that once a model has been built for a specific semantic type (e.g.
 people, companies or faces) it can be used for joining any two datasets which share that semantic type.
-It is also efficient because it uses space partitioning algorithms (such as approximate nearest neighbor) to find surface forms that are potentially joinable, thus eliminating large parts of the vector space from consideration.
-Further, implementations exist for nearest neighbor algorithms that have been applied to billions of vectors \cite{JDH17}, so the approach is practical for most datasets.
+It is also efficient because indexing uses space partitioning algorithms (such as approximate nearest neighbor) to find surface forms that are potentially joinable, thus eliminating large parts of the vector space from consideration.
+Further, nearest neighbor algorithms have been applied to billions of vectors \cite{JDH17}, so the approach is practical for most datasets.
 
@@
 For the problem of building models for datasets dominated by hard negatives, we found that an adaptation to the triplet loss function proposed in \cite{DBLP:conf/cvpr/SchroffKP15} was better than three other functions that have been used in the literature.
+All code and models for this paper are at \url{https://github.com/yehudagale/fuzzyjoiner} and \url{https://drive.google.com/open?id=1zivCTGkq2_AkfjGLHMnlehzTmYUwcQ9e} respectively.
 %

### 2018-09-05 arxiv2018/triplet_selection.tex
adding fig

--- 2018-09-02 paper2018/triplet_selection.tex
@@
 \begin{figure}
-\includegraphics[width=1.0\linewidth]{triplet_selection}
+\includegraphics[width=1.0\linewidth]{triplet_selection_fig}
 \caption{Batch based triplet selection}
@@
 For the problem of joins, we ideally want the anchor and all of its positives to be clustered closest together and separated from the nearest negatives as clearly as possible.
-Approximate nearest neighbor indexes are highly efficient methods for selecting the top-K neighbors of a given vector by Euclidean distance, cosine similarity or other distance metrics.
+Approximate nearest neighbor (ANN) indexes are highly efficient methods for selecting the top-K neighbors of a given vector by Euclidean distance, cosine similarity or other distance metrics.
 They are based on space partitioning algorithms, such as \textit{k-d trees}, where the vector space is iteratively bisected into two disjoint regions.
@@
 Implementations exist now for fast, memory-efficient ANN indexes that scale up to a billion vectors \cite{JDH17} using techniques to compress vectors in memory efficiently.
-In our work, we used the Annoy ANN implementation \cite{annoy_git} in our work which is based on the refinements to \textit{k-d trees} ideas described in \cite{ann_paper}.
+In our work, we used the Annoy ANN implementation\footnote{\url{https://github.com/spotify/annoy}} in our work which is based on the refinements to \textit{k-d trees} ideas described in \cite{ann_paper}.
 
@@
 Selection of negatives is the set of all nearest neighbors that are \textit{negatives}.
-There is no explicit attempt to filter out\textit{hard negatives} in the approach.
+There is no explicit attempt to filter out \textit{hard negatives} in the approach.
 The overall idea is that the set of negatives that appear in the nearest neighbor set at input are in fact the most important elements for the network to learn to discriminate from positives for a join.

### 2018-10-21 build_model.py
renamed two files and added attemtp at preloaded model CHANGED ONE IMPORT

@@ -1,0 +1,627 @@
+from random import shuffle
+
+import numpy as np
+# import pandas
+import tensorflow as tf
+import random as random
+import json
+
+from keras import backend as K
+
+from keras.preprocessing.text import Tokenizer
+from keras.preprocessing.sequence import pad_sequences
+
+from keras.layers import Dense, Input, Flatten, Dropout, Lambda, GRU, Activation
+from keras.layers.wrappers import Bidirectional
+
+from keras.layers import Conv1D, MaxPooling1D, Embedding
+
+from keras.models import Model, model_from_json, Sequential
+
+from embeddings import KazumaCharEmbedding
+
+from annoy import AnnoyIndex
+
+from keras.callbacks import ModelCheckpoint, EarlyStopping
+
+from names_cleanser import NameDataCleanser, CompanyDataCleanser
+
+import sys
+
+import statistics 
+from scipy.stats.mstats import gmean
+
+import argparse
+
+#must fix
+MAX_NB_WORDS = 140000
+EMBEDDING_DIM = 100
+MAX_SEQUENCE_LENGTH = 10
+MARGIN=10
+ALPHA=45
+
+DEBUG = False
+DEBUG_DATA_LENGTH = 100
+DEBUG_ANN = False
+
+USE_ANGULAR_LOSS=False
+LOSS_FUNCTION=None
+TRAIN_NEIGHBOR_LEN=20
+TEST_NEIGHBOR_LEN=20
+EMBEDDING_TYPE = 'Kazuma'
+NUM_LAYERS = 3
+USE_L2_NORM = False
+filepath="weights.best.hdf5"
+
+output_file_name_for_hpo = "val_dict_list.json"
+
+def f1score(positive, negative):
+    #labels[predictions.ravel() < 0.5].sum()
+    fsocre = 0.0
+    true_positive = 0.0
+    false_positive = 0
+    false_negitive = 0
+    for i in range(len(positive)):
+        if positive[i] <= negative[i]:
+            true_positive += 1
+        else:
+            false_negitive += 1
+            false_positive += 1
+    print('tp' + str(true_positive))
+    print('fp' + str(false_positive))
+    print('fn' + str(false_negitive))
+    fscore = (2 * true_positive) / ((2 * true_positive) + false_negitive + false_positive)
+    return fscore 
+
+
+def get_embedding_layer(tokenizer):
+    word_index = tokenizer.word_index
+    num_words = len(word_index) + 1
[…]

### 2018-10-21 preloaded_runner.py

@@ -1,0 +1,592 @@
+from random import shuffle
+
+import numpy as np
+
+import tensorflow as tf
+print('yay')
+import random as random
+import json
+from keras import backend as K
+
+from keras.preprocessing.text import Tokenizer
+from keras.preprocessing.sequence import pad_sequences
+
+from keras.layers import Dense, Input, Flatten, Dropout, Lambda, GRU, Activation
+from keras.layers.wrappers import Bidirectional
+
+from keras.layers import Conv1D, MaxPooling1D, Embedding
+
+from keras.models import Model, model_from_json, Sequential
+
+from embeddings import KazumaCharEmbedding
+
+from annoy import AnnoyIndex
+
+from keras.callbacks import ModelCheckpoint, EarlyStopping
+
+from names_cleanser import NameDataCleanser, CompanyDataCleanser
+
+import sys
+
+import statistics 
+from scipy.stats.mstats import gmean
+
+import argparse
+# from build_model import read_entities, generate_names, build_unique_entities, get_embedding_layer, embedded_representation_model,generate_triplets_from_ANN
+#must fix
+MAX_NB_WORDS = 140000
+EMBEDDING_DIM = 100
+MAX_SEQUENCE_LENGTH = 10
+MARGIN=10
+ALPHA=45
+
+DEBUG = False
+DEBUG_DATA_LENGTH = 100
+DEBUG_ANN = False
+
+USE_ANGULAR_LOSS=False
+LOSS_FUNCTION=None
+TRAIN_NEIGHBOR_LEN=20
+TEST_NEIGHBOR_LEN=20
+EMBEDDING_TYPE = 'Kazuma'
+NUM_LAYERS = 3
+USE_L2_NORM = False
+filepath="weights.best.hdf5"
+
+
+def f1score(positive, negative):
+    #labels[predictions.ravel() < 0.5].sum()
+    fsocre = 0.0
+    true_positive = 0.0
+    false_positive = 0
+    false_negitive = 0
+    for i in range(len(positive)):
+        if positive[i] <= negative[i]:
+            true_positive += 1
+        else:
+            false_negitive += 1
+            false_positive += 1
+    print('tp' + str(true_positive))
+    print('fp' + str(false_positive))
+    print('fn' + str(false_negitive))
+    fscore = (2 * true_positive) / ((2 * true_positive) + false_negitive + false_positive)
+    return fscore 
+
+
+def get_embedding_layer(tokenizer):
[…]

### 2018-10-21 preloaded_runner.py
working loading

@@ -429,11 +429,12 @@ def embedded_representation_model(embedding_layer):
     return seq
 
 
-def build_model_from_weights(embedder, weights_file):
+def build_model_from_weights(weights_file):
+    embedder = embedding_layer = Embedding(157495, EMBEDDING_DIM, input_length=MAX_SEQUENCE_LENGTH, trainable=False)
     main_input = Input(shape=(MAX_SEQUENCE_LENGTH,))
     net = embedder(main_input)
 
-    for i in range(0, 3):
+    for i in range(0, 2):
         net = GRU(128, return_sequences=True, activation='relu', name='embed' + str(i))(net)
     net = GRU(128, activation='relu', name='embed' + str(i+1))(net)
     
@@ -558,22 +559,22 @@ sequences_test = pad_sequences(sequences_test, maxlen=MAX_SEQUENCE_LENGTH)
 
 # build models
 embedder =  get_embedding_layer(tokenizer)
-model, test_positive_model, test_negative_model, inter_model = build_model(embedder, args.model)
-embedder_model =  embedded_representation_model(embedder)
+model, test_positive_model, test_negative_model, inter_model = build_model_from_weights(args.model)
+#embedder_model =  embedded_representation_model(embedder)
 
 
-test_data, test_match_stats = generate_triplets_from_ANN(embedder_model, sequences_test, entity2unique_test, entity2same_test, unique_text_test, False)
-test_seq = get_sequences(test_data, tokenizer)
-print("Test stats:" + str(test_match_stats))
+#test_data, test_match_stats = generate_triplets_from_ANN(embedder_model, sequences_test, entity2unique_test, entity2same_test, unique_text_test, False)
+#test_seq = get_sequences(test_data, tokenizer)
+#print("Test stats:" + str(test_match_stats))
 
-counter = 0
-current_model = embedder_model
-prev_match_stats = 0
+#counter = 0
+#current_model = embedder_model
+#prev_match_stats = 0
 
 
-number_of_names = len(test_data['anchor'])
+#number_of_names = len(test_data['anchor'])
 # print(train_data['anchor'])
-print("number of names" + str(number_of_names))
+#print("number of names" + str(number_of_names))
 
 
 
@@ -583,9 +584,9 @@ current_model = inter_model
 # print some statistics on this epoch
 
 print("test data predictions")
-positives = test_positive_model.predict([test_seq['anchor'], test_seq['positive'], test_seq['negative']])
[…]

### 2018-10-21 preloaded_runner.py
finished preloaded runner

@@ -429,8 +429,8 @@ def embedded_representation_model(embedding_layer):
     return seq
 
 
-def build_model_from_weights(weights_file):
-    embedder = embedding_layer = Embedding(157495, EMBEDDING_DIM, input_length=MAX_SEQUENCE_LENGTH, trainable=False)
+def build_model_from_weights(weights_file, embbeding_dimensions):
+    embedder = embedding_layer = Embedding(embbeding_dimensions, EMBEDDING_DIM, input_length=MAX_SEQUENCE_LENGTH, trainable=False)
     main_input = Input(shape=(MAX_SEQUENCE_LENGTH,))
     net = embedder(main_input)
 
@@ -463,7 +463,13 @@ def build_model_from_weights(weights_file):
                     name='stacked_dists', output_shape=(3, 1)
                     )([a_p, n_c])
         model = Model([input_anchor, input_positive, input_negative], stacked_dists, name='triple_siamese')
-        model.load_weights(weights_file)
+        try:
+            model.load_weights(weights_file)
+        except ValueError as e:
+            full = str(e)
+            #https://stackoverflow.com/questions/4289331/python-extract-numbers-from-a-string
+            new_emb = [int(num) for num in full.replace('.', ' ').split() if num.isdigit()]
+            return build_model_from_weights(weights_file, new_emb[2])
         model.compile(optimizer="rmsprop", loss=angular_loss, metrics=[accuracy])
     else:
         exemplar_negative_dist = Lambda(euclidean_distance, name='exemplar_neg_dist', output_shape=(1,))([net_positive, net_negative])
@@ -474,7 +480,13 @@ def build_model_from_weights(weights_file):
                     )([positive_dist, negative_dist, exemplar_negative_dist])
 
         model = Model([input_anchor, input_positive, input_negative], stacked_dists, name='triple_siamese')
-        model.load_weights(weights_file)
+        try:
+            model.load_weights(weights_file)
+        except ValueError as e:
+            full = str(e)
+            #https://stackoverflow.com/questions/4289331/python-extract-numbers-from-a-string
+            new_emb = [int(num) for num in full.replace('.', ' ').split() if num.isdigit()]
+            return build_model_from_weights(weights_file, new_emb[2])
         model.compile(optimizer="rmsprop", loss=LOSS_FUNCTION, metrics=[accuracy])
     test_positive_model = Model([input_anchor, input_positive, input_negative], positive_dist)
[…]

### 2018-10-21 random_test_selecter.py

@@ -1,0 +1,11 @@
+from sys import argv
+from random import shuffle
+input_file = open(argv[1], 'r')
+output_file = open(argv[2], 'w')
+lines = input_file.readlines()
+shuffle(lines)
+lines = lines[-int(argv[3]):]
+for line in lines:
+	output_file.write(line)
+input_file.close()
+output_file.close()

### 2018-10-21 old/paper/previos_work.tex
reorgonized directory

\section{Related Works}
There have been a number of attempts to solve the fuzzy join problem. Many of the attempts use various string matching algorithms for example \cite{Wang:String}. The main issue with using string matching comparisons is that they do not work across a wide variety of entities. To our knowledge no serious machine learning approach has been used for this problem. The problem of blocking has also been dealt with using MapReduce \cite{Vernica:MapReduce}. This approach requires a lot of computing power and, since they use a string matching approach in the end, is hard to generalize across many types of entities. There has also been work done on a related yet different problem of fuzzy joining on whole rows \cite{he_ganjam_chu_2015}. We deal with the case where we only have one column of information.

### 2018-10-21 old/paper/vldb_sample.tex
reorgonized directory

% THIS IS AN EXAMPLE DOCUMENT FOR VLDB 2012
% based on ACM SIGPROC-SP.TEX VERSION 2.7
% Modified by  Gerald Weber <gerald@cs.auckland.ac.nz>
% Removed the requirement to include *bbl file in here. (AhmetSacan, Sep2012)
% Fixed the equation on page 3 to prevent line overflow. (AhmetSacan, Sep2012)

\documentclass{vldb}
\usepackage{graphicx}
\usepackage{balance}  % for  \balance command ON LAST PAGE  (only there!)

\begin{document}

% ****************** TITLE ****************************************

\title{A Sample {\ttlit Proceedings of the VLDB Endowment} Paper in LaTeX
Format\titlenote{for use with vldb.cls}}

% possible, but not really needed or used for PVLDB:
%\subtitle{[Extended Abstract]
%\titlenote{A full version of this paper is available as\textit{Author's Guide to Preparing ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and BibTeX} at \texttt{www.acm.org/eaddress.htm}}}

% ****************** AUTHORS **************************************

% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{8} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.

\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Ben Trovato\titlenote{Dr.~Trovato insisted his name be first.}\\
       \affaddr{Institute for Clarity in Documentation}\\
       \affaddr{1932 Wallamaloo Lane}\\
       \affaddr{Wallamaloo, New Zealand}\\
       \email{trovato@corporation.com}
% 2nd. author
\alignauthor
G.K.M. Tobin\titlenote{The secretary disavows
any knowledge of this author's actions.}\\
       \affaddr{Institute for Clarity in Documentation}\\
       \affaddr{P.O. Box 1212}\\
       \affaddr{Dublin, Ohio 43017-6221}\\
       \email{webmaster@marysville-ohio.com}
% 3rd. author
\alignauthor Lars Th{\Large{\sf{\o}}}rv{$\ddot{\mbox{a}}$}ld\titlenote{This author is the
one who did all the really hard work.}\\
       \affaddr{The Th{\large{\sf{\o}}}rv{$\ddot{\mbox{a}}$}ld Group}\\
       \affaddr{1 Th{\large{\sf{\o}}}rv{$\ddot{\mbox{a}}$}ld Circle}\\
       \affaddr{Hekla, Iceland}\\
       \email{larst@affiliation.org}
\and  % use '\and' if you need 'another row' of author names
% 4th. author
\alignauthor Lawrence P. Leipuner\\
       \affaddr{Brookhaven Laboratories}\\
       \affaddr{Brookhaven National Lab}\\
       \affaddr{P.O. Box 5000}\\
       \email{lleipuner@researchlabs.org}
% 5th. author
\alignauthor Sean Fogarty\\
       \affaddr{NASA Ames Research Center}\\
       \affaddr{Moffett Field}\\
       \affaddr{California 94035}\\
       \email{fogartys@amesres.org}
% 6th. author
\alignauthor Charles Palmer\\
       \affaddr{Palmer Research Laboratories}\\
       \affaddr{8600 Datapoint Drive}\\
       \affaddr{San Antonio, Texas 78229}\\
       \email{cpalmer@prl.com}
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
\additionalauthors{Additional authors: John Smith (The Th{\o}rv\"{a}ld Group, {\texttt{jsmith@affiliation.org}}), Julius P.~Kumquat
(The \raggedright{Kumquat} Consortium, {\small \texttt{jpkumquat@consortium.net}}), and Ahmet Sacan (Drexel University, {\small \texttt{ahmetdevel@gmail.com}})}
\date{30 July 1999}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

\maketitle

\begin{abstract}
The abstract for your paper for the PVLDB Journal submission.
The template and the example document are based on the ACM SIG Proceedings  templates. This file is part of a package for preparing the submissions for review. These files are in the camera-ready format, but they do not contain the full copyright note.
Note that after the notification of acceptance, there will be an updated style file for the camera-ready submission containing the copyright note.
\end{abstract}

\section{Introduction}
The \textit{proceedings} are the records of a conference.
ACM, as well as PVLDB, seeks to give these conference by-products a uniform,
high-quality appearance.  To do this, ACM / PVLDB has some rigid
requirements for the format of the proceedings documents: there
is a specified format (balanced  double columns), a specified
set of fonts (Arial or Helvetica and Times Roman) in
certain specified sizes (for instance, 9 point for body copy),
a specified live area (18 $\times$ 23.5 cm [7" $\times$ 9.25"]) centered on
the page, specified size of margins (2.54cm [1"] top and
bottom and 1.9cm [.75"] left and right; specified column width
(8.45cm [3.33"]) and gutter size (.083cm [.33"]).

The good news is, with only a handful of manual
settings\footnote{Two of these, the {\texttt{\char'134 numberofauthors}}
and {\texttt{\char'134 alignauthor}} commands, you have
already used; another, {\texttt{\char'134 balancecolumns}}, will
be used in your very last run of \LaTeX\ to ensure
balanced column heights on the last page.}, the \LaTeX\ document
class file handles all of this for you.

The remainder of this document is concerned with showing, in
the context of an ``actual'' document, the \LaTeX\ commands
specifically available for denoting the structure of a
proceedings paper, rather than with giving rigorous descriptions
or explanations of such commands.

\section{The {\secit Body} of The Paper}
Typically, the body of a paper is organized
into a hierarchical structure, with numbered or unnumbered
headings for sections, subsections, sub-subsections, and even
smaller sections.  The command \texttt{{\char'134}section} that
precedes this paragraph is part of such a
hierarchy.\footnote{This is the second footnote.  It
starts a series of three footnotes that add nothing
informational, but just give an idea of how footnotes work
and look. It is a wordy one, just so you see
how a longish one plays out.} \LaTeX\ handles the numbering
and placement of these headings for you, when you use
the appropriate heading commands around the titles
of the headings.  If you want a sub-subsection or
smaller part to be unnumbered in your output, simply append an
asterisk to the command name.  Examples of both
numbered and unnumbered headings will appear throughout the
balance of this sample document.

Because the entire article is contained in
the \textbf{document} environment, you can indicate the
start of a new paragraph with a blank line in your
input file; that is why this sentence forms a separate paragraph.

\subsection{Type Changes and {\subsecit Special} Characters}
We have already seen several typeface changes in this sample.  You
can indicate italicized words or phrases in your text with
the command \texttt{{\char'134}textit}; emboldening with the
command \texttt{{\char'134}textbf}
and typewriter-style (for instance, for computer code) with
\texttt{{\char'134}texttt}.  But remember, you do not
have to indicate typestyle changes when such changes are
part of the \textit{structural} elements of your
article; for instance, the heading of this subsection will
be in a sans serif\footnote{A third footnote, here.
Let's make this a rather short one to
see how it looks.} typeface, but that is handled by the
document class file. Take care with the use
of\footnote{A fourth, and last, footnote.}
the curly braces in typeface changes; they mark
the beginning and end of
the text that is to be in the different typeface.

You can use whatever symbols, accented characters, or
non-English characters you need anywhere in your document;
you can find a complete list of what is
available in the \textit{\LaTeX\
User's Guide}\cite{Lamport:LaTeX}.

\subsection{Math Equations}
You may want to display math equations in three distinct styles:
inline, numbered or non-numbered display.  Each of
the three are discussed in the next sections.

\subsubsection{Inline (In-text) Equations}
A formula that appears in the running text is called an
inline or in-text formula.  It is produced by the
\textbf{math} environment, which can be
invoked with the usual \texttt{{\char'134}begin. . .{\char'134}end}
construction or with the short form \texttt{\$. . .\$}. You
can use any of the symbols and structures,
from $\alpha$ to $\omega$, available in
\LaTeX\cite{Lamport:LaTeX}; this section will simply show a
few examples of in-text equations in context. Notice how
this equation: \begin{math}\lim_{n\rightarrow \infty}x=0\end{math},
set here in in-line math style, looks slightly different when
set in display style.  (See next section).

\subsubsection{Display Equations}
A numbered display equation -- one set off by vertical space
from the text and centered horizontally -- is produced
by the \textbf{equation} environment. An unnumbered display
equation is produced by the \textbf{displaymath} environment.

Again, in either environment, you can use any of the symbols
and structures available in \LaTeX; this section will just
give a couple of examples of display equations in context.
First, consider the equation, shown as an inline equation above:
\begin{equation}\lim_{n\rightarrow \infty}x=0\end{equation}
Notice how it is formatted somewhat differently in
the \textbf{displaymath}
environment.  Now, we'll enter an unnumbered equation:
\begin{displaymath}\sum_{i=0}^{\infty} x + 1\end{displaymath}
and follow it with another numbered equation:
\begin{equation}\sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f\end{equation}
just to demonstrate \LaTeX's able handling of numbering.

\subsection{Citations}
Citations to articles \cite{bowman:reasoning, clark:pct, braams:babel, herlihy:methodology},
conference
proceedings \cite{clark:pct} or books \cite{salas:calculus, Lamport:LaTeX} listed
in the Bibliography section of your
article will occur throughout the text of your article.
You should use BibTeX to automatically produce this bibliography;
you simply need to insert one of several citation commands with
a key of the item cited in the proper location in
the \texttt{.tex} file \cite{Lamport:LaTeX}.
The key is a short reference you invent to uniquely
identify each work; in this sample document, the key is
the first author's surname and a
word from the title.  This identifying key is included
with each item in the \texttt{.bib} file for your article.

The details of the construction of the \texttt{.bib} file
are beyond the scope of this sample document, but more
information can be found in the \textit{Author's Guide},
and exhaustive details in the \textit{\LaTeX\ User's
Guide}\cite{Lamport:LaTeX}.

This article shows only the plainest form
of the citation command, using \texttt{{\char'134}cite}.
This is what is stipulated in the SIGS style specifications.
No other citation format is endorsed.

\subsection{Tables}
Because tables cannot be split across pages, the best
placement for them is typically the top of the page
nearest their initial cite.  To
ensure this proper ``floating'' placement of tables, use the
environment \textbf{table} to enclose the table's contents and
the table caption.  The contents of the table itself must go
in the \textbf{tabular} environment, to
be aligned properly in rows and columns, with the desired
horizontal and vertical rules.  Again, detailed instructions
on \textbf{tabular} material
is found in the \textit{\LaTeX\ User's Guide}.

Immediately following this sentence is the point at which
Table 1 is included in the input file; compare the
placement of the table here with the table in the printed
dvi output of this document.

\begin{table}
\centering
\caption{Frequency of Special Characters}
\begin{tabular}{|c|c|l|} \hline
Non-English or Math&Frequency&Comments\\ \hline
\O & 1 in 1,000& For Swedish names\\ \hline
$\pi$ & 1 in 5& Common in math\\ \hline
\$ & 4 in 5 & Used in business\\ \hline
$\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
\hline\end{tabular}
\end{table}

To set a wider table, which takes up the whole width of
the page's live area, use the environment
\textbf{table*} to enclose the table's contents and
the table caption.  As with a single-column table, this wide
table will ``float" to a location deemed more desirable.
Immediately following this sentence is the point at which
Table 2 is included in the input file; again, it is
instructive to compare the placement of the
table here with the table in the printed dvi
output of this document.

\begin{table*}
\centering
\caption{Some Typical Commands}
\begin{tabular}{|c|c|l|} \hline
Command&A Number&Comments\\ \hline
\texttt{{\char'134}alignauthor} & 100& Author alignment\\ \hline
\texttt{{\char'134}numberofauthors}& 200& Author enumeration\\ \hline
\texttt{{\char'134}table}& 300 & For tables\\ \hline
\texttt{{\char'134}table*}& 400& For wider tables\\ \hline\end{tabular}
\end{table*}
% end the environment with {table*}, NOTE not {table}!

\subsection{Figures}
Like tables, figures cannot be split across pages; the
best placement for them
is typically the top or the bottom of the page nearest
their initial cite.  To ensure this proper ``floating'' placement
of figures, use the environment
\textbf{figure} to enclose the figure and its caption.

This sample document contains examples of \textbf{.pdf} files to be
displayable with \LaTeX (See Figures \ref{fig:fly} and \ref{fig:bigfly}).  More details on each of these is found in the
\textit{Author's Guide}.

\begin{figure}
\centering
\includegraphics{fly}
\caption{A sample black and white graphic (.pdf format).}
\label{fig:fly}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=1in,height=1in]{fly}
\caption{A sample black and white graphic (.pdf format)
that has been resized with the \texttt{includegraphics} command.}
\label{fig:bigfly}
\end{figure}

As was the case with tables, you may want a figure
that spans two columns.  To do this, and still to
ensure proper ``floating'' placement of tables, use the environment
\textbf{figure*} to enclose the figure and its caption (See Figure~\ref{fig:flies}). And don't forget to end the environment with {figure*}, not {figure}!

\begin{figure*}
\centering
\includegraphics{flies}
\caption{A sample black and white graphic (.pdf format)
that needs to span two columns of text.}
\label{fig:flies}
\end{figure*}

Note that only {\textbf{.pdf}} files were used; if you want to include
{\textbf{.ps}} or {\textbf{.eps}} formats, you can use the
\texttt{{\char'134}epsfig} or \texttt{{\char'134}psfig}
commands as appropriate for the different file types.

\subsection{Theorem-like Constructs}
Other common constructs that may occur in your article are
the forms for logical constructs like theorems, axioms,
corollaries and proofs.  There are
two forms, one produced by the
command \texttt{{\char'134}newtheorem} and the
other by the command \texttt{{\char'134}newdef}; perhaps
the clearest and easiest way to distinguish them is
to compare the two in the output of this sample document:

This uses the \textbf{theorem} environment, created by
the\linebreak\texttt{{\char'134}newtheorem} command:
\newtheorem{theorem}{Theorem}
\begin{theorem}
Let $f$ be continuous on $[a,b]$.  If $G$ is
an antiderivative for $f$ on $[a,b]$, then
\begin{displaymath}\int^b_af(t)dt = G(b) - G(a).\end{displaymath}
\end{theorem}

The other uses the \textbf{definition} environment, created
by the \texttt{{\char'134}newdef} command:
\newdef{definition}{Definition}
\begin{definition}
If $z$ is irrational, then by $e^z$ we mean the
unique number which has
logarithm $z$: \begin{displaymath}{\log e^z = z}\end{displaymath}
\end{definition}

Two lists of constructs that use one of these
forms is given in the
\textit{Author's  Guidelines}.

There is one other similar construct environment, which is
already set up
for you; i.e. you must \textit{not} use
a \texttt{{\char'134}newdef} command to
create it: the \textbf{proof} environment.  Here
is a example of its use:
\begin{proof}
Suppose on the contrary there exists a real number $L$ such that
\begin{displaymath}
\lim_{x\rightarrow\infty} \frac{f(x)}{g(x)} = L.
\end{displaymath}
Then
\begin{align*}
l&=\lim_{x\rightarrow c} f(x)
= \lim_{x\rightarrow c}
\left[ g{x} \cdot \frac{f(x)}{g(x)} \right ] \\
&= \lim_{x\rightarrow c} g(x) \cdot \lim_{x\rightarrow c}
\frac{f(x)}{g(x)} = 0\cdot L = 0,
\end{align*}
which contradicts our assumption that $l\neq 0$.
\end{proof}

Complete rules about using these environments and using the
two different creation commands are in the
\textit{Author's Guide}; please consult it for more
detailed instructions.  If you need to use another construct,
not listed therein, which you want to have the same
formatting as the Theorem
or the Definition\cite{salas:calculus} shown above,
use the \texttt{{\char'134}newtheorem} or the
\texttt{{\char'134}newdef} command,
respectively, to create it.

\subsection*{A {\secit Caveat} for the \TeX\ Expert}
Because you have just been given permission to
use the \texttt{{\char'134}newdef} command to create a
new form, you might think you can
use \TeX's \texttt{{\char'134}def} to create a
new command: \textit{Please refrain from doing this!}
Remember that your \LaTeX\ source code is primarily intended
to create camera-ready copy, but may be converted
to other forms -- e.g. HTML. If you inadvertently omit
some or all of the \texttt{{\char'134}def}s recompilation will
be, to say the least, problematic.

\section{Conclusions}
This paragraph will end the body of this sample document.
Remember that you might still have Acknowledgments or
Appendices; brief samples of these
follow.  There is still the Bibliography to deal with; and
we will make a disclaimer about that here: with the exception
of the reference to the \LaTeX\ book, the citations in
this paper are to articles which have nothing to
do with the present subject and are used as
examples only.
%\end{document}  % This is where a 'short' article might terminate

% ensure same length columns on last page (might need two sub-sequent latex runs)
\balance

%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}
This section is optional; it is a location for you
to acknowledge grants, funding, editing assistance and
what have you.  In the present case, for example, the
authors would like to thank Gerald Murray of ACM for
his help in codifying this \textit{Author's Guide}
and the \textbf{.cls} and \textbf{.tex} files that it describes.

% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{vldb_sample}  % vldb_sample.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references

\subsection{References}
Generated by bibtex from your ~.bib file.  Run latex,
then bibtex, then latex twice (to resolve references).

%APPENDIX is optional.
% ****************** APPENDIX **************************************
% Example of an appendix; typically would start on a new page
%pagebreak

\begin{appendix}
You can use an appendix for optional proofs or details of your evaluation which are not absolutely necessary to the core understanding of your paper.

\section{Final Thoughts on Good Layout}
Please use readable font sizes in the figures and graphs. Avoid tempering with the correct border values, and the spacing (and format) of both text and captions of the PVLDB format (e.g. captions are bold).

At the end, please check for an overall pleasant layout, e.g. by ensuring a readable and logical positioning of any floating figures and tables. Please also check for any line overflows, which are only allowed in extraordinary circumstances (such as wide formulas or URLs where a line wrap would be counterintuitive).

Use the \texttt{balance} package together with a \texttt{\char'134 balance} command at the end of your document to ensure that the last page has balanced (i.e. same length) columns.

\end{appendix}

\end{document}

### 2018-10-21 old/paper2018/introduction.tex
reorgonized directory

--- 2018-08-20 paper2018/introduction.tex
@@
 
-Merging datasets is a key operation for data analytics.
-A frequent requirement for merging is a join between two columns that frequently have different surface representations for the same entity (e.g., the name of a person might be represented as \textit{Douglas Adams} or \textit{Douglas Noel Adams}, as shown in Table~\ref{table-example}.
+Merging datasets is a key operation for data analytics.  A frequent
+requirement for merging is joining across columns that have
+different surface forms for the same entity (e.g., the name of a
+person might be represented as \textit{Douglas Adams},
+\textit{Adams, Douglas} or \textit{Douglas Noel Adams}).  Similarly,
+ontology alignment can require recognizing distinct surface forms of
+the same entity, especially when ontologies are independently
+developed.
 This problem occurs for many entity types such as people's names, company names, addresses, product descriptions, conference venues, or even people's faces.
@@
 In applying fuzzy joins, a key problem is to avoid quadratic comparisons between pairs of strings drawn from the two columns.
-A blocking strategy is used to reduce the number of pairs for fuzzy joins, such that only strings that share a common prefix, or suffix will be compared further.
-String matching algorithms often do not work however, because transformations of entity names in perfectly valid ways can yield very different strings.
+A blocking strategy is used to reduce the number of pairs for fuzzy joins, e.g.
+only strings that share a common prefix or suffix will be compared further.
+But such strategies based on strings often do not work because transformations of entity names in perfectly valid ways can yield very different strings.
 As shown in Table~\ref{table-example}, \textit{John Smith} is more similar to \textit{John Adams} than \textit{Adams, John}, but of course it is \textit{Adams, John} that is the valid alternate surface form for \textit{John Adams}.
@@
 
-Specifically, our solution to the join problem involves building a system that performs deep metric learning.
-That is, the network learns is to map input vectors corresponding to same entity closer in vector space compared to vectors that correspond to different entities.
+Specifically, our solution to the join problem involves building a system that performs deep metric learning: the network learns to map input vectors corresponding to same entity closer in vector space than vectors corresponding to different entities.
 For the closely related problem of face recognition and person re-identification, deep learning networks have been used successfully to discriminate pairs that represent the same entity from pairs that do not.
 However, simply building a model that discriminates pairs of entities is not sufficient; if used naively, this would mean a quadratic comparison between cell values in the two columns to be joined.
-We know of no work that has adapted these techniques to the problem of how to use such deep learning models to perform joins efficiently for different surface forms of the same entity.
+We know of no prior work that has adapted these techniques to the problem of how to use such deep learning models to perform joins efficiently for different surface forms of the same entity.
 
 As in face recognition, our system for metric learning is built by training a `triplet siamese network' to learn to map different surface forms of the same entity closer in vector space than different forms of the same entity.
-Entity names have very different properties from faces, so we needed to adapt the approaches used in face recognition to the problem of matching entity names with a novel method to choose the sample for training, and novel loss functions as objectives for the metric learning problem.
+Entity names have very different properties from faces, so we needed to adapt the approaches used in face recognition to the problem of matching entity names.
+We use a novel method to choose the sample for training, and novel loss functions as objectives for the metric learning problem.
 At training, the network is given a triplet consisting of an `anchor' (e.g.
 \textit{Douglas Adams}), a positive element (e.g.
-\textit{Douglas Noel Adams}) and a negative element (e.g., John Adams), and it learns to produce a small distance estimate for the positive pair (close to 0), and a large distance estimate for the negative pair, using an objective function.
+\textit{Adams, Douglas}) and a negative element (e.g., \textit{John Adams}), and it learns to produce a small distance estimate for the positive pair (close to 0), and a large distance estimate for the negative pair, using an objective function.
 A classification form of this function that simply learns whether two names belong to the same entity can be used to perform fuzzy joins, but then we would need a blocking strategy analogous to what has been used in the literature to identify the set of joinable pairs \cite{auto-join-joining-tables-leveraging-transformations}.

### 2018-10-21 preloaded_runner.py
wrote a simple readme

@@ -3,7 +3,6 @@ from random import shuffle
 import numpy as np
 
 import tensorflow as tf
-print('yay')
 import random as random
 import json
 from keras import backend as K

### 2018-10-22 build_model.py
added serializing

@@ -1,5 +1,5 @@
 from random import shuffle
-
+import pickle
 import numpy as np
 # import pandas
 import tensorflow as tf
@@ -607,6 +607,7 @@ early_stop = EarlyStopping(monitor='val_accuracy', patience=1, mode='max')
 callbacks_list = [checkpoint, early_stop]
 
 train_seq = get_sequences(train_data, tokenizer)
+pickle.dump( tokenizer, open( 'tokenizer' + args.model, "wb" ))
 
 # check just for 5 epochs because this gets called many times
 model.fit([train_seq['anchor'], train_seq['positive'], train_seq['negative']], Y_train, epochs=100,  batch_size=40, callbacks=callbacks_list, validation_split=0.2)

### 2018-10-22 build_model.py
added serializing to tokenizer

@@ -607,7 +607,7 @@ early_stop = EarlyStopping(monitor='val_accuracy', patience=1, mode='max')
 callbacks_list = [checkpoint, early_stop]
 
 train_seq = get_sequences(train_data, tokenizer)
-pickle.dump( tokenizer, open( 'tokenizer' + args.model, "wb" ))
+pickle.dump( tokenizer, open( filepath + '.tokenizer.pickle' , "wb" ))
 
 # check just for 5 epochs because this gets called many times
 model.fit([train_seq['anchor'], train_seq['positive'], train_seq['negative']], Y_train, epochs=100,  batch_size=40, callbacks=callbacks_list, validation_split=0.2)

### 2018-10-22 preloaded_runner.py

@@ -1,5 +1,5 @@
 from random import shuffle
-
+import pickle
 import numpy as np
 
 import tensorflow as tf
@@ -553,7 +553,8 @@ print(str(entity2same_test).encode('utf-8'))
 
 # change the default behavior of the tokenizer to ignore all punctuation except , - and . which are important
 # clues for entity names
-tokenizer = Tokenizer(num_words=MAX_NB_WORDS, lower=True, filters='!"#$%&()*+/:;<=>?@[\]^_`{|}~', split=" ")   
+tokenizer = pickle.load(open(args.model + '.tokenizer.pickle', 'rb'))
+#Tokenizer(num_words=MAX_NB_WORDS, lower=True, filters='!"#$%&()*+/:;<=>?@[\]^_`{|}~', split=" ")   
 
 # build a set of data structures useful for annoy, the set of unique entities (unique_text), 
 # a mapping of entities in texts to an index in unique_text, a mapping of entities to other same entities, and the actual
@@ -563,14 +564,16 @@ unique_text_test, entity2unique_test =  build_unique_entities(entity2same_test)
 
 print("test text len:" + str(len(unique_text_test)))
 
-tokenizer.fit_on_texts(unique_text_test)
+#tokenizer.fit_on_texts(unique_text_test)
 
 sequences_test = tokenizer.texts_to_sequences(unique_text_test)
 sequences_test = pad_sequences(sequences_test, maxlen=MAX_SEQUENCE_LENGTH)
 
 # build models
 #embedder =  get_embedding_layer(tokenizer)
-model, test_positive_model, test_negative_model, inter_model = build_model_from_weights(args.model, 0)
+word_index = tokenizer.word_index
+num_words = len(word_index) + 1
+model, test_positive_model, test_negative_model, inter_model = build_model_from_weights(args.model, num_words)
 #embedder_model =  embedded_representation_model(embedder)
 
 

### 2018-10-22 build_model.py
added serializing test data

@@ -547,7 +547,7 @@ print("TRAIN")
 print(str(train).encode('utf-8'))
 print("TEST")
 print(str(test).encode('utf-8'))
-
+pickle.dump(test, open(filepath + '.test_data.pickle', 'wb'))
 entity2same_train = generate_names(train, people)
 entity2same_test = generate_names(test, people, limit_pairs=True)
 print(str(entity2same_train).encode('utf-8'))

### 2018-10-22 preloaded_runner.py

@@ -513,6 +513,7 @@ parser.add_argument('--entity_type', type=str, help='people or companies')
 
 parser.add_argument('--model', type=str, help='name for model file')
 
+parser.add_argument('--previos_test', type=str, help='use previos test data')
 
 args = parser.parse_args()
 
@@ -542,7 +543,10 @@ print('Loss function: ' + args.loss_function)
 people = 'people' in args.entity_type
 
 # read all entities and create positive parts of a triplet
-test =  read_entities(args.input)
+if args.previos_test and args.previos_test.lower() in ("yes", "true", "t", "1"):
+    test = pickle.load(open(filepath + '.test_data.pickle', 'rb'))
+else:
+    test =  read_entities(args.input)
 
 print("TEST")
 print(str(test).encode('utf-8'))

### 2018-10-22 old/paper/drlim.tex

--- 2018-03-08 paper/drlim.tex
@@
-\subsection{Dimensionality Reduction by Learning an Invariant Mapping}
+\subsection{Siamese Network}
 
-The problem of dimensionality reduction, mapping a high dimensional group of entities onto a low dimensional manifold, is an important problem in many areas of machine learning.
-Dimensionality Reduction by Learning an Invariant Mapping is a technique for solving this problem by mapping points onto the manifold using a set of previously known matches and non-matches described by \cite{Hasdell:Siamese}.
+ A method for logically mapping a set of points onto a manifold using a set of previously known matches and non-matches is described by \cite{Hasdell:Siamese}.
 The goal of this technique is to minimize the distance between matched pairs and maximize the distance between unmatched pairs.
-This is accomplished using a network architecture know as a \textit{siamese} network.
+This is accomplished using a network architecture know as a \textit{Siamese} network.
 In this architecture there are two deep neural networks that share weights attached to a final layer that determines the distance between the output of the two hidden networks and minimizes the loss function.
-.
 To train the network a set of matched and non-matched pairs of inputs is sent through the network and the weights are adjusted to maximize or minimize distance accordingly.
+This is accomplished using the following loss function \[ L(W, Y, \vec{X}_1, \vec{X}_2) = (1 - Y)\frac{1}{2}(D_W)^2 + (Y)\frac{1}{2}\{max(0, m - (D_W))\}^2\] Where \(D_W\) is the euclidean distance between the two outputs, \textit{m} is a radius beyond which we ignore dissimilar points, and Y is the dissimilar label.
 

### 2018-10-22 old/paper/paper.tex

--- 2018-05-09 paper/paper.tex
@@
 \subsection{Rule Based}
-If we treat it as a success if there is a correct match in any of the first three slots, we get an F\textsubscript{1} score of 0.7.
-Since the issue is mostly false negatives, and therefore even some of the first three slots were often empty, so even if we accept any of the top 1000 as a success, we get FSCORE2, not much better.
+To test the rule based matcher we ran the blocker followed by the matcher and calculated F-scores based on how many correct matches were in the top 3.
+We got an F-score of 0.6.
+Since the issue is mostly false negatives, and therefore even some of the first three slots were often empty, so even if we accept any of the top 1000 as a success, we get an F-score of 0.63, not much better.
 \input{siamese_exper}

### 2018-10-22 old/paper/toread.tex

[15] R. Vernica, M. J. Carey, and C. Li, “Efficient parallel set-
similarity joins using mapreduce,” in SIGMOD ’10.
[16] R. Baraglia, G. D. F. Morales, and C. Lucchese, “Document
similarity self-join with mapreduce,” in ICDM ’10.
[17] S. Chaudhuri, V. Ganti, and R. Kaushik, “A primitive operator
for similarity joins in data cleaning,” in ICDE ’06.
[18] C. Xiao, W. Wang, X. Lin, and J. X. Yu, “Efficient similarity
joins for near duplicate detection,” in WWW ’08, 2008.

http://ilpubs.stanford.edu:8090/1006/1/fuzzy-joins.pdf

### 2018-10-22 build_model.py
square stuff for improved loss

@@ -183,9 +183,9 @@ def improved_loss(y_true, y_pred):
     margin = K.constant(1)
     lambda_p = K.constant(0.02)
     threshold = K.constant(0.1)
-    a_p_distance = y_pred[:,0,0]
-    a_n_distance = y_pred[:,1,0]
-    p_n_distance = y_pred[:,2,0]
+    a_p_distance = K.square(y_pred[:,0,0])
+    a_n_distance = K.square(y_pred[:,1,0])
+    p_n_distance = K.square(y_pred[:,2,0])
     phi = a_p_distance - ((a_n_distance + p_n_distance) / K.constant(2)) + margin
     psi = a_p_distance - threshold 
 

### 2018-11-03 build_model.py
iuse hard, not semi-hard

@@ -581,7 +581,7 @@ embedder_model = embedded_representation_model(embedder)
 
 
 if DEBUG_ANN:
-    triplets = generate_semi_hard_triplets_from_ANN(embedder_model, sequences, entity2unique, entity2same_train, unique_text, True)
+    triplets = generate_triplets_from_ANN(embedder_model, sequences, entity2unique, entity2same_train, unique_text, True)
     print(len(triplets['anchor']))
     sys.exit()
 
@@ -593,7 +593,7 @@ counter = 0
 current_model = embedder_model
 prev_match_stats = 0
 
-train_data = generate_semi_hard_triplets_from_ANN(current_model, sequences, entity2unique, entity2same_train, unique_text, False)
+train_data, train_match_stats = generate_triplets_from_ANN(current_model, sequences, entity2unique, entity2same_train, unique_text, False)
 
 number_of_names = len(train_data['anchor'])
 # print(train_data['anchor'])
@@ -602,7 +602,7 @@ Y_train = np.random.randint(2, size=(1,2,number_of_names)).T
 
 checkpoint = ModelCheckpoint(filepath, monitor='val_accuracy', verbose=1, save_best_only=True, mode='max')
 
-early_stop = EarlyStopping(monitor='val_accuracy', patience=1, mode='max')
+early_stop = EarlyStopping(monitor='val_accuracy', patience=2, mode='max')
 
 callbacks_list = [checkpoint, early_stop]
 

### 2018-11-03 old/TripletLossFacenetLSTM-8.31.18.py

@@ -581,7 +581,7 @@ embedder_model = embedded_representation_model(embedder)
 
 
 if DEBUG_ANN:
-    triplets = generate_semi_hard_triplets_from_ANN(embedder_model, sequences, entity2unique, entity2same_train, unique_text, True)
+    triplets = generate_triplets_from_ANN(embedder_model, sequences, entity2unique, entity2same_train, unique_text, True)
     print(len(triplets['anchor']))
     sys.exit()
 
@@ -593,7 +593,7 @@ counter = 0
 current_model = embedder_model
 prev_match_stats = 0
 
-train_data = generate_semi_hard_triplets_from_ANN(current_model, sequences, entity2unique, entity2same_train, unique_text, False)
+train_data, train_match_stats = generate_triplets_from_ANN(current_model, sequences, entity2unique, entity2same_train, unique_text, False)
 
 number_of_names = len(train_data['anchor'])
 # print(train_data['anchor'])

### 2018-11-05 old/paper2018/datasets.tex
llncs stuff for eswc

--- 2018-09-05 paper2018/datasets.tex
@@
 \begin{figure}[htb]
-    \centering
-    \begin{subfigure}[t]{0.23\textwidth}
-        \centering
-        \includegraphics[width=.95\linewidth]{people_recall}
-        \caption{Recall rate as a function of neighborhood size}
-        \label{people_recall}
-    \end{subfigure}%
+    \subfloat[Recall rate as a function of neighborhood size\label{people_recall}]{% 
+        \includegraphics[width=.5\linewidth]{people_recall}
+    }
     ~ 
-    \begin{subfigure}[t]{0.23\textwidth}
-        \centering 
-        \includegraphics[width=.95\linewidth]{people_distances}
-        \caption{Mean negative distance as a function of neighborhood size}
-        \label{modified_loss}
-    \end{subfigure}
+    \subfloat[Mean negative distance as a function of neighborhood size\label{modified_loss}]{%
+        \includegraphics[width=.5\linewidth]{people_distances}
+     }
     \label{people_distances}
@@
 \begin{figure}[htb]
-    \centering
-    \begin{subfigure}[t]{0.23\textwidth}
-        \centering
-        \includegraphics[width=.99\linewidth]{company_recall}
-        \caption{Recall rate as a function of neighborhood size}
-        \label{company_recall}
-    \end{subfigure}%                                                                                                   
+   \subfloat[Recall rate as a function of neighborhood size\label{company_recall}]{%
+        \includegraphics[width=.5\linewidth]{company_recall}
+   }
    ~
-    \begin{subfigure}[t]{0.23\textwidth}
-        \centering
-        \includegraphics[width=.99\linewidth]{company_distances}
-        \caption{Mean negative distance from anchor as a function of neighborhood size}
-        \label{modified_loss}
-    \end{subfigure}
+   \subfloat[Mean negative distance from anchor as a function of neighborhood size \label{modified_loss}]{%
+        \includegraphics[width=.5\linewidth]{company_distances}
+   }
     \label{company_distances}

### 2018-11-06 old/paper2018/samplepaper.tex

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
\usepackage[caption=false]{subfig}
\usepackage{multirow}

% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
%
\title{Contribution Title\thanks{Supported by organization x.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and
Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Princeton University, Princeton NJ 08544, USA \and
Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
\email{lncs@springer.com}\\
\url{http://www.springer.com/gp/computer-science/lncs} \and
ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
\email{\{abc,lncs\}@uni-heidelberg.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
The abstract should briefly summarize the contents of the paper in
150--250 words.

\keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}
%
%
%

\input{introduction2}
\input{relatedWork}
\input{siamese_networks}
\input{joins}
\input{datasets}
\input{evaluation}

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\begin{thebibliography}{8}
\bibitem{ref_article1}
Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)

\bibitem{ref_lncs1}
Author, F., Author, S.: Title of a proceedings paper. In: Editor,
F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
Springer, Heidelberg (2016). \doi{10.10007/1234567890}

\bibitem{ref_book1}
Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
Location (1999)

\bibitem{ref_proc1}
Author, A.-B.: Contribution title. In: 9th International Proceedings
on Proceedings, pp. 1--2. Publisher, Location (2010)

\bibitem{ref_url1}
LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
Oct 2017
\end{thebibliography}
\end{document}

### 2018-11-07 old/paper2018/samplepaper.tex
adding abstract

@@
 %
-\title{Contribution Title\thanks{Supported by organization x.}}
+\title{Name matching through deep learning}
 %
@@
 %
-\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and
-Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
-Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
+\author{Kavitha Srinivas\inst{1} \and
+Yehuda Gale\inst{2} \and
+Julian Dolby\inst{1}}
 %
-\authorrunning{F. Author et al.}
+\authorrunning{K. Srinivas et al.}
 % First names are abbreviated in the running head.
@@
 %
-\institute{Princeton University, Princeton NJ 08544, USA \and
-Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
-\email{lncs@springer.com}\\
-\url{http://www.springer.com/gp/computer-science/lncs} \and
-ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
-\email{\{abc,lncs\}@uni-heidelberg.de}}
+\institute{IBM Research \and
+Rutgers University}
+
 %
@@
 \begin{abstract}
-The abstract should briefly summarize the contents of the paper in
-150--250 words.
+Merging datasets is a key operation for data analytics.  A frequent
+requirement for merging is joining across columns that have
+different surface forms for the same entity (e.g., the name of a
+person might be represented as \textit{Douglas Adams} or
+\textit{Adams, Douglas}).  Similarly,
+ontology alignment can require recognizing distinct surface forms of
+the same entity, especially when ontologies are independently
+developed.  However, data management systems are currently limited
+to performing merges based on string equality, or at best using
+string similarity.  We propose an approach to performing merges
+based on deep learning models.  Our approach depends on (a) creating
+a deep learning model that maps surface forms of an entity into a
+set of vectors such that alternate forms for the same entity are
+closest in vector space, (b) indexing these vectors using a nearest
+neighbors algorithm to find the forms that can be potentially joined
+together.  To build these models, we had to adapt techniques from
+metric learning due to the characteristics of the data; specifically we describe 
+novel sample selection techniques and loss functions that work for this problem.  
+To evaluate our approach, we used Wikidata as ground truth
+and built models from datasets with approximately 1.1M people's names
+(200K identities) and 130K company names (70K identities).  We developed models that 
+allow for joins with precision@1 of .75-.81 and
+recall of .74-.81.  We make the models available for aligning people or companies across multiple datasets.
 
-\keywords{First keyword  \and Second keyword \and Another keyword.}
+\keywords{Name matching  \and Fuzzy join}
 \end{abstract}

### 2018-11-13 old/paper2018/datasets.tex
figure hacking

@@
 \subsection{Dataset characteristics}
+
+\begin{wrapfigure}{r}{.65\textwidth}
+    \subfloat[Recall rate as a function of neighborhood size\label{people_recall}]{% 
+        \includegraphics[width=.35\linewidth]{people_recall}
+    }
+    ~ 
+    \subfloat[Mean negative distance as a function of neighborhood size\label{modified_loss}]{%
+        \includegraphics[width=.35\linewidth]{people_distances}
+     }
+    \label{people_distances}
+    \caption{Characteristics of people data}
+\label{people_characteristics}
+\end{wrapfigure}
+
  As a baseline, we measured how the anchors, positives and negatives were laid out in vector space based on character embeddings alone.
@@
 
-\begin{figure}[htb]
-    \subfloat[Recall rate as a function of neighborhood size\label{people_recall}]{% 
-        \includegraphics[width=.5\linewidth]{people_recall}
-    }
-    ~ 
-    \subfloat[Mean negative distance as a function of neighborhood size\label{modified_loss}]{%
-        \includegraphics[width=.5\linewidth]{people_distances}
-     }
-    \label{people_distances}
-    \caption{Characteristics of people data}
-\label{people_characteristics}
-\end{figure}
-
-\begin{figure}[htb]
+\begin{wrapfigure}{r}{.65\textwidth}
    \subfloat[Recall rate as a function of neighborhood size\label{company_recall}]{%
-        \includegraphics[width=.5\linewidth]{company_recall}
+        \includegraphics[width=.35\linewidth]{company_recall}
    }
@@
    \subfloat[Mean negative distance from anchor as a function of neighborhood size \label{modified_loss}]{%
-        \includegraphics[width=.5\linewidth]{company_distances}
+        \includegraphics[width=.35\linewidth]{company_distances}
    }
@@
 \label{company_characteristics}
-\end{figure}
+\end{wrapfigure}

### 2018-11-16 old/paper2018/introduction2.tex
reorgonized directory
added mudgal ref

--- 2018-09-05 arxiv2018/introduction2.tex
@@
 
-Merging datasets is a key operation for data analytics.  A frequent
-requirement for merging is joining across columns that have
+Merging datasets frequently requires joining across columns that have
 different surface forms for the same entity.
@@
 The approach is general, in the sense that once a model has been built for a specific semantic type (e.g.
-people, companies or faces) it can be used for joining any two datasets which share that semantic type.
+people, companies or faces) it can be used for joining any two datasets which share that semantic type, provided of course that the sample characteristics match.
 It is also efficient because indexing uses space partitioning algorithms (such as approximate nearest neighbor) to find surface forms that are potentially joinable, thus eliminating large parts of the vector space from consideration.
@@
 The problem of mapping vectors for the same entity closer in vector space than vectors for other entities is known in the literature as deep metric learning.
-Deep metric learning is known to be a difficult problem as studied in the space of face recognition and person-re-identification \cite{DBLP:conf/cvpr/SchroffKP15}, \cite{8445716}, \cite{DBLP:journals/corr/abs-1802-03170}.
+Deep metric learning is known to be a difficult problem as studied in the space of face recognition and person-re-identification \cite{DBLP:conf/cvpr/SchroffKP15}.
 As a result, there is a significant amount of research on two aspects of training these networks: (a) how to choose samples for efficient learning, and (b) what constitutes a good loss function.
@@
 For the problem of building models for datasets dominated by hard negatives, we found that an adaptation to the triplet loss function proposed in \cite{DBLP:conf/cvpr/SchroffKP15} was better than three other functions that have been used in the literature.
-All code and models for this paper are at \url{https://github.com/yehudagale/fuzzyjoiner} and \url{https://drive.google.com/open?id=1zivCTGkq2_AkfjGLHMnlehzTmYUwcQ9e} respectively.
 %

### 2018-11-16 old/paper2018/relatedWork.tex
added mudgal ref

--- 2018-09-05 paper2018/relatedWork.tex
@@
 
-The idea of building joint embeddings for merging datasets followed by nearest neighbors search has been applied recently to the problem of linking relational tuple embeddings with embeddings of other relational tuples or unstructured text \cite{Bordawekar18}, \cite{IDEL18}).
-For the problem of linking tuples, each model that is learnt is specific to the database it was trained on.
-Our focus is on techniques that can be used to develop general purpose embedding models for merging alternate surface forms of key entities.
-Once such models are built, they can be applied to joining any two datasets that share that semantic type.
+The idea of building joint embeddings has been applied recently to the problem of linking relational tuples for entity resolution \cite{Mudgal},\cite{Bordawekar18}).
+For the problem of linking tuples, each model that is learnt is specific to the database it was trained on because the attributes of an entity vary significantly across databases.
+Our focus is on techniques for name matching, and we develop general purpose embedding models for merging alternate surface forms of key entities.
 
-Metric learning is a well studied problem in the face recognition literature, e.g., \cite{DBLP:conf/cvpr/SchroffKP15}, with a rich literature in triplet mining techniques.
+Metric learning is a well studied problem in face recognition, e.g., \cite{DBLP:conf/cvpr/SchroffKP15}, with a rich literature in triplet mining techniques.
 The closest approach to ours is the use of nearest neighbors algorithms for semi-hard triplet mining \cite{DBLP:journals/corr/KumarHC0D17}.

### 2018-11-16 old/paper2018/samplepaper.tex
merge
figure hacking
added mudgal ref

@@
 \usepackage{multirow}
+\usepackage{wrapfig}
 
@@
 \author{Kavitha Srinivas\inst{1} \and
-Yehuda Gale\inst{2} \and
+Abraham Gale\inst{2} \and
 Julian Dolby\inst{1}}
@@
 \begin{abstract}
-Merging datasets is a key operation for data analytics.  A frequent
-requirement for merging is joining across columns that have
+Merging datasets frequently requires joining across columns that have
 different surface forms for the same entity (e.g., the name of a
 person might be represented as \textit{Douglas Adams} or
-\textit{Adams, Douglas}).  Similarly,
-ontology alignment can require recognizing distinct surface forms of
-the same entity, especially when ontologies are independently
-developed.  However, data management systems are currently limited
+\textit{Adams, Douglas}).  However, data management systems are currently limited
 to performing merges based on string equality, or at best using
-string similarity.  We propose an approach to performing merges
-based on deep learning models.  Our approach depends on (a) creating
-a deep learning model that maps surface forms of an entity into a
-set of vectors such that alternate forms for the same entity are
-closest in vector space, (b) indexing these vectors using a nearest
+string similarity.  We propose an approach to name matching based on deep learning models.  
+Our approach depends on (a) creating
+a deep learning model that maps alternate forms for the same entity into vector space such that alternate forms are closest, (b) indexing these vectors using a nearest
 neighbors algorithm to find the forms that can be potentially joined
@@
 %
-% \bibliographystyle{splncs04}
-% \bibliography{mybibliography}
-%
-\begin{thebibliography}{8}
-\bibitem{ref_article1}
-Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)
+\bibliographystyle{splncs04}
+\bibliography{paper}
 
-\bibitem{ref_lncs1}
-Author, F., Author, S.: Title of a proceedings paper. In: Editor,
-F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
-Springer, Heidelberg (2016). \doi{10.10007/1234567890}
-
-\bibitem{ref_book1}
-Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
-Location (1999)
-
-\bibitem{ref_proc1}
-Author, A.-B.: Contribution title. In: 9th International Proceedings
-on Proceedings, pp. 1--2. Publisher, Location (2010)
-
-\bibitem{ref_url1}
-LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
-Oct 2017
-\end{thebibliography}
 \end{document}

### 2018-11-19 old/paper2018/datasets.tex
fix multiply-defined labels

@@
     ~ 
-    \subfloat[Mean negative distance as a function of neighborhood size\label{modified_loss}]{%
+    \subfloat[Mean negative distance as a function of neighborhood size\label{people_distance}]{%
         \includegraphics[width=.35\linewidth]{people_distances}
@@
    ~
-   \subfloat[Mean negative distance from anchor as a function of neighborhood size \label{modified_loss}]{%
+   \subfloat[Mean negative distance from anchor as a function of neighborhood size \label{company_distance}]{%
         \includegraphics[width=.35\linewidth]{company_distances}

### 2018-11-19 old/paper2018/evaluation.tex
figure format
figure hacking
fixing table ref

--- 2018-09-05 paper2018/evaluation.tex
@@
 
-\begin{table}[ht]
-\caption{Precision and Recall by loss functions}
-\label{precision_recall}
-\begin{center}
-%{\scriptsize
+\begin{wrapfigure}{r}{.4\textwidth}
+\subfloat[Precision and Recall by loss functions\label{precision_recall}]{%
+{\scriptsize
 \begin{tabular}{|l|l|r|r|r|}
@@
 \hline
-\end{tabular} %}
-\end{center}
-\end{table}
-
-\begin{table}[ht]
-\caption{Distance estimates after training}
-\label{distance}
-\begin{center}
-%{\scriptsize 
+\end{tabular}}}\\
+\subfloat[Distance estimates after training\label{distance}]{%
+{\scriptsize
 \begin{tabular}{|l|l|r|r|r|r|}
@@
 \hline
-\end{tabular}%}
-\end{center}
-\end{table}
+\end{tabular}}}
+\end{wrapfigure}
 
@@
  We also assessed our learning mechanism more directly by examining how the nearest neighborhood changed from before to after training.
-As can be seen from Table \ref{distance}, recall is improved greatly, with the bigger change for people, in which case it improves from 3\% to 81\%.
+As can be seen from Table \ref{precision_recall}, recall is improved greatly, with the bigger change for people, in which case it improves from 3\% to 81\%.
 For companies, it is from 16\% to 74\%.
@@
 
-\begin{table}[ht]
+\begin{wrapfigure}{r}{.4\textwidth}
+\begin{center}
 \caption{Precision and Recall for hard and semi-hard training}
 \label{hard-semi-hard}
-\begin{center}
-%{\scriptsize
+{\scriptsize 
 \begin{tabular}{|l|r|r|r|}
@@
 \hline 
-\end{tabular}%}
+\end{tabular}}
 \end{center}
-\end{table}
+\end{wrapfigure}
 

### 2018-11-19 old/paper2018/samplepaper.tex
wording

@@
 neighbors algorithm to find the forms that can be potentially joined
-together.  To build these models, we had to adapt techniques from
-metric learning due to the characteristics of the data; specifically we describe 
+together.  To build these models, we adapted techniques from
+metric learning to the characteristics of the data; specifically we describe 
 novel sample selection techniques and loss functions that work for this problem.  

### 2018-11-19 old/paper2018/introduction2.tex
words

@@
 This problem occurs for many entity types such as people's names, company names, addresses, product descriptions, conference venues, or even people's faces.
-Data management systems have however, largely focussed solely on equi-joins, where string or numeric equality determines which rows should be joined, because such joins are efficient.
+Data management systems, though, largely focus on efficient joins on string or numeric equality.
 
-We propose a different approach to joining different surface representations of the same entity, inspired by recent advances in deep learning.
-Our approach depends on (a) mapping surface forms into sets of vectors such that forms for the same entity are closest in vector space, (b) indexing these vectors to find the forms that can be potentially joined together.
-The approach is general, in the sense that once a model has been built for a specific semantic type (e.g.
-people, companies or faces) it can be used for joining any two datasets which share that semantic type, provided of course that the sample characteristics match.
-It is also efficient because indexing uses space partitioning algorithms (such as approximate nearest neighbor) to find surface forms that are potentially joinable, thus eliminating large parts of the vector space from consideration.
-Further, nearest neighbor algorithms have been applied to billions of vectors \cite{JDH17}, so the approach is practical for most datasets.
+We propose a different approach to joining different surface representations of the same entity, inspired by recent advances in deep learning: (a) map surface forms into sets of vectors such that forms for the same entity are closest in vector space, (b) index these vectors to find the forms that can be potentially joined together.
+Once a model has been built for a specific semantic type (e.g.
+people, companies or faces) it can be used for joining any two datasets which share that semantic type, provided the sample characteristics match.
+It is efficient by using space partitioning algorithms (such as approximate nearest neighbor) to find surface forms that are potentially joinable.
+Nearest neighbor algorithms have been applied to billions of vectors \cite{JDH17}, so the approach is practical for most datasets.
 
-To test the feasibility of these ideas, we used Wikidata as ground truth to build models for datasets with 1.1M people's names (about 200K identities) and 130K company names (70K identities).
-The problem of mapping vectors for the same entity closer in vector space than vectors for other entities is known in the literature as deep metric learning.
-Deep metric learning is known to be a difficult problem as studied in the space of face recognition and person-re-identification \cite{DBLP:conf/cvpr/SchroffKP15}.
-As a result, there is a significant amount of research on two aspects of training these networks: (a) how to choose samples for efficient learning, and (b) what constitutes a good loss function.
-In building models for entity names, we had to adapt these techniques for triplet selection and loss functions because matching entity names has different characteristics, as we describe below.
+We evaluate using Wikidata as ground truth to build models for datasets with 1.1M people's names (about 200K identities) and 130K company names (70K identities).
+The problem of mapping vectors for the same entity closer in vector space than vectors for other entities is known in the literature as deep metric learning (e.g.
+\cite{DBLP:conf/cvpr/SchroffKP15}), and there is research on two aspects of training these networks: (a) how to choose samples for efficient learning, and (b) what constitutes a good loss function.
+In building models for entity names, we adapt these techniques for triplet selection and loss functions because matching entity names has different characteristics.
 
-As in face recognition, our system for metric learning is built by training a so-called triplet based `siamese triplet' network to learn to produce a small distance estimate for two surface forms for the same entity (between an arbitrarily chosen \textit{anchor} and \textit{positive}), and a large distance estimate for surface forms of different entities (an \textit{anchor} and a \textit{negative}).
-A key problem in effective training of such networks is the problem of how to select negative pairs for training, because one cannot exhaustively show all negative pairs to the network.
-In prior work for instance, this problem is solved by so-called `triplet mining' where so-called `semi-hard' negatives are gleaned after an all-pairs comparison of input vectors in a batch, e.g., \cite{DBLP:conf/cvpr/SchroffKP15}.
+As in face recognition, we use a triplet based `siamese triplet' network to learn to produce a small distance estimate for two surface forms for the same entity (between an arbitrarily chosen \textit{anchor} and \textit{positive}), and a large distance estimate for surface forms of different entities (an \textit{anchor} and a \textit{negative}).
+A key problem in effective training of such networks is how to select negative pairs for training, because one cannot exhaustively show all negative pairs to the network.
+In prior work for instance, this done by finding `semi-hard' negatives after an all-pairs comparison of input vectors in a batch, e.g., \cite{DBLP:conf/cvpr/SchroffKP15}.
 `Semi-hard' negatives are negatives that are further away from the anchor than positives, but not by a sufficient margin.
 The idea of focusing on semi-hard negatives is to avoid mining noisy regions of the embedding space.
-However, for matching across entity names, most positive forms for the entity names are actually substantially further away from the anchor than are negatives, as we show empirically in this paper.
-In other words, `hard negatives' dominate the space, and are the norm.
-Our approach to the problem of triplet mining was therefore to use an approximate nearest neighbors algorithm to choose negatives for training that were in the nearest neighbor set, which means that most of the time, our negatives are `hard negatives', where the negative is closer to the anchor than positives.
-This approach has three key benefits.
-First, it lays out the entities based on their input vectors, and thus allows an efficient gathering of all nearest neighbors without a quadratic comparison of vectors in a batch to determine suitable negatives.
+However, for matching across entity names, most positive forms for the entity names are actually substantially further away from the anchor than some negatives, as we show empirically in this paper, so `hard negatives' dominate the space.
+We therefore use an approximate nearest neighbors (ANN) algorithm to choose negatives for training that were in the nearest neighbor set, and hence are `hard negatives', being closer to the anchor than positives.
+This approach has three benefits.
+First, an ANN allows an efficient gathering of all nearest neighbors without a quadratic comparison of vectors in a batch.
 Second, it provides a baseline against which one can objectively measure the effects of training.
-Third, it examines whether focusing on hard negatives is really detrimental to deep metric learning, at least for learning to map entity names in vector space.
+Third, it examines whether hard negatives really are detrimental to deep metric learning, at least for learning to map entity names in vector space.
 As we show empirically in this paper, this technique is better for building models that are suitable for use in joins than semi-hard triplet mining when the dataset is dominated by hard negatives.
@@
 
-We also investigated the effect of using multiple local loss functions which have been proposed in the literature for improving deep metric learning, e.g., the triplet loss \cite{DBLP:conf/cvpr/SchroffKP15}, improved loss \cite{Zhang:2016:DML:3088616.3088665}, and angular loss \cite{DBLP:journals/corr/abs-1708-01682} functions.
-For the problem of building models for datasets dominated by hard negatives, we found that an adaptation to the triplet loss function proposed in \cite{DBLP:conf/cvpr/SchroffKP15} was better than three other functions that have been used in the literature.
+We compared multiple proposed local loss functions---Schroff\cite{DBLP:conf/cvpr/SchroffKP15}, improved\cite{Zhang:2016:DML:3088616.3088665}, and angularcite{DBLP:journals/corr/abs-1708-01682}---and we found an adaptation of the triplet loss function proposed in \cite{DBLP:conf/cvpr/SchroffKP15} was better.
+
 %

### 2018-11-19 old/paper2018/introduction2.tex
words

@@
 
-We compared multiple proposed local loss functions---Schroff\cite{DBLP:conf/cvpr/SchroffKP15}, improved\cite{Zhang:2016:DML:3088616.3088665}, and angularcite{DBLP:journals/corr/abs-1708-01682}---and we found an adaptation of the triplet loss function proposed in \cite{DBLP:conf/cvpr/SchroffKP15} was better.
+We compared multiple proposed local loss functions---Schroff\cite{DBLP:conf/cvpr/SchroffKP15}, improved\cite{Zhang:2016:DML:3088616.3088665}, and angular\cite{DBLP:journals/corr/abs-1708-01682}---and we found an adaptation of the triplet loss function proposed in \cite{DBLP:conf/cvpr/SchroffKP15} was better.
 

### 2018-11-19 old/paper2018/relatedWork.tex
words

@@
 \section{Related Work}
-Extensions in data management systems for handling joins typically use string similarity algorithms such as edit-distance, Jaro-Winkler and TF-IDF; e.g., \cite{Cohen2003}.
-String matching algorithms often do not work for merging different forms of the same entity because valid transformations of entity names can yield very different strings.
-More recently, data driven approaches have emerged as a powerful alternative for merging data.
-Data driven approaches mine patterns to determine the `rules' for joining a given entity type.
-One example of such an approach is illustrated in \cite{He:2015:SJS:2824032.2824036}, which determines which cell values should be joined based on whether those cell values co-occur on the same row across disparate tables in a very large corpus of data.
-Another example is work by \cite{auto-join-joining-tables-leveraging-transformations} where program synthesis techniques are used to learn the right set of transformations needed to perform the entity matching operation.
-Our approach for merging datasets is much more general than either approach because the mapping function generalizes the set of transformations that are allowed across surface forms of an entity, even if they cannot be directly expressed as program transforms.
+Extensions in data management systems for joins typically use string similarity algorithms such as edit-distance, Jaro-Winkler and TF-IDF; e.g., \cite{Cohen2003}.
+String matching algorithms work poorly for merging the same entity because valid transformations of entity names can yield very different strings.
+More recently, data driven approaches mine patterns to determine the `rules' for joining a given entity type.
+One example is \cite{He:2015:SJS:2824032.2824036}, which determines which cell values should be joined based on whether those cell values co-occur on the same row across disparate tables in a very large corpus of data.
+Another example is\cite{auto-join-joining-tables-leveraging-transformations} where program synthesis techniques are used to learn the right set of transformations needed to perform the entity matching operation.
+Our approach for merging datasets is more general because the mapping function generalizes the set of transformations that are allowed across surface forms of an entity, even if they cannot be directly expressed as program transforms.
 
-The idea of building joint embeddings has been applied recently to the problem of linking relational tuples for entity resolution \cite{Mudgal},\cite{Bordawekar18}).
-For the problem of linking tuples, each model that is learnt is specific to the database it was trained on because the attributes of an entity vary significantly across databases.
+Joint embeddings have been applied recently to linking relational tuples for entity resolution \cite{Mudgal},\cite{Bordawekar18}).
+Here, each model is specific to the database on which it was trained because the attributes of an entity vary among databases.
 Our focus is on techniques for name matching, and we develop general purpose embedding models for merging alternate surface forms of key entities.

### 2018-11-21 preloaded_runner.py
made improvments to readme

@@ -405,7 +405,7 @@ parser.add_argument('--input', type=str, help='Input file')
 parser.add_argument('--entity_type', type=str, help='people or companies')
 
 parser.add_argument('--model', type=str, help='name for model file')
-
+parser.add_argument('--tokenizer', type=str, help='location of tokenizer file')
 parser.add_argument('--previos_test', type=str, help='use previos test data')
 
 args = parser.parse_args()
@@ -443,7 +443,7 @@ entity2same_test =  generate_names(test, people, limit_pairs=True)
 print(str(entity2same_test).encode('utf-8'))
 
 #load tokenizer
-tokenizer = pickle.load(open(args.model + '.tokenizer.pickle', 'rb'))
+tokenizer = pickle.load(open(args.tokenizer, 'rb'))
 #Tokenizer(num_words=MAX_NB_WORDS, lower=True, filters='!"#$%&()*+/:;<=>?@[\]^_`{|}~', split=" ")   
 
 # build a set of data structures useful for annoy, the set of unique entities (unique_text), 

### 2018-11-21 preloaded_runner.py
further improved readme

@@ -406,7 +406,7 @@ parser.add_argument('--entity_type', type=str, help='people or companies')
 
 parser.add_argument('--model', type=str, help='name for model file')
 parser.add_argument('--tokenizer', type=str, help='location of tokenizer file')
-parser.add_argument('--previos_test', type=str, help='use previos test data')
+parser.add_argument('--previous_test', type=str, help='use previous test data')
 
 args = parser.parse_args()
 
@@ -430,7 +430,7 @@ print('Loss function: ' + args.loss_function)
 people = 'people' in args.entity_type
 
 # Load test data if specified
-if args.previos_test and args.previos_test.lower() in ("yes", "true", "t", "1"):
+if args.previous_test and args.previous_test.lower() in ("yes", "true", "t", "1"):
     test = pickle.load(open(filepath + '.test_data.pickle', 'rb'))
 else:
     test =  read_entities(args.input)

### 2018-11-27 old/paper2018/introduction2.tex

--- 2018-11-19 old/paper2018/introduction2.tex
@@
 
-We compared multiple proposed local loss functions---Schroff\cite{DBLP:conf/cvpr/SchroffKP15}, improved\cite{Zhang:2016:DML:3088616.3088665}, and angularcite{DBLP:journals/corr/abs-1708-01682}---and we found an adaptation of the triplet loss function proposed in \cite{DBLP:conf/cvpr/SchroffKP15} was better.
+We compared multiple proposed local loss functions---Schroff\cite{DBLP:conf/cvpr/SchroffKP15}, improved\cite{Zhang:2016:DML:3088616.3088665}, and angular\cite{DBLP:journals/corr/abs-1708-01682}---and we found an adaptation of the Schroff loss function worked best.
 

### 2018-11-30 old/paper2018/evaluation.tex
new results
fixed numbers for new runs
fixed wording

@@
 Because we compared across different losses, the results are categorized by each loss function for each dataset we tested.
-For all the results reported here, we ran multiple runs because of the stochastic nature of neural network models; the results here are means across two runs.
+For all the results reported here, we ran multiple runs because of the stochastic nature of neural network models; the results here are for the better of the two runs.
 
@@
 \hline
-\multirow{4}{*}{People} & Adapted & .81 & .81 & .63 \\
+\multirow{4}{*}{People} & Adapted & .79 & .82 & .61 \\
 \cline{2-5}
-& Triplet & .74 & .84 & .55 \\
+& Triplet & .74 & .81 & .53 \\
 \cline{2-5}
-& Improved & .71 & .52 & .45 \\
+& Improved & .74 & .75 & .52 \\
 \cline{2-5}
-& Angular & .04 & .09 & .02 \\
+& Angular & .03 & .09 & .02 \\
 \hline
-\multirow{4}{*}{Corps} & Adapted & .74 & .73 & .66 \\
+\multirow{4}{*}{Corps} & Adapted & .72 & .72 & .64 \\
 \cline{2-5}
-& Triplet & .74 & .75 & .67 \\
+& Triplet & .74 & .76 & .67 \\
 \cline{2-5}
-& Improved & .74 & .72 & .65 \\
+& Improved & .68 & .70 & .61 \\
 \cline{2-5}
-& Angular & .26 & .32 & .22 \\
+& Angular & .24 & .30 & .21 \\
 \hline
@@
 \hline
-\multirow{4}{*}{People} & Adapted & 1.59 & 4.05 & 2.44 & 2.45 \\
+\multirow{4}{*}{People} & Adapted & .76 & .58 & 2.47 & 1.36 \\
 \cline{2-6}
-& Triplet & .46 & .18 & .55 & .10 \\
+& Triplet & .36 & .13 & .53 & .11 \\
 \cline{2-6}
-& Improved & .15 & .38 & .21 & .18 \\
+& Improved & .21 & .18 & .51 & .21 \\
 \cline{2-6}
-& Angular & .51 & .25 & .06 & .02 \\
+& Angular & .04 & .03 & .06 & .02 \\
 \hline
-\multirow{4}{*}{Corps} & Adapted & 2.39 & 3.62 & 3.59 & 2.72 \\
+\multirow{4}{*}{Corps} & Adapted & .37 & .76 & 2.82 & 1.58 \\
 \cline{2-6}
-& Triplet & .43 & .31 & .59 & .09 \\
+& Triplet & .27 & .17 & .59 & .09 \\
 \cline{2-6}
-& Improved & .32 & .50 & .42 & .19 \\
+& Improved & .18 & .18 & .56 & .17 \\
 \cline{2-6}
-& Angular & .07 & .04 & .04 & .01 \\
+& Angular & .03 & .02 & .05 & .02 \\
 \hline

### 2018-11-30 old/paper2018/evaluation.tex
fixing more numbers to be consistent with tables

@@
 Without high precision, a join will mistakenly join many inappropriate names.
-The numbers for the adapted loss function were 81\% for people and 74\% for companies, so a join could capture most similar names.
+The best numbers across the models were 82\% for people and 76\% for companies, so a join could capture most similar names.
 For people, the adapted loss function showed overall better performance than triplet loss (see Table \ref{precision_recall}).
 Furthermore, it appears that triplet loss outperformed improved loss, which in turn is better than angular loss for learning this problem.
-On the other hand, for companies the only significant difference was that angular was worse.
+On the other hand, for companies, triplet loss seemed the best, which suggests that the properties of the dataset combine with loss functions to influence performance.
 
@@
 That metric gives a picture of how many names would be correctly found, on average, by a join.
-Adapted loss is at 63\% by this metric for people and 66\% for companies, so about two thirds of recalled names would be found before finding a single error.
+Adapted loss is at 61\% by this metric for people and triplet loss is at 67\% for companies, so about two thirds of recalled names would be found before finding a single error.
 Since every name has at least one other name for the same entity, we also measure precision at 1, which is the probability that the very nearest neighbor is a true match.
-For that, the very best performance we get is 84\% for people and 75\% for companies.
+For that, the very best performance we get is 82\% for people and 76\% for companies.
 
@@
  We also assessed our learning mechanism more directly by examining how the nearest neighborhood changed from before to after training.
-As can be seen from Table \ref{precision_recall}, recall is improved greatly, with the bigger change for people, in which case it improves from 3\% to 81\%.
-For companies, it is from 16\% to 74\%.
+As can be seen from Table \ref{precision_recall}, recall is improved greatly, with the bigger change for people, in which case it improves from 3\% to 82\%.
+For companies, it is from 16\% to 76\%.
 Thus training is clearly effective in moving actual names for the same entity into the nearest neighbors.
-For precision, the fraction of true matches found before the first error improves from 16\% to 73\% for people and 16\% to 64\% for companies.
-Precision@1 improves from 10\% to 81\% for people and from 26\% to 75\% for companies.
+For precision, the fraction of true matches found before the first error improves from 16\% to 61\% for people and 16\% to 67\% for companies.
+Precision@1 improves from 10\% to 82\% for people and from 26\% to 76\% for companies.
 In both these cases, demonstrable training occurred.

### 2018-11-30 old/paper2018/evaluation.tex
merge

--- 2018-11-30 old/paper2018/evaluation.tex
@@
 Accuracy was defined as the percentage of validation triples where positive distances from anchor were less than negative distances from anchor.
-For all our runs, test accuracy as measured by this metric ranged in the 97-99\% range for the people dataset and 92-94\% companies dataset for all losses except angular loss which was poor throughout.
+For all our runs, test accuracy as measured by this metric ranged in the 97-98\% range for the people dataset and 99\% companies dataset for all losses except angular loss which was poor throughout.
 Table \ref{precision_recall} shows the results for the people and company datasets, run with a fixed $k$ of 20 neighbors.
@@
 \end{tabular}}}
+\caption{Effect of training}
+\label{training-impact}
 \end{wrapfigure}
@@
 We thus chose the hardest semi-hard triplets: the negatives are as close to the positive as possible while still being further from the entity.
-We ran experiments again for adapted loss on our people dataset, changing only the triplets used; these results are in Table~\ref{hard-semi-hard}.
+We ran experiments again for adapted loss on our people dataset, changing only the triplets used; these results are in Figure~\ref{hard-semi-hard}.
 The same comparison on the company dataset showed no difference, mostly because company data seems easier and seems more immune to differences in loss functions or training regimens.

### 2018-12-02 old/paper2018/evaluation.tex
fixed a set of typos and errors

@@
 For all our runs, test accuracy as measured by this metric ranged in the 97-98\% range for the people dataset and 99\% companies dataset for all losses except angular loss which was poor throughout.
-Table \ref{precision_recall} shows the results for the people and company datasets, run with a fixed $k$ of 20 neighbors.
+Figure \ref{training-impact} shows the results for the people and company datasets, run with a fixed $k$ of 20 neighbors.
 Because we compared across different losses, the results are categorized by each loss function for each dataset we tested.
@@
 Without high precision, a join will mistakenly join many inappropriate names.
-The best numbers across the models were 82\% for people and 76\% for companies, so a join could capture most similar names.
-For people, the adapted loss function showed overall better performance than triplet loss (see Table \ref{precision_recall}).
+The best recall across the models were 79\% for people and 74\% for companies, so a join could capture most similar names.
+For people, the adapted loss function showed overall better performance across precision and recall than triplet loss (see Figure \ref{precision_recall}).
 Furthermore, it appears that triplet loss outperformed improved loss, which in turn is better than angular loss for learning this problem.
@@
 We ran experiments again for adapted loss on our people dataset, changing only the triplets used; these results are in Figure~\ref{hard-semi-hard}.
-The same comparison on the company dataset showed no difference, mostly because company data seems easier and seems more immune to differences in loss functions or training regimens.
+The same comparison on the company dataset showed no difference, mostly because company data seems easier and seems more robust to differences in loss functions or training regimens.
 
@@
 We show that deep learning models can be used effectively for joins, and we provide these models to the community for use.
-In the future, we will evaluate our work on other entity types and continue to explore refinements of both loss functions and triplet selection.
+This suggests that deep learning can be applied for matching other surface forms of entities such as addresses or product names.
+Future extensions to this work is how to use these models in the problem of entity matching, where each database often has different attributes for the same entity.

### 2018-12-02 old/paper2018/introduction2.tex
fixed a set of typos and errors

@@
 people, companies or faces) it can be used for joining any two datasets which share that semantic type, provided the sample characteristics match.
-It is efficient by using space partitioning algorithms (such as approximate nearest neighbor) to find surface forms that are potentially joinable.
+It can be made efficient by using space partitioning algorithms (such as approximate nearest neighbor) to find surface forms that are potentially joinable.
 Nearest neighbor algorithms have been applied to billions of vectors \cite{JDH17}, so the approach is practical for most datasets.
 
-We evaluate using Wikidata as ground truth to build models for datasets with 1.1M people's names (about 200K identities) and 130K company names (70K identities).
+We evaluate this approach by using Wikidata as ground truth to build models for datasets with 1.1M people's names (about 200K identities) and 130K company names (70K identities).
 The problem of mapping vectors for the same entity closer in vector space than vectors for other entities is known in the literature as deep metric learning (e.g.
@@
 A key problem in effective training of such networks is how to select negative pairs for training, because one cannot exhaustively show all negative pairs to the network.
-In prior work for instance, this done by finding `semi-hard' negatives after an all-pairs comparison of input vectors in a batch, e.g., \cite{DBLP:conf/cvpr/SchroffKP15}.
+In prior work for instance, this was done by finding `semi-hard' negatives after an all-pairs comparison of input vectors in a batch, e.g., \cite{DBLP:conf/cvpr/SchroffKP15}.
 `Semi-hard' negatives are negatives that are further away from the anchor than positives, but not by a sufficient margin.
@@
 
-We compared multiple proposed local loss functions---Schroff\cite{DBLP:conf/cvpr/SchroffKP15}, improved\cite{Zhang:2016:DML:3088616.3088665}, and angular\cite{DBLP:journals/corr/abs-1708-01682}---and we found an adaptation of the Schroff loss function worked best.
+We compared also compared multiple proposed local loss functions: triplet loss \cite{DBLP:conf/cvpr/SchroffKP15}, improved loss \cite{Zhang:2016:DML:3088616.3088665}, and angular loss \cite{DBLP:journals/corr/abs-1708-01682} along with an adaptation of the triplet loss function for both sorts of datasets.
+The main finding here was that the effectiveness of the loss function varied by dataset.
+For the harder problem of learning people's names, an adaptation of triplet loss worked best, whereas for easier problem of company names learning, Schroff produced the best learning.
 

### 2018-12-02 old/paper2018/relatedWork.tex
fixed a set of typos and errors

@@
 One example is \cite{He:2015:SJS:2824032.2824036}, which determines which cell values should be joined based on whether those cell values co-occur on the same row across disparate tables in a very large corpus of data.
-Another example is\cite{auto-join-joining-tables-leveraging-transformations} where program synthesis techniques are used to learn the right set of transformations needed to perform the entity matching operation.
+Another example is \cite{auto-join-joining-tables-leveraging-transformations} where program synthesis techniques are used to learn the right set of transformations needed to perform the entity matching operation.
 Our approach for merging datasets is more general because the mapping function generalizes the set of transformations that are allowed across surface forms of an entity, even if they cannot be directly expressed as program transforms.

### 2018-12-04 build_model.py
latest code

@@ -611,7 +611,7 @@ embedder_model = embedded_representation_model(embedder)
 
 
 if DEBUG_ANN:
-    triplets = generate_semi_hard_triplets_from_ANN(embedder_model, sequences, entity2unique, entity2same_train, unique_text, True)
+    triplets = generate_triplets_from_ANN(embedder_model, sequences, entity2unique, entity2same_train, unique_text, True)
     print(len(triplets['anchor']))
     sys.exit()
 
@@ -625,7 +625,7 @@ counter = 0
 current_model = embedder_model
 prev_match_stats = 0
 
-train_data = generate_semi_hard_triplets_from_ANN(current_model, sequences, entity2unique, entity2same_train, unique_text, False)
+train_data, train_match_stats = generate_triplets_from_ANN(current_model, sequences, entity2unique, entity2same_train, unique_text, False)
 
 number_of_names = len(train_data['anchor'])
 # print(train_data['anchor'])
@@ -635,7 +635,7 @@ Y_val = np.random.randint(2, size=(1,2,len(validation_data['anchor']))).T
 
 checkpoint = ModelCheckpoint(filepath, monitor='val_accuracy', verbose=1, save_best_only=True, mode='max')
 
-early_stop = EarlyStopping(monitor='val_accuracy', patience=1, mode='max')
+early_stop = EarlyStopping(monitor='val_accuracy', patience=2, mode='max')
 
 callbacks_list = [checkpoint, early_stop]
 

### 2018-12-10 old/paper2018/introduction2.tex
more edits

@@
 The main finding here was that the effectiveness of the loss function varied by dataset.
-For the harder problem of learning people's names, an adaptation of triplet loss worked best, whereas for easier problem of company names learning, Schroff produced the best learning.
+For the harder problem of learning people's names, an adaptation of triplet loss worked best, whereas for easier problem of company names learning, triplet loss produced the best learning.
+We provide the models, code, and datasets\footnote{\url{https://github.com/yehudagale/fuzzyjoiner}} for re-use.
 

### 2018-12-10 old/paper2018/siamese_networks.tex
llncs stuff for eswc
figure hacking
more edits

--- 2018-09-05 paper2018/siamese_networks.tex
@@
 \begin{figure}
-\includegraphics[width=1.0\linewidth]{triplet_siamese_network}
+\begin{center}
+\includegraphics[width=0.8\linewidth]{triplet_siamese_network}
+\end{center}
 \caption{Architecture of the siamese network}
@@
 As stated earlier, input is initially triples of a name, i.e., an \textit{anchor}, a \textit{positive} and a \textit{negative}.
-During the tokenization process, we kept punctuation such as `-', `,', and `.' in the name because they are important signals in processing a name.
-For the network, input vectors are computed for each entity assuming a maximum name length of 10 for each entity.
-A 100 dimensional character embedding was computed for each token in the entity using pretrained character embeddings \cite{hashimoto-jmt:2017:EMNLP2017}, which resulted in a 100 x 10 character encoding for each name used in a triplet.
+Our first step was to convert these into input vectors, one for each name part.
+We tokenized the name, keeping punctuation such as `-', `,', and `.' because they are important signals in processing a name.
+For the network, input vectors are computed for each entity assuming a maximum name length of 10 name parts for each entity.
+A 100 dimensional character embedding was computed for each name part in the entity name using pretrained character embeddings \cite{hashimoto-jmt:2017:EMNLP2017}, which resulted in a 100 x 10 character encoding for each name used in a triplet.
 We used character rather than word embeddings primarily because many names were missing from word based vector embeddings.
@@
 GRUs are a type of recurrent network \cite{cho-al-emnlp14} where each hidden unit updates its weights at a specific step in the sequence $t$ based on the current input $x_t$ and the value of the hidden unit from the prior step $h_{t-1}$.
-For name and textual data, positional information is critical, so we used GRUs instead of the convolutional neural networks (CNNs) that have been traditionally used in metric learning for face and image recognition.
+For name and textual data, positional information of name parts is critical, so we used GRUs instead of the convolutional neural networks (CNNs) that have been traditionally used in metric learning for face and image recognition.
 
@@
 \begin{figure}[htb]
-    \centering
-    \begin{subfigure}[t]{0.31\linewidth}
-        \centering
-        \includegraphics[width=\linewidth]{schroff_triplet}
-        \caption{Triplet loss}
-        \label{schroff_loss}
-    \end{subfigure}%
+    \subfloat[Triplet loss\label{schroff_loss}]{%
+        \includegraphics[width=.3\linewidth]{schroff_triplet}
+     }
     ~ 
-    \begin{subfigure}[t]{0.31\linewidth}
-        \centering 
-        \includegraphics[width=\linewidth]{modified_loss}
-        \caption{Modified loss}
-        \label{modified_loss}
-    \end{subfigure}
+    \subfloat[Triplet loss\label{modified_loss}]{%
+        \includegraphics[width=.3\linewidth]{modified_loss}
+     }
     ~ 
-    \begin{subfigure}[t]{0.31\linewidth}
-        \centering 
-        \includegraphics[width=\linewidth]{angular_loss}
-        \caption{Angular loss}
-        \label{angular_loss}
-    \end{subfigure}
-    \caption{Loss functions}
+    \subfloat[Triplet loss\label{angular_loss}]{%
+        \includegraphics[width=.3\linewidth]{angular_loss}
+     }
 \end{figure}

### 2018-12-17 preloaded_runner.py
use tokenizer option

@@ -408,6 +408,8 @@ parser.add_argument('--model', type=str, help='name for model file')
 
 parser.add_argument('--previos_test', type=str, help='use previos test data')
 
+parser.add_argument('--tokenizer', type=str, help='file with tokenizer to use')
+
 args = parser.parse_args()
 
 filepath = args.model
@@ -431,7 +433,7 @@ people = 'people' in args.entity_type
 
 # Load test data if specified
 if args.previos_test and args.previos_test.lower() in ("yes", "true", "t", "1"):
-    test = pickle.load(open(filepath + '.test_data.pickle', 'rb'))
+    test = pickle.load(open(args.input, 'rb'))
 else:
     test =  read_entities(args.input)
 
@@ -443,7 +445,7 @@ entity2same_test =  generate_names(test, people, limit_pairs=True)
 print(str(entity2same_test).encode('utf-8'))
 
 #load tokenizer
-tokenizer = pickle.load(open(args.model + '.tokenizer.pickle', 'rb'))
+tokenizer = pickle.load(open(args.tokenizer, 'rb'))
 #Tokenizer(num_words=MAX_NB_WORDS, lower=True, filters='!"#$%&()*+/:;<=>?@[\]^_`{|}~', split=" ")   
 
 # build a set of data structures useful for annoy, the set of unique entities (unique_text), 

### 2018-12-17 old/paper2018/evaluation.tex

@@
  We also assessed our learning mechanism more directly by examining how the nearest neighborhood changed from before to after training.
-As can be seen from Table \ref{precision_recall}, recall is improved greatly, with the bigger change for people, in which case it improves from 3\% to 82\%.
+As can be seen from Figure\ref{precision_recall}, recall is improved greatly, with the bigger change for people, in which case it improves from 3\% to 82\%.
 For companies, it is from 16\% to 76\%.

### 2018-12-17 old/paper2018/introduction.tex

@@
 
-Merging datasets is a key operation for data analytics.  A frequent
-requirement for merging is joining across columns that have
+Merging datasets freuently requires joining across columns that have
 different surface forms for the same entity (e.g., the name of a
 person might be represented as \textit{Douglas Adams},
-\textit{Adams, Douglas} or \textit{Douglas Noel Adams}).  Similarly,
-ontology alignment can require recognizing distinct surface forms of
+\textit{Adams, Douglas}).  Similarly,
+ontology alignment often requires mapping different surface forms of
 the same entity, especially when ontologies are independently
@@
 This problem occurs for many entity types such as people's names, company names, addresses, product descriptions, conference venues, or even people's faces.
-Data management systems have however, largely focussed solely on equi-joins, where string or numeric equality determines which rows should be joined, because such joins are efficient.
+Data management systems have however, largely focused solely on equi-joins, where string or numeric equality determines which rows should be joined, because such joins are efficient.
 
@@
 Our approach relies on building supervised deep learning models to automatically learn the correct set of transformations needed to compute the equality of two cell values.
-Because a deep learning model can learn the features necessary for matching from the data, it should in theory be able to generalize better to new datasets than the data driven approaches outlined in \cite{He:2015:SJS:2824032.2824036}.
 Conceptually, our approach is similar in spirit to the approach described in \cite{auto-join-joining-tables-leveraging-transformations}, but we use deep neural networks to learn the right function for the join operation instead of synthesizing different programs for different entity types.

### 2018-12-17 old/paper2018/samplepaper.tex

@@
 (200K identities) and 130K company names (70K identities).  We developed models that 
-allow for joins with precision@1 of .75-.81 and
-recall of .74-.81.  We make the models available for aligning people or companies across multiple datasets.
+allow for joins with precision@1 of .76-.82 and
+recall of .74-.79.  We make the models available for aligning people or company names across multiple datasets.
 

### 2018-12-18 preloaded_runner.py
fix merge problem

@@ -408,8 +408,6 @@ parser.add_argument('--model', type=str, help='name for model file')
 parser.add_argument('--tokenizer', type=str, help='location of tokenizer file')
 parser.add_argument('--previous_test', type=str, help='use previous test data')
 
-parser.add_argument('--tokenizer', type=str, help='file with tokenizer to use')
-
 args = parser.parse_args()
 
 filepath = args.model
